### 2010-12-15 paper.tex
Just adding the TeXmacs output + bibliography

\documentclass{acmconf}
\usepackage{geometry,amsmath,amssymb,wasysym,enumerate,bbm,color}
\geometry{letterpaper}

%%%%%%%%%% Start TeXmacs macros
\newcommand{\assign}{:=}
\newcommand{\nin}{\not\in}
\newcommand{\tmem}[1]{{\em #1\/}}
\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
\newcommand{\tmstrong}[1]{\textbf{#1}}
\newcommand{\tmtextbf}[1]{{\bfseries{#1}}}
\newcommand{\tmtextit}[1]{{\itshape{#1}}}
\newcommand{\tmtextsf}[1]{{\sffamily{#1}}}
\newcommand{\tmtextup}[1]{{\upshape{#1}}}
\newenvironment{descriptioncompact}{\begin{description} }{\end{description}}
\newenvironment{descriptiondash}{\begin{description} }{\end{description}}
\newenvironment{enumeratenumeric}{\begin{enumerate}[1.] }{\end{enumerate}}
\newenvironment{enumerateroman}{\begin{enumerate}[i.] }{\end{enumerate}}
\newenvironment{itemizedot}{\begin{itemize} \renewcommand{\labelitemi}{$\bullet$}\renewcommand{\labelitemii}{$\bullet$}\renewcommand{\labelitemiii}{$\bullet$}\renewcommand{\labelitemiv}{$\bullet$}}{\end{itemize}}
\newenvironment{proof}{\noindent\textbf{Proof\ }}{\hspace*{\fill}$\Box$\medskip}
\definecolor{grey}{rgb}{0.75,0.75,0.75}
\definecolor{orange}{rgb}{1.0,0.5,0.5}
\definecolor{brown}{rgb}{0.5,0.25,0.0}
\definecolor{pink}{rgb}{1.0,0.5,0.5}
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
%%%%%%%%%% End TeXmacs macros

\begin{document}

\title{Epistemic Logics For Knowledge Bases}\author{Matthew P.
Wampler-Doty}\maketitle

\begin{abstract}
  In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem
  proposed a research program for logic of \tmtextit{explicit knowledge}. \
  Two efforts have since emerged with proposals for logic of explicit
  knowledge: the \tmtextit{Dynamics of Awareness}
  {\cite{van_benthem_inference_2009}} and \tmtextit{Justification Logic}
  {\cite{artemov_introducing_2005}}. \ The purpose of this paper is to
  repurpose various epistemic logics from these previous efforts for reasoning
  about logical closures over knowledge bases. \ The results in this paper are
  based on previous work carried out in
  {\cite{wampler-doty_evidentialist_2010}}.
\end{abstract}

\section{Introduction\label{intro}}

The modern tradition in epistemic logic is to assume knowledge modalities
conform to the $S 5$ axiom schema. \ As noted in
{\cite{halpern_set-theoretic_1999,rubinstein_modeling_1998}}, the semantics of
$S 5$ knowledge correspond exactly to partitioning a collection of situations
into \tmtextit{information sets}, which is the traditional approach in game
theory and decision theory. \ While it is not commonly acknowledged in
epistemic logic, economists and philosophers accept that traditional decision
theory is externalist and behaviourist in nature{\footnote{An early essay by
Amartya Sen on the philosophical foundations of traditional decision theory
makes the behaviorist reading of decision theory clear
{\cite{sen_behaviour_1973}}. \ Kaushik Basu also discusses the behaviorist
nature of decision theory {\cite[pgs. 53--54]{basu\_revealed\_1980}}. \
Finally, Donald Davidson appeals to decision theory to motivate an externalist
epistemology in {\cite{davidson_could_1995}}.}}.

In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem proposed
a research program to find logics for explicit knowledge, providing the first
suggestion of an internalist perspective on epistemic logic. \ Subsequently,
Sergei Artemov and Elena Nogina proposed a logic of explicit justification,
which has come to be known as \tmtextit{Justification Logic} (JL)
{\cite{artemov_introducing_2005}}, based on Artemov's \tmtextit{Logic of
Proofs} {\cite{artemov_logic_1994}}. \ While the original semantics of JL was
interpretability into Peano Arithmetic, Melvin Fitting proposed Kripke
semantics for JL in {\cite{fitting_logic_2005}}. \ Recently, Fernando
Vel\'azquez-Quesada and Johan van Benthem have developed a simpler framework
for explicit epistemics in {\cite{van_benthem_inference_2009}}, entitled the
\tmtextit{Dynamics of Awareness}. \ This work was based on Joseph Halpern and
Ronald Fagin's original \tmtextit{Awareness Logic} {\cite{fagin_belief_1987}}.

In this essay we repurpose various externalist logics to take on an
internalist reading. \ The concept of a \tmtextit{knowledge base}, from which
beliefs may be implicitly deduced, will play a crucial role in our discussion.
\ We propose this as an avenue for representing foundationalist perspectives
on epistemology in epistemic logic. \ Our philosophical motivation is taken
from two sources. \ The first is Vincent Hendricks in
{\cite{hendricks_mainstream_2006}}, where he characterizes the principal of
{\tmem{logical omniscience}} for implicit knowledge in epistemic
logic{\footnote{We have modified Hendricks' notation here slightly to match
our own.}}:

\begin{quote}
  {\tmem{Whenever an agent $\Xi$ knows all of the formulae in $\mathcal{A}$,
  and $\phi$ follows logically from $\mathcal{A}$, then $\Xi$ [implicitly]
  knows $\phi$.}}
\end{quote}

We will design our semantics such that ``$\Box \phi$'' may be equated with
``$\phi$ follows logically from a knowledge base $\mathcal{A}$,'' which is
sometimes written as $\phi \in \tmop{Cn} ( \mathcal{A})$ in the artificial
intelligence literature. \ Our second inspiration comes from what Hilary
Kornblith calls the \tmtextit{the arguments on paper thesis}
{\cite{kornblith_beyond_1980}}, which he feels characterizes apsychological,
internalist theories of knowledge:

\begin{quote}
  Let us suppose that, for any person, it is possible, at least in principle,
  to list all of the propositions that person believes. \ The
  arguments-on-paper thesis is just the view that a person has a justified
  belief that a particular proposition is true just in case that proposition
  appears on the list of propositions that person believes, and either it
  requires no argument, or a {\tmem{good argument}} can be given for it which
  takes as premises certain other propositions on the list.
\end{quote}

Kornblith asserts that foundationalism and coherentism vie for accounts of a
``good argument'' in the above thesis. \ He provides an extensive bibliography
citing proposals for this principle by a number of 20th century
epistemologists, including figures such as A.J. Ayer and C.I. Lewis. \ The
rest of Kornblith's paper is devoted to attacking this view and proposing a
form of naturalized epistemology; we will not address this debate here,
however.

We adopt a arguments-on-paper-thesis perspective on epistemic logic in this
paper. \ We consider a \tmtextit{good argument} to be a logical derivation
from propositions present in a knowledge base. \ In this fashion, our \ \
Special attention will be given to \tmtextit{sound derivations}, which will be
thought of as a form of knowledge. \ In Awareness Logic, we will interpret
awareness of a formula as membership in a knowledge base. \ We prove
completeness for basic awareness logic and a hybrid logic extension. \ Logics
of multiple knowledge bases are also presented: a simplified form of
Justification Logic, a logic with neighborhood semantics, an a logic with
modalities for quantifying over knowledge bases. \ We conclude with an
application to naturalized epistemology found in the psychological literature.

\section{Basic Explicit Logics of Knowledge Bases}

\subsection{Awareness Logic\label{awarenesslogic}}

In this section, we give the explicit semantics to basic awareness logic,
originally presented in {\cite{fagin_belief_1987}}, with an additional axiom.
\ One difference in our presentation is the inclusion of a novel letter and a
superficial change in notation. \ This work is inspired by the developments in
van Benthem and Vel\'azquez-Quesada {\cite{van_benthem_inference_2009}}.

\begin{definition}
  Let $\Phi$ be a set of letters and define the language $\mathcal{L}_A
  (\Phi)$ as:
  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
     \hspace{1em} \circlearrowleft \hspace{1em} | \hspace{1em} \bot
     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
     \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A : \phi \hspace{1em}
  \]
\end{definition}

We define the other connectives and modal operators as usual for classical
modal logics.

\begin{definition}
  \label{awarenessmodels}An {\tmstrong{awareness model}} $\mathbbm{M}= \langle
  W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V : \Phi
  \cup \{\circlearrowleft\} \rightarrow 2^W$ and an awareness function
  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$. \ We will usually
  denote $\mathcal{A} (w)$ as $\mathcal{A}_w$.

  Define the semantic entailment relation $\vDash$ where atomic propositions,
  logical connectives and modality are interpreted as usual. \ We employ the
  following novel definition:
  \begin{eqnarray*}
    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \mathcal{A_w}
  \end{eqnarray*}
\end{definition}

The following definition distinguishes us from previously investigations of
awareness logic:

\begin{definition}
  Define the ``\tmtextbf{theory of a model} $\mathbbm{M}$'' as:
  \[ \tmop{Th} (\mathbbm{M}) \assign \{\phi \hspace{1em} | \hspace{1em}
     \mathbbm{M}, v \vDash \phi \text{ for all } v \in W\} \]
  We define the following properties that a model $\mathbbm{M}$ may posses:

  \begin{descriptiondash}
    \item[CSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff } \tmop{Th}
    (\mathbbm{M}) \cup \mathcal{A}_w \vdash \phi$

    \item[SND] $\mathbbm{M}, w \vDash \circlearrowleft \text{ iff }
    \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w$
  \end{descriptiondash}

  Here $\vdash$ is any logical consequence relation which is sound for
  $\vDash$, making true \tmtextbf{modus ponens} and \tmtextbf{reflection} (ie,
  $\Gamma \vdash \phi$ if $\phi \in \Gamma$)
\end{definition}

Neither \tmtextbf{CSQ} nor \tmtextbf{SND} correspond to simple modally
definable properties.

Intuitively, the \tmtextbf{CSQ} asserts that an agent believes a formula
$\phi$ if and only if it follows logically from their knowledge base and their
background knowledge, represented by $\tmop{Th} (\mathbbm{M})$. \
\tmtextbf{CSQ} is Vincent Hendrik's principle of logical omniscience mentioned
in {\S}\ref{intro}.

\tmtextbf{SND} asserts that $\circlearrowleft$ corresponds to the agent's
knowledge base being sound. A sound knowledge base will only render true
conclusions when used in deductions. \ If one considers ``the existance of a
sound deduction'' sufficient for a kind of knowledge, then $\circlearrowleft$
is suitable for investigating this notion of epistemology. \ That is, if
$\mathbbm{M}, w \vDash \circlearrowleft \wedge \Box \phi$, then we may
naturally say that the agent (implicitly) {\tmem{knows}} $\phi$ on the basis
of $\mathcal{A}_w$, rather than merely {\tmem{believing}} $\phi$ on the basis
of $\mathcal{A}_w$.

The logic of models making true \tmtextbf{CSQ} and \tmtextbf{SND} is provided
in Table \ref{logic1}.

\begin{table}[h]
  \begin{tabular}{l}
    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
    \rightarrow \psi \rightarrow \phi$\\
    $\vdash \Box(\phi \rightarrow \psi) \rightarrow \Box \phi \rightarrow \Box
    \psi$\\
    $\vdash A : \phi \rightarrow \Box \phi$\\
    $\vdash \circlearrowleft \rightarrow \Box \phi \rightarrow \phi$\\
    \\
    \begin{tabular}{lll}
      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box \phi}$
    \end{tabular}
  \end{tabular}
  \caption{\label{logic1}Awareness Logic for \tmtextbf{CSQ} and
  \tmtextbf{SND}}
\end{table}

\begin{theorem}
  \label{completeness1}Assuming an infinite store of proposition letters
  $\Phi$, the awareness logic presented is sound and weakly complete for
  awareness models making true \tmtextbf{CSQ} and \tmtextbf{SND}.
\end{theorem}

\begin{proof}
  Soundness is straightforward, so we will only address completeness. \ Assume
  $\nvdash \psi$. \ Consider the finite canonical model $\mathbbm{M}= \langle
  W, V, R, \mathcal{A} \rangle$ formed of maximally consistent sets of
  subformulae of $\phi$ (closed under single negations{\footnote{A discussion
  of this property may be found in {\cite[pg.
  243]{blackburn\_modal\_2001}}.}}), as per the finitary modal completeness
  proofs found in {\cite[chapter 4.8]{blackburn\_modal\_2001}} and
  {\cite[chapter 5]{boolos\_logic\_1995}}. \ Typical presentations do not
  include awareness, however it is defined intuitively in this case:
  \[ \phi \in \mathcal{A}_w \Longleftrightarrow A : \phi \in w \]
  Since $\psi$ is a subformula of itself, we have $\mathbbm{M}, w \nvDash
  \psi$ for some world $w$ by a finitary {\tmem{Lindenbaum Lemma}} and
  {\tmem{Truth Theorem}}. \ Moreover, it is straightforward to verify that
  $\mathbbm{M}$ makes true the following properties:
  \begin{enumeratenumeric}
    \item $W$ and $\mathcal{A}_v$ are finite, and $\psi \in \mathcal{A}_v$
    only if $\psi$ is a (possibly negated) subformula of $\phi$

    \item if $\mathbbm{M}, v \vDash A : \psi$ then $\mathbbm{M}, v \vDash \Box
    \psi$

    \item if $\mathbbm{M}, v \vDash \circlearrowleft$ then $v R v$
  \end{enumeratenumeric}

  We next produce a bisimular{\footnote{The notion of bisimulation is
  discussed at length in {\cite[chapter 2.2]{blackburn\_modal\_2001}}. \ We
  note that the basic definition and all of the usual theorems (modal
  equivalence, Henessy Milner, etc.) may be generalized to awareness models in
  a straightforward fashion. }} model $\mathbbm{M}'$ which makes true (1), (2)
  and a stronger from of (3):

  {\hspace*{\fill}}\begin{tabular}{ll}
    \tmtextbf{3$'$.} & $\mathbbm{M}', v \vDash \circlearrowleft$ iff $v R v$
  \end{tabular}{\hspace*{\fill}}

  To this end define $\mathbbm{M}' \assign \langle W', V', R', \mathcal{A}'
  \rangle$ such that{\footnote{Throughout this article, we use $l$ and $r$ to
  denote the two canonical injections associated with the coproduct $W \uplus
  W$. We will use $v_l$ and $v_r$ as the shorthand for $l (v)$ and $r (v)$
  respectively.}}: {\hspace*{\fill}}
  \begin{itemizedot}
    \item $W' \assign W \uplus W$

    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
    (p)\}$

    \item $R' \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v R
    u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em} \mathbbm{M},
    v \vDash \circlearrowleft\}$

    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
    (v)$
  \end{itemizedot}

  It is straightforward to verify that $\mathbbm{M}'$ makes true the desired
  properties. \ Let $Z \assign \{(v, v_l), (v, v_r) \hspace{1em} |
  \hspace{1em} v \in W\}$; \ then $Z$ is a bisimulation between $\mathbbm{M}$
  and $\mathbbm{M}'$. \ Therefore we know there is some $w \in W$ such that
  $\mathbbm{M}', w_l \nvDash \psi$ and $\mathbbm{M}', w_r \nvDash \psi$.

  Finally we construct a model $\mathbbm{M}''$ which agrees with
  $\mathbbm{M}'$ for all subformulae of $\psi$, which makes true
  \tmtextbf{CSQ} and \tmtextbf{SND}. \ Let $\Lambda$ be the set of proposition
  letters occuring in $\psi$. \ We will make use members of $\Phi \backslash
  \Lambda$ as {\tmem{nominals}}, as per the tradition in hybrid logic. \ This
  is possible since both $W'$ and $\Lambda$ are finite and $\Phi$ is infinite
  by hypothesis. \ Let $\iota : W \uplus W \hookrightarrow \Phi \backslash
  \Lambda$ be an injection assigning a fresh nominal associated with each
  world in $\mathbbm{M}'$. \ Now define $\mathbbm{M}'' \assign \langle W'',
  V'', R'', \mathcal{A}'' \rangle$, where:

  \begin{center}
    \begin{tabular}{lllll}
      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
      \begin{array}{ll}
        V' (p) & p \in \Lambda\\
        \{v\} & p = \iota (v)\\
        \varnothing & o / w
      \end{array} \right.$\\
      $\bullet$ & $R'' \assign R'$ & {\hspace{3em}} & $\bullet$ &
      $\mathcal{A}''_v \assign \{\phi \hspace{1em} | \phi \in \mathcal{A}'_v
      \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em} \neg v R' u\}$
    \end{tabular}
  \end{center}

  By induction we have that for every subformula $\phi$ of $\psi$ that
  $\mathbbm{M}', v \vDash \phi$ if and only if $\mathbbm{M}'', v \vDash \phi$,
  hence $\mathbbm{M}'', w_l \nvDash \psi$.

  All that is left to show is that $\mathbbm{M}''$ makes true \tmtextbf{CSQ}
  and \tmtextbf{SND}. \ $\mathbbm{M}''$ has three further properties:
  \begin{enumerateroman}
    \item $\mathcal{A}''_v$ is finite for all worlds $v$

    \item  $v R' u$ if and only if $\mathbbm{M}'', u \vDash \bigwedge
    \mathcal{A}'' (v)$

    \item The logic presented in Table \ref{logic1} is sound for
    $\mathbbm{M}''$
  \end{enumerateroman}
  From (ii) and the fact that $\mathbbm{M}'$ makes true (3$'$), we have
  \tmtextbf{SND} for $\mathbbm{M}''$.

  All that is left is to demonstrate \tmtextbf{CSQ} for some sound logic. \ We
  will use the logic in Table \ref{logic1} itself. \ From (i), (ii), (iii),
  and the \tmtextit{deduction theorem} for modal logic, we have the following
  line of reasoning:

  \begin{align*}
    Th({\mathbbm{M}}''){\cup}\mathcal{A}''_v{\vdash}{\phi} &
    {\Longleftrightarrow}Th({\mathbbm{M}}''){\vdash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\\
    &
    {\Longleftrightarrow}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}{\in}Th({\mathbbm{M}}'')\\
    &
    {\Longleftrightarrow}{\mathbbm{M}}'',u{\vDash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\text{
    for all $u \in W''$}\\
    & {\Longleftrightarrow}\text{ for all $u \in W''$, if
    }{\mathbbm{M}}'',u{\vDash}\mathcal{A}''_v\text{ then
    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
    & {\Longleftrightarrow}\text{ for all $u \in W''$, if }v R 'u \text{ then
    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
    & {\Longleftrightarrow}{\mathbbm{M}}'',v{\models}\Box{\phi}
  \end{align*}
\end{proof}

\subsection{Hybrid Awareness Logic}

The method of the above completeness proof makes implicit use of concepts from
hybrid logic{\footnote{Hybrid logic was first presented in
{\cite{prior_revised_1969}} and later formally developed in
{\cite{bull_approach_1970}}.}}. \ In this section we adapt hybrid logic and
show that it is a complete for reasoning about knowledge bases. \ We note that
because of the increased expressive power of hybrid logic, our completeness
theorem is simpler.

\begin{definition}
  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
  language $\mathcal{L}_H (\Phi, \Psi)$ as:
  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
     \hspace{1em} i \in \Psi \hspace{1em} | \hspace{1em} \bot \hspace{1em} |
     \hspace{1em} \phi \rightarrow \psi \hspace{1em} | \hspace{1em} \Box \phi
     \hspace{1em} | \hspace{1em} A : \phi \hspace{1em} | \hspace{1em} \forall
     \phi \]
\end{definition}

Our approach in hybrid logic is to employ a universal modality along with
nominals. \ This framework presents a logic where the agent may reason about
various labeled scenarios. \ Scenarios may be multiply labeled or not labeled
at all. \ From these intuitions we have the following definition:

\begin{definition}
  \label{hybridsemantics}Let a \tmtextbf{hybrid model} $\mathbbm{M}= \langle
  W, V, R, \mathcal{A}, \ell \rangle$ be an awareness model as in Definition
  \ref{awarenessmodels}, along with a partial labeling function $\ell : \Psi
  \nrightarrow W$

  The semantics for $\vDash$ are the same as in Definition
  \ref{awarenessmodels}, only we have
  \begin{eqnarray*}
    \mathbbm{M}, w \vDash \forall \phi & \text{iff} & \forall v \in
    W.\mathbbm{M}, v \vDash \phi\\
    \mathbbm{M}, w \vDash i & \text{iff} & \ell (i) = w
  \end{eqnarray*}
\end{definition}

The other connectives and operators are defined as usual, although we employ a
few special shorthands:

\begin{definition}
  We employ the following special abbreviations:
  \begin{eqnarray}
    \text{\tmtextup{@}}_i \phi \assign \forall (i \rightarrow \phi)
    \hspace{2em} & \exists \phi \assign \neg \forall \neg \phi \hspace{3em} &
    \circlearrowleft_i \assign \diamondsuit i \nonumber
  \end{eqnarray}
\end{definition}

This gives rise to a validity reflecting one of the axioms we saw in
{\S}\ref{awarenesslogic}:
\[ \vDash \circlearrowleft_i \rightarrow \Box \phi \rightarrow
   \text{\tmtextup{@}}_i \phi \]
This can be read as ``If the agent's knowledge base is sound at world $i$,
then if they can deduce something from their knowledge base, what they deduce
must be true at world $i$.'' \ In a way, this may be considered as
{\tmem{relativising}} knowledge particular named situations.

The semantics in Definition \ref{hybridsemantics} obviates the \tmtextbf{SND}
principle we previously presented, since there is no explicit
$\circlearrowleft$ symbol in this setting. \tmtextbf{CSQ} still makes sense
without modification, however. \ The following gives a logic for hybrid models
making true \tmtextbf{CSQ}:

\begin{table}[h]
  \begin{tabular}{ll}
    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & $\vdash \forall (\phi
    \rightarrow \psi) \rightarrow \forall \phi \rightarrow \forall \psi$\\
    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & $\vdash \forall
    \phi \rightarrow \phi$\\
    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
    \rightarrow \psi \rightarrow \phi$ & $\vdash \forall \phi \rightarrow
    \forall \forall \phi$\\
    $\vdash \Box(\phi \rightarrow \psi) \rightarrow \Box \phi \rightarrow \Box
    \psi$ & $\vdash \exists \phi \rightarrow \forall \exists \phi$\\
    $\vdash A : \phi \rightarrow \Box \phi$ & $\vdash \forall \phi \rightarrow
    \Box \phi$\\
    & $\vdash i \rightarrow \phi \rightarrow \text{\tmtextup{@}}_i \phi$\\
    & \\
    \begin{tabular}{llll}
      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi}{\vdash \Box \phi}$ &
      {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \forall \phi}$
    \end{tabular} & 
  \end{tabular}
  \caption{\label{logic2}Hybrid Awareness Logic for \tmtextbf{CSQ}}
\end{table}

\begin{theorem}
  \label{completeness2}Assuming an infinite store of nominals $\Psi$, the
  hybrid awareness logic presented is sound and weakly complete for all hybrid
  models making true \tmtextbf{CSQ}.
\end{theorem}

\begin{proof}
  As before, soundness is trivial. \ Completeness is based on a modification
  of techniques found in {\cite[chapter 5]{boolos\_logic\_1995}}. \ Assume
  that $\nvdash \psi$ and let $\Sigma_0$ be the set of subformulae of $\psi$,
  and let $\Upsilon$ be the set of nominals occuring in $\psi$. \ Define:

  \begin{align*}
    {\Sigma}_1 &
    {\assign}{\Sigma}_0{\cup}\{{\forall}{\phi}{\hspace{1em}}|{\hspace{1em}}\Box{\phi}{\in}{\Sigma}_0\}\\
    {\Sigma}_2 &
    {\assign}{\Sigma}_1{\cup}\{\text{@}_i{\phi}{\hspace{1em}},i{\rightarrow}{\phi}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1{\hspace{1em}}\&{\hspace{1em}}i{\in}{\Upsilon}\}\\
    {\Sigma}_3 &
    {\assign}{\Sigma}_2{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_2\}
  \end{align*}

  It is easy to see that $\Sigma_3$ is finite and closed under subformulae and
  single negations. Let $\mathbbm{M}= \langle W, V, R_{\Box}, \sim_{\forall},
  \mathcal{A} \rangle$ be the finite cannonical model formed of maximally
  consistent subsets of $\Sigma_3$, where everything is defined as usual,
  except $\sim_{\forall}$, which obeys the following specification:

  \begin{align*}
    w {\sim}_{{\forall}}v & {\Longleftrightarrow}(({\forall}{\phi}){\in}w
    {\Longleftrightarrow}({\forall}{\phi}){\in}v)
  \end{align*}

  This model makes true the following properties:
  \begin{enumerateroman}
    \item $\sim_{\forall}$ is an equivalence relation

    \item $R_{\Box} \subseteq \sim_{\forall}$

    \item In each equivalence class specified by $\sim_{\forall}$, there is at
    most one world making true $i$ for all $i \in \Upsilon$
  \end{enumerateroman}
  As in our previous construction we have that there is some world $w$ where
  $\mathbbm{M}, w \nvDash \psi$. \ Let $\mathbbm{M}^1 = \langle W', V',
  R_{\Box}', \sim_{\forall}', \mathcal{A}' \rangle$ be the submodel generated
  by $\{w\}$; we have that $\mathbbm{M}', w \nvDash \psi$ (see {\cite[chapter
  2.1]{blackburn\_modal\_2001}} for details on generated submodels). \ In this
  model $\forall$ is a universal modality and either $\left\llbracket i
  \right\rrbracket^{\mathbbm{M}'} = \varnothing$ or $\left\llbracket i
  \right\rrbracket^{\mathbbm{M}'} =\{v\}${\footnote{As per the usual
  convention, here $\left\llbracket \phi \right\rrbracket^{\mathbbm{M}}$
  denotes $\{w \in W \hspace{1em} | \hspace{1em} \mathbbm{M}, w \vDash
  \phi\}$. \ We will drop $\mathbbm{M}$ where it is unambiguous.}}. Since the
  store $\Psi$ of nominals is infinite and $\Upsilon$ is finite, we have that
  $\Psi \backslash \Upsilon$ is infinite, so there is some injection $\iota :
  W' \hookrightarrow \Psi \backslash \Upsilon$ which assigns a fresh nominal
  to every world. \ Let $\mathbbm{M}'' = \langle W'', V'', R'', \mathcal{A}'',
  \ell \rangle$, where:

  \begin{center}
    \begin{tabular}{lllll}
      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign V' (p)$\\
      $\bullet$ & $R'' \assign R'_{\Box}$ & {\hspace{3em}} & $\bullet$ &
      $\mathcal{A}'' (v) \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
      \mathcal{A}' (v)\} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
      \neg v R' u\}$\\
      \begin{tabular}{ll}
        $\bullet$ & $\ell (i) \assign \left\{ \begin{array}{ll}
          w & i \in \Upsilon \hspace{1em} \& \hspace{1em} \mathbbm{M}, w
          \vDash i\\
          \iota^{- 1} (i) & i \in \iota [W]\\
          \text{undefined} & \text{o/w}
        \end{array} \right.$
      \end{tabular} & $R'' \assign R'_{\Box}$ &  &  & 
    \end{tabular}
  \end{center}

  The the worlds is $\mathbbm{M}'$ and $\mathbbm{M}''$ agree on all
  subformulae of $\psi$, hence $\mathbbm{M}'', w \nvDash \psi$. The same
  reasoning as in the proof of Theorem \ref{completeness1} establishes and
  that the logic in Table \ref{logic2} itself is sound for $\mathbbm{M}''$ and
  makes true \tmtextbf{CSQ}, establishing completeness.
\end{proof}

\section{Logics of Multiple Knowledge Bases}

So far, we have only dealt with systems that reason over a single knowledge
base. \ In this section, we present various logics for reasoning over multiple
knowledge bases.

\subsection{Simple Justification Logic}

Justification Logic (JL) was originally developed by Artemov as the
\tmtextit{Logic of Proofs} (LP) {\cite{artemov_logic_1994}}. \ Its original
purpose was to provide a framework for reasoning about explicit provability in
Peano Arithmetic. \ The first introduction of Justification Logic can be found
in {\cite{artemov_introducing_2005}}, where Artemov and Nogina propose LP as a
logic for reasoning about evidence. \ In {\cite{fitting_logic_2005}}, Melvin
Fitting provided JL with Kripke model based semantics.

The principle innovation of LP/JL is to extend awareness logic, such that
awareness operations are now \tmtextit{proof terms}. \ Informally, we say that
``a proof term $X$ witnesses proposition $\phi$'', denoted ``$X : \phi$'',
whenever $X$ represents a proof of $\phi$. \ Proofs may have
{\tmstrong{multiple-conclusions}} in this system, so it is possible that $X :
\phi$ and $X : \psi$ can be true where $\phi \neq \psi$. \ In Fitting's Kripke
semantics, $X : \phi$ means that $\phi$ is in awareness set corresponding to
$X$. \ Proof terms are thought be operating in a \tmtextit{multi-conclusion}
proof system, so the same proof term may witness many different propositions.

The logics LP/JL include operators over proofs terms, so that new proof terms
may be assembled. \ One operation of particular interest to us is
{\tmem{choice}}, denoted $\oplus$. \ The expression ``$X \oplus Y : \phi$''
denotes that either $X$ or $Y$ are proofs witnessing $\phi$. \ There are other
operations which correspond to \tmtextit{modus ponens} and
\tmtextit{proof-theoretic reflection}, however we do not consider these
operations here.

In this section we consider a simplified form of JL suitable for reasoning
over multiple knowledge bases, which we call \tmtextit{simple justification
logic} (SJL). However, instead of thinking of terms as representing proofs, we
use them to represent knowledge bases. This is in the spirit of JL as a logic
of evidence: we consider each knowledge base to be a corpus of evidence. \
Each term ``names'' a different knowledge base at a particular world. \ Terms
may not refer to the same knowledge base at different worlds, just as in how
in awareness logic the agent need not be aware of the same formulae at
different worlds. \ Finally, we will make use of JL's {\tmem{choice}} operator
as a mechanism for forming the union of knowledge bases, creating new ones.

\begin{definition}
  Let $\Pi$ be a set of primitive terms. \ Define $\tau (\Pi)$ with the
  following grammar:
  \[ X \hspace{1em} : : = \hspace{1em} t \in \Pi \hspace{1em} | \hspace{1em} X
     \oplus Y \]

  Let $\Phi$ be a set of letters and $\Pi$ a set of primitive terms, and
  define the language $\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)$ as:
  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi \]
  where $X \in \tau (\Pi)$
\end{definition}

\begin{definition}
  \label{justmodels}A {\tmstrong{simple justification model}} $\mathbbm{M}=
  \langle W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V
  : \Phi \cup \{\circlearrowleft_X \hspace{1em} | \hspace{1em} X \in \tau
  (\Pi)\} \rightarrow 2^W$, an indexed relation $R : \tau (\Pi) \rightarrow
  2^{W \times W}$, along with a modified awareness function $\mathcal{A} : W
  \times \tau (\Pi) \rightarrow 2^{\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)}$. \
  In practice we will denote $\mathcal{A} (w, X)$ by a curried shorthand,
  namely $\mathcal{A}_w (X)$.

  The semantics for $\vDash$ have the following modifications:
  \begin{eqnarray*}
    \mathbbm{M}, w \vDash \Box_X \phi & \text{iff} & \text{for all $v \in W$
    where $w R_X v$ we have $\mathbbm{M}, v \vDash v$}\\
    \mathbbm{M}, w \vDash X : \phi & \text{iff} & \phi \in \mathcal{A}_w (X)
  \end{eqnarray*}
\end{definition}

\begin{definition}
  The following defines properties a simple justification model may make true:

  \begin{descriptiondash}
    \item[JCSQ] $\mathbbm{M}, w \vDash \Box_X \phi \text{ iff } \tmop{Th}
    (\mathbbm{M}) \cup \mathcal{A}_w (X) \vdash \phi$

    \item[JSND] $\mathbbm{M}, w \vDash \circlearrowleft_X \text{ iff
    $\mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w (X)$}$

    \item[CHOICE] $\mathcal{A}_w (X \oplus Y) = \mathcal{A}_w (X) \cup
    \mathcal{A}_w (Y)$
  \end{descriptiondash}

  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
\end{definition}

The above semantics are similar to the ones given in previous sections. \
\tmtextbf{JCSQ} is the same as \tmtextbf{CSQ} from {\S}\ref{awarenesslogic},
only it is relativized to a knowledge base denoted by $X$ at $w$. \ The
awareness logic of knowledge bases is special case of simple justification
logic where there is only one term.

Simplified justification logic is given in Table \ref{logic5}. \ We assert
without proof that this is a conservative extension of the awareness logic in
{\S}\ref{awarenesslogic}.

\begin{table}[h]
  \begin{tabular}{ll}
    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
    \rightarrow \psi \rightarrow \phi$ & \\
    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
    \Box_X \psi$ & \\
    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
    \\
    $\vdash (X \oplus Y : \phi) \rightarrow X : \phi$ & $\vdash (X \oplus Y :
    \phi) \rightarrow Y : \phi$\\
    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
    \circlearrowleft_{X \oplus Y}$ & \\
    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_X$ &
    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_Y$\\
    $\vdash \Box_X \phi \rightarrow \Box_{X \oplus Y} \phi$ & \\
    $\vdash \Box_{X \oplus X} \phi \rightarrow \Box_X \phi$ & $\vdash \Box_{(X
    \oplus X) \oplus Y} \phi \rightarrow \Box_{X \oplus Y} \phi$ \\
    $\vdash \Box_{X \oplus Y} \phi \rightarrow \Box_{Y \oplus X} \phi$ &
    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{(Y \oplus X)
    \oplus Z} \phi$\\
    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{X \oplus (Y
    \oplus Z)} \phi$ & \\
    & \\
    \begin{tabular}{lll}
      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
    \end{tabular} & 
  \end{tabular}
  \caption{\label{logic5}Simple Justification Logic}
\end{table}

\begin{theorem}
  \label{completeness5}Assuming an infinite store of proposition letters
  $\Phi$, SJL is sound and weakly complete for simple justification models
  making true \tmtextbf{JCSQ}, \tmtextbf{JSND} and \tmtextbf{CHOICE}
\end{theorem}

\begin{proof}
  As in the previous proofs, we only show completeness. \ Assume that $\nvdash
  \psi$. \ Let $\Xi \subseteq \tau (\Pi)$ be all of the subterms occurring in
  $\psi$; we assume that $\Xi$ is non-empty, since otherwise we may obtain the
  theorem via the usual completeness theorem for classical propositional
  logic. Let $\Sigma_0$ be the subformulae of $\psi$. \ Define:

  \begin{align*}
    {\Sigma}_1 &
    {\assign}{\Sigma}_0{\cup}\{\Box_Y{\phi}{\hspace{1em}}|{\hspace{1em}}\Box_X{\phi}{\in}{\Sigma}_0{\hspace{1em}}\&{\hspace{1em}}Y{\in}{\Xi}\}\\
    {\Sigma}_2 &
    {\assign}{\Sigma}_1{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1\}
  \end{align*}

  As in the proof of Theorem \ref{completeness2}, it is simple to verify that
  $\Sigma_2$ is closed under subformulae and single negations. \ Let
  $\mathbbm{M} \assign \langle W, V, R, \mathcal{A} \rangle$ be the finite
  cannonical model formed of maximally consistent subsets of $\Sigma_2$, where
  $V$ and $\mathcal{A}$ are defined as usual, and $R : \Xi \rightarrow 2^{W
  \times W}$ is defined by:
  \[ w R_X v \Longleftrightarrow \{\phi \hspace{1em} | \hspace{1em} \Box_X
     \phi \in w\} \subseteq v \]
  As in previous constructions we may prove the usual Lindenbaum and Truth
  Lemmas an use them obtain a world $w \in W$ where $\mathbbm{M}, w \nvDash
  \psi$.

  Next, define an operator $\twonotes : \tau (\Pi) \rightarrow 2^{\Pi}$ where:
  \[ \twonotes (X) \assign \{t \in \Pi \hspace{1em} | \hspace{1em} t \text{
     occurs in } X\} \]
  In other words, $\twonotes (X)$ is the set of atomic terms in $X$. \ As in
  our construction for Theorem \ref{completeness1}, $\mathbbm{M}$ makes true
  certain properties, along with some new properties:
  \begin{enumeratenumeric}
    \item \label{fin}$W$ and $\mathcal{A}_v (X)$ are finite, and $\phi \in
    \mathcal{A}_v (X)$ only if $\phi \in \Sigma_2$

    \item if $\mathbbm{M}, v \vDash X : \phi$ then $\mathbbm{M}, v \vDash
    \Box_X \phi$

    \item \label{refl}if $\mathbbm{M}, v \vDash \circlearrowleft_X$ then $v
    R_X v$

    \item \label{sndness}For all $X \oplus Y \in \Xi$, $\mathbbm{M}, v \vDash
    \circlearrowleft_{X \oplus Y}$ if and only if $\mathbbm{M}, v \vDash
    \circlearrowleft_X$ and $\mathbbm{M}, v \vDash \circlearrowleft_Y$

    \item \label{union}For all $X \oplus Y \in \Xi$, $\mathcal{A}_v (X \oplus
    Y) = \mathcal{A}_v (X) \cup \mathcal{A}_v (Y)$

    \item \label{sub}For all $X, Y \in \Xi$, if $\twonotes (X) \subseteq
    \twonotes (Y)$ then $R_Y \subseteq R_X$
  \end{enumeratenumeric}
  As in our previous constructions, it is necessary to refine this model using
  bisimulations to achieve properties which are not modally definable. \ In
  particular, we shall strengthen (\ref{refl}) to a biconditional and
  (\ref{sub}) to:

  \begin{center}
    \begin{tabular}{ll}
      \tmtextbf{6$'$.} & For all $X, Y \in \Xi$, $R_{X \oplus Y} = R_X \cap
      R_Y$
    \end{tabular}
  \end{center}

  We first strengthen (\ref{refl}) by constructing $\mathbbm{M}' \assign
  \langle W', V', R', \mathcal{A}' \rangle$, just as in Theorem
  \ref{completeness1}: {\hspace*{\fill}}
  \begin{itemizedot}
    \item $W' \assign W \uplus W$

    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
    (p)\}$

    \item $R'_X \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v
    R_X u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em}
    \mathbbm{M}, v \vDash \circlearrowleft_X \}$

    \item $\mathcal{A}' (v_l, X) \assign \mathcal{A}' (v_r, X) \assign
    \mathcal{A} (v, X)$
  \end{itemizedot}
  The same bisimulation relation $Z$ previously given suffices.

  We next make a strengthened the model where (\ref{sub}$'$) holds. \ Define
  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
  that{\footnote{Let $\{i_X \hspace{1em} | \hspace{1em} X \in \Xi\}$ be the
  family of canonical injections into the coproduct $\uplus_{\Xi} W$. As per
  our previous convention, we use $v_X$ as shorthand for $i_X (v)$.}}:
  \begin{itemizedot}
    \item $W'' \assign \uplus_{\Xi} W'$

    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$

    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em}
    \twonotes (X) \subseteq \twonotes (Z)\}$

    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
  \end{itemizedot}
  Note that this construction makes use of the assumption that $\Xi$ is
  non-empty. \ Let $Z \assign \{(v, v_X) \hspace{1em} | \hspace{1em} X \in \Xi
  \hspace{1em} \& \hspace{1em} v \in W' \}$; it is straightforward to prove
  that $Z$ is a bisimulation between $\mathbbm{M}'$ and $\mathbbm{M}''$, for
  all relations corresponding to terms $X \in \Xi$. Hence $\mathbbm{M}'', w_X
  \nvDash \psi$ for some $w_X \in W''$. \ In addition, $\mathbbm{M}''$
  inherits (\ref{fin}) through (\ref{sub}) from $\mathbbm{M}'$, as well as the
  converse of (\ref{refl}). \ Next observe, forall $X \oplus Y \in \Xi$:
  \begin{eqnarray*}
    \text{$(v_V, u_Z) \in R''_X \cap R''_Y$} & \Longleftrightarrow & \exists Z
    \in \Xi . \text{$v R'_Z u \hspace{1em} \& \hspace{1em} \twonotes (X)
    \subseteq \twonotes (Z) \hspace{1em} \& \hspace{1em} \twonotes (Y)
    \subseteq \twonotes (Z)$}\\
    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
    \& \hspace{1em} \twonotes (X) \cup \twonotes (Y) \subseteq \twonotes
    (Z)$}\\
    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
    \& \hspace{1em} \twonotes (X \oplus Y) \subseteq \twonotes (Z)$}\\
    & \Longleftrightarrow &  \text{$(v_V, u_Z) \in R''_{X \oplus Y}$}
  \end{eqnarray*}
  We now turn to our final construction. As in previous constructions, let
  $\iota : W'' \hookrightarrow \Phi \backslash \Psi$ be an injection assigning
  fresh nominals to worlds. \ Define $\mathbbm{M}''' \assign \langle W''',
  V''', R''', \mathcal{A}''' \rangle$ just as in the final construction in the
  proof of Theorem \ref{completeness1}, except that $R'''_X$ and
  $\mathcal{A}_v''' (X)$ are defined inductively as follows:

  \begin{center}
    \begin{tabular}{lll}
      $\bullet$ & $R'''_t \assign \left\{ \begin{array}{ll}
        R''_t & t \in \Xi\\
        W''' \times W''' & o / w
      \end{array} \right.$ & \\
      $\bullet$ & $R'''_{X \oplus Y} \assign R'''_X \cap R'''_Y$ & \\
      &  & \\
      $\bullet$ & $\mathcal{A}'''_v (t) \assign \{\phi \hspace{1em} | \phi \in
      \mathcal{A}''_v \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
      \neg v R'''_t u\}$ & where $t \in \Pi$\\
      $\bullet$ & $\mathcal{A}'''_v (X \oplus Y) \assign \mathcal{A}'''_v (X)
      \cup \mathcal{A}'''_v (Y)$ & 
    \end{tabular}
  \end{center}

  Induction over complexity of subformulae $\phi$ of $\psi$ yields
  $\mathbbm{M}'', w \vDash \phi \Longleftrightarrow \mathbbm{M}''', w \vDash
  \phi$, so we know that there is some world $w \in W'''$ such that
  $\mathbbm{M}''', w \nvDash \psi$. \ All that is left is to illustrate that
  $\mathbbm{M}'''$ has the properties we desire.

  First note that by definition, $\mathbbm{M}'''$ makes true
  \tmtextbf{CHOICE}. \ Next, an induction argument on the complexity of a
  terms $X$, making essential use of (\ref{sub}$'$), yields:
  \[ u R_X''' v \Longleftrightarrow \mathbbm{M}''', v \vDash \bigwedge
     \mathcal{A}'''_v (X) \]
  With this, $\mathbbm{M}'''$ makes true \tmtextbf{JSND} since it inherits
  (\ref{refl}). \ Finally, we note that we may repeat our previous arguments
  from Theorem \ref{completeness1} to prove \tmtextbf{JCSQ}.
\end{proof}

\subsection{Lattice Justification Logic}

{\color{red} NOTE: \ THIS SECTION HAS SOME SERIOUS PROBLEMS AND IT'S PROBABLY
WRONG...}

Implicit in our previous presentation of SJL: \ $\oplus$ behaves like a union
operation for knowledge bases, and dually like an intersection operation on
accessibility relations. \ It is natural to think of $\oplus$ as a join/meet
operator over a {\tmem{semi-lattice}}. \ In this section we make this
explicit, by increasing the expressive power of simple JL to express the order
theory inherent in knowledge bases. \ We call the novel logic presented in
this section \tmtextit{Lattice Justification Logic} (LJL){\footnote{We note
that ``Semi-Lattice Justification Logic'' may be a more appropriate name,
however we have decided to shorten semic-lattice to lattice in this article
for purposes of concision.}}. \ Lattice JL may be considered a novel logic for
studying the dynamics of \tmtextit{theory change}, where the logic employed by
the changing theories could be LJL itself.

\begin{definition}
  $\mathcal{L}_{\tmop{LJL}} (\Phi, \Pi)$ extends $\mathcal{L}_{\tmop{SJL}}
  (\Phi, \Pi)$ to:
  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi
     \hspace{1em} | \hspace{1em} X \sqsubseteq Y \]
  where $X, Y \in \tau (\Pi)$
\end{definition}

\begin{definition}
  \label{justmodels}A {\tmstrong{lattice justification model}} $\mathbbm{M}=
  \langle W, V, R, \mathcal{A}, \preccurlyeq \rangle$ is a simple
  justification model with a new relation $\preccurlyeq : W \rightarrow
  2^{\tau (\Pi) \times \tau (\Pi)}$ between terms, indexed by worlds. \ The
  semantics of $\sqsubseteq$ correspond to $\preccurlyeq$ as follows:
  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow X
     \preccurlyeq_w Y \]
\end{definition}

\begin{definition}
  A lattices justification model is said to make true \tmtextbf{LATTICE} if
  and only if:
  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow \mathcal{A}_w
     (X) \subseteq \mathcal{A}_w (Y) \]
\end{definition}

Table \ref{logic6} lists the axioms for the logic of lattice justification
models with the properties we have been investigating:

\begin{table}[h]
  \begin{tabular}{ll}
    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
    \rightarrow \psi \rightarrow \phi$ & \\
    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
    \Box_X \psi$ & \\
    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
    \\
    $\vdash X \sqsubseteq Y \rightarrow (X : \phi) \rightarrow Y : \phi$ & \\
    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
    \circlearrowleft_{X \oplus Y}$ & \\
    $\vdash X \sqsubseteq Y \rightarrow \circlearrowleft_Y \rightarrow
    \circlearrowleft_X$ & \\
    $\vdash X \sqsubseteq Y \rightarrow \Box_X \phi \rightarrow \Box_Y \phi$ &
    \\
    $\vdash X \sqsubseteq X$ & \\
    $\vdash X \sqsubseteq Y \rightarrow Y \sqsubseteq Z \rightarrow X
    \sqsubseteq Z$ & \\
    $\vdash X \sqsubseteq Y \rightarrow X \sqsubseteq Z \oplus Y$ & $\vdash X
    \sqsubseteq Y \rightarrow X \sqsubseteq Y \oplus Z$\\
    $\vdash X \sqsubseteq Z \rightarrow Y \sqsubseteq Z \rightarrow X \oplus Y
    \sqsubseteq Z$ & \\
    & \\
    \begin{tabular}{lll}
      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
    \end{tabular} & 
  \end{tabular}
  \caption{\label{logic6}Lattice Justification Logic}
\end{table}

\begin{theorem}
  \label{completeness6}Assuming an infinite store of proposition letters
  $\Phi$, LJL is sound and weakly complete for lattice justification models
  making true \tmtextbf{JCSQ}, \tmtextbf{JSND}, \tmtextbf{CHOICE} and
  \tmtextbf{LATTICE}
\end{theorem}

\begin{proof}
  Assume $\nvdash \psi$. \ Let $\mathbbm{M} \assign \langle W, V, R,
  \mathcal{A}, \preccurlyeq \rangle$ be the same as the finitary canonical
  model we initially constructed in Theorem \ref{completeness5}, only
  $\preccurlyeq$ is defined as:
  \[ X \preccurlyeq_w Y \Longleftrightarrow w \vdash X \sqsubseteq Y \]
  We may deduce that there is a world $w \in W$ such that $\mathbbm{M}, w
  \nvDash \psi$. \ This canonical model makes true properties (\ref{fin})
  through (\ref{union}) we listed in Theorem \ref{completeness5}, as well as a
  certain new properties:

  \begin{descriptioncompact}
    \item[6$\preccurlyeq$] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$
    then $R_Y [v] \subseteq R_X [v]$

    \item[7] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$ then
    $\mathcal{A}_v (X) \subseteq \mathcal{A}_v (Y)$

    \item[8] If $X \nin \Xi$, then $R_X = W \times W$ and $\mathcal{A}_v (X) =
    \varnothing$ for all $v \in W$

    \item[9] $\langle \preccurlyeq_v, \oplus \rangle$ is a join-semilattice
    over $\tau (\Pi)$ for all $v \in W$
  \end{descriptioncompact}

  As in previous constructions, completeness is achieved by through a series
  of model refinements. \ Note that property 8 has been implicitly true in all
  of our previous constructions, although we have not been interested in
  enforcing it to be inherited by model refinements previously.

  We first construct a model $\mathbbm{M}'$ which is bisimular to
  $\mathbbm{M}$, where (\ref{refl}) is strengthened to a biconditional. \ This
  is done exactly as we proceeded in previous constructions. We note that the
  notion of ``bisimulation'' here includes that two bisimular worlds $v$ and
  $u$ must have isomorphic semi-lattices $\preccurlyeq_v$ and
  $\preccurlyeq_w$. \ This is achieved by enforcing that $\preccurlyeq_{v_l}
  \assign \preccurlyeq_{v_r} \assign \preccurlyeq_v$. As before, we have that
  $\mathbbm{M}', w \nvDash \psi$ for some world $w \in W'$.

  We next strengthen (6$\preccurlyeq$) to a biconditional. \ Define
  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
  that:
  \begin{itemizedot}
    \item $W'' \assign \uplus_{\Xi} W'$

    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$

    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em} X
    \preccurlyeq_v Z\}$

    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
  \end{itemizedot}
  $\mathbbm{M}''$ is bisimular to $\mathbbm{M}'$ by the same mechanism as the
  previous construction. \ The important feature of this structure is to
  observe that the converse of (6$\preccurlyeq$) holds:
  \begin{eqnarray*}
    R_Y [v] \subseteq R_X [v] & \Longleftrightarrow & \forall Z \in \Xi
    \forall u_Z \in W'' (v_Q R'_Z u_Z \Longrightarrow v_Q R_X' u_Z)\\
    & \Longleftrightarrow & \forall Z \in \Xi \forall u_Z \in W'' (v R'_Z
    \Longrightarrow v_Q R_X u_Z)
  \end{eqnarray*}

  Our first transformation strengthens (\ref{union}), (6$\preccurlyeq$a) and
  (6$\preccurlyeq$b) so that they hold for all terms in $\tau (\Pi)$, rather
  than being restricted to $\Xi$. \ To this end define $\mathbbm{M}' \assign
  \langle W', V', R', \mathcal{A}', \preccurlyeq' \rangle$ where $W'$, $R'$
  and $\preccurlyeq'$ are the same as in $\mathbbm{M}$, but $R'$ and
  $\mathcal{A}'$ have the following modifications:
  \begin{eqnarray}
    R'_Y [v] & \assign & \bigcap_{X \preccurlyeq_v Y} R_X [v] \nonumber\\
    \mathcal{A}'_v (Y) & \assign & \bigcup_{X \preccurlyeq_v Y} \mathcal{A}'_v
    (X) \nonumber
  \end{eqnarray}

\end{proof}

\subsection{Neighborhood Semantics}

Neighborhood semantics were originally developed by Dana Scott and Richard
Montague in the early 1970s as a generalization of Kripke semantics \
{\cite{montague_universal_2008,scott_advice_1970}}. \ In
{\cite{fagin_belief_1988}}, Halpern and Fagin adapted neighborhood semantics
for reasoning about epistemic agents without logical omniscience. \ In this
section will demonstrate how these semantics may be modified so that
neighborhoods corresponds to the logical consequences of a different knowledge
bases. \ This allows for using logics with neighborhood semantics for
reasoning about multiple knowledge bases. \ A point of distinction of
neighborhood semantics from JL is that it may be possible that two distinct
knowledge bases cannot be merged by the agent.

\begin{definition}
  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
  language $\mathcal{L}_N (\Phi)$ as:
  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
     \hspace{1em} \bot \hspace{1em} | \hspace{1em} \phi \rightarrow \psi
     \hspace{1em} | \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A :
     \phi \hspace{1em} | \hspace{1em} K \phi \]
\end{definition}

Just as previous semantics, ``$\Box \phi$'' is intended to mean that the agent
has an argument for $\phi$ from some knowledge base. \ A novelty we present
here is that ``$K \phi$'' means that the agent has an argument for $\phi$ from
some \tmtextit{sound} knowledge base.

\begin{definition}
  \label{neighborhoodmodels}A {\tmstrong{neighborhood model}} $\mathbbm{M}=
  \langle W, V, \mathcal{N}, \mathcal{A} \rangle$ has a neighborhood function
  $\mathcal{N} : W \rightarrow 2^{2^W}$ and a multi-awareness function
  $\mathcal{A} : W \rightarrow 2^{2^{\mathcal{L}_N (\Phi)}}$

  The semantics for $\vDash$ have the following modifications:
  \begin{eqnarray*}
    \mathbbm{M}, w \vDash \Box \phi & \text{iff} & \text{there exists a $U \in
    \mathcal{N}_w$ where $\mathbbm{M}, v \vDash \phi$ for all $v \in U$}\\
    \mathbbm{M}, w \vDash K \phi & \text{iff} & \text{there exists a $U \in
    \mathcal{N}_w$ where $w \in U$ and $\mathbbm{M}, v \vDash \phi$ for all $v
    \in U$}\\
    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \bigcup
    \mathcal{A_w}
  \end{eqnarray*}
\end{definition}

Here we modify our previous notion of \tmtextbf{CSQ} and \tmtextbf{SND} to
match how our semantics are intended for reasoning over multiple bases:

\begin{definition}
  The following defines properties a neighborhood model may make true:

  \begin{descriptiondash}
    \item[NCSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff there exists a set
    $X \in \mathcal{A}_w$ such that } \tmop{Th} (\mathbbm{M}) \cup X \vdash
    \phi$

    \item[NSND] $\mathbbm{M}, w \vDash K \phi \text{ iff there exists a set $X
    \in \mathcal{A}_w$ such that $\mathbbm{M}, w \vDash X$ and } \tmop{Th}
    (\mathbbm{M}) \cup X \vdash \phi$
  \end{descriptiondash}

  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
\end{definition}

\begin{table}[h]
  \begin{tabular}{l}
    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
    \rightarrow \psi \rightarrow \phi$\\
    $\vdash K \phi \rightarrow \Box \phi$\\
    $\vdash K \phi \rightarrow \phi$\\
    $\vdash A : \phi \rightarrow \Box \phi$\\
    \\
    \begin{tabular}{llll}
      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi \rightarrow \psi}{\vdash \Box
      \phi \rightarrow \Box \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi
      \rightarrow \psi}{\vdash K \phi \rightarrow K \psi}$
    \end{tabular}
  \end{tabular}
  \caption{\label{logic3}A Neighborhood Logic for \tmtextbf{NCSQ} and
  {\tmstrong{NSND}}}
\end{table}

\begin{theorem}
  Assuming an infinite store of letters $\Phi$, the logic in Table
  \ref{logic3} is sound and weakly complete for neighborhood semantics making
  true \tmtextbf{NCSQ} and \tmtextbf{NSND}.
\end{theorem}

\begin{proof}
  Assume that $\nvdash \psi$, and define the finitary canonical model
  $\mathbbm{M}= \langle W, V, \mathcal{K}, \mathcal{N}, \mathcal{A} \rangle$
  where:
  \begin{itemizedot}
    \item $W \assign \text{the maximally consistent sets of subformulae of
    $\psi$, closed under single negation}$

    \item $V (p) \assign \{v \in W \hspace{1em} | \hspace{1em} p \in v\}$

    \item $\mathcal{K}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
    \hspace{1em} K \phi \in w\}$

    \item $\mathcal{N}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
    \hspace{1em} \Box \phi \in w\}$

    \item $\mathcal{A}_w \assign \{\{\phi\} \hspace{1em} | \hspace{1em} A :
    \phi \in w\}$
  \end{itemizedot}
  Note that in this model, there are neighborhoods for both knowledge and
  belief; more work is necessary to find a model based on this one which
  conforms to the semantics in Definition \ref{neighborhoodmodels}. \ For now,
  assume that $K$ is just another modality governed by the neighborhoods in
  $\mathcal{K}_w$. \ In both neighborhood functions, our idea is that the
  neighborhoods of $w$ in are supersets $S \supseteq \left\llbracket \phi
  \right\rrbracket$ where $\Box \phi \in w$ or $K \phi \in w$, respectively.

  There are steps of the inductive proof of the Truth Lemma for this structure
  which are not obvious nor obviously documented elsewhere. \ Assume
  $\mathbbm{M}, w \vDash \Box \chi$, where the Truth Lemma has been proven to
  hold for $\chi$; we must show $\Box \chi \in w$. \ By our assumption there
  is some $\phi$ and $S$ where $\Box \phi \in w$ and $S \supseteq \{v \in W
  \hspace{1em} | \hspace{1em} \phi \in v\}$. \ We argue that $\vdash \phi
  \rightarrow \chi$; for if not then by the finitary Lindenbaum lemma there is
  some $u \in W$ where $\phi \in u$ and $\chi \nin u$. \ Hence $u \in S$ and
  $\mathbbm{M}, u \nvDash \chi$, a contradiction. \ Since $\vdash \phi
  \rightarrow \chi$ then we know that $\vdash \Box \phi \rightarrow \Box \chi$
  by our rules, which means that $\Box \chi \in w$ by maximality.

  By the Lindenbaum Lemma we have that there is some $w \in W$ where
  $\mathbbm{M}, w \nvDash \psi$. \ $\mathbbm{M}$ makes true a number of
  properties:
  \begin{enumeratenumeric}
    \item $W$ and $\mathcal{A}_v$ are finite for all $v \in W$, and $\psi \in
    \bigcup \mathcal{A_w}$ only if $\psi$ is a subformula of $\phi$

    \item $\mathcal{K}_w \subseteq \mathcal{N}_w$

    \item If $S \in \mathcal{K}_w$ then $w \in S$

    \item $\mathbbm{M}, v \vDash A : \phi \rightarrow \Box \phi$ for all $v
    \in W$

    \item $\mathcal{N}_w$ and $\mathcal{K}_w$ are closed under supersets
  \end{enumeratenumeric}

  As in the proof of Theorem \ref{completeness1}, we use a bisimulation to
  move to a model where property (3) is strengthened to (3$'$): for all $S \in
  \mathcal{N}_w$, $w \in S$ if and only if $S \in \mathcal{K}'_w$. \ We defer
  the reader to {\cite{hansen_bisimulation_2007,pauly_bisimulation_1999}} for
  details regarding bisimulation in neighborhood semantics. \ Define
  $\mathbbm{M}' \assign \langle W', V', \mathcal{K}', \mathcal{N}',
  \mathcal{A}' \rangle$ such that:
  \begin{itemizedot}
    \item $W' \assign W \uplus W$ where \ $l, r$ its associated canonical
    injections and $\theta (v_l) \assign \theta (v_r) \assign v$ is a
    left-inverse of $l, r$

    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
    (p)\}$

    \item $\mathcal{K}' (v_i) \assign \{S \hspace{1em} | \hspace{1em} v_i \in
    S \hspace{1em} \& \hspace{1em} \theta [S] \in \mathcal{K_v} \}$ where $i =
    l, r$

    \item $\mathcal{N}' (v_i) \assign \mathcal{K}' (v_i) \cup \{S \hspace{1em}
    | \hspace{1em} v_i \nin S \hspace{1em} \& \hspace{1em} \theta [S] \in
    \mathcal{N_v} \}$ where $i = l, r$

    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
    (v)$
  \end{itemizedot}

  If we let $Z \assign \{(v, v_r), (v, v_l) \hspace{1em} | \hspace{1em} v \in
  W\}$, it is straightforward to verify that $Z$ is a neighborhood
  bisimulation. \ Hence $\mathbbm{M}, w_l \nvDash \psi$. \ Along with (3$'$),
  this model makes true (1), (2), (4). \ In fact, in light of ($3'$), we can
  see that this model does not need $\mathcal{K}'$, and conforms to the
  semantics in Definition \ref{neighborhoodmodels}.{\hspace*{\fill}}

  As in previous proofs, let $\Lambda$ be the proposition letters occuring in
  $\psi$ and define an injection $\iota : W' \hookrightarrow \Phi \backslash
  \Lambda$, assigning a nominal to every world in $\mathbbm{M}'$. \ Define
  $\mathbbm{M}'' \assign \langle W'', V'', \mathcal{N}'', \mathcal{A}''
  \rangle$ such that:

  \begin{center}
    \begin{tabular}{lllll}
      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
      \begin{array}{ll}
        V' (p) & p \in \Lambda\\
        \{v\} & p = i (v)\\
        \varnothing & o / w
      \end{array} \right.$\\
      $\bullet$ & $\mathcal{N}''_w \assign \mathcal{N}'_w$ & {\hspace{3em}} &
      $\bullet$ & $\mathcal{A}''_v \assign \{\partial_v S \hspace{1em} |
      \hspace{1em} S \in \mathcal{N}'_w \}$
    \end{tabular}
  \end{center}

  Where $\partial_v S \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
  \bigcup \mathcal{A}_v', \text{$\phi$ is a subformula of $\psi$ and}
  \hspace{1em} S \subseteq \left\llbracket \phi
  \right\rrbracket^{\mathbbm{M}'} \} \cup \{\neg \iota (u) \hspace{1em} |
  \hspace{1em} u \nin S\}$.

  As before, this model agrees with $\mathbbm{M}'$ on all subformulae of
  $\psi$, using the semantics in Definition \ref{neighborhoodmodels}, hence
  $\mathbbm{M}'', w_l \nvDash \phi$. \

  All that is left is to show \tmtextbf{NCSQ} and \tmtextbf{NSND} from three
  new properties:
  \begin{enumerateroman}
    \item For all words $v$ and all $X \in \mathcal{A}_v''$, $X$ is finite and
    \ $X = \partial_v S$ for some $S \in \mathcal{N}_v''$

    \item For all $v$ and all $S \in \mathcal{N}_v$, $u \in S$ if and only if
    $\mathbbm{M}'', u \vDash \bigwedge \partial_v S$

    \item The logic presented in Table \ref{logic3} is sound for
    $\mathbbm{M}''$
  \end{enumerateroman}
  Along with the deduction theorem for $\vdash$, these properties establish
  \tmtextbf{NCSQ} for this model using the logic of Table \ref{logic3} itself:

  \begin{align*}
    \text{$\exists X \in \mathcal{A''_v} \text{ s.t. } \tmop{Th}
    (\mathbbm{M}'') \cup X \vdash \phi$} & {\Longleftrightarrow}\text{$\exists
    S \in \mathcal{N''_v} \text{ s.t. } \tmop{Th} (\mathbbm{M}'') \cup
    \partial_v S \vdash \phi$}\\
    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
    \tmop{Th} (\mathbbm{M}'') \vdash \bigwedge \partial_v S \rightarrow
    \phi$}\\
    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
    \bigwedge \partial_v S \rightarrow \phi \in \tmop{Th} (\mathbbm{M}'')$}\\
    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
    \left\llbracket \bigwedge \partial_v S \right\rrbracket \subseteq
    \left\llbracket \phi \right\rrbracket$}\\
    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t.
    $\forall u \in W$ if } \mathbbm{M}, u \vDash \bigwedge \partial_v S \text{
    then } \mathbbm{M}, u \vDash \phi$}\\
    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
    \mathbbm{M}, u \vDash \phi \text{ for all } u \in S$}\\
    & {\Longleftrightarrow}{\mathbbm{M}},v{\vDash}\Box{\phi}
  \end{align*}

  \tmtextbf{NSND} follows from \tmtextbf{NCSQ} and the semantics of Definition
  \ref{neighborhoodmodels}.
\end{proof}

It is not too hard to identify the fragment of this logic that governs
knowledge alone. \ The fragment given in Table \ref{logic4} has special
significance to us, since it governs the notion of knowledge presented in
{\S}\ref{quantifying}.

\begin{table}[h]
  \begin{tabular}{l}
    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
    \rightarrow \psi \rightarrow \phi$\\
    $\vdash K \phi \rightarrow \phi$\\
    \\
    \begin{tabular}{llll}
      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
      \psi}$ &  &  & $\frac{\vdash \phi \rightarrow \psi}{\vdash K \phi
      \rightarrow K \psi}$
    \end{tabular}
  \end{tabular}
  \caption{\label{logic4}A knowledge-only neighborhood logic for
  \tmtextbf{NCSQ} and {\tmstrong{NSND}}}
\end{table}

\begin{proposition}
  The knowledge-only logic presented governs the $\Box$-free fragment of the
  logic in Table \ref{logic3}
\end{proposition}

This concludes our analysis of knowledge bases using neighborhood semantics.

\subsection{\label{quantifying}Using Modalities to Quantify over Knowledge
Bases}

\section{Conclusions \& Further Research}

The logic presented in Table \ref{logic1} is a conservative extension of the
basic modal logic $K$, which means that its decision problem is
\tmtextsf{PSPACE} hard (a lower bound). \ Our finitary completeness proof
establishes that its complexity is in \tmtextsf{EXP2-TIME} (an upper bound).

Worlds in epistemic logic might correspond to fantastic, pretend scenarios;
however, it may be desirable for some philosophers to model knowledge about
imaginary lands. \ After all, many children ``know'' a lot about Tolkien's
{\tmem{middle earth}} or Rowling's {\tmem{Hogwarts}} (the school Harry Potter
attends).

\begin{thebibliography}{10}
  \bibitem[1]{artemov\_logic\_1994}S.~N Artemov. {\newblock}Logic of proofs.
  {\newblock}\tmtextit{Annals of Pure and Applied Logic}, 67(1):29--60, 1994.

  \bibitem[2]{artemov\_introducing\_2005}S.~N Artemov and E.~Nogina.
  {\newblock}Introducing justification into epistemic logic.
  {\newblock}\tmtextit{Journal of Logic and Computation}, 15(6):1059, 2005.

  \bibitem[3]{basu\_revealed\_1980}Kaushik Basu. {\newblock}\tmtextit{Revealed
  preference of government}. {\newblock}Cambridge University Press, Cambridge;
  New York, 1980.

  \bibitem[4]{blackburn\_modal\_2001}P.~Blackburn, M.~De Rijke, and Y.~Venema.
  {\newblock}\tmtextit{Modal logic}. {\newblock}Cambridge Univ Pr, 2001.

  \bibitem[5]{boolos\_logic\_1995}George Boolos. {\newblock}\tmtextit{The
  logic of provability}. {\newblock}Cambridge University Press, 1995.

  \bibitem[6]{bull\_approach\_1970}R.~A. Bull. {\newblock}An approach to tense
  logic. {\newblock}\tmtextit{Theoria}, 36(3):282--300, December 1970.

  \bibitem[7]{davidson\_could\_1995}Donald Davidson. {\newblock}Could there be
  a science of rationality? {\newblock}\tmtextit{International Journal of
  Philosophical Studies}, 3(1):1--16, 1995.

  \bibitem[8]{fagin\_belief\_1988}R.~Fagin and J.~Y Halpern.
  {\newblock}Belief, awareness, and limited reasoning.
  {\newblock}\tmtextit{Artificial Intelligence}, 34(1):39--76, 1988.

  \bibitem[9]{fitting\_logic\_2005}M.~Fitting. {\newblock}The logic of proofs,
  semantically. {\newblock}\tmtextit{Annals of Pure and Applied Logic},
  132(1):1--25, 2005.

  \bibitem[10]{halpern\_set-theoretic\_1999}Joseph~Y. Halpern.
  {\newblock}Set-theoretic completeness for epistemic and conditional logic.
  {\newblock}\tmtextit{Annals of Mathematics and Artificial Intelligence},
  26(1-4):1--27, 1999.

  \bibitem[11]{hansen\_bisimulation\_2007}Helle~Hvid Hansen, Clemens Kupke,
  and Eric Pacuit. {\newblock}Bisimulation for neighbourhood structures.
  {\newblock}In \tmtextit{Proceedings of the 2nd international conference on
  Algebra and coalgebra in computer science}, pages 279--293, Bergen, Norway,
  2007. Springer-Verlag.

  \bibitem[12]{hendricks\_mainstream\_2006}V.~F Hendricks.
  {\newblock}\tmtextit{Mainstream and formal epistemology}.
  {\newblock}Cambridge Univ Pr, 2006.

  \bibitem[13]{kornblith\_beyond\_1980}Hilary Kornblith. {\newblock}Beyond
  foundationalism and the coherence theory. {\newblock}\tmtextit{The Journal
  of Philosophy}, 77(10):597--612, October 1980.

  \bibitem[14]{montague\_universal\_2008}Richard Montague.
  {\newblock}Universal grammar. {\newblock}\tmtextit{Theoria}, 36(3):373--398,
  2008.

  \bibitem[15]{pauly\_bisimulation\_1999}M.~Pauly. {\newblock}Bisimulation for
  general non-normal modal logic. {\newblock}\tmtextit{Manuscript}, 1999.

  \bibitem[16]{prior\_revised\_1969}Arthur~N. Prior.
  {\newblock}\tmtextit{Revised and Expanded Edition of Arthur N. Prior: Papers
  on Time and Tense}. {\newblock}Oxford University Press, 1969.
  {\newblock}reprinted in 2003.

  \bibitem[17]{rubinstein\_modeling\_1998}Ariel Rubinstein.
  {\newblock}\tmtextit{Modeling Bounded Rationality}. {\newblock}MIT Press,
  1998.

  \bibitem[18]{scott\_advice\_1970}D.~Scott. {\newblock}Advice on modal logic.
  {\newblock}\tmtextit{Philosophical problems in Logic}, 143:74, 1970.

  \bibitem[19]{sen\_behaviour\_1973}Amartya Sen. {\newblock}Behaviour and the
  concept of preference. {\newblock}\tmtextit{Economica}, 40(159):241--259,
  August 1973.

  \bibitem[20]{wampler-doty\_evidentialist\_2010}Matthew Wampler-Doty.
  {\newblock}Evidentialist logic. {\newblock}MSc thesis, Universiteit van
  Amsterdam, Amsterdam, North-Holland, September 2010.
\end{thebibliography}

\end{document}

### 2010-12-15 paper.tex
The paper should now build correctly by simply typing "make"

@@
-\documentclass{acmconf}
+\documentclass{article}
 \usepackage{geometry,amsmath,amssymb,wasysym,enumerate,bbm,color}
 \geometry{letterpaper}
+
+\usepackage{stmaryrd}
 
@@
   {\cite{van_benthem_inference_2009}} and \tmtextit{Justification Logic}
-  {\cite{artemov_introducing_2005}}. \ The purpose of this paper is to
+  {\cite{artemov_introducing_2005}}.  The purpose of this paper is to
   repurpose various epistemic logics from these previous efforts for reasoning
-  about logical closures over knowledge bases. \ The results in this paper are
+  about logical closures over knowledge bases.  The results in this paper are
   based on previous work carried out in
@@
 The modern tradition in epistemic logic is to assume knowledge modalities
-conform to the $S 5$ axiom schema. \ As noted in
+conform to the $S 5$ axiom schema.  As noted in
 {\cite{halpern_set-theoretic_1999,rubinstein_modeling_1998}}, the semantics of
@@
 into \tmtextit{information sets}, which is the traditional approach in game
-theory and decision theory. \ While it is not commonly acknowledged in
+theory and decision theory.  While it is not commonly acknowledged in
 epistemic logic, economists and philosophers accept that traditional decision
-theory is externalist and behaviourist in nature{\footnote{An early essay by
+theory is externalist and behaviourist in nature
+(FIXME)
+\footnote{An early essay by
 Amartya Sen on the philosophical foundations of traditional decision theory
 makes the behaviorist reading of decision theory clear
-{\cite{sen_behaviour_1973}}. \ Kaushik Basu also discusses the behaviorist
-nature of decision theory {\cite[pgs. 53--54]{basu\_revealed\_1980}}. \
+\cite{sen_behaviour_1973}.  Kaushik Basu also discusses the behaviorist
+nature of decision theory {\cite[pgs. 53--54]{basu_revealed_1980}}. 
 Finally, Donald Davidson appeals to decision theory to motivate an externalist
-epistemology in {\cite{davidson_could_1995}}.}}.
+epistemology in \cite{davidson_could_1995}.}.
 
@@
 a research program to find logics for explicit knowledge, providing the first
-suggestion of an internalist perspective on epistemic logic. \ Subsequently,
+suggestion of an internalist perspective on epistemic logic.  Subsequently,
 Sergei Artemov and Elena Nogina proposed a logic of explicit justification,
@@
 {\cite{artemov_introducing_2005}}, based on Artemov's \tmtextit{Logic of
-Proofs} {\cite{artemov_logic_1994}}. \ While the original semantics of JL was
+Proofs} {\cite{artemov_logic_1994}}.  While the original semantics of JL was
 interpretability into Peano Arithmetic, Melvin Fitting proposed Kripke
-semantics for JL in {\cite{fitting_logic_2005}}. \ Recently, Fernando
+semantics for JL in {\cite{fitting_logic_2005}}.  Recently, Fernando
 Vel\'azquez-Quesada and Johan van Benthem have developed a simpler framework
 for explicit epistemics in {\cite{van_benthem_inference_2009}}, entitled the
-\tmtextit{Dynamics of Awareness}. \ This work was based on Joseph Halpern and
+\tmtextit{Dynamics of Awareness}.  This work was based on Joseph Halpern and
 Ronald Fagin's original \tmtextit{Awareness Logic} {\cite{fagin_belief_1987}}.
@@
 In this essay we repurpose various externalist logics to take on an
-internalist reading. \ The concept of a \tmtextit{knowledge base}, from which
+internalist reading.  The concept of a \tmtextit{knowledge base}, from which
 beliefs may be implicitly deduced, will play a crucial role in our discussion.
 \ We propose this as an avenue for representing foundationalist perspectives
-on epistemology in epistemic logic. \ Our philosophical motivation is taken
-from two sources. \ The first is Vincent Hendricks in
+on epistemology in epistemic logic.  Our philosophical motivation is taken
+from two sources.  The first is Vincent Hendricks in
 {\cite{hendricks_mainstream_2006}}, where he characterizes the principal of
@@
 sometimes written as $\phi \in \tmop{Cn} ( \mathcal{A})$ in the artificial
-intelligence literature. \ Our second inspiration comes from what Hilary
+intelligence literature.  Our second inspiration comes from what Hilary
 Kornblith calls the \tmtextit{the arguments on paper thesis}
@@
   Let us suppose that, for any person, it is possible, at least in principle,
-  to list all of the propositions that person believes. \ The
+  to list all of the propositions that person believes.  The
   arguments-on-paper thesis is just the view that a person has a justified
@@
 Kornblith asserts that foundationalism and coherentism vie for accounts of a
-``good argument'' in the above thesis. \ He provides an extensive bibliography
+``good argument'' in the above thesis.  He provides an extensive bibliography
 citing proposals for this principle by a number of 20th century
-epistemologists, including figures such as A.J. Ayer and C.I. Lewis. \ The
+epistemologists, including figures such as A.J. Ayer and C.I. Lewis.  The
 rest of Kornblith's paper is devoted to attacking this view and proposing a
@@
 We adopt a arguments-on-paper-thesis perspective on epistemic logic in this
-paper. \ We consider a \tmtextit{good argument} to be a logical derivation
-from propositions present in a knowledge base. \ In this fashion, our \ \
+paper.  We consider a \tmtextit{good argument} to be a logical derivation
+from propositions present in a knowledge base.  In this fashion, ou.  \
 Special attention will be given to \tmtextit{sound derivations}, which will be
-thought of as a form of knowledge. \ In Awareness Logic, we will interpret
-awareness of a formula as membership in a knowledge base. \ We prove
-completeness for basic awareness logic and a hybrid logic extension. \ Logics
+thought of as a form of knowledge.  In Awareness Logic, we will interpret
+awareness of a formula as membership in a knowledge base.  We prove
+completeness for basic awareness logic and a hybrid logic extension.  Logics
 of multiple knowledge bases are also presented: a simplified form of
 Justification Logic, a logic with neighborhood semantics, an a logic with
-modalities for quantifying over knowledge bases. \ We conclude with an
+modalities for quantifying over knowledge bases.  We conclude with an
 application to naturalized epistemology found in the psychological literature.
@@
 \ One difference in our presentation is the inclusion of a novel letter and a
-superficial change in notation. \ This work is inspired by the developments in
+superficial change in notation.  This work is inspired by the developments in
 van Benthem and Vel\'azquez-Quesada {\cite{van_benthem_inference_2009}}.
@@
   \cup \{\circlearrowleft\} \rightarrow 2^W$ and an awareness function
-  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$. \ We will usually
+  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$.  We will usually
   denote $\mathcal{A} (w)$ as $\mathcal{A}_w$.
@@
   Define the semantic entailment relation $\vDash$ where atomic propositions,
-  logical connectives and modality are interpreted as usual. \ We employ the
+  logical connectives and modality are interpreted as usual.  We employ the
   following novel definition:
@@
 knowledge base being sound. A sound knowledge base will only render true
-conclusions when used in deductions. \ If one considers ``the existance of a
+conclusions when used in deductions.  If one considers ``the existance of a
 sound deduction'' sufficient for a kind of knowledge, then $\circlearrowleft$
-is suitable for investigating this notion of epistemology. \ That is, if
+is suitable for investigating this notion of epistemology.  That is, if
 $\mathbbm{M}, w \vDash \circlearrowleft \wedge \Box \phi$, then we may
@@
 \begin{proof}
-  Soundness is straightforward, so we will only address completeness. \ Assume
-  $\nvdash \psi$. \ Consider the finite canonical model $\mathbbm{M}= \langle
+  Soundness is straightforward, so we will only address completeness.  Assume
+  $\nvdash \psi$.  Consider the finite canonical model $\mathbbm{M}= \langle
   W, V, R, \mathcal{A} \rangle$ formed of maximally consistent sets of
@@
   of this property may be found in {\cite[pg.
-  243]{blackburn\_modal\_2001}}.}}), as per the finitary modal completeness
-  proofs found in {\cite[chapter 4.8]{blackburn\_modal\_2001}} and
-  {\cite[chapter 5]{boolos\_logic\_1995}}. \ Typical presentations do not
+  243]{blackburn_modal_2001}}.}}), as per the finitary modal completeness
+  proofs found in {\cite[chapter 4.8]{blackburn_modal_2001}} and
+  {\cite[chapter 5]{boolos_logic_1995}}.  Typical presentations do not
   include awareness, however it is defined intuitively in this case:
@@
   \psi$ for some world $w$ by a finitary {\tmem{Lindenbaum Lemma}} and
-  {\tmem{Truth Theorem}}. \ Moreover, it is straightforward to verify that
+  {\tmem{Truth Theorem}}.  Moreover, it is straightforward to verify that
   $\mathbbm{M}$ makes true the following properties:
@@
   We next produce a bisimular{\footnote{The notion of bisimulation is
-  discussed at length in {\cite[chapter 2.2]{blackburn\_modal\_2001}}. \ We
+  discussed at length in {\cite[chapter 2.2]{blackburn_modal_2001}}.  We
   note that the basic definition and all of the usual theorems (modal
@@
   It is straightforward to verify that $\mathbbm{M}'$ makes true the desired
-  properties. \ Let $Z \assign \{(v, v_l), (v, v_r) \hspace{1em} |
-  \hspace{1em} v \in W\}$; \ then $Z$ is a bisimulation between $\mathbbm{M}$
-  and $\mathbbm{M}'$. \ Therefore we know there is some $w \in W$ such that
+  properties.  Let $Z \assign \{(v, v_l), (v, v_r) \hspace{1em} |
+  \hspace{1em} v \in W\}$.  then $Z$ is a bisimulation between $\mathbbm{M}$
+  and $\mathbbm{M}'$.  Therefore we know there is some $w \in W$ such that
   $\mathbbm{M}', w_l \nvDash \psi$ and $\mathbbm{M}', w_r \nvDash \psi$.
@@
   $\mathbbm{M}'$ for all subformulae of $\psi$, which makes true
-  \tmtextbf{CSQ} and \tmtextbf{SND}. \ Let $\Lambda$ be the set of proposition
-  letters occuring in $\psi$. \ We will make use members of $\Phi \backslash
-  \Lambda$ as {\tmem{nominals}}, as per the tradition in hybrid logic. \ This
+  \tmtextbf{CSQ} and \tmtextbf{SND}.  Let $\Lambda$ be the set of proposition
+  letters occuring in $\psi$.  We will make use members of $\Phi \backslash
+  \Lambda$ as {\tmem{nominals}}, as per the tradition in hybrid logic.  This
   is possible since both $W'$ and $\Lambda$ are finite and $\Phi$ is infinite
-  by hypothesis. \ Let $\iota : W \uplus W \hookrightarrow \Phi \backslash
+  by hypothesis.  Let $\iota : W \uplus W \hookrightarrow \Phi \backslash
   \Lambda$ be an injection assigning a fresh nominal associated with each
-  world in $\mathbbm{M}'$. \ Now define $\mathbbm{M}'' \assign \langle W'',
+  world in $\mathbbm{M}'$.  Now define $\mathbbm{M}'' \assign \langle W'',
   V'', R'', \mathcal{A}'' \rangle$, where:
@@
   All that is left to show is that $\mathbbm{M}''$ makes true \tmtextbf{CSQ}
-  and \tmtextbf{SND}. \ $\mathbbm{M}''$ has three further properties:
+  and \tmtextbf{SND}.  $\mathbbm{M}''$ has three further properties:
   \begin{enumerateroman}
@@
 
-  All that is left is to demonstrate \tmtextbf{CSQ} for some sound logic. \ We
-  will use the logic in Table \ref{logic1} itself. \ From (i), (ii), (iii),
+  All that is left is to demonstrate \tmtextbf{CSQ} for some sound logic.  We
+  will use the logic in Table \ref{logic1} itself.  From (i), (ii), (iii),
   and the \tmtextit{deduction theorem} for modal logic, we have the following
@@
 {\cite{prior_revised_1969}} and later formally developed in
-{\cite{bull_approach_1970}}.}}. \ In this section we adapt hybrid logic and
-show that it is a complete for reasoning about knowledge bases. \ We note that
+{\cite{bull_approach_1970}}.}}.  In this section we adapt hybrid logic and
+show that it is a complete for reasoning about knowledge bases.  We note that
 because of the increased expressive power of hybrid logic, our completeness
@@
 Our approach in hybrid logic is to employ a universal modality along with
-nominals. \ This framework presents a logic where the agent may reason about
-various labeled scenarios. \ Scenarios may be multiply labeled or not labeled
-at all. \ From these intuitions we have the following definition:
+nominals.  This framework presents a logic where the agent may reason about
+various labeled scenarios.  Scenarios may be multiply labeled or not labeled
+at all.  From these intuitions we have the following definition:
 
@@
 then if they can deduce something from their knowledge base, what they deduce
-must be true at world $i$.'' \ In a way, this may be considered as
+must be true at world $i$.'.  In a way, this may be considered as
 {\tmem{relativising}} knowledge particular named situations.
@@
 $\circlearrowleft$ symbol in this setting. \tmtextbf{CSQ} still makes sense
-without modification, however. \ The following gives a logic for hybrid models
+without modification, however.  The following gives a logic for hybrid models
 making true \tmtextbf{CSQ}:
@@
 \begin{proof}
-  As before, soundness is trivial. \ Completeness is based on a modification
-  of techniques found in {\cite[chapter 5]{boolos\_logic\_1995}}. \ Assume
+  As before, soundness is trivial.  Completeness is based on a modification
+  of techniques found in {\cite[chapter 5]{boolos_logic_1995}}.  Assume
   that $\nvdash \psi$ and let $\Sigma_0$ be the set of subformulae of $\psi$,
-  and let $\Upsilon$ be the set of nominals occuring in $\psi$. \ Define:
+  and let $\Upsilon$ be the set of nominals occuring in $\psi$.  Define:
 
@@
   As in our previous construction we have that there is some world $w$ where
-  $\mathbbm{M}, w \nvDash \psi$. \ Let $\mathbbm{M}^1 = \langle W', V',
+  $\mathbbm{M}, w \nvDash \psi$.  Let $\mathbbm{M}^1 = \langle W', V',
   R_{\Box}', \sim_{\forall}', \mathcal{A}' \rangle$ be the submodel generated
   by $\{w\}$; we have that $\mathbbm{M}', w \nvDash \psi$ (see {\cite[chapter
-  2.1]{blackburn\_modal\_2001}} for details on generated submodels). \ In this
+  2.1]{blackburn_modal_2001}} for details on generated submodels).  In this
   model $\forall$ is a universal modality and either $\left\llbracket i
@@
   denotes $\{w \in W \hspace{1em} | \hspace{1em} \mathbbm{M}, w \vDash
-  \phi\}$. \ We will drop $\mathbbm{M}$ where it is unambiguous.}}. Since the
+  \phi\}$.  We will drop $\mathbbm{M}$ where it is unambiguous.}}. Since the
   store $\Psi$ of nominals is infinite and $\Upsilon$ is finite, we have that
@@
   W' \hookrightarrow \Psi \backslash \Upsilon$ which assigns a fresh nominal
-  to every world. \ Let $\mathbbm{M}'' = \langle W'', V'', R'', \mathcal{A}'',
+  to every world.  Let $\mathbbm{M}'' = \langle W'', V'', R'', \mathcal{A}'',
   \ell \rangle$, where:
@@
 So far, we have only dealt with systems that reason over a single knowledge
-base. \ In this section, we present various logics for reasoning over multiple
+base.  In this section, we present various logics for reasoning over multiple
 knowledge bases.
@@
 Justification Logic (JL) was originally developed by Artemov as the
-\tmtextit{Logic of Proofs} (LP) {\cite{artemov_logic_1994}}. \ Its original
+\tmtextit{Logic of Proofs} (LP) {\cite{artemov_logic_1994}}.  Its original
 purpose was to provide a framework for reasoning about explicit provability in
-Peano Arithmetic. \ The first introduction of Justification Logic can be found
+Peano Arithmetic.  The first introduction of Justification Logic can be found
 in {\cite{artemov_introducing_2005}}, where Artemov and Nogina propose LP as a
-logic for reasoning about evidence. \ In {\cite{fitting_logic_2005}}, Melvin
+logic for reasoning about evidence.  In {\cite{fitting_logic_2005}}, Melvin
 Fitting provided JL with Kripke model based semantics.
@@
 The principle innovation of LP/JL is to extend awareness logic, such that
-awareness operations are now \tmtextit{proof terms}. \ Informally, we say that
+awareness operations are now \tmtextit{proof terms}.  Informally, we say that
 ``a proof term $X$ witnesses proposition $\phi$'', denoted ``$X : \phi$'',
-whenever $X$ represents a proof of $\phi$. \ Proofs may have
+whenever $X$ represents a proof of $\phi$.  Proofs may have
 {\tmstrong{multiple-conclusions}} in this system, so it is possible that $X :
-\phi$ and $X : \psi$ can be true where $\phi \neq \psi$. \ In Fitting's Kripke
+\phi$ and $X : \psi$ can be true where $\phi \neq \psi$.  In Fitting's Kripke
 semantics, $X : \phi$ means that $\phi$ is in awareness set corresponding to
-$X$. \ Proof terms are thought be operating in a \tmtextit{multi-conclusion}
+$X$.  Proof terms are thought be operating in a \tmtextit{multi-conclusion}
 proof system, so the same proof term may witness many different propositions.
@@
 The logics LP/JL include operators over proofs terms, so that new proof terms
-may be assembled. \ One operation of particular interest to us is
-{\tmem{choice}}, denoted $\oplus$. \ The expression ``$X \oplus Y : \phi$''
-denotes that either $X$ or $Y$ are proofs witnessing $\phi$. \ There are other
+may be assembled.  One operation of particular interest to us is
+{\tmem{choice}}, denoted $\oplus$.  The expression ``$X \oplus Y : \phi$''
+denotes that either $X$ or $Y$ are proofs witnessing $\phi$.  There are other
 operations which correspond to \tmtextit{modus ponens} and
@@
 of evidence: we consider each knowledge base to be a corpus of evidence. \
-Each term ``names'' a different knowledge base at a particular world. \ Terms
+Each term ``names'' a different knowledge base at a particular world.  Terms
 may not refer to the same knowledge base at different worlds, just as in how
 in awareness logic the agent need not be aware of the same formulae at
-different worlds. \ Finally, we will make use of JL's {\tmem{choice}} operator
+different worlds.  Finally, we will make use of JL's {\tmem{choice}} operator
 as a mechanism for forming the union of knowledge bases, creating new ones.
@@
 \begin{definition}
-  Let $\Pi$ be a set of primitive terms. \ Define $\tau (\Pi)$ with the
+  Let $\Pi$ be a set of primitive terms.  Define $\tau (\Pi)$ with the
   following grammar:
@@
 \tmtextbf{JCSQ} is the same as \tmtextbf{CSQ} from {\S}\ref{awarenesslogic},
-only it is relativized to a knowledge base denoted by $X$ at $w$. \ The
+only it is relativized to a knowledge base denoted by $X$ at $w$.  The
 awareness logic of knowledge bases is special case of simple justification
@@
 
-Simplified justification logic is given in Table \ref{logic5}. \ We assert
+Simplified justification logic is given in Table \ref{logic5}.  We assert
 without proof that this is a conservative extension of the awareness logic in
@@
 \begin{proof}
-  As in the previous proofs, we only show completeness. \ Assume that $\nvdash
-  \psi$. \ Let $\Xi \subseteq \tau (\Pi)$ be all of the subterms occurring in
+  As in the previous proofs, we only show completeness.  Assume that $\nvdash
+  \psi$.  Let $\Xi \subseteq \tau (\Pi)$ be all of the subterms occurring in
   $\psi$; we assume that $\Xi$ is non-empty, since otherwise we may obtain the
   theorem via the usual completeness theorem for classical propositional
-  logic. Let $\Sigma_0$ be the subformulae of $\psi$. \ Define:
+  logic. Let $\Sigma_0$ be the subformulae of $\psi$.  Define:
 
@@
   As in the proof of Theorem \ref{completeness2}, it is simple to verify that
-  $\Sigma_2$ is closed under subformulae and single negations. \ Let
+  $\Sigma_2$ is closed under subformulae and single negations.  Let
   $\mathbbm{M} \assign \langle W, V, R, \mathcal{A} \rangle$ be the finite
@@
      occurs in } X\} \]
-  In other words, $\twonotes (X)$ is the set of atomic terms in $X$. \ As in
+  In other words, $\twonotes (X)$ is the set of atomic terms in $X$.  As in
   our construction for Theorem \ref{completeness1}, $\mathbbm{M}$ makes true
@@
   As in our previous constructions, it is necessary to refine this model using
-  bisimulations to achieve properties which are not modally definable. \ In
+  bisimulations to achieve properties which are not modally definable.  In
   particular, we shall strengthen (\ref{refl}) to a biconditional and
@@
 
-  We next make a strengthened the model where (\ref{sub}$'$) holds. \ Define
+  We next make a strengthened the model where (\ref{sub}$'$) holds.  Define
   $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
@@
   Note that this construction makes use of the assumption that $\Xi$ is
-  non-empty. \ Let $Z \assign \{(v, v_X) \hspace{1em} | \hspace{1em} X \in \Xi
+  non-empty.  Let $Z \assign \{(v, v_X) \hspace{1em} | \hspace{1em} X \in \Xi
   \hspace{1em} \& \hspace{1em} v \in W' \}$; it is straightforward to prove
@@
   all relations corresponding to terms $X \in \Xi$. Hence $\mathbbm{M}'', w_X
-  \nvDash \psi$ for some $w_X \in W''$. \ In addition, $\mathbbm{M}''$
+  \nvDash \psi$ for some $w_X \in W''$.  In addition, $\mathbbm{M}''$
   inherits (\ref{fin}) through (\ref{sub}) from $\mathbbm{M}'$, as well as the
-  converse of (\ref{refl}). \ Next observe, forall $X \oplus Y \in \Xi$:
+  converse of (\ref{refl}).  Next observe, forall $X \oplus Y \in \Xi$:
   \begin{eqnarray*}
@@
   $\iota : W'' \hookrightarrow \Phi \backslash \Psi$ be an injection assigning
-  fresh nominals to worlds. \ Define $\mathbbm{M}''' \assign \langle W''',
+  fresh nominals to worlds.  Define $\mathbbm{M}''' \assign \langle W''',
   V''', R''', \mathcal{A}''' \rangle$ just as in the final construction in the
@@
   \phi$, so we know that there is some world $w \in W'''$ such that
-  $\mathbbm{M}''', w \nvDash \psi$. \ All that is left is to illustrate that
+  $\mathbbm{M}''', w \nvDash \psi$.  All that is left is to illustrate that
   $\mathbbm{M}'''$ has the properties we desire.
@@
   First note that by definition, $\mathbbm{M}'''$ makes true
-  \tmtextbf{CHOICE}. \ Next, an induction argument on the complexity of a
+  \tmtextbf{CHOICE}.  Next, an induction argument on the complexity of a
   terms $X$, making essential use of (\ref{sub}$'$), yields:
@@
   With this, $\mathbbm{M}'''$ makes true \tmtextbf{JSND} since it inherits
-  (\ref{refl}). \ Finally, we note that we may repeat our previous arguments
+  (\ref{refl}).  Finally, we note that we may repeat our previous arguments
   from Theorem \ref{completeness1} to prove \tmtextbf{JCSQ}.
@@
 
-{\color{red} NOTE: \ THIS SECTION HAS SOME SERIOUS PROBLEMS AND IT'S PROBABLY
+{\color{red} NOTE.  THIS SECTION HAS SOME SERIOUS PROBLEMS AND IT'S PROBABLY
 WRONG...}
 
-Implicit in our previous presentation of SJL: \ $\oplus$ behaves like a union
+Implicit in our previous presentation of SJL.  $\oplus$ behaves like a union
 operation for knowledge bases, and dually like an intersection operation on
-accessibility relations. \ It is natural to think of $\oplus$ as a join/meet
-operator over a {\tmem{semi-lattice}}. \ In this section we make this
+accessibility relations.  It is natural to think of $\oplus$ as a join/meet
+operator over a {\tmem{semi-lattice}}.  In this section we make this
 explicit, by increasing the expressive power of simple JL to express the order
-theory inherent in knowledge bases. \ We call the novel logic presented in
+theory inherent in knowledge bases.  We call the novel logic presented in
 this section \tmtextit{Lattice Justification Logic} (LJL){\footnote{We note
@@
 however we have decided to shorten semic-lattice to lattice in this article
-for purposes of concision.}}. \ Lattice JL may be considered a novel logic for
+for purposes of concision.}}.  Lattice JL may be considered a novel logic for
 studying the dynamics of \tmtextit{theory change}, where the logic employed by
@@
   justification model with a new relation $\preccurlyeq : W \rightarrow
-  2^{\tau (\Pi) \times \tau (\Pi)}$ between terms, indexed by worlds. \ The
+  2^{\tau (\Pi) \times \tau (\Pi)}$ between terms, indexed by worlds.  The
   semantics of $\sqsubseteq$ correspond to $\preccurlyeq$ as follows:
@@
 \begin{proof}
-  Assume $\nvdash \psi$. \ Let $\mathbbm{M} \assign \langle W, V, R,
+  Assume $\nvdash \psi$.  Let $\mathbbm{M} \assign \langle W, V, R,
   \mathcal{A}, \preccurlyeq \rangle$ be the same as the finitary canonical
@@
   We may deduce that there is a world $w \in W$ such that $\mathbbm{M}, w
-  \nvDash \psi$. \ This canonical model makes true properties (\ref{fin})
+  \nvDash \psi$.  This canonical model makes true properties (\ref{fin})
   through (\ref{union}) we listed in Theorem \ref{completeness5}, as well as a
@@
   As in previous constructions, completeness is achieved by through a series
-  of model refinements. \ Note that property 8 has been implicitly true in all
+  of model refinements.  Note that property 8 has been implicitly true in all
   of our previous constructions, although we have not been interested in
@@
   We first construct a model $\mathbbm{M}'$ which is bisimular to
-  $\mathbbm{M}$, where (\ref{refl}) is strengthened to a biconditional. \ This
+  $\mathbbm{M}$, where (\ref{refl}) is strengthened to a biconditional.  This
   is done exactly as we proceeded in previous constructions. We note that the
@@
   $u$ must have isomorphic semi-lattices $\preccurlyeq_v$ and
-  $\preccurlyeq_w$. \ This is achieved by enforcing that $\preccurlyeq_{v_l}
+  $\preccurlyeq_w$.  This is achieved by enforcing that $\preccurlyeq_{v_l}
   \assign \preccurlyeq_{v_r} \assign \preccurlyeq_v$. As before, we have that
@@
 
-  We next strengthen (6$\preccurlyeq$) to a biconditional. \ Define
+  We next strengthen (6$\preccurlyeq$) to a biconditional.  Define
   $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
@@
   $\mathbbm{M}''$ is bisimular to $\mathbbm{M}'$ by the same mechanism as the
-  previous construction. \ The important feature of this structure is to
+  previous construction.  The important feature of this structure is to
   observe that the converse of (6$\preccurlyeq$) holds:
@@
   (6$\preccurlyeq$b) so that they hold for all terms in $\tau (\Pi)$, rather
-  than being restricted to $\Xi$. \ To this end define $\mathbbm{M}' \assign
+  than being restricted to $\Xi$.  To this end define $\mathbbm{M}' \assign
   \langle W', V', R', \mathcal{A}', \preccurlyeq' \rangle$ where $W'$, $R'$
@@
 Montague in the early 1970s as a generalization of Kripke semantics \
-{\cite{montague_universal_2008,scott_advice_1970}}. \ In
+{\cite{montague_universal_2008,scott_advice_1970}}.  In
 {\cite{fagin_belief_1988}}, Halpern and Fagin adapted neighborhood semantics
-for reasoning about epistemic agents without logical omniscience. \ In this
+for reasoning about epistemic agents without logical omniscience.  In this
 section will demonstrate how these semantics may be modified so that
 neighborhoods corresponds to the logical consequences of a different knowledge
-bases. \ This allows for using logics with neighborhood semantics for
-reasoning about multiple knowledge bases. \ A point of distinction of
+bases.  This allows for using logics with neighborhood semantics for
+reasoning about multiple knowledge bases.  A point of distinction of
 neighborhood semantics from JL is that it may be possible that two distinct
@@
 Just as previous semantics, ``$\Box \phi$'' is intended to mean that the agent
-has an argument for $\phi$ from some knowledge base. \ A novelty we present
+has an argument for $\phi$ from some knowledge base.  A novelty we present
 here is that ``$K \phi$'' means that the agent has an argument for $\phi$ from
@@
   belief; more work is necessary to find a model based on this one which
-  conforms to the semantics in Definition \ref{neighborhoodmodels}. \ For now,
+  conforms to the semantics in Definition \ref{neighborhoodmodels}.  For now,
   assume that $K$ is just another modality governed by the neighborhoods in
-  $\mathcal{K}_w$. \ In both neighborhood functions, our idea is that the
+  $\mathcal{K}_w$.  In both neighborhood functions, our idea is that the
   neighborhoods of $w$ in are supersets $S \supseteq \left\llbracket \phi
@@
   There are steps of the inductive proof of the Truth Lemma for this structure
-  which are not obvious nor obviously documented elsewhere. \ Assume
+  which are not obvious nor obviously documented elsewhere.  Assume
   $\mathbbm{M}, w \vDash \Box \chi$, where the Truth Lemma has been proven to
-  hold for $\chi$; we must show $\Box \chi \in w$. \ By our assumption there
+  hold for $\chi$; we must show $\Box \chi \in w$.  By our assumption there
   is some $\phi$ and $S$ where $\Box \phi \in w$ and $S \supseteq \{v \in W
-  \hspace{1em} | \hspace{1em} \phi \in v\}$. \ We argue that $\vdash \phi
+  \hspace{1em} | \hspace{1em} \phi \in v\}$.  We argue that $\vdash \phi
   \rightarrow \chi$; for if not then by the finitary Lindenbaum lemma there is
-  some $u \in W$ where $\phi \in u$ and $\chi \nin u$. \ Hence $u \in S$ and
-  $\mathbbm{M}, u \nvDash \chi$, a contradiction. \ Since $\vdash \phi
+  some $u \in W$ where $\phi \in u$ and $\chi \nin u$.  Hence $u \in S$ and
+  $\mathbbm{M}, u \nvDash \chi$, a contradiction.  Since $\vdash \phi
   \rightarrow \chi$ then we know that $\vdash \Box \phi \rightarrow \Box \chi$
@@
   By the Lindenbaum Lemma we have that there is some $w \in W$ where
-  $\mathbbm{M}, w \nvDash \psi$. \ $\mathbbm{M}$ makes true a number of
+  $\mathbbm{M}, w \nvDash \psi$.  $\mathbbm{M}$ makes true a number of
   properties:
@@
   move to a model where property (3) is strengthened to (3$'$): for all $S \in
-  \mathcal{N}_w$, $w \in S$ if and only if $S \in \mathcal{K}'_w$. \ We defer
+  \mathcal{N}_w$, $w \in S$ if and only if $S \in \mathcal{K}'_w$.  We defer
   the reader to {\cite{hansen_bisimulation_2007,pauly_bisimulation_1999}} for
-  details regarding bisimulation in neighborhood semantics. \ Define
+  details regarding bisimulation in neighborhood semantics.  Define
   $\mathbbm{M}' \assign \langle W', V', \mathcal{K}', \mathcal{N}',
@@
   \begin{itemizedot}
-    \item $W' \assign W \uplus W$ where \ $l, r$ its associated canonical
+    \item $W' \assign W \uplus W$ wher.  $l, r$ its associated canonical
     injections and $\theta (v_l) \assign \theta (v_r) \assign v$ is a
@@
   W\}$, it is straightforward to verify that $Z$ is a neighborhood
-  bisimulation. \ Hence $\mathbbm{M}, w_l \nvDash \psi$. \ Along with (3$'$),
-  this model makes true (1), (2), (4). \ In fact, in light of ($3'$), we can
+  bisimulation.  Hence $\mathbbm{M}, w_l \nvDash \psi$.  Along with (3$'$),
+  this model makes true (1), (2), (4).  In fact, in light of ($3'$), we can
   see that this model does not need $\mathcal{K}'$, and conforms to the
@@
   $\psi$ and define an injection $\iota : W' \hookrightarrow \Phi \backslash
-  \Lambda$, assigning a nominal to every world in $\mathbbm{M}'$. \ Define
+  \Lambda$, assigning a nominal to every world in $\mathbbm{M}'$.  Define
   $\mathbbm{M}'' \assign \langle W'', V'', \mathcal{N}'', \mathcal{A}''
@@
     \item For all words $v$ and all $X \in \mathcal{A}_v''$, $X$ is finite and
-    \ $X = \partial_v S$ for some $S \in \mathcal{N}_v''$
+  .  $X = \partial_v S$ for some $S \in \mathcal{N}_v''$
 
@@
 It is not too hard to identify the fragment of this logic that governs
-knowledge alone. \ The fragment given in Table \ref{logic4} has special
+knowledge alone.  The fragment given in Table \ref{logic4} has special
 significance to us, since it governs the notion of knowledge presented in
@@
 basic modal logic $K$, which means that its decision problem is
-\tmtextsf{PSPACE} hard (a lower bound). \ Our finitary completeness proof
+\tmtextsf{PSPACE} hard (a lower bound).  Our finitary completeness proof
 establishes that its complexity is in \tmtextsf{EXP2-TIME} (an upper bound).
@@
 however, it may be desirable for some philosophers to model knowledge about
-imaginary lands. \ After all, many children ``know'' a lot about Tolkien's
+imaginary lands.  After all, many children ``know'' a lot about Tolkien's
 {\tmem{middle earth}} or Rowling's {\tmem{Hogwarts}} (the school Harry Potter
@@
 
-\begin{thebibliography}{10}
-  \bibitem[1]{artemov\_logic\_1994}S.~N Artemov. {\newblock}Logic of proofs.
-  {\newblock}\tmtextit{Annals of Pure and Applied Logic}, 67(1):29--60, 1994.
-
-  \bibitem[2]{artemov\_introducing\_2005}S.~N Artemov and E.~Nogina.
-  {\newblock}Introducing justification into epistemic logic.
-  {\newblock}\tmtextit{Journal of Logic and Computation}, 15(6):1059, 2005.
-
-  \bibitem[3]{basu\_revealed\_1980}Kaushik Basu. {\newblock}\tmtextit{Revealed
-  preference of government}. {\newblock}Cambridge University Press, Cambridge;
-  New York, 1980.
-
-  \bibitem[4]{blackburn\_modal\_2001}P.~Blackburn, M.~De Rijke, and Y.~Venema.
-  {\newblock}\tmtextit{Modal logic}. {\newblock}Cambridge Univ Pr, 2001.
-
-  \bibitem[5]{boolos\_logic\_1995}George Boolos. {\newblock}\tmtextit{The
-  logic of provability}. {\newblock}Cambridge University Press, 1995.
-
-  \bibitem[6]{bull\_approach\_1970}R.~A. Bull. {\newblock}An approach to tense
-  logic. {\newblock}\tmtextit{Theoria}, 36(3):282--300, December 1970.
-
-  \bibitem[7]{davidson\_could\_1995}Donald Davidson. {\newblock}Could there be
-  a science of rationality? {\newblock}\tmtextit{International Journal of
-  Philosophical Studies}, 3(1):1--16, 1995.
-
-  \bibitem[8]{fagin\_belief\_1988}R.~Fagin and J.~Y Halpern.
-  {\newblock}Belief, awareness, and limited reasoning.
-  {\newblock}\tmtextit{Artificial Intelligence}, 34(1):39--76, 1988.
-
-  \bibitem[9]{fitting\_logic\_2005}M.~Fitting. {\newblock}The logic of proofs,
-  semantically. {\newblock}\tmtextit{Annals of Pure and Applied Logic},
-  132(1):1--25, 2005.
-
-  \bibitem[10]{halpern\_set-theoretic\_1999}Joseph~Y. Halpern.
-  {\newblock}Set-theoretic completeness for epistemic and conditional logic.
-  {\newblock}\tmtextit{Annals of Mathematics and Artificial Intelligence},
-  26(1-4):1--27, 1999.
-
-  \bibitem[11]{hansen\_bisimulation\_2007}Helle~Hvid Hansen, Clemens Kupke,
-  and Eric Pacuit. {\newblock}Bisimulation for neighbourhood structures.
-  {\newblock}In \tmtextit{Proceedings of the 2nd international conference on
-  Algebra and coalgebra in computer science}, pages 279--293, Bergen, Norway,
-  2007. Springer-Verlag.
-
-  \bibitem[12]{hendricks\_mainstream\_2006}V.~F Hendricks.
-  {\newblock}\tmtextit{Mainstream and formal epistemology}.
-  {\newblock}Cambridge Univ Pr, 2006.
-
-  \bibitem[13]{kornblith\_beyond\_1980}Hilary Kornblith. {\newblock}Beyond
-  foundationalism and the coherence theory. {\newblock}\tmtextit{The Journal
-  of Philosophy}, 77(10):597--612, October 1980.
-
-  \bibitem[14]{montague\_universal\_2008}Richard Montague.
-  {\newblock}Universal grammar. {\newblock}\tmtextit{Theoria}, 36(3):373--398,
-  2008.
-
-  \bibitem[15]{pauly\_bisimulation\_1999}M.~Pauly. {\newblock}Bisimulation for
-  general non-normal modal logic. {\newblock}\tmtextit{Manuscript}, 1999.
-
-  \bibitem[16]{prior\_revised\_1969}Arthur~N. Prior.
-  {\newblock}\tmtextit{Revised and Expanded Edition of Arthur N. Prior: Papers
-  on Time and Tense}. {\newblock}Oxford University Press, 1969.
-  {\newblock}reprinted in 2003.
-
-  \bibitem[17]{rubinstein\_modeling\_1998}Ariel Rubinstein.
-  {\newblock}\tmtextit{Modeling Bounded Rationality}. {\newblock}MIT Press,
-  1998.
-
-  \bibitem[18]{scott\_advice\_1970}D.~Scott. {\newblock}Advice on modal logic.
-  {\newblock}\tmtextit{Philosophical problems in Logic}, 143:74, 1970.
-
-  \bibitem[19]{sen\_behaviour\_1973}Amartya Sen. {\newblock}Behaviour and the
-  concept of preference. {\newblock}\tmtextit{Economica}, 40(159):241--259,
-  August 1973.
-
-  \bibitem[20]{wampler-doty\_evidentialist\_2010}Matthew Wampler-Doty.
-  {\newblock}Evidentialist logic. {\newblock}MSc thesis, Universiteit van
-  Amsterdam, Amsterdam, North-Holland, September 2010.
-\end{thebibliography}
+\bibliographystyle{plain}
+\bibliography{zotero}
 

### 2010-12-15 awareness.tex
Refactored paper so all sections are seperate documents

--- 2010-12-15 paper.tex
@@
-\documentclass{article}
-\usepackage{geometry,amsmath,amssymb,wasysym,enumerate,bbm,color}
-\geometry{letterpaper}
-
-\usepackage{stmaryrd}
-
-%%%%%%%%%% Start TeXmacs macros
-\newcommand{\assign}{:=}
-\newcommand{\nin}{\not\in}
-\newcommand{\tmem}[1]{{\em #1\/}}
-\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
-\newcommand{\tmstrong}[1]{\textbf{#1}}
-\newcommand{\tmtextbf}[1]{{\bfseries{#1}}}
-\newcommand{\tmtextit}[1]{{\itshape{#1}}}
-\newcommand{\tmtextsf}[1]{{\sffamily{#1}}}
-\newcommand{\tmtextup}[1]{{\upshape{#1}}}
-\newenvironment{descriptioncompact}{\begin{description} }{\end{description}}
-\newenvironment{descriptiondash}{\begin{description} }{\end{description}}
-\newenvironment{enumeratenumeric}{\begin{enumerate}[1.] }{\end{enumerate}}
-\newenvironment{enumerateroman}{\begin{enumerate}[i.] }{\end{enumerate}}
-\newenvironment{itemizedot}{\begin{itemize} \renewcommand{\labelitemi}{$\bullet$}\renewcommand{\labelitemii}{$\bullet$}\renewcommand{\labelitemiii}{$\bullet$}\renewcommand{\labelitemiv}{$\bullet$}}{\end{itemize}}
-\newenvironment{proof}{\noindent\textbf{Proof\ }}{\hspace*{\fill}$\Box$\medskip}
-\definecolor{grey}{rgb}{0.75,0.75,0.75}
-\definecolor{orange}{rgb}{1.0,0.5,0.5}
-\definecolor{brown}{rgb}{0.5,0.25,0.0}
-\definecolor{pink}{rgb}{1.0,0.5,0.5}
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}{Proposition}
-\newtheorem{theorem}{Theorem}
-%%%%%%%%%% End TeXmacs macros
-
-\begin{document}
-
-\title{Epistemic Logics For Knowledge Bases}\author{Matthew P.
-Wampler-Doty}\maketitle
-
-\begin{abstract}
-  In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem
-  proposed a research program for logic of \tmtextit{explicit knowledge}. \
-  Two efforts have since emerged with proposals for logic of explicit
-  knowledge: the \tmtextit{Dynamics of Awareness}
-  {\cite{van_benthem_inference_2009}} and \tmtextit{Justification Logic}
-  {\cite{artemov_introducing_2005}}.  The purpose of this paper is to
-  repurpose various epistemic logics from these previous efforts for reasoning
-  about logical closures over knowledge bases.  The results in this paper are
-  based on previous work carried out in
-  {\cite{wampler-doty_evidentialist_2010}}.
-\end{abstract}
-
-\section{Introduction\label{intro}}
-
-The modern tradition in epistemic logic is to assume knowledge modalities
-conform to the $S 5$ axiom schema.  As noted in
-{\cite{halpern_set-theoretic_1999,rubinstein_modeling_1998}}, the semantics of
-$S 5$ knowledge correspond exactly to partitioning a collection of situations
-into \tmtextit{information sets}, which is the traditional approach in game
-theory and decision theory.  While it is not commonly acknowledged in
-epistemic logic, economists and philosophers accept that traditional decision
-theory is externalist and behaviourist in nature
-(FIXME)
-\footnote{An early essay by
-Amartya Sen on the philosophical foundations of traditional decision theory
-makes the behaviorist reading of decision theory clear
-\cite{sen_behaviour_1973}.  Kaushik Basu also discusses the behaviorist
-nature of decision theory {\cite[pgs. 53--54]{basu_revealed_1980}}. 
-Finally, Donald Davidson appeals to decision theory to motivate an externalist
-epistemology in \cite{davidson_could_1995}.}.
-
-In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem proposed
-a research program to find logics for explicit knowledge, providing the first
-suggestion of an internalist perspective on epistemic logic.  Subsequently,
-Sergei Artemov and Elena Nogina proposed a logic of explicit justification,
-which has come to be known as \tmtextit{Justification Logic} (JL)
-{\cite{artemov_introducing_2005}}, based on Artemov's \tmtextit{Logic of
-Proofs} {\cite{artemov_logic_1994}}.  While the original semantics of JL was
-interpretability into Peano Arithmetic, Melvin Fitting proposed Kripke
-semantics for JL in {\cite{fitting_logic_2005}}.  Recently, Fernando
-Vel\'azquez-Quesada and Johan van Benthem have developed a simpler framework
-for explicit epistemics in {\cite{van_benthem_inference_2009}}, entitled the
-\tmtextit{Dynamics of Awareness}.  This work was based on Joseph Halpern and
-Ronald Fagin's original \tmtextit{Awareness Logic} {\cite{fagin_belief_1987}}.
-
-In this essay we repurpose various externalist logics to take on an
-internalist reading.  The concept of a \tmtextit{knowledge base}, from which
-beliefs may be implicitly deduced, will play a crucial role in our discussion.
-\ We propose this as an avenue for representing foundationalist perspectives
-on epistemology in epistemic logic.  Our philosophical motivation is taken
-from two sources.  The first is Vincent Hendricks in
-{\cite{hendricks_mainstream_2006}}, where he characterizes the principal of
-{\tmem{logical omniscience}} for implicit knowledge in epistemic
-logic{\footnote{We have modified Hendricks' notation here slightly to match
-our own.}}:
-
-\begin{quote}
-  {\tmem{Whenever an agent $\Xi$ knows all of the formulae in $\mathcal{A}$,
-  and $\phi$ follows logically from $\mathcal{A}$, then $\Xi$ [implicitly]
-  knows $\phi$.}}
-\end{quote}
-
-We will design our semantics such that ``$\Box \phi$'' may be equated with
-``$\phi$ follows logically from a knowledge base $\mathcal{A}$,'' which is
-sometimes written as $\phi \in \tmop{Cn} ( \mathcal{A})$ in the artificial
-intelligence literature.  Our second inspiration comes from what Hilary
-Kornblith calls the \tmtextit{the arguments on paper thesis}
-{\cite{kornblith_beyond_1980}}, which he feels characterizes apsychological,
-internalist theories of knowledge:
-
-\begin{quote}
-  Let us suppose that, for any person, it is possible, at least in principle,
-  to list all of the propositions that person believes.  The
-  arguments-on-paper thesis is just the view that a person has a justified
-  belief that a particular proposition is true just in case that proposition
-  appears on the list of propositions that person believes, and either it
-  requires no argument, or a {\tmem{good argument}} can be given for it which
-  takes as premises certain other propositions on the list.
-\end{quote}
-
-Kornblith asserts that foundationalism and coherentism vie for accounts of a
-``good argument'' in the above thesis.  He provides an extensive bibliography
-citing proposals for this principle by a number of 20th century
-epistemologists, including figures such as A.J. Ayer and C.I. Lewis.  The
-rest of Kornblith's paper is devoted to attacking this view and proposing a
-form of naturalized epistemology; we will not address this debate here,
-however.
-
-We adopt a arguments-on-paper-thesis perspective on epistemic logic in this
-paper.  We consider a \tmtextit{good argument} to be a logical derivation
-from propositions present in a knowledge base.  In this fashion, ou.  \
-Special attention will be given to \tmtextit{sound derivations}, which will be
-thought of as a form of knowledge.  In Awareness Logic, we will interpret
-awareness of a formula as membership in a knowledge base.  We prove
-completeness for basic awareness logic and a hybrid logic extension.  Logics
-of multiple knowledge bases are also presented: a simplified form of
-Justification Logic, a logic with neighborhood semantics, an a logic with
-modalities for quantifying over knowledge bases.  We conclude with an
-application to naturalized epistemology found in the psychological literature.
-
-\section{Basic Explicit Logics of Knowledge Bases}
-
-\subsection{Awareness Logic\label{awarenesslogic}}
-
 In this section, we give the explicit semantics to basic awareness logic,
 originally presented in {\cite{fagin_belief_1987}}, with an additional axiom.
-\ One difference in our presentation is the inclusion of a novel letter and a
+ One difference in our presentation is the inclusion of a novel letter and a
 superficial change in notation.  This work is inspired by the developments in
@@
 
-\subsection{Hybrid Awareness Logic}
-
-The method of the above completeness proof makes implicit use of concepts from
-hybrid logic{\footnote{Hybrid logic was first presented in
-{\cite{prior_revised_1969}} and later formally developed in
-{\cite{bull_approach_1970}}.}}.  In this section we adapt hybrid logic and
-show that it is a complete for reasoning about knowledge bases.  We note that
-because of the increased expressive power of hybrid logic, our completeness
-theorem is simpler.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
-  language $\mathcal{L}_H (\Phi, \Psi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} i \in \Psi \hspace{1em} | \hspace{1em} \bot \hspace{1em} |
-     \hspace{1em} \phi \rightarrow \psi \hspace{1em} | \hspace{1em} \Box \phi
-     \hspace{1em} | \hspace{1em} A : \phi \hspace{1em} | \hspace{1em} \forall
-     \phi \]
-\end{definition}
-
-Our approach in hybrid logic is to employ a universal modality along with
-nominals.  This framework presents a logic where the agent may reason about
-various labeled scenarios.  Scenarios may be multiply labeled or not labeled
-at all.  From these intuitions we have the following definition:
-
-\begin{definition}
-  \label{hybridsemantics}Let a \tmtextbf{hybrid model} $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A}, \ell \rangle$ be an awareness model as in Definition
-  \ref{awarenessmodels}, along with a partial labeling function $\ell : \Psi
-  \nrightarrow W$
-
-  The semantics for $\vDash$ are the same as in Definition
-  \ref{awarenessmodels}, only we have
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \forall \phi & \text{iff} & \forall v \in
-    W.\mathbbm{M}, v \vDash \phi\\
-    \mathbbm{M}, w \vDash i & \text{iff} & \ell (i) = w
-  \end{eqnarray*}
-\end{definition}
-
-The other connectives and operators are defined as usual, although we employ a
-few special shorthands:
-
-\begin{definition}
-  We employ the following special abbreviations:
-  \begin{eqnarray}
-    \text{\tmtextup{@}}_i \phi \assign \forall (i \rightarrow \phi)
-    \hspace{2em} & \exists \phi \assign \neg \forall \neg \phi \hspace{3em} &
-    \circlearrowleft_i \assign \diamondsuit i \nonumber
-  \end{eqnarray}
-\end{definition}
-
-This gives rise to a validity reflecting one of the axioms we saw in
-{\S}\ref{awarenesslogic}:
-\[ \vDash \circlearrowleft_i \rightarrow \Box \phi \rightarrow
-   \text{\tmtextup{@}}_i \phi \]
-This can be read as ``If the agent's knowledge base is sound at world $i$,
-then if they can deduce something from their knowledge base, what they deduce
-must be true at world $i$.'.  In a way, this may be considered as
-{\tmem{relativising}} knowledge particular named situations.
-
-The semantics in Definition \ref{hybridsemantics} obviates the \tmtextbf{SND}
-principle we previously presented, since there is no explicit
-$\circlearrowleft$ symbol in this setting. \tmtextbf{CSQ} still makes sense
-without modification, however.  The following gives a logic for hybrid models
-making true \tmtextbf{CSQ}:
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & $\vdash \forall (\phi
-    \rightarrow \psi) \rightarrow \forall \phi \rightarrow \forall \psi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & $\vdash \forall
-    \phi \rightarrow \phi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & $\vdash \forall \phi \rightarrow
-    \forall \forall \phi$\\
-    $\vdash \Box(\phi \rightarrow \psi) \rightarrow \Box \phi \rightarrow \Box
-    \psi$ & $\vdash \exists \phi \rightarrow \forall \exists \phi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$ & $\vdash \forall \phi \rightarrow
-    \Box \phi$\\
-    & $\vdash i \rightarrow \phi \rightarrow \text{\tmtextup{@}}_i \phi$\\
-    & \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi}{\vdash \Box \phi}$ &
-      {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \forall \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic2}Hybrid Awareness Logic for \tmtextbf{CSQ}}
-\end{table}
-
-\begin{theorem}
-  \label{completeness2}Assuming an infinite store of nominals $\Psi$, the
-  hybrid awareness logic presented is sound and weakly complete for all hybrid
-  models making true \tmtextbf{CSQ}.
-\end{theorem}
-
-\begin{proof}
-  As before, soundness is trivial.  Completeness is based on a modification
-  of techniques found in {\cite[chapter 5]{boolos_logic_1995}}.  Assume
-  that $\nvdash \psi$ and let $\Sigma_0$ be the set of subformulae of $\psi$,
-  and let $\Upsilon$ be the set of nominals occuring in $\psi$.  Define:
-
-  \begin{align*}
-    {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{{\forall}{\phi}{\hspace{1em}}|{\hspace{1em}}\Box{\phi}{\in}{\Sigma}_0\}\\
-    {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{\text{@}_i{\phi}{\hspace{1em}},i{\rightarrow}{\phi}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1{\hspace{1em}}\&{\hspace{1em}}i{\in}{\Upsilon}\}\\
-    {\Sigma}_3 &
-    {\assign}{\Sigma}_2{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_2\}
-  \end{align*}
-
-  It is easy to see that $\Sigma_3$ is finite and closed under subformulae and
-  single negations. Let $\mathbbm{M}= \langle W, V, R_{\Box}, \sim_{\forall},
-  \mathcal{A} \rangle$ be the finite cannonical model formed of maximally
-  consistent subsets of $\Sigma_3$, where everything is defined as usual,
-  except $\sim_{\forall}$, which obeys the following specification:
-
-  \begin{align*}
-    w {\sim}_{{\forall}}v & {\Longleftrightarrow}(({\forall}{\phi}){\in}w
-    {\Longleftrightarrow}({\forall}{\phi}){\in}v)
-  \end{align*}
-
-  This model makes true the following properties:
-  \begin{enumerateroman}
-    \item $\sim_{\forall}$ is an equivalence relation
-
-    \item $R_{\Box} \subseteq \sim_{\forall}$
-
-    \item In each equivalence class specified by $\sim_{\forall}$, there is at
-    most one world making true $i$ for all $i \in \Upsilon$
-  \end{enumerateroman}
-  As in our previous construction we have that there is some world $w$ where
-  $\mathbbm{M}, w \nvDash \psi$.  Let $\mathbbm{M}^1 = \langle W', V',
-  R_{\Box}', \sim_{\forall}', \mathcal{A}' \rangle$ be the submodel generated
-  by $\{w\}$; we have that $\mathbbm{M}', w \nvDash \psi$ (see {\cite[chapter
-  2.1]{blackburn_modal_2001}} for details on generated submodels).  In this
-  model $\forall$ is a universal modality and either $\left\llbracket i
-  \right\rrbracket^{\mathbbm{M}'} = \varnothing$ or $\left\llbracket i
-  \right\rrbracket^{\mathbbm{M}'} =\{v\}${\footnote{As per the usual
-  convention, here $\left\llbracket \phi \right\rrbracket^{\mathbbm{M}}$
-  denotes $\{w \in W \hspace{1em} | \hspace{1em} \mathbbm{M}, w \vDash
-  \phi\}$.  We will drop $\mathbbm{M}$ where it is unambiguous.}}. Since the
-  store $\Psi$ of nominals is infinite and $\Upsilon$ is finite, we have that
-  $\Psi \backslash \Upsilon$ is infinite, so there is some injection $\iota :
-  W' \hookrightarrow \Psi \backslash \Upsilon$ which assigns a fresh nominal
-  to every world.  Let $\mathbbm{M}'' = \langle W'', V'', R'', \mathcal{A}'',
-  \ell \rangle$, where:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign V' (p)$\\
-      $\bullet$ & $R'' \assign R'_{\Box}$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}'' (v) \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
-      \mathcal{A}' (v)\} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
-      \neg v R' u\}$\\
-      \begin{tabular}{ll}
-        $\bullet$ & $\ell (i) \assign \left\{ \begin{array}{ll}
-          w & i \in \Upsilon \hspace{1em} \& \hspace{1em} \mathbbm{M}, w
-          \vDash i\\
-          \iota^{- 1} (i) & i \in \iota [W]\\
-          \text{undefined} & \text{o/w}
-        \end{array} \right.$
-      \end{tabular} & $R'' \assign R'_{\Box}$ &  &  & 
-    \end{tabular}
-  \end{center}
-
-  The the worlds is $\mathbbm{M}'$ and $\mathbbm{M}''$ agree on all
-  subformulae of $\psi$, hence $\mathbbm{M}'', w \nvDash \psi$. The same
-  reasoning as in the proof of Theorem \ref{completeness1} establishes and
-  that the logic in Table \ref{logic2} itself is sound for $\mathbbm{M}''$ and
-  makes true \tmtextbf{CSQ}, establishing completeness.
-\end{proof}
-
-\section{Logics of Multiple Knowledge Bases}
-
-So far, we have only dealt with systems that reason over a single knowledge
-base.  In this section, we present various logics for reasoning over multiple
-knowledge bases.
-
-\subsection{Simple Justification Logic}
-
-Justification Logic (JL) was originally developed by Artemov as the
-\tmtextit{Logic of Proofs} (LP) {\cite{artemov_logic_1994}}.  Its original
-purpose was to provide a framework for reasoning about explicit provability in
-Peano Arithmetic.  The first introduction of Justification Logic can be found
-in {\cite{artemov_introducing_2005}}, where Artemov and Nogina propose LP as a
-logic for reasoning about evidence.  In {\cite{fitting_logic_2005}}, Melvin
-Fitting provided JL with Kripke model based semantics.
-
-The principle innovation of LP/JL is to extend awareness logic, such that
-awareness operations are now \tmtextit{proof terms}.  Informally, we say that
-``a proof term $X$ witnesses proposition $\phi$'', denoted ``$X : \phi$'',
-whenever $X$ represents a proof of $\phi$.  Proofs may have
-{\tmstrong{multiple-conclusions}} in this system, so it is possible that $X :
-\phi$ and $X : \psi$ can be true where $\phi \neq \psi$.  In Fitting's Kripke
-semantics, $X : \phi$ means that $\phi$ is in awareness set corresponding to
-$X$.  Proof terms are thought be operating in a \tmtextit{multi-conclusion}
-proof system, so the same proof term may witness many different propositions.
-
-The logics LP/JL include operators over proofs terms, so that new proof terms
-may be assembled.  One operation of particular interest to us is
-{\tmem{choice}}, denoted $\oplus$.  The expression ``$X \oplus Y : \phi$''
-denotes that either $X$ or $Y$ are proofs witnessing $\phi$.  There are other
-operations which correspond to \tmtextit{modus ponens} and
-\tmtextit{proof-theoretic reflection}, however we do not consider these
-operations here.
-
-In this section we consider a simplified form of JL suitable for reasoning
-over multiple knowledge bases, which we call \tmtextit{simple justification
-logic} (SJL). However, instead of thinking of terms as representing proofs, we
-use them to represent knowledge bases. This is in the spirit of JL as a logic
-of evidence: we consider each knowledge base to be a corpus of evidence. \
-Each term ``names'' a different knowledge base at a particular world.  Terms
-may not refer to the same knowledge base at different worlds, just as in how
-in awareness logic the agent need not be aware of the same formulae at
-different worlds.  Finally, we will make use of JL's {\tmem{choice}} operator
-as a mechanism for forming the union of knowledge bases, creating new ones.
-
-\begin{definition}
-  Let $\Pi$ be a set of primitive terms.  Define $\tau (\Pi)$ with the
-  following grammar:
-  \[ X \hspace{1em} : : = \hspace{1em} t \in \Pi \hspace{1em} | \hspace{1em} X
-     \oplus Y \]
-
-  Let $\Phi$ be a set of letters and $\Pi$ a set of primitive terms, and
-  define the language $\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi \]
-  where $X \in \tau (\Pi)$
-\end{definition}
-
-\begin{definition}
-  \label{justmodels}A {\tmstrong{simple justification model}} $\mathbbm{M}=
-  \langle W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V
-  : \Phi \cup \{\circlearrowleft_X \hspace{1em} | \hspace{1em} X \in \tau
-  (\Pi)\} \rightarrow 2^W$, an indexed relation $R : \tau (\Pi) \rightarrow
-  2^{W \times W}$, along with a modified awareness function $\mathcal{A} : W
-  \times \tau (\Pi) \rightarrow 2^{\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)}$. \
-  In practice we will denote $\mathcal{A} (w, X)$ by a curried shorthand,
-  namely $\mathcal{A}_w (X)$.
-
-  The semantics for $\vDash$ have the following modifications:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box_X \phi & \text{iff} & \text{for all $v \in W$
-    where $w R_X v$ we have $\mathbbm{M}, v \vDash v$}\\
-    \mathbbm{M}, w \vDash X : \phi & \text{iff} & \phi \in \mathcal{A}_w (X)
-  \end{eqnarray*}
-\end{definition}
-
-\begin{definition}
-  The following defines properties a simple justification model may make true:
-
-  \begin{descriptiondash}
-    \item[JCSQ] $\mathbbm{M}, w \vDash \Box_X \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w (X) \vdash \phi$
-
-    \item[JSND] $\mathbbm{M}, w \vDash \circlearrowleft_X \text{ iff
-    $\mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w (X)$}$
-
-    \item[CHOICE] $\mathcal{A}_w (X \oplus Y) = \mathcal{A}_w (X) \cup
-    \mathcal{A}_w (Y)$
-  \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
-\end{definition}
-
-The above semantics are similar to the ones given in previous sections. \
-\tmtextbf{JCSQ} is the same as \tmtextbf{CSQ} from {\S}\ref{awarenesslogic},
-only it is relativized to a knowledge base denoted by $X$ at $w$.  The
-awareness logic of knowledge bases is special case of simple justification
-logic where there is only one term.
-
-Simplified justification logic is given in Table \ref{logic5}.  We assert
-without proof that this is a conservative extension of the awareness logic in
-{\S}\ref{awarenesslogic}.
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
-    \Box_X \psi$ & \\
-    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash (X \oplus Y : \phi) \rightarrow X : \phi$ & $\vdash (X \oplus Y :
-    \phi) \rightarrow Y : \phi$\\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_X$ &
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_Y$\\
-    $\vdash \Box_X \phi \rightarrow \Box_{X \oplus Y} \phi$ & \\
-    $\vdash \Box_{X \oplus X} \phi \rightarrow \Box_X \phi$ & $\vdash \Box_{(X
-    \oplus X) \oplus Y} \phi \rightarrow \Box_{X \oplus Y} \phi$ \\
-    $\vdash \Box_{X \oplus Y} \phi \rightarrow \Box_{Y \oplus X} \phi$ &
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{(Y \oplus X)
-    \oplus Z} \phi$\\
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{X \oplus (Y
-    \oplus Z)} \phi$ & \\
-    & \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic5}Simple Justification Logic}
-\end{table}
-
-\begin{theorem}
-  \label{completeness5}Assuming an infinite store of proposition letters
-  $\Phi$, SJL is sound and weakly complete for simple justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND} and \tmtextbf{CHOICE}
-\end{theorem}
-
-\begin{proof}
-  As in the previous proofs, we only show completeness.  Assume that $\nvdash
-  \psi$.  Let $\Xi \subseteq \tau (\Pi)$ be all of the subterms occurring in
-  $\psi$; we assume that $\Xi$ is non-empty, since otherwise we may obtain the
-  theorem via the usual completeness theorem for classical propositional
-  logic. Let $\Sigma_0$ be the subformulae of $\psi$.  Define:
-
-  \begin{align*}
-    {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{\Box_Y{\phi}{\hspace{1em}}|{\hspace{1em}}\Box_X{\phi}{\in}{\Sigma}_0{\hspace{1em}}\&{\hspace{1em}}Y{\in}{\Xi}\}\\
-    {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1\}
-  \end{align*}
-
-  As in the proof of Theorem \ref{completeness2}, it is simple to verify that
-  $\Sigma_2$ is closed under subformulae and single negations.  Let
-  $\mathbbm{M} \assign \langle W, V, R, \mathcal{A} \rangle$ be the finite
-  cannonical model formed of maximally consistent subsets of $\Sigma_2$, where
-  $V$ and $\mathcal{A}$ are defined as usual, and $R : \Xi \rightarrow 2^{W
-  \times W}$ is defined by:
-  \[ w R_X v \Longleftrightarrow \{\phi \hspace{1em} | \hspace{1em} \Box_X
-     \phi \in w\} \subseteq v \]
-  As in previous constructions we may prove the usual Lindenbaum and Truth
-  Lemmas an use them obtain a world $w \in W$ where $\mathbbm{M}, w \nvDash
-  \psi$.
-
-  Next, define an operator $\twonotes : \tau (\Pi) \rightarrow 2^{\Pi}$ where:
-  \[ \twonotes (X) \assign \{t \in \Pi \hspace{1em} | \hspace{1em} t \text{
-     occurs in } X\} \]
-  In other words, $\twonotes (X)$ is the set of atomic terms in $X$.  As in
-  our construction for Theorem \ref{completeness1}, $\mathbbm{M}$ makes true
-  certain properties, along with some new properties:
-  \begin{enumeratenumeric}
-    \item \label{fin}$W$ and $\mathcal{A}_v (X)$ are finite, and $\phi \in
-    \mathcal{A}_v (X)$ only if $\phi \in \Sigma_2$
-
-    \item if $\mathbbm{M}, v \vDash X : \phi$ then $\mathbbm{M}, v \vDash
-    \Box_X \phi$
-
-    \item \label{refl}if $\mathbbm{M}, v \vDash \circlearrowleft_X$ then $v
-    R_X v$
-
-    \item \label{sndness}For all $X \oplus Y \in \Xi$, $\mathbbm{M}, v \vDash
-    \circlearrowleft_{X \oplus Y}$ if and only if $\mathbbm{M}, v \vDash
-    \circlearrowleft_X$ and $\mathbbm{M}, v \vDash \circlearrowleft_Y$
-
-    \item \label{union}For all $X \oplus Y \in \Xi$, $\mathcal{A}_v (X \oplus
-    Y) = \mathcal{A}_v (X) \cup \mathcal{A}_v (Y)$
-
-    \item \label{sub}For all $X, Y \in \Xi$, if $\twonotes (X) \subseteq
-    \twonotes (Y)$ then $R_Y \subseteq R_X$
-  \end{enumeratenumeric}
-  As in our previous constructions, it is necessary to refine this model using
-  bisimulations to achieve properties which are not modally definable.  In
-  particular, we shall strengthen (\ref{refl}) to a biconditional and
-  (\ref{sub}) to:
-
-  \begin{center}
-    \begin{tabular}{ll}
-      \tmtextbf{6$'$.} & For all $X, Y \in \Xi$, $R_{X \oplus Y} = R_X \cap
-      R_Y$
-    \end{tabular}
-  \end{center}
-
-  We first strengthen (\ref{refl}) by constructing $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}' \rangle$, just as in Theorem
-  \ref{completeness1}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $R'_X \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v
-    R_X u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em}
-    \mathbbm{M}, v \vDash \circlearrowleft_X \}$
-
-    \item $\mathcal{A}' (v_l, X) \assign \mathcal{A}' (v_r, X) \assign
-    \mathcal{A} (v, X)$
-  \end{itemizedot}
-  The same bisimulation relation $Z$ previously given suffices.
-
-  We next make a strengthened the model where (\ref{sub}$'$) holds.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that{\footnote{Let $\{i_X \hspace{1em} | \hspace{1em} X \in \Xi\}$ be the
-  family of canonical injections into the coproduct $\uplus_{\Xi} W$. As per
-  our previous convention, we use $v_X$ as shorthand for $i_X (v)$.}}:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em}
-    \twonotes (X) \subseteq \twonotes (Z)\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  Note that this construction makes use of the assumption that $\Xi$ is
-  non-empty.  Let $Z \assign \{(v, v_X) \hspace{1em} | \hspace{1em} X \in \Xi
-  \hspace{1em} \& \hspace{1em} v \in W' \}$; it is straightforward to prove
-  that $Z$ is a bisimulation between $\mathbbm{M}'$ and $\mathbbm{M}''$, for
-  all relations corresponding to terms $X \in \Xi$. Hence $\mathbbm{M}'', w_X
-  \nvDash \psi$ for some $w_X \in W''$.  In addition, $\mathbbm{M}''$
-  inherits (\ref{fin}) through (\ref{sub}) from $\mathbbm{M}'$, as well as the
-  converse of (\ref{refl}).  Next observe, forall $X \oplus Y \in \Xi$:
-  \begin{eqnarray*}
-    \text{$(v_V, u_Z) \in R''_X \cap R''_Y$} & \Longleftrightarrow & \exists Z
-    \in \Xi . \text{$v R'_Z u \hspace{1em} \& \hspace{1em} \twonotes (X)
-    \subseteq \twonotes (Z) \hspace{1em} \& \hspace{1em} \twonotes (Y)
-    \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X) \cup \twonotes (Y) \subseteq \twonotes
-    (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X \oplus Y) \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow &  \text{$(v_V, u_Z) \in R''_{X \oplus Y}$}
-  \end{eqnarray*}
-  We now turn to our final construction. As in previous constructions, let
-  $\iota : W'' \hookrightarrow \Phi \backslash \Psi$ be an injection assigning
-  fresh nominals to worlds.  Define $\mathbbm{M}''' \assign \langle W''',
-  V''', R''', \mathcal{A}''' \rangle$ just as in the final construction in the
-  proof of Theorem \ref{completeness1}, except that $R'''_X$ and
-  $\mathcal{A}_v''' (X)$ are defined inductively as follows:
-
-  \begin{center}
-    \begin{tabular}{lll}
-      $\bullet$ & $R'''_t \assign \left\{ \begin{array}{ll}
-        R''_t & t \in \Xi\\
-        W''' \times W''' & o / w
-      \end{array} \right.$ & \\
-      $\bullet$ & $R'''_{X \oplus Y} \assign R'''_X \cap R'''_Y$ & \\
-      &  & \\
-      $\bullet$ & $\mathcal{A}'''_v (t) \assign \{\phi \hspace{1em} | \phi \in
-      \mathcal{A}''_v \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
-      \neg v R'''_t u\}$ & where $t \in \Pi$\\
-      $\bullet$ & $\mathcal{A}'''_v (X \oplus Y) \assign \mathcal{A}'''_v (X)
-      \cup \mathcal{A}'''_v (Y)$ & 
-    \end{tabular}
-  \end{center}
-
-  Induction over complexity of subformulae $\phi$ of $\psi$ yields
-  $\mathbbm{M}'', w \vDash \phi \Longleftrightarrow \mathbbm{M}''', w \vDash
-  \phi$, so we know that there is some world $w \in W'''$ such that
-  $\mathbbm{M}''', w \nvDash \psi$.  All that is left is to illustrate that
-  $\mathbbm{M}'''$ has the properties we desire.
-
-  First note that by definition, $\mathbbm{M}'''$ makes true
-  \tmtextbf{CHOICE}.  Next, an induction argument on the complexity of a
-  terms $X$, making essential use of (\ref{sub}$'$), yields:
-  \[ u R_X''' v \Longleftrightarrow \mathbbm{M}''', v \vDash \bigwedge
-     \mathcal{A}'''_v (X) \]
-  With this, $\mathbbm{M}'''$ makes true \tmtextbf{JSND} since it inherits
-  (\ref{refl}).  Finally, we note that we may repeat our previous arguments
-  from Theorem \ref{completeness1} to prove \tmtextbf{JCSQ}.
-\end{proof}
-
-\subsection{Lattice Justification Logic}
-
-{\color{red} NOTE.  THIS SECTION HAS SOME SERIOUS PROBLEMS AND IT'S PROBABLY
-WRONG...}
-
-Implicit in our previous presentation of SJL.  $\oplus$ behaves like a union
-operation for knowledge bases, and dually like an intersection operation on
-accessibility relations.  It is natural to think of $\oplus$ as a join/meet
-operator over a {\tmem{semi-lattice}}.  In this section we make this
-explicit, by increasing the expressive power of simple JL to express the order
-theory inherent in knowledge bases.  We call the novel logic presented in
-this section \tmtextit{Lattice Justification Logic} (LJL){\footnote{We note
-that ``Semi-Lattice Justification Logic'' may be a more appropriate name,
-however we have decided to shorten semic-lattice to lattice in this article
-for purposes of concision.}}.  Lattice JL may be considered a novel logic for
-studying the dynamics of \tmtextit{theory change}, where the logic employed by
-the changing theories could be LJL itself.
-
-\begin{definition}
-  $\mathcal{L}_{\tmop{LJL}} (\Phi, \Pi)$ extends $\mathcal{L}_{\tmop{SJL}}
-  (\Phi, \Pi)$ to:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi
-     \hspace{1em} | \hspace{1em} X \sqsubseteq Y \]
-  where $X, Y \in \tau (\Pi)$
-\end{definition}
-
-\begin{definition}
-  \label{justmodels}A {\tmstrong{lattice justification model}} $\mathbbm{M}=
-  \langle W, V, R, \mathcal{A}, \preccurlyeq \rangle$ is a simple
-  justification model with a new relation $\preccurlyeq : W \rightarrow
-  2^{\tau (\Pi) \times \tau (\Pi)}$ between terms, indexed by worlds.  The
-  semantics of $\sqsubseteq$ correspond to $\preccurlyeq$ as follows:
-  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow X
-     \preccurlyeq_w Y \]
-\end{definition}
-
-\begin{definition}
-  A lattices justification model is said to make true \tmtextbf{LATTICE} if
-  and only if:
-  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow \mathcal{A}_w
-     (X) \subseteq \mathcal{A}_w (Y) \]
-\end{definition}
-
-Table \ref{logic6} lists the axioms for the logic of lattice justification
-models with the properties we have been investigating:
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
-    \Box_X \psi$ & \\
-    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash X \sqsubseteq Y \rightarrow (X : \phi) \rightarrow Y : \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_X$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow \Box_X \phi \rightarrow \Box_Y \phi$ &
-    \\
-    $\vdash X \sqsubseteq X$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow Y \sqsubseteq Z \rightarrow X
-    \sqsubseteq Z$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow X \sqsubseteq Z \oplus Y$ & $\vdash X
-    \sqsubseteq Y \rightarrow X \sqsubseteq Y \oplus Z$\\
-    $\vdash X \sqsubseteq Z \rightarrow Y \sqsubseteq Z \rightarrow X \oplus Y
-    \sqsubseteq Z$ & \\
-    & \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic6}Lattice Justification Logic}
-\end{table}
-
-\begin{theorem}
-  \label{completeness6}Assuming an infinite store of proposition letters
-  $\Phi$, LJL is sound and weakly complete for lattice justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND}, \tmtextbf{CHOICE} and
-  \tmtextbf{LATTICE}
-\end{theorem}
-
-\begin{proof}
-  Assume $\nvdash \psi$.  Let $\mathbbm{M} \assign \langle W, V, R,
-  \mathcal{A}, \preccurlyeq \rangle$ be the same as the finitary canonical
-  model we initially constructed in Theorem \ref{completeness5}, only
-  $\preccurlyeq$ is defined as:
-  \[ X \preccurlyeq_w Y \Longleftrightarrow w \vdash X \sqsubseteq Y \]
-  We may deduce that there is a world $w \in W$ such that $\mathbbm{M}, w
-  \nvDash \psi$.  This canonical model makes true properties (\ref{fin})
-  through (\ref{union}) we listed in Theorem \ref{completeness5}, as well as a
-  certain new properties:
-
-  \begin{descriptioncompact}
-    \item[6$\preccurlyeq$] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$
-    then $R_Y [v] \subseteq R_X [v]$
-
-    \item[7] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$ then
-    $\mathcal{A}_v (X) \subseteq \mathcal{A}_v (Y)$
-
-    \item[8] If $X \nin \Xi$, then $R_X = W \times W$ and $\mathcal{A}_v (X) =
-    \varnothing$ for all $v \in W$
-
-    \item[9] $\langle \preccurlyeq_v, \oplus \rangle$ is a join-semilattice
-    over $\tau (\Pi)$ for all $v \in W$
-  \end{descriptioncompact}
-
-  As in previous constructions, completeness is achieved by through a series
-  of model refinements.  Note that property 8 has been implicitly true in all
-  of our previous constructions, although we have not been interested in
-  enforcing it to be inherited by model refinements previously.
-
-  We first construct a model $\mathbbm{M}'$ which is bisimular to
-  $\mathbbm{M}$, where (\ref{refl}) is strengthened to a biconditional.  This
-  is done exactly as we proceeded in previous constructions. We note that the
-  notion of ``bisimulation'' here includes that two bisimular worlds $v$ and
-  $u$ must have isomorphic semi-lattices $\preccurlyeq_v$ and
-  $\preccurlyeq_w$.  This is achieved by enforcing that $\preccurlyeq_{v_l}
-  \assign \preccurlyeq_{v_r} \assign \preccurlyeq_v$. As before, we have that
-  $\mathbbm{M}', w \nvDash \psi$ for some world $w \in W'$.
-
-  We next strengthen (6$\preccurlyeq$) to a biconditional.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em} X
-    \preccurlyeq_v Z\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  $\mathbbm{M}''$ is bisimular to $\mathbbm{M}'$ by the same mechanism as the
-  previous construction.  The important feature of this structure is to
-  observe that the converse of (6$\preccurlyeq$) holds:
-  \begin{eqnarray*}
-    R_Y [v] \subseteq R_X [v] & \Longleftrightarrow & \forall Z \in \Xi
-    \forall u_Z \in W'' (v_Q R'_Z u_Z \Longrightarrow v_Q R_X' u_Z)\\
-    & \Longleftrightarrow & \forall Z \in \Xi \forall u_Z \in W'' (v R'_Z
-    \Longrightarrow v_Q R_X u_Z)
-  \end{eqnarray*}
-
-  Our first transformation strengthens (\ref{union}), (6$\preccurlyeq$a) and
-  (6$\preccurlyeq$b) so that they hold for all terms in $\tau (\Pi)$, rather
-  than being restricted to $\Xi$.  To this end define $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}', \preccurlyeq' \rangle$ where $W'$, $R'$
-  and $\preccurlyeq'$ are the same as in $\mathbbm{M}$, but $R'$ and
-  $\mathcal{A}'$ have the following modifications:
-  \begin{eqnarray}
-    R'_Y [v] & \assign & \bigcap_{X \preccurlyeq_v Y} R_X [v] \nonumber\\
-    \mathcal{A}'_v (Y) & \assign & \bigcup_{X \preccurlyeq_v Y} \mathcal{A}'_v
-    (X) \nonumber
-  \end{eqnarray}
-
-\end{proof}
-
-\subsection{Neighborhood Semantics}
-
-Neighborhood semantics were originally developed by Dana Scott and Richard
-Montague in the early 1970s as a generalization of Kripke semantics \
-{\cite{montague_universal_2008,scott_advice_1970}}.  In
-{\cite{fagin_belief_1988}}, Halpern and Fagin adapted neighborhood semantics
-for reasoning about epistemic agents without logical omniscience.  In this
-section will demonstrate how these semantics may be modified so that
-neighborhoods corresponds to the logical consequences of a different knowledge
-bases.  This allows for using logics with neighborhood semantics for
-reasoning about multiple knowledge bases.  A point of distinction of
-neighborhood semantics from JL is that it may be possible that two distinct
-knowledge bases cannot be merged by the agent.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
-  language $\mathcal{L}_N (\Phi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \bot \hspace{1em} | \hspace{1em} \phi \rightarrow \psi
-     \hspace{1em} | \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A :
-     \phi \hspace{1em} | \hspace{1em} K \phi \]
-\end{definition}
-
-Just as previous semantics, ``$\Box \phi$'' is intended to mean that the agent
-has an argument for $\phi$ from some knowledge base.  A novelty we present
-here is that ``$K \phi$'' means that the agent has an argument for $\phi$ from
-some \tmtextit{sound} knowledge base.
-
-\begin{definition}
-  \label{neighborhoodmodels}A {\tmstrong{neighborhood model}} $\mathbbm{M}=
-  \langle W, V, \mathcal{N}, \mathcal{A} \rangle$ has a neighborhood function
-  $\mathcal{N} : W \rightarrow 2^{2^W}$ and a multi-awareness function
-  $\mathcal{A} : W \rightarrow 2^{2^{\mathcal{L}_N (\Phi)}}$
-
-  The semantics for $\vDash$ have the following modifications:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box \phi & \text{iff} & \text{there exists a $U \in
-    \mathcal{N}_w$ where $\mathbbm{M}, v \vDash \phi$ for all $v \in U$}\\
-    \mathbbm{M}, w \vDash K \phi & \text{iff} & \text{there exists a $U \in
-    \mathcal{N}_w$ where $w \in U$ and $\mathbbm{M}, v \vDash \phi$ for all $v
-    \in U$}\\
-    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \bigcup
-    \mathcal{A_w}
-  \end{eqnarray*}
-\end{definition}
-
-Here we modify our previous notion of \tmtextbf{CSQ} and \tmtextbf{SND} to
-match how our semantics are intended for reasoning over multiple bases:
-
-\begin{definition}
-  The following defines properties a neighborhood model may make true:
-
-  \begin{descriptiondash}
-    \item[NCSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff there exists a set
-    $X \in \mathcal{A}_w$ such that } \tmop{Th} (\mathbbm{M}) \cup X \vdash
-    \phi$
-
-    \item[NSND] $\mathbbm{M}, w \vDash K \phi \text{ iff there exists a set $X
-    \in \mathcal{A}_w$ such that $\mathbbm{M}, w \vDash X$ and } \tmop{Th}
-    (\mathbbm{M}) \cup X \vdash \phi$
-  \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
-\end{definition}
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash K \phi \rightarrow \Box \phi$\\
-    $\vdash K \phi \rightarrow \phi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$\\
-    \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi \rightarrow \psi}{\vdash \Box
-      \phi \rightarrow \Box \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi
-      \rightarrow \psi}{\vdash K \phi \rightarrow K \psi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic3}A Neighborhood Logic for \tmtextbf{NCSQ} and
-  {\tmstrong{NSND}}}
-\end{table}
-
-\begin{theorem}
-  Assuming an infinite store of letters $\Phi$, the logic in Table
-  \ref{logic3} is sound and weakly complete for neighborhood semantics making
-  true \tmtextbf{NCSQ} and \tmtextbf{NSND}.
-\end{theorem}
-
-\begin{proof}
-  Assume that $\nvdash \psi$, and define the finitary canonical model
-  $\mathbbm{M}= \langle W, V, \mathcal{K}, \mathcal{N}, \mathcal{A} \rangle$
-  where:
-  \begin{itemizedot}
-    \item $W \assign \text{the maximally consistent sets of subformulae of
-    $\psi$, closed under single negation}$
-
-    \item $V (p) \assign \{v \in W \hspace{1em} | \hspace{1em} p \in v\}$
-
-    \item $\mathcal{K}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
-    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
-    \hspace{1em} K \phi \in w\}$
-
-    \item $\mathcal{N}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
-    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
-    \hspace{1em} \Box \phi \in w\}$
-
-    \item $\mathcal{A}_w \assign \{\{\phi\} \hspace{1em} | \hspace{1em} A :
-    \phi \in w\}$
-  \end{itemizedot}
-  Note that in this model, there are neighborhoods for both knowledge and
-  belief; more work is necessary to find a model based on this one which
-  conforms to the semantics in Definition \ref{neighborhoodmodels}.  For now,
-  assume that $K$ is just another modality governed by the neighborhoods in
-  $\mathcal{K}_w$.  In both neighborhood functions, our idea is that the
-  neighborhoods of $w$ in are supersets $S \supseteq \left\llbracket \phi
-  \right\rrbracket$ where $\Box \phi \in w$ or $K \phi \in w$, respectively.
-
-  There are steps of the inductive proof of the Truth Lemma for this structure
-  which are not obvious nor obviously documented elsewhere.  Assume
-  $\mathbbm{M}, w \vDash \Box \chi$, where the Truth Lemma has been proven to
-  hold for $\chi$; we must show $\Box \chi \in w$.  By our assumption there
-  is some $\phi$ and $S$ where $\Box \phi \in w$ and $S \supseteq \{v \in W
-  \hspace{1em} | \hspace{1em} \phi \in v\}$.  We argue that $\vdash \phi
-  \rightarrow \chi$; for if not then by the finitary Lindenbaum lemma there is
-  some $u \in W$ where $\phi \in u$ and $\chi \nin u$.  Hence $u \in S$ and
-  $\mathbbm{M}, u \nvDash \chi$, a contradiction.  Since $\vdash \phi
-  \rightarrow \chi$ then we know that $\vdash \Box \phi \rightarrow \Box \chi$
-  by our rules, which means that $\Box \chi \in w$ by maximality.
-
-  By the Lindenbaum Lemma we have that there is some $w \in W$ where
-  $\mathbbm{M}, w \nvDash \psi$.  $\mathbbm{M}$ makes true a number of
-  properties:
-  \begin{enumeratenumeric}
-    \item $W$ and $\mathcal{A}_v$ are finite for all $v \in W$, and $\psi \in
-    \bigcup \mathcal{A_w}$ only if $\psi$ is a subformula of $\phi$
-
-    \item $\mathcal{K}_w \subseteq \mathcal{N}_w$
-
-    \item If $S \in \mathcal{K}_w$ then $w \in S$
-
-    \item $\mathbbm{M}, v \vDash A : \phi \rightarrow \Box \phi$ for all $v
-    \in W$
-
-    \item $\mathcal{N}_w$ and $\mathcal{K}_w$ are closed under supersets
-  \end{enumeratenumeric}
-
-  As in the proof of Theorem \ref{completeness1}, we use a bisimulation to
-  move to a model where property (3) is strengthened to (3$'$): for all $S \in
-  \mathcal{N}_w$, $w \in S$ if and only if $S \in \mathcal{K}'_w$.  We defer
-  the reader to {\cite{hansen_bisimulation_2007,pauly_bisimulation_1999}} for
-  details regarding bisimulation in neighborhood semantics.  Define
-  $\mathbbm{M}' \assign \langle W', V', \mathcal{K}', \mathcal{N}',
-  \mathcal{A}' \rangle$ such that:
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$ wher.  $l, r$ its associated canonical
-    injections and $\theta (v_l) \assign \theta (v_r) \assign v$ is a
-    left-inverse of $l, r$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $\mathcal{K}' (v_i) \assign \{S \hspace{1em} | \hspace{1em} v_i \in
-    S \hspace{1em} \& \hspace{1em} \theta [S] \in \mathcal{K_v} \}$ where $i =
-    l, r$
-
-    \item $\mathcal{N}' (v_i) \assign \mathcal{K}' (v_i) \cup \{S \hspace{1em}
-    | \hspace{1em} v_i \nin S \hspace{1em} \& \hspace{1em} \theta [S] \in
-    \mathcal{N_v} \}$ where $i = l, r$
-
-    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
-    (v)$
-  \end{itemizedot}
-
-  If we let $Z \assign \{(v, v_r), (v, v_l) \hspace{1em} | \hspace{1em} v \in
-  W\}$, it is straightforward to verify that $Z$ is a neighborhood
-  bisimulation.  Hence $\mathbbm{M}, w_l \nvDash \psi$.  Along with (3$'$),
-  this model makes true (1), (2), (4).  In fact, in light of ($3'$), we can
-  see that this model does not need $\mathcal{K}'$, and conforms to the
-  semantics in Definition \ref{neighborhoodmodels}.{\hspace*{\fill}}
-
-  As in previous proofs, let $\Lambda$ be the proposition letters occuring in
-  $\psi$ and define an injection $\iota : W' \hookrightarrow \Phi \backslash
-  \Lambda$, assigning a nominal to every world in $\mathbbm{M}'$.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', \mathcal{N}'', \mathcal{A}''
-  \rangle$ such that:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
-      \begin{array}{ll}
-        V' (p) & p \in \Lambda\\
-        \{v\} & p = i (v)\\
-        \varnothing & o / w
-      \end{array} \right.$\\
-      $\bullet$ & $\mathcal{N}''_w \assign \mathcal{N}'_w$ & {\hspace{3em}} &
-      $\bullet$ & $\mathcal{A}''_v \assign \{\partial_v S \hspace{1em} |
-      \hspace{1em} S \in \mathcal{N}'_w \}$
-    \end{tabular}
-  \end{center}
-
-  Where $\partial_v S \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
-  \bigcup \mathcal{A}_v', \text{$\phi$ is a subformula of $\psi$ and}
-  \hspace{1em} S \subseteq \left\llbracket \phi
-  \right\rrbracket^{\mathbbm{M}'} \} \cup \{\neg \iota (u) \hspace{1em} |
-  \hspace{1em} u \nin S\}$.
-
-  As before, this model agrees with $\mathbbm{M}'$ on all subformulae of
-  $\psi$, using the semantics in Definition \ref{neighborhoodmodels}, hence
-  $\mathbbm{M}'', w_l \nvDash \phi$. \
-
-  All that is left is to show \tmtextbf{NCSQ} and \tmtextbf{NSND} from three
-  new properties:
-  \begin{enumerateroman}
-    \item For all words $v$ and all $X \in \mathcal{A}_v''$, $X$ is finite and
-  .  $X = \partial_v S$ for some $S \in \mathcal{N}_v''$
-
-    \item For all $v$ and all $S \in \mathcal{N}_v$, $u \in S$ if and only if
-    $\mathbbm{M}'', u \vDash \bigwedge \partial_v S$
-
-    \item The logic presented in Table \ref{logic3} is sound for
-    $\mathbbm{M}''$
-  \end{enumerateroman}
-  Along with the deduction theorem for $\vdash$, these properties establish
-  \tmtextbf{NCSQ} for this model using the logic of Table \ref{logic3} itself:
-
-  \begin{align*}
-    \text{$\exists X \in \mathcal{A''_v} \text{ s.t. } \tmop{Th}
-    (\mathbbm{M}'') \cup X \vdash \phi$} & {\Longleftrightarrow}\text{$\exists
-    S \in \mathcal{N''_v} \text{ s.t. } \tmop{Th} (\mathbbm{M}'') \cup
-    \partial_v S \vdash \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \tmop{Th} (\mathbbm{M}'') \vdash \bigwedge \partial_v S \rightarrow
-    \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \bigwedge \partial_v S \rightarrow \phi \in \tmop{Th} (\mathbbm{M}'')$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \left\llbracket \bigwedge \partial_v S \right\rrbracket \subseteq
-    \left\llbracket \phi \right\rrbracket$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t.
-    $\forall u \in W$ if } \mathbbm{M}, u \vDash \bigwedge \partial_v S \text{
-    then } \mathbbm{M}, u \vDash \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \mathbbm{M}, u \vDash \phi \text{ for all } u \in S$}\\
-    & {\Longleftrightarrow}{\mathbbm{M}},v{\vDash}\Box{\phi}
-  \end{align*}
-
-  \tmtextbf{NSND} follows from \tmtextbf{NCSQ} and the semantics of Definition
-  \ref{neighborhoodmodels}.
-\end{proof}
-
-It is not too hard to identify the fragment of this logic that governs
-knowledge alone.  The fragment given in Table \ref{logic4} has special
-significance to us, since it governs the notion of knowledge presented in
-{\S}\ref{quantifying}.
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash K \phi \rightarrow \phi$\\
-    \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ &  &  & $\frac{\vdash \phi \rightarrow \psi}{\vdash K \phi
-      \rightarrow K \psi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic4}A knowledge-only neighborhood logic for
-  \tmtextbf{NCSQ} and {\tmstrong{NSND}}}
-\end{table}
-
-\begin{proposition}
-  The knowledge-only logic presented governs the $\Box$-free fragment of the
-  logic in Table \ref{logic3}
-\end{proposition}
-
-This concludes our analysis of knowledge bases using neighborhood semantics.
-
-\subsection{\label{quantifying}Using Modalities to Quantify over Knowledge
-Bases}
-
-\section{Conclusions \& Further Research}
-
-The logic presented in Table \ref{logic1} is a conservative extension of the
-basic modal logic $K$, which means that its decision problem is
-\tmtextsf{PSPACE} hard (a lower bound).  Our finitary completeness proof
-establishes that its complexity is in \tmtextsf{EXP2-TIME} (an upper bound).
-
-Worlds in epistemic logic might correspond to fantastic, pretend scenarios;
-however, it may be desirable for some philosophers to model knowledge about
-imaginary lands.  After all, many children ``know'' a lot about Tolkien's
-{\tmem{middle earth}} or Rowling's {\tmem{Hogwarts}} (the school Harry Potter
-attends).
-
-\bibliographystyle{plain}
-\bibliography{zotero}
-
-\end{document}
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "paper"
+%%% End:

### 2010-12-15 hybrid_awareness.tex
Refactored paper so all sections are seperate documents

--- 2010-12-15 paper.tex
@@
-\documentclass{article}
-\usepackage{geometry,amsmath,amssymb,wasysym,enumerate,bbm,color}
-\geometry{letterpaper}
-
-\usepackage{stmaryrd}
-
-%%%%%%%%%% Start TeXmacs macros
-\newcommand{\assign}{:=}
-\newcommand{\nin}{\not\in}
-\newcommand{\tmem}[1]{{\em #1\/}}
-\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
-\newcommand{\tmstrong}[1]{\textbf{#1}}
-\newcommand{\tmtextbf}[1]{{\bfseries{#1}}}
-\newcommand{\tmtextit}[1]{{\itshape{#1}}}
-\newcommand{\tmtextsf}[1]{{\sffamily{#1}}}
-\newcommand{\tmtextup}[1]{{\upshape{#1}}}
-\newenvironment{descriptioncompact}{\begin{description} }{\end{description}}
-\newenvironment{descriptiondash}{\begin{description} }{\end{description}}
-\newenvironment{enumeratenumeric}{\begin{enumerate}[1.] }{\end{enumerate}}
-\newenvironment{enumerateroman}{\begin{enumerate}[i.] }{\end{enumerate}}
-\newenvironment{itemizedot}{\begin{itemize} \renewcommand{\labelitemi}{$\bullet$}\renewcommand{\labelitemii}{$\bullet$}\renewcommand{\labelitemiii}{$\bullet$}\renewcommand{\labelitemiv}{$\bullet$}}{\end{itemize}}
-\newenvironment{proof}{\noindent\textbf{Proof\ }}{\hspace*{\fill}$\Box$\medskip}
-\definecolor{grey}{rgb}{0.75,0.75,0.75}
-\definecolor{orange}{rgb}{1.0,0.5,0.5}
-\definecolor{brown}{rgb}{0.5,0.25,0.0}
-\definecolor{pink}{rgb}{1.0,0.5,0.5}
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}{Proposition}
-\newtheorem{theorem}{Theorem}
-%%%%%%%%%% End TeXmacs macros
-
-\begin{document}
-
-\title{Epistemic Logics For Knowledge Bases}\author{Matthew P.
-Wampler-Doty}\maketitle
-
-\begin{abstract}
-  In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem
-  proposed a research program for logic of \tmtextit{explicit knowledge}. \
-  Two efforts have since emerged with proposals for logic of explicit
-  knowledge: the \tmtextit{Dynamics of Awareness}
-  {\cite{van_benthem_inference_2009}} and \tmtextit{Justification Logic}
-  {\cite{artemov_introducing_2005}}.  The purpose of this paper is to
-  repurpose various epistemic logics from these previous efforts for reasoning
-  about logical closures over knowledge bases.  The results in this paper are
-  based on previous work carried out in
-  {\cite{wampler-doty_evidentialist_2010}}.
-\end{abstract}
-
-\section{Introduction\label{intro}}
-
-The modern tradition in epistemic logic is to assume knowledge modalities
-conform to the $S 5$ axiom schema.  As noted in
-{\cite{halpern_set-theoretic_1999,rubinstein_modeling_1998}}, the semantics of
-$S 5$ knowledge correspond exactly to partitioning a collection of situations
-into \tmtextit{information sets}, which is the traditional approach in game
-theory and decision theory.  While it is not commonly acknowledged in
-epistemic logic, economists and philosophers accept that traditional decision
-theory is externalist and behaviourist in nature
-(FIXME)
-\footnote{An early essay by
-Amartya Sen on the philosophical foundations of traditional decision theory
-makes the behaviorist reading of decision theory clear
-\cite{sen_behaviour_1973}.  Kaushik Basu also discusses the behaviorist
-nature of decision theory {\cite[pgs. 53--54]{basu_revealed_1980}}. 
-Finally, Donald Davidson appeals to decision theory to motivate an externalist
-epistemology in \cite{davidson_could_1995}.}.
-
-In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem proposed
-a research program to find logics for explicit knowledge, providing the first
-suggestion of an internalist perspective on epistemic logic.  Subsequently,
-Sergei Artemov and Elena Nogina proposed a logic of explicit justification,
-which has come to be known as \tmtextit{Justification Logic} (JL)
-{\cite{artemov_introducing_2005}}, based on Artemov's \tmtextit{Logic of
-Proofs} {\cite{artemov_logic_1994}}.  While the original semantics of JL was
-interpretability into Peano Arithmetic, Melvin Fitting proposed Kripke
-semantics for JL in {\cite{fitting_logic_2005}}.  Recently, Fernando
-Vel\'azquez-Quesada and Johan van Benthem have developed a simpler framework
-for explicit epistemics in {\cite{van_benthem_inference_2009}}, entitled the
-\tmtextit{Dynamics of Awareness}.  This work was based on Joseph Halpern and
-Ronald Fagin's original \tmtextit{Awareness Logic} {\cite{fagin_belief_1987}}.
-
-In this essay we repurpose various externalist logics to take on an
-internalist reading.  The concept of a \tmtextit{knowledge base}, from which
-beliefs may be implicitly deduced, will play a crucial role in our discussion.
-\ We propose this as an avenue for representing foundationalist perspectives
-on epistemology in epistemic logic.  Our philosophical motivation is taken
-from two sources.  The first is Vincent Hendricks in
-{\cite{hendricks_mainstream_2006}}, where he characterizes the principal of
-{\tmem{logical omniscience}} for implicit knowledge in epistemic
-logic{\footnote{We have modified Hendricks' notation here slightly to match
-our own.}}:
-
-\begin{quote}
-  {\tmem{Whenever an agent $\Xi$ knows all of the formulae in $\mathcal{A}$,
-  and $\phi$ follows logically from $\mathcal{A}$, then $\Xi$ [implicitly]
-  knows $\phi$.}}
-\end{quote}
-
-We will design our semantics such that ``$\Box \phi$'' may be equated with
-``$\phi$ follows logically from a knowledge base $\mathcal{A}$,'' which is
-sometimes written as $\phi \in \tmop{Cn} ( \mathcal{A})$ in the artificial
-intelligence literature.  Our second inspiration comes from what Hilary
-Kornblith calls the \tmtextit{the arguments on paper thesis}
-{\cite{kornblith_beyond_1980}}, which he feels characterizes apsychological,
-internalist theories of knowledge:
-
-\begin{quote}
-  Let us suppose that, for any person, it is possible, at least in principle,
-  to list all of the propositions that person believes.  The
-  arguments-on-paper thesis is just the view that a person has a justified
-  belief that a particular proposition is true just in case that proposition
-  appears on the list of propositions that person believes, and either it
-  requires no argument, or a {\tmem{good argument}} can be given for it which
-  takes as premises certain other propositions on the list.
-\end{quote}
-
-Kornblith asserts that foundationalism and coherentism vie for accounts of a
-``good argument'' in the above thesis.  He provides an extensive bibliography
-citing proposals for this principle by a number of 20th century
-epistemologists, including figures such as A.J. Ayer and C.I. Lewis.  The
-rest of Kornblith's paper is devoted to attacking this view and proposing a
-form of naturalized epistemology; we will not address this debate here,
-however.
-
-We adopt a arguments-on-paper-thesis perspective on epistemic logic in this
-paper.  We consider a \tmtextit{good argument} to be a logical derivation
-from propositions present in a knowledge base.  In this fashion, ou.  \
-Special attention will be given to \tmtextit{sound derivations}, which will be
-thought of as a form of knowledge.  In Awareness Logic, we will interpret
-awareness of a formula as membership in a knowledge base.  We prove
-completeness for basic awareness logic and a hybrid logic extension.  Logics
-of multiple knowledge bases are also presented: a simplified form of
-Justification Logic, a logic with neighborhood semantics, an a logic with
-modalities for quantifying over knowledge bases.  We conclude with an
-application to naturalized epistemology found in the psychological literature.
-
-\section{Basic Explicit Logics of Knowledge Bases}
-
-\subsection{Awareness Logic\label{awarenesslogic}}
-
-In this section, we give the explicit semantics to basic awareness logic,
-originally presented in {\cite{fagin_belief_1987}}, with an additional axiom.
-\ One difference in our presentation is the inclusion of a novel letter and a
-superficial change in notation.  This work is inspired by the developments in
-van Benthem and Vel\'azquez-Quesada {\cite{van_benthem_inference_2009}}.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and define the language $\mathcal{L}_A
-  (\Phi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A : \phi \hspace{1em}
-  \]
-\end{definition}
-
-We define the other connectives and modal operators as usual for classical
-modal logics.
-
-\begin{definition}
-  \label{awarenessmodels}An {\tmstrong{awareness model}} $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V : \Phi
-  \cup \{\circlearrowleft\} \rightarrow 2^W$ and an awareness function
-  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$.  We will usually
-  denote $\mathcal{A} (w)$ as $\mathcal{A}_w$.
-
-  Define the semantic entailment relation $\vDash$ where atomic propositions,
-  logical connectives and modality are interpreted as usual.  We employ the
-  following novel definition:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \mathcal{A_w}
-  \end{eqnarray*}
-\end{definition}
-
-The following definition distinguishes us from previously investigations of
-awareness logic:
-
-\begin{definition}
-  Define the ``\tmtextbf{theory of a model} $\mathbbm{M}$'' as:
-  \[ \tmop{Th} (\mathbbm{M}) \assign \{\phi \hspace{1em} | \hspace{1em}
-     \mathbbm{M}, v \vDash \phi \text{ for all } v \in W\} \]
-  We define the following properties that a model $\mathbbm{M}$ may posses:
-
-  \begin{descriptiondash}
-    \item[CSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w \vdash \phi$
-
-    \item[SND] $\mathbbm{M}, w \vDash \circlearrowleft \text{ iff }
-    \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w$
-  \end{descriptiondash}
-
-  Here $\vdash$ is any logical consequence relation which is sound for
-  $\vDash$, making true \tmtextbf{modus ponens} and \tmtextbf{reflection} (ie,
-  $\Gamma \vdash \phi$ if $\phi \in \Gamma$)
-\end{definition}
-
-Neither \tmtextbf{CSQ} nor \tmtextbf{SND} correspond to simple modally
-definable properties.
-
-Intuitively, the \tmtextbf{CSQ} asserts that an agent believes a formula
-$\phi$ if and only if it follows logically from their knowledge base and their
-background knowledge, represented by $\tmop{Th} (\mathbbm{M})$. \
-\tmtextbf{CSQ} is Vincent Hendrik's principle of logical omniscience mentioned
-in {\S}\ref{intro}.
-
-\tmtextbf{SND} asserts that $\circlearrowleft$ corresponds to the agent's
-knowledge base being sound. A sound knowledge base will only render true
-conclusions when used in deductions.  If one considers ``the existance of a
-sound deduction'' sufficient for a kind of knowledge, then $\circlearrowleft$
-is suitable for investigating this notion of epistemology.  That is, if
-$\mathbbm{M}, w \vDash \circlearrowleft \wedge \Box \phi$, then we may
-naturally say that the agent (implicitly) {\tmem{knows}} $\phi$ on the basis
-of $\mathcal{A}_w$, rather than merely {\tmem{believing}} $\phi$ on the basis
-of $\mathcal{A}_w$.
-
-The logic of models making true \tmtextbf{CSQ} and \tmtextbf{SND} is provided
-in Table \ref{logic1}.
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash \Box(\phi \rightarrow \psi) \rightarrow \Box \phi \rightarrow \Box
-    \psi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$\\
-    $\vdash \circlearrowleft \rightarrow \Box \phi \rightarrow \phi$\\
-    \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box \phi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic1}Awareness Logic for \tmtextbf{CSQ} and
-  \tmtextbf{SND}}
-\end{table}
-
-\begin{theorem}
-  \label{completeness1}Assuming an infinite store of proposition letters
-  $\Phi$, the awareness logic presented is sound and weakly complete for
-  awareness models making true \tmtextbf{CSQ} and \tmtextbf{SND}.
-\end{theorem}
-
-\begin{proof}
-  Soundness is straightforward, so we will only address completeness.  Assume
-  $\nvdash \psi$.  Consider the finite canonical model $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A} \rangle$ formed of maximally consistent sets of
-  subformulae of $\phi$ (closed under single negations{\footnote{A discussion
-  of this property may be found in {\cite[pg.
-  243]{blackburn_modal_2001}}.}}), as per the finitary modal completeness
-  proofs found in {\cite[chapter 4.8]{blackburn_modal_2001}} and
-  {\cite[chapter 5]{boolos_logic_1995}}.  Typical presentations do not
-  include awareness, however it is defined intuitively in this case:
-  \[ \phi \in \mathcal{A}_w \Longleftrightarrow A : \phi \in w \]
-  Since $\psi$ is a subformula of itself, we have $\mathbbm{M}, w \nvDash
-  \psi$ for some world $w$ by a finitary {\tmem{Lindenbaum Lemma}} and
-  {\tmem{Truth Theorem}}.  Moreover, it is straightforward to verify that
-  $\mathbbm{M}$ makes true the following properties:
-  \begin{enumeratenumeric}
-    \item $W$ and $\mathcal{A}_v$ are finite, and $\psi \in \mathcal{A}_v$
-    only if $\psi$ is a (possibly negated) subformula of $\phi$
-
-    \item if $\mathbbm{M}, v \vDash A : \psi$ then $\mathbbm{M}, v \vDash \Box
-    \psi$
-
-    \item if $\mathbbm{M}, v \vDash \circlearrowleft$ then $v R v$
-  \end{enumeratenumeric}
-
-  We next produce a bisimular{\footnote{The notion of bisimulation is
-  discussed at length in {\cite[chapter 2.2]{blackburn_modal_2001}}.  We
-  note that the basic definition and all of the usual theorems (modal
-  equivalence, Henessy Milner, etc.) may be generalized to awareness models in
-  a straightforward fashion. }} model $\mathbbm{M}'$ which makes true (1), (2)
-  and a stronger from of (3):
-
-  {\hspace*{\fill}}\begin{tabular}{ll}
-    \tmtextbf{3$'$.} & $\mathbbm{M}', v \vDash \circlearrowleft$ iff $v R v$
-  \end{tabular}{\hspace*{\fill}}
-
-  To this end define $\mathbbm{M}' \assign \langle W', V', R', \mathcal{A}'
-  \rangle$ such that{\footnote{Throughout this article, we use $l$ and $r$ to
-  denote the two canonical injections associated with the coproduct $W \uplus
-  W$. We will use $v_l$ and $v_r$ as the shorthand for $l (v)$ and $r (v)$
-  respectively.}}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $R' \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v R
-    u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em} \mathbbm{M},
-    v \vDash \circlearrowleft\}$
-
-    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
-    (v)$
-  \end{itemizedot}
-
-  It is straightforward to verify that $\mathbbm{M}'$ makes true the desired
-  properties.  Let $Z \assign \{(v, v_l), (v, v_r) \hspace{1em} |
-  \hspace{1em} v \in W\}$.  then $Z$ is a bisimulation between $\mathbbm{M}$
-  and $\mathbbm{M}'$.  Therefore we know there is some $w \in W$ such that
-  $\mathbbm{M}', w_l \nvDash \psi$ and $\mathbbm{M}', w_r \nvDash \psi$.
-
-  Finally we construct a model $\mathbbm{M}''$ which agrees with
-  $\mathbbm{M}'$ for all subformulae of $\psi$, which makes true
-  \tmtextbf{CSQ} and \tmtextbf{SND}.  Let $\Lambda$ be the set of proposition
-  letters occuring in $\psi$.  We will make use members of $\Phi \backslash
-  \Lambda$ as {\tmem{nominals}}, as per the tradition in hybrid logic.  This
-  is possible since both $W'$ and $\Lambda$ are finite and $\Phi$ is infinite
-  by hypothesis.  Let $\iota : W \uplus W \hookrightarrow \Phi \backslash
-  \Lambda$ be an injection assigning a fresh nominal associated with each
-  world in $\mathbbm{M}'$.  Now define $\mathbbm{M}'' \assign \langle W'',
-  V'', R'', \mathcal{A}'' \rangle$, where:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
-      \begin{array}{ll}
-        V' (p) & p \in \Lambda\\
-        \{v\} & p = \iota (v)\\
-        \varnothing & o / w
-      \end{array} \right.$\\
-      $\bullet$ & $R'' \assign R'$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}''_v \assign \{\phi \hspace{1em} | \phi \in \mathcal{A}'_v
-      \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em} \neg v R' u\}$
-    \end{tabular}
-  \end{center}
-
-  By induction we have that for every subformula $\phi$ of $\psi$ that
-  $\mathbbm{M}', v \vDash \phi$ if and only if $\mathbbm{M}'', v \vDash \phi$,
-  hence $\mathbbm{M}'', w_l \nvDash \psi$.
-
-  All that is left to show is that $\mathbbm{M}''$ makes true \tmtextbf{CSQ}
-  and \tmtextbf{SND}.  $\mathbbm{M}''$ has three further properties:
-  \begin{enumerateroman}
-    \item $\mathcal{A}''_v$ is finite for all worlds $v$
-
-    \item  $v R' u$ if and only if $\mathbbm{M}'', u \vDash \bigwedge
-    \mathcal{A}'' (v)$
-
-    \item The logic presented in Table \ref{logic1} is sound for
-    $\mathbbm{M}''$
-  \end{enumerateroman}
-  From (ii) and the fact that $\mathbbm{M}'$ makes true (3$'$), we have
-  \tmtextbf{SND} for $\mathbbm{M}''$.
-
-  All that is left is to demonstrate \tmtextbf{CSQ} for some sound logic.  We
-  will use the logic in Table \ref{logic1} itself.  From (i), (ii), (iii),
-  and the \tmtextit{deduction theorem} for modal logic, we have the following
-  line of reasoning:
-
-  \begin{align*}
-    Th({\mathbbm{M}}''){\cup}\mathcal{A}''_v{\vdash}{\phi} &
-    {\Longleftrightarrow}Th({\mathbbm{M}}''){\vdash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\\
-    &
-    {\Longleftrightarrow}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}{\in}Th({\mathbbm{M}}'')\\
-    &
-    {\Longleftrightarrow}{\mathbbm{M}}'',u{\vDash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\text{
-    for all $u \in W''$}\\
-    & {\Longleftrightarrow}\text{ for all $u \in W''$, if
-    }{\mathbbm{M}}'',u{\vDash}\mathcal{A}''_v\text{ then
-    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
-    & {\Longleftrightarrow}\text{ for all $u \in W''$, if }v R 'u \text{ then
-    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
-    & {\Longleftrightarrow}{\mathbbm{M}}'',v{\models}\Box{\phi}
-  \end{align*}
-\end{proof}
-
-\subsection{Hybrid Awareness Logic}
-
-The method of the above completeness proof makes implicit use of concepts from
+The method of the previous completeness proof makes implicit use of concepts from
 hybrid logic{\footnote{Hybrid logic was first presented in
@@
 \end{proof}
-
-\section{Logics of Multiple Knowledge Bases}
-
-So far, we have only dealt with systems that reason over a single knowledge
-base.  In this section, we present various logics for reasoning over multiple
-knowledge bases.
-
-\subsection{Simple Justification Logic}
-
-Justification Logic (JL) was originally developed by Artemov as the
-\tmtextit{Logic of Proofs} (LP) {\cite{artemov_logic_1994}}.  Its original
-purpose was to provide a framework for reasoning about explicit provability in
-Peano Arithmetic.  The first introduction of Justification Logic can be found
-in {\cite{artemov_introducing_2005}}, where Artemov and Nogina propose LP as a
-logic for reasoning about evidence.  In {\cite{fitting_logic_2005}}, Melvin
-Fitting provided JL with Kripke model based semantics.
-
-The principle innovation of LP/JL is to extend awareness logic, such that
-awareness operations are now \tmtextit{proof terms}.  Informally, we say that
-``a proof term $X$ witnesses proposition $\phi$'', denoted ``$X : \phi$'',
-whenever $X$ represents a proof of $\phi$.  Proofs may have
-{\tmstrong{multiple-conclusions}} in this system, so it is possible that $X :
-\phi$ and $X : \psi$ can be true where $\phi \neq \psi$.  In Fitting's Kripke
-semantics, $X : \phi$ means that $\phi$ is in awareness set corresponding to
-$X$.  Proof terms are thought be operating in a \tmtextit{multi-conclusion}
-proof system, so the same proof term may witness many different propositions.
-
-The logics LP/JL include operators over proofs terms, so that new proof terms
-may be assembled.  One operation of particular interest to us is
-{\tmem{choice}}, denoted $\oplus$.  The expression ``$X \oplus Y : \phi$''
-denotes that either $X$ or $Y$ are proofs witnessing $\phi$.  There are other
-operations which correspond to \tmtextit{modus ponens} and
-\tmtextit{proof-theoretic reflection}, however we do not consider these
-operations here.
-
-In this section we consider a simplified form of JL suitable for reasoning
-over multiple knowledge bases, which we call \tmtextit{simple justification
-logic} (SJL). However, instead of thinking of terms as representing proofs, we
-use them to represent knowledge bases. This is in the spirit of JL as a logic
-of evidence: we consider each knowledge base to be a corpus of evidence. \
-Each term ``names'' a different knowledge base at a particular world.  Terms
-may not refer to the same knowledge base at different worlds, just as in how
-in awareness logic the agent need not be aware of the same formulae at
-different worlds.  Finally, we will make use of JL's {\tmem{choice}} operator
-as a mechanism for forming the union of knowledge bases, creating new ones.
-
-\begin{definition}
-  Let $\Pi$ be a set of primitive terms.  Define $\tau (\Pi)$ with the
-  following grammar:
-  \[ X \hspace{1em} : : = \hspace{1em} t \in \Pi \hspace{1em} | \hspace{1em} X
-     \oplus Y \]
-
-  Let $\Phi$ be a set of letters and $\Pi$ a set of primitive terms, and
-  define the language $\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi \]
-  where $X \in \tau (\Pi)$
-\end{definition}
-
-\begin{definition}
-  \label{justmodels}A {\tmstrong{simple justification model}} $\mathbbm{M}=
-  \langle W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V
-  : \Phi \cup \{\circlearrowleft_X \hspace{1em} | \hspace{1em} X \in \tau
-  (\Pi)\} \rightarrow 2^W$, an indexed relation $R : \tau (\Pi) \rightarrow
-  2^{W \times W}$, along with a modified awareness function $\mathcal{A} : W
-  \times \tau (\Pi) \rightarrow 2^{\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)}$. \
-  In practice we will denote $\mathcal{A} (w, X)$ by a curried shorthand,
-  namely $\mathcal{A}_w (X)$.
-
-  The semantics for $\vDash$ have the following modifications:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box_X \phi & \text{iff} & \text{for all $v \in W$
-    where $w R_X v$ we have $\mathbbm{M}, v \vDash v$}\\
-    \mathbbm{M}, w \vDash X : \phi & \text{iff} & \phi \in \mathcal{A}_w (X)
-  \end{eqnarray*}
-\end{definition}
-
-\begin{definition}
-  The following defines properties a simple justification model may make true:
-
-  \begin{descriptiondash}
-    \item[JCSQ] $\mathbbm{M}, w \vDash \Box_X \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w (X) \vdash \phi$
-
-    \item[JSND] $\mathbbm{M}, w \vDash \circlearrowleft_X \text{ iff
-    $\mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w (X)$}$
-
-    \item[CHOICE] $\mathcal{A}_w (X \oplus Y) = \mathcal{A}_w (X) \cup
-    \mathcal{A}_w (Y)$
-  \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
-\end{definition}
-
-The above semantics are similar to the ones given in previous sections. \
-\tmtextbf{JCSQ} is the same as \tmtextbf{CSQ} from {\S}\ref{awarenesslogic},
-only it is relativized to a knowledge base denoted by $X$ at $w$.  The
-awareness logic of knowledge bases is special case of simple justification
-logic where there is only one term.
-
-Simplified justification logic is given in Table \ref{logic5}.  We assert
-without proof that this is a conservative extension of the awareness logic in
-{\S}\ref{awarenesslogic}.
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
-    \Box_X \psi$ & \\
-    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash (X \oplus Y : \phi) \rightarrow X : \phi$ & $\vdash (X \oplus Y :
-    \phi) \rightarrow Y : \phi$\\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_X$ &
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_Y$\\
-    $\vdash \Box_X \phi \rightarrow \Box_{X \oplus Y} \phi$ & \\
-    $\vdash \Box_{X \oplus X} \phi \rightarrow \Box_X \phi$ & $\vdash \Box_{(X
-    \oplus X) \oplus Y} \phi \rightarrow \Box_{X \oplus Y} \phi$ \\
-    $\vdash \Box_{X \oplus Y} \phi \rightarrow \Box_{Y \oplus X} \phi$ &
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{(Y \oplus X)
-    \oplus Z} \phi$\\
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{X \oplus (Y
-    \oplus Z)} \phi$ & \\
-    & \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic5}Simple Justification Logic}
-\end{table}
-
-\begin{theorem}
-  \label{completeness5}Assuming an infinite store of proposition letters
-  $\Phi$, SJL is sound and weakly complete for simple justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND} and \tmtextbf{CHOICE}
-\end{theorem}
-
-\begin{proof}
-  As in the previous proofs, we only show completeness.  Assume that $\nvdash
-  \psi$.  Let $\Xi \subseteq \tau (\Pi)$ be all of the subterms occurring in
-  $\psi$; we assume that $\Xi$ is non-empty, since otherwise we may obtain the
-  theorem via the usual completeness theorem for classical propositional
-  logic. Let $\Sigma_0$ be the subformulae of $\psi$.  Define:
-
-  \begin{align*}
-    {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{\Box_Y{\phi}{\hspace{1em}}|{\hspace{1em}}\Box_X{\phi}{\in}{\Sigma}_0{\hspace{1em}}\&{\hspace{1em}}Y{\in}{\Xi}\}\\
-    {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1\}
-  \end{align*}
-
-  As in the proof of Theorem \ref{completeness2}, it is simple to verify that
-  $\Sigma_2$ is closed under subformulae and single negations.  Let
-  $\mathbbm{M} \assign \langle W, V, R, \mathcal{A} \rangle$ be the finite
-  cannonical model formed of maximally consistent subsets of $\Sigma_2$, where
-  $V$ and $\mathcal{A}$ are defined as usual, and $R : \Xi \rightarrow 2^{W
-  \times W}$ is defined by:
-  \[ w R_X v \Longleftrightarrow \{\phi \hspace{1em} | \hspace{1em} \Box_X
-     \phi \in w\} \subseteq v \]
-  As in previous constructions we may prove the usual Lindenbaum and Truth
-  Lemmas an use them obtain a world $w \in W$ where $\mathbbm{M}, w \nvDash
-  \psi$.
-
-  Next, define an operator $\twonotes : \tau (\Pi) \rightarrow 2^{\Pi}$ where:
-  \[ \twonotes (X) \assign \{t \in \Pi \hspace{1em} | \hspace{1em} t \text{
-     occurs in } X\} \]
-  In other words, $\twonotes (X)$ is the set of atomic terms in $X$.  As in
-  our construction for Theorem \ref{completeness1}, $\mathbbm{M}$ makes true
-  certain properties, along with some new properties:
-  \begin{enumeratenumeric}
-    \item \label{fin}$W$ and $\mathcal{A}_v (X)$ are finite, and $\phi \in
-    \mathcal{A}_v (X)$ only if $\phi \in \Sigma_2$
-
-    \item if $\mathbbm{M}, v \vDash X : \phi$ then $\mathbbm{M}, v \vDash
-    \Box_X \phi$
-
-    \item \label{refl}if $\mathbbm{M}, v \vDash \circlearrowleft_X$ then $v
-    R_X v$
-
-    \item \label{sndness}For all $X \oplus Y \in \Xi$, $\mathbbm{M}, v \vDash
-    \circlearrowleft_{X \oplus Y}$ if and only if $\mathbbm{M}, v \vDash
-    \circlearrowleft_X$ and $\mathbbm{M}, v \vDash \circlearrowleft_Y$
-
-    \item \label{union}For all $X \oplus Y \in \Xi$, $\mathcal{A}_v (X \oplus
-    Y) = \mathcal{A}_v (X) \cup \mathcal{A}_v (Y)$
-
-    \item \label{sub}For all $X, Y \in \Xi$, if $\twonotes (X) \subseteq
-    \twonotes (Y)$ then $R_Y \subseteq R_X$
-  \end{enumeratenumeric}
-  As in our previous constructions, it is necessary to refine this model using
-  bisimulations to achieve properties which are not modally definable.  In
-  particular, we shall strengthen (\ref{refl}) to a biconditional and
-  (\ref{sub}) to:
-
-  \begin{center}
-    \begin{tabular}{ll}
-      \tmtextbf{6$'$.} & For all $X, Y \in \Xi$, $R_{X \oplus Y} = R_X \cap
-      R_Y$
-    \end{tabular}
-  \end{center}
-
-  We first strengthen (\ref{refl}) by constructing $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}' \rangle$, just as in Theorem
-  \ref{completeness1}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $R'_X \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v
-    R_X u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em}
-    \mathbbm{M}, v \vDash \circlearrowleft_X \}$
-
-    \item $\mathcal{A}' (v_l, X) \assign \mathcal{A}' (v_r, X) \assign
-    \mathcal{A} (v, X)$
-  \end{itemizedot}
-  The same bisimulation relation $Z$ previously given suffices.
-
-  We next make a strengthened the model where (\ref{sub}$'$) holds.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that{\footnote{Let $\{i_X \hspace{1em} | \hspace{1em} X \in \Xi\}$ be the
-  family of canonical injections into the coproduct $\uplus_{\Xi} W$. As per
-  our previous convention, we use $v_X$ as shorthand for $i_X (v)$.}}:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em}
-    \twonotes (X) \subseteq \twonotes (Z)\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  Note that this construction makes use of the assumption that $\Xi$ is
-  non-empty.  Let $Z \assign \{(v, v_X) \hspace{1em} | \hspace{1em} X \in \Xi
-  \hspace{1em} \& \hspace{1em} v \in W' \}$; it is straightforward to prove
-  that $Z$ is a bisimulation between $\mathbbm{M}'$ and $\mathbbm{M}''$, for
-  all relations corresponding to terms $X \in \Xi$. Hence $\mathbbm{M}'', w_X
-  \nvDash \psi$ for some $w_X \in W''$.  In addition, $\mathbbm{M}''$
-  inherits (\ref{fin}) through (\ref{sub}) from $\mathbbm{M}'$, as well as the
-  converse of (\ref{refl}).  Next observe, forall $X \oplus Y \in \Xi$:
-  \begin{eqnarray*}
-    \text{$(v_V, u_Z) \in R''_X \cap R''_Y$} & \Longleftrightarrow & \exists Z
-    \in \Xi . \text{$v R'_Z u \hspace{1em} \& \hspace{1em} \twonotes (X)
-    \subseteq \twonotes (Z) \hspace{1em} \& \hspace{1em} \twonotes (Y)
-    \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X) \cup \twonotes (Y) \subseteq \twonotes
-    (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X \oplus Y) \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow &  \text{$(v_V, u_Z) \in R''_{X \oplus Y}$}
-  \end{eqnarray*}
-  We now turn to our final construction. As in previous constructions, let
-  $\iota : W'' \hookrightarrow \Phi \backslash \Psi$ be an injection assigning
-  fresh nominals to worlds.  Define $\mathbbm{M}''' \assign \langle W''',
-  V''', R''', \mathcal{A}''' \rangle$ just as in the final construction in the
-  proof of Theorem \ref{completeness1}, except that $R'''_X$ and
-  $\mathcal{A}_v''' (X)$ are defined inductively as follows:
-
-  \begin{center}
-    \begin{tabular}{lll}
-      $\bullet$ & $R'''_t \assign \left\{ \begin{array}{ll}
-        R''_t & t \in \Xi\\
-        W''' \times W''' & o / w
-      \end{array} \right.$ & \\
-      $\bullet$ & $R'''_{X \oplus Y} \assign R'''_X \cap R'''_Y$ & \\
-      &  & \\
-      $\bullet$ & $\mathcal{A}'''_v (t) \assign \{\phi \hspace{1em} | \phi \in
-      \mathcal{A}''_v \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
-      \neg v R'''_t u\}$ & where $t \in \Pi$\\
-      $\bullet$ & $\mathcal{A}'''_v (X \oplus Y) \assign \mathcal{A}'''_v (X)
-      \cup \mathcal{A}'''_v (Y)$ & 
-    \end{tabular}
-  \end{center}
-
-  Induction over complexity of subformulae $\phi$ of $\psi$ yields
-  $\mathbbm{M}'', w \vDash \phi \Longleftrightarrow \mathbbm{M}''', w \vDash
-  \phi$, so we know that there is some world $w \in W'''$ such that
-  $\mathbbm{M}''', w \nvDash \psi$.  All that is left is to illustrate that
-  $\mathbbm{M}'''$ has the properties we desire.
-
-  First note that by definition, $\mathbbm{M}'''$ makes true
-  \tmtextbf{CHOICE}.  Next, an induction argument on the complexity of a
-  terms $X$, making essential use of (\ref{sub}$'$), yields:
-  \[ u R_X''' v \Longleftrightarrow \mathbbm{M}''', v \vDash \bigwedge
-     \mathcal{A}'''_v (X) \]
-  With this, $\mathbbm{M}'''$ makes true \tmtextbf{JSND} since it inherits
-  (\ref{refl}).  Finally, we note that we may repeat our previous arguments
-  from Theorem \ref{completeness1} to prove \tmtextbf{JCSQ}.
-\end{proof}
-
-\subsection{Lattice Justification Logic}
-
-{\color{red} NOTE.  THIS SECTION HAS SOME SERIOUS PROBLEMS AND IT'S PROBABLY
-WRONG...}
-
-Implicit in our previous presentation of SJL.  $\oplus$ behaves like a union
-operation for knowledge bases, and dually like an intersection operation on
-accessibility relations.  It is natural to think of $\oplus$ as a join/meet
-operator over a {\tmem{semi-lattice}}.  In this section we make this
-explicit, by increasing the expressive power of simple JL to express the order
-theory inherent in knowledge bases.  We call the novel logic presented in
-this section \tmtextit{Lattice Justification Logic} (LJL){\footnote{We note
-that ``Semi-Lattice Justification Logic'' may be a more appropriate name,
-however we have decided to shorten semic-lattice to lattice in this article
-for purposes of concision.}}.  Lattice JL may be considered a novel logic for
-studying the dynamics of \tmtextit{theory change}, where the logic employed by
-the changing theories could be LJL itself.
-
-\begin{definition}
-  $\mathcal{L}_{\tmop{LJL}} (\Phi, \Pi)$ extends $\mathcal{L}_{\tmop{SJL}}
-  (\Phi, \Pi)$ to:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi
-     \hspace{1em} | \hspace{1em} X \sqsubseteq Y \]
-  where $X, Y \in \tau (\Pi)$
-\end{definition}
-
-\begin{definition}
-  \label{justmodels}A {\tmstrong{lattice justification model}} $\mathbbm{M}=
-  \langle W, V, R, \mathcal{A}, \preccurlyeq \rangle$ is a simple
-  justification model with a new relation $\preccurlyeq : W \rightarrow
-  2^{\tau (\Pi) \times \tau (\Pi)}$ between terms, indexed by worlds.  The
-  semantics of $\sqsubseteq$ correspond to $\preccurlyeq$ as follows:
-  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow X
-     \preccurlyeq_w Y \]
-\end{definition}
-
-\begin{definition}
-  A lattices justification model is said to make true \tmtextbf{LATTICE} if
-  and only if:
-  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow \mathcal{A}_w
-     (X) \subseteq \mathcal{A}_w (Y) \]
-\end{definition}
-
-Table \ref{logic6} lists the axioms for the logic of lattice justification
-models with the properties we have been investigating:
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
-    \Box_X \psi$ & \\
-    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash X \sqsubseteq Y \rightarrow (X : \phi) \rightarrow Y : \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_X$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow \Box_X \phi \rightarrow \Box_Y \phi$ &
-    \\
-    $\vdash X \sqsubseteq X$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow Y \sqsubseteq Z \rightarrow X
-    \sqsubseteq Z$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow X \sqsubseteq Z \oplus Y$ & $\vdash X
-    \sqsubseteq Y \rightarrow X \sqsubseteq Y \oplus Z$\\
-    $\vdash X \sqsubseteq Z \rightarrow Y \sqsubseteq Z \rightarrow X \oplus Y
-    \sqsubseteq Z$ & \\
-    & \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic6}Lattice Justification Logic}
-\end{table}
-
-\begin{theorem}
-  \label{completeness6}Assuming an infinite store of proposition letters
-  $\Phi$, LJL is sound and weakly complete for lattice justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND}, \tmtextbf{CHOICE} and
-  \tmtextbf{LATTICE}
-\end{theorem}
-
-\begin{proof}
-  Assume $\nvdash \psi$.  Let $\mathbbm{M} \assign \langle W, V, R,
-  \mathcal{A}, \preccurlyeq \rangle$ be the same as the finitary canonical
-  model we initially constructed in Theorem \ref{completeness5}, only
-  $\preccurlyeq$ is defined as:
-  \[ X \preccurlyeq_w Y \Longleftrightarrow w \vdash X \sqsubseteq Y \]
-  We may deduce that there is a world $w \in W$ such that $\mathbbm{M}, w
-  \nvDash \psi$.  This canonical model makes true properties (\ref{fin})
-  through (\ref{union}) we listed in Theorem \ref{completeness5}, as well as a
-  certain new properties:
-
-  \begin{descriptioncompact}
-    \item[6$\preccurlyeq$] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$
-    then $R_Y [v] \subseteq R_X [v]$
-
-    \item[7] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$ then
-    $\mathcal{A}_v (X) \subseteq \mathcal{A}_v (Y)$
-
-    \item[8] If $X \nin \Xi$, then $R_X = W \times W$ and $\mathcal{A}_v (X) =
-    \varnothing$ for all $v \in W$
-
-    \item[9] $\langle \preccurlyeq_v, \oplus \rangle$ is a join-semilattice
-    over $\tau (\Pi)$ for all $v \in W$
-  \end{descriptioncompact}
-
-  As in previous constructions, completeness is achieved by through a series
-  of model refinements.  Note that property 8 has been implicitly true in all
-  of our previous constructions, although we have not been interested in
-  enforcing it to be inherited by model refinements previously.
-
-  We first construct a model $\mathbbm{M}'$ which is bisimular to
-  $\mathbbm{M}$, where (\ref{refl}) is strengthened to a biconditional.  This
-  is done exactly as we proceeded in previous constructions. We note that the
-  notion of ``bisimulation'' here includes that two bisimular worlds $v$ and
-  $u$ must have isomorphic semi-lattices $\preccurlyeq_v$ and
-  $\preccurlyeq_w$.  This is achieved by enforcing that $\preccurlyeq_{v_l}
-  \assign \preccurlyeq_{v_r} \assign \preccurlyeq_v$. As before, we have that
-  $\mathbbm{M}', w \nvDash \psi$ for some world $w \in W'$.
-
-  We next strengthen (6$\preccurlyeq$) to a biconditional.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em} X
-    \preccurlyeq_v Z\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  $\mathbbm{M}''$ is bisimular to $\mathbbm{M}'$ by the same mechanism as the
-  previous construction.  The important feature of this structure is to
-  observe that the converse of (6$\preccurlyeq$) holds:
-  \begin{eqnarray*}
-    R_Y [v] \subseteq R_X [v] & \Longleftrightarrow & \forall Z \in \Xi
-    \forall u_Z \in W'' (v_Q R'_Z u_Z \Longrightarrow v_Q R_X' u_Z)\\
-    & \Longleftrightarrow & \forall Z \in \Xi \forall u_Z \in W'' (v R'_Z
-    \Longrightarrow v_Q R_X u_Z)
-  \end{eqnarray*}
-
-  Our first transformation strengthens (\ref{union}), (6$\preccurlyeq$a) and
-  (6$\preccurlyeq$b) so that they hold for all terms in $\tau (\Pi)$, rather
-  than being restricted to $\Xi$.  To this end define $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}', \preccurlyeq' \rangle$ where $W'$, $R'$
-  and $\preccurlyeq'$ are the same as in $\mathbbm{M}$, but $R'$ and
-  $\mathcal{A}'$ have the following modifications:
-  \begin{eqnarray}
-    R'_Y [v] & \assign & \bigcap_{X \preccurlyeq_v Y} R_X [v] \nonumber\\
-    \mathcal{A}'_v (Y) & \assign & \bigcup_{X \preccurlyeq_v Y} \mathcal{A}'_v
-    (X) \nonumber
-  \end{eqnarray}
-
-\end{proof}
-
-\subsection{Neighborhood Semantics}
-
-Neighborhood semantics were originally developed by Dana Scott and Richard
-Montague in the early 1970s as a generalization of Kripke semantics \
-{\cite{montague_universal_2008,scott_advice_1970}}.  In
-{\cite{fagin_belief_1988}}, Halpern and Fagin adapted neighborhood semantics
-for reasoning about epistemic agents without logical omniscience.  In this
-section will demonstrate how these semantics may be modified so that
-neighborhoods corresponds to the logical consequences of a different knowledge
-bases.  This allows for using logics with neighborhood semantics for
-reasoning about multiple knowledge bases.  A point of distinction of
-neighborhood semantics from JL is that it may be possible that two distinct
-knowledge bases cannot be merged by the agent.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
-  language $\mathcal{L}_N (\Phi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \bot \hspace{1em} | \hspace{1em} \phi \rightarrow \psi
-     \hspace{1em} | \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A :
-     \phi \hspace{1em} | \hspace{1em} K \phi \]
-\end{definition}
-
-Just as previous semantics, ``$\Box \phi$'' is intended to mean that the agent
-has an argument for $\phi$ from some knowledge base.  A novelty we present
-here is that ``$K \phi$'' means that the agent has an argument for $\phi$ from
-some \tmtextit{sound} knowledge base.
-
-\begin{definition}
-  \label{neighborhoodmodels}A {\tmstrong{neighborhood model}} $\mathbbm{M}=
-  \langle W, V, \mathcal{N}, \mathcal{A} \rangle$ has a neighborhood function
-  $\mathcal{N} : W \rightarrow 2^{2^W}$ and a multi-awareness function
-  $\mathcal{A} : W \rightarrow 2^{2^{\mathcal{L}_N (\Phi)}}$
-
-  The semantics for $\vDash$ have the following modifications:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box \phi & \text{iff} & \text{there exists a $U \in
-    \mathcal{N}_w$ where $\mathbbm{M}, v \vDash \phi$ for all $v \in U$}\\
-    \mathbbm{M}, w \vDash K \phi & \text{iff} & \text{there exists a $U \in
-    \mathcal{N}_w$ where $w \in U$ and $\mathbbm{M}, v \vDash \phi$ for all $v
-    \in U$}\\
-    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \bigcup
-    \mathcal{A_w}
-  \end{eqnarray*}
-\end{definition}
-
-Here we modify our previous notion of \tmtextbf{CSQ} and \tmtextbf{SND} to
-match how our semantics are intended for reasoning over multiple bases:
-
-\begin{definition}
-  The following defines properties a neighborhood model may make true:
-
-  \begin{descriptiondash}
-    \item[NCSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff there exists a set
-    $X \in \mathcal{A}_w$ such that } \tmop{Th} (\mathbbm{M}) \cup X \vdash
-    \phi$
-
-    \item[NSND] $\mathbbm{M}, w \vDash K \phi \text{ iff there exists a set $X
-    \in \mathcal{A}_w$ such that $\mathbbm{M}, w \vDash X$ and } \tmop{Th}
-    (\mathbbm{M}) \cup X \vdash \phi$
-  \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
-\end{definition}
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash K \phi \rightarrow \Box \phi$\\
-    $\vdash K \phi \rightarrow \phi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$\\
-    \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi \rightarrow \psi}{\vdash \Box
-      \phi \rightarrow \Box \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi
-      \rightarrow \psi}{\vdash K \phi \rightarrow K \psi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic3}A Neighborhood Logic for \tmtextbf{NCSQ} and
-  {\tmstrong{NSND}}}
-\end{table}
-
-\begin{theorem}
-  Assuming an infinite store of letters $\Phi$, the logic in Table
-  \ref{logic3} is sound and weakly complete for neighborhood semantics making
-  true \tmtextbf{NCSQ} and \tmtextbf{NSND}.
-\end{theorem}
-
-\begin{proof}
-  Assume that $\nvdash \psi$, and define the finitary canonical model
-  $\mathbbm{M}= \langle W, V, \mathcal{K}, \mathcal{N}, \mathcal{A} \rangle$
-  where:
-  \begin{itemizedot}
-    \item $W \assign \text{the maximally consistent sets of subformulae of
-    $\psi$, closed under single negation}$
-
-    \item $V (p) \assign \{v \in W \hspace{1em} | \hspace{1em} p \in v\}$
-
-    \item $\mathcal{K}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
-    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
-    \hspace{1em} K \phi \in w\}$
-
-    \item $\mathcal{N}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
-    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
-    \hspace{1em} \Box \phi \in w\}$
-
-    \item $\mathcal{A}_w \assign \{\{\phi\} \hspace{1em} | \hspace{1em} A :
-    \phi \in w\}$
-  \end{itemizedot}
-  Note that in this model, there are neighborhoods for both knowledge and
-  belief; more work is necessary to find a model based on this one which
-  conforms to the semantics in Definition \ref{neighborhoodmodels}.  For now,
-  assume that $K$ is just another modality governed by the neighborhoods in
-  $\mathcal{K}_w$.  In both neighborhood functions, our idea is that the
-  neighborhoods of $w$ in are supersets $S \supseteq \left\llbracket \phi
-  \right\rrbracket$ where $\Box \phi \in w$ or $K \phi \in w$, respectively.
-
-  There are steps of the inductive proof of the Truth Lemma for this structure
-  which are not obvious nor obviously documented elsewhere.  Assume
-  $\mathbbm{M}, w \vDash \Box \chi$, where the Truth Lemma has been proven to
-  hold for $\chi$; we must show $\Box \chi \in w$.  By our assumption there
-  is some $\phi$ and $S$ where $\Box \phi \in w$ and $S \supseteq \{v \in W
-  \hspace{1em} | \hspace{1em} \phi \in v\}$.  We argue that $\vdash \phi
-  \rightarrow \chi$; for if not then by the finitary Lindenbaum lemma there is
-  some $u \in W$ where $\phi \in u$ and $\chi \nin u$.  Hence $u \in S$ and
-  $\mathbbm{M}, u \nvDash \chi$, a contradiction.  Since $\vdash \phi
-  \rightarrow \chi$ then we know that $\vdash \Box \phi \rightarrow \Box \chi$
-  by our rules, which means that $\Box \chi \in w$ by maximality.
-
-  By the Lindenbaum Lemma we have that there is some $w \in W$ where
-  $\mathbbm{M}, w \nvDash \psi$.  $\mathbbm{M}$ makes true a number of
-  properties:
-  \begin{enumeratenumeric}
-    \item $W$ and $\mathcal{A}_v$ are finite for all $v \in W$, and $\psi \in
-    \bigcup \mathcal{A_w}$ only if $\psi$ is a subformula of $\phi$
-
-    \item $\mathcal{K}_w \subseteq \mathcal{N}_w$
-
-    \item If $S \in \mathcal{K}_w$ then $w \in S$
-
-    \item $\mathbbm{M}, v \vDash A : \phi \rightarrow \Box \phi$ for all $v
-    \in W$
-
-    \item $\mathcal{N}_w$ and $\mathcal{K}_w$ are closed under supersets
-  \end{enumeratenumeric}
-
-  As in the proof of Theorem \ref{completeness1}, we use a bisimulation to
-  move to a model where property (3) is strengthened to (3$'$): for all $S \in
-  \mathcal{N}_w$, $w \in S$ if and only if $S \in \mathcal{K}'_w$.  We defer
-  the reader to {\cite{hansen_bisimulation_2007,pauly_bisimulation_1999}} for
-  details regarding bisimulation in neighborhood semantics.  Define
-  $\mathbbm{M}' \assign \langle W', V', \mathcal{K}', \mathcal{N}',
-  \mathcal{A}' \rangle$ such that:
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$ wher.  $l, r$ its associated canonical
-    injections and $\theta (v_l) \assign \theta (v_r) \assign v$ is a
-    left-inverse of $l, r$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $\mathcal{K}' (v_i) \assign \{S \hspace{1em} | \hspace{1em} v_i \in
-    S \hspace{1em} \& \hspace{1em} \theta [S] \in \mathcal{K_v} \}$ where $i =
-    l, r$
-
-    \item $\mathcal{N}' (v_i) \assign \mathcal{K}' (v_i) \cup \{S \hspace{1em}
-    | \hspace{1em} v_i \nin S \hspace{1em} \& \hspace{1em} \theta [S] \in
-    \mathcal{N_v} \}$ where $i = l, r$
-
-    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
-    (v)$
-  \end{itemizedot}
-
-  If we let $Z \assign \{(v, v_r), (v, v_l) \hspace{1em} | \hspace{1em} v \in
-  W\}$, it is straightforward to verify that $Z$ is a neighborhood
-  bisimulation.  Hence $\mathbbm{M}, w_l \nvDash \psi$.  Along with (3$'$),
-  this model makes true (1), (2), (4).  In fact, in light of ($3'$), we can
-  see that this model does not need $\mathcal{K}'$, and conforms to the
-  semantics in Definition \ref{neighborhoodmodels}.{\hspace*{\fill}}
-
-  As in previous proofs, let $\Lambda$ be the proposition letters occuring in
-  $\psi$ and define an injection $\iota : W' \hookrightarrow \Phi \backslash
-  \Lambda$, assigning a nominal to every world in $\mathbbm{M}'$.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', \mathcal{N}'', \mathcal{A}''
-  \rangle$ such that:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
-      \begin{array}{ll}
-        V' (p) & p \in \Lambda\\
-        \{v\} & p = i (v)\\
-        \varnothing & o / w
-      \end{array} \right.$\\
-      $\bullet$ & $\mathcal{N}''_w \assign \mathcal{N}'_w$ & {\hspace{3em}} &
-      $\bullet$ & $\mathcal{A}''_v \assign \{\partial_v S \hspace{1em} |
-      \hspace{1em} S \in \mathcal{N}'_w \}$
-    \end{tabular}
-  \end{center}
-
-  Where $\partial_v S \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
-  \bigcup \mathcal{A}_v', \text{$\phi$ is a subformula of $\psi$ and}
-  \hspace{1em} S \subseteq \left\llbracket \phi
-  \right\rrbracket^{\mathbbm{M}'} \} \cup \{\neg \iota (u) \hspace{1em} |
-  \hspace{1em} u \nin S\}$.
-
-  As before, this model agrees with $\mathbbm{M}'$ on all subformulae of
-  $\psi$, using the semantics in Definition \ref{neighborhoodmodels}, hence
-  $\mathbbm{M}'', w_l \nvDash \phi$. \
-
-  All that is left is to show \tmtextbf{NCSQ} and \tmtextbf{NSND} from three
-  new properties:
-  \begin{enumerateroman}
-    \item For all words $v$ and all $X \in \mathcal{A}_v''$, $X$ is finite and
-  .  $X = \partial_v S$ for some $S \in \mathcal{N}_v''$
-
-    \item For all $v$ and all $S \in \mathcal{N}_v$, $u \in S$ if and only if
-    $\mathbbm{M}'', u \vDash \bigwedge \partial_v S$
-
-    \item The logic presented in Table \ref{logic3} is sound for
-    $\mathbbm{M}''$
-  \end{enumerateroman}
-  Along with the deduction theorem for $\vdash$, these properties establish
-  \tmtextbf{NCSQ} for this model using the logic of Table \ref{logic3} itself:
-
-  \begin{align*}
-    \text{$\exists X \in \mathcal{A''_v} \text{ s.t. } \tmop{Th}
-    (\mathbbm{M}'') \cup X \vdash \phi$} & {\Longleftrightarrow}\text{$\exists
-    S \in \mathcal{N''_v} \text{ s.t. } \tmop{Th} (\mathbbm{M}'') \cup
-    \partial_v S \vdash \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \tmop{Th} (\mathbbm{M}'') \vdash \bigwedge \partial_v S \rightarrow
-    \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \bigwedge \partial_v S \rightarrow \phi \in \tmop{Th} (\mathbbm{M}'')$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \left\llbracket \bigwedge \partial_v S \right\rrbracket \subseteq
-    \left\llbracket \phi \right\rrbracket$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t.
-    $\forall u \in W$ if } \mathbbm{M}, u \vDash \bigwedge \partial_v S \text{
-    then } \mathbbm{M}, u \vDash \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \mathbbm{M}, u \vDash \phi \text{ for all } u \in S$}\\
-    & {\Longleftrightarrow}{\mathbbm{M}},v{\vDash}\Box{\phi}
-  \end{align*}
-
-  \tmtextbf{NSND} follows from \tmtextbf{NCSQ} and the semantics of Definition
-  \ref{neighborhoodmodels}.
-\end{proof}
-
-It is not too hard to identify the fragment of this logic that governs
-knowledge alone.  The fragment given in Table \ref{logic4} has special
-significance to us, since it governs the notion of knowledge presented in
-{\S}\ref{quantifying}.
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash K \phi \rightarrow \phi$\\
-    \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ &  &  & $\frac{\vdash \phi \rightarrow \psi}{\vdash K \phi
-      \rightarrow K \psi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic4}A knowledge-only neighborhood logic for
-  \tmtextbf{NCSQ} and {\tmstrong{NSND}}}
-\end{table}
-
-\begin{proposition}
-  The knowledge-only logic presented governs the $\Box$-free fragment of the
-  logic in Table \ref{logic3}
-\end{proposition}
-
-This concludes our analysis of knowledge bases using neighborhood semantics.
-
-\subsection{\label{quantifying}Using Modalities to Quantify over Knowledge
-Bases}
-
-\section{Conclusions \& Further Research}
-
-The logic presented in Table \ref{logic1} is a conservative extension of the
-basic modal logic $K$, which means that its decision problem is
-\tmtextsf{PSPACE} hard (a lower bound).  Our finitary completeness proof
-establishes that its complexity is in \tmtextsf{EXP2-TIME} (an upper bound).
-
-Worlds in epistemic logic might correspond to fantastic, pretend scenarios;
-however, it may be desirable for some philosophers to model knowledge about
-imaginary lands.  After all, many children ``know'' a lot about Tolkien's
-{\tmem{middle earth}} or Rowling's {\tmem{Hogwarts}} (the school Harry Potter
-attends).
-
-\bibliographystyle{plain}
-\bibliography{zotero}
-
-\end{document}
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "paper"
+%%% End:

### 2010-12-15 introduction.tex
Refactored paper so all sections are seperate documents

--- 2010-12-15 paper.tex
@@
-\documentclass{article}
-\usepackage{geometry,amsmath,amssymb,wasysym,enumerate,bbm,color}
-\geometry{letterpaper}
-
-\usepackage{stmaryrd}
-
-%%%%%%%%%% Start TeXmacs macros
-\newcommand{\assign}{:=}
-\newcommand{\nin}{\not\in}
-\newcommand{\tmem}[1]{{\em #1\/}}
-\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
-\newcommand{\tmstrong}[1]{\textbf{#1}}
-\newcommand{\tmtextbf}[1]{{\bfseries{#1}}}
-\newcommand{\tmtextit}[1]{{\itshape{#1}}}
-\newcommand{\tmtextsf}[1]{{\sffamily{#1}}}
-\newcommand{\tmtextup}[1]{{\upshape{#1}}}
-\newenvironment{descriptioncompact}{\begin{description} }{\end{description}}
-\newenvironment{descriptiondash}{\begin{description} }{\end{description}}
-\newenvironment{enumeratenumeric}{\begin{enumerate}[1.] }{\end{enumerate}}
-\newenvironment{enumerateroman}{\begin{enumerate}[i.] }{\end{enumerate}}
-\newenvironment{itemizedot}{\begin{itemize} \renewcommand{\labelitemi}{$\bullet$}\renewcommand{\labelitemii}{$\bullet$}\renewcommand{\labelitemiii}{$\bullet$}\renewcommand{\labelitemiv}{$\bullet$}}{\end{itemize}}
-\newenvironment{proof}{\noindent\textbf{Proof\ }}{\hspace*{\fill}$\Box$\medskip}
-\definecolor{grey}{rgb}{0.75,0.75,0.75}
-\definecolor{orange}{rgb}{1.0,0.5,0.5}
-\definecolor{brown}{rgb}{0.5,0.25,0.0}
-\definecolor{pink}{rgb}{1.0,0.5,0.5}
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}{Proposition}
-\newtheorem{theorem}{Theorem}
-%%%%%%%%%% End TeXmacs macros
-
-\begin{document}
-
-\title{Epistemic Logics For Knowledge Bases}\author{Matthew P.
-Wampler-Doty}\maketitle
-
-\begin{abstract}
-  In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem
-  proposed a research program for logic of \tmtextit{explicit knowledge}. \
-  Two efforts have since emerged with proposals for logic of explicit
-  knowledge: the \tmtextit{Dynamics of Awareness}
-  {\cite{van_benthem_inference_2009}} and \tmtextit{Justification Logic}
-  {\cite{artemov_introducing_2005}}.  The purpose of this paper is to
-  repurpose various epistemic logics from these previous efforts for reasoning
-  about logical closures over knowledge bases.  The results in this paper are
-  based on previous work carried out in
-  {\cite{wampler-doty_evidentialist_2010}}.
-\end{abstract}
-
-\section{Introduction\label{intro}}
-
 The modern tradition in epistemic logic is to assume knowledge modalities
@@
 epistemic logic, economists and philosophers accept that traditional decision
-theory is externalist and behaviourist in nature
-(FIXME)
+theory is externalist and behaviorist in nature
 \footnote{An early essay by
@@
 {\cite{artemov_introducing_2005}}, based on Artemov's \tmtextit{Logic of
-Proofs} {\cite{artemov_logic_1994}}.  While the original semantics of JL was
-interpretability into Peano Arithmetic, Melvin Fitting proposed Kripke
+Proofs} {\cite{artemov_logic_1994}}.  While the original semantics of
+JL were based on interpretability into Peano Arithmetic, Melvin Fitting proposed Kripke
 semantics for JL in {\cite{fitting_logic_2005}}.  Recently, Fernando
@@
 paper.  We consider a \tmtextit{good argument} to be a logical derivation
-from propositions present in a knowledge base.  In this fashion, ou.  \
+from propositions present in a knowledge base in this setting.  \
 Special attention will be given to \tmtextit{sound derivations}, which will be
-thought of as a form of knowledge.  In Awareness Logic, we will interpret
+thought of as a form of knowledge.  In \emph{Awareness Logic}, we will interpret
 awareness of a formula as membership in a knowledge base.  We prove
@@
 modalities for quantifying over knowledge bases.  We conclude with an
-application to naturalized epistemology found in the psychological literature.
-
-\section{Basic Explicit Logics of Knowledge Bases}
-
-\subsection{Awareness Logic\label{awarenesslogic}}
-
-In this section, we give the explicit semantics to basic awareness logic,
-originally presented in {\cite{fagin_belief_1987}}, with an additional axiom.
-\ One difference in our presentation is the inclusion of a novel letter and a
-superficial change in notation.  This work is inspired by the developments in
-van Benthem and Vel\'azquez-Quesada {\cite{van_benthem_inference_2009}}.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and define the language $\mathcal{L}_A
-  (\Phi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A : \phi \hspace{1em}
-  \]
-\end{definition}
-
-We define the other connectives and modal operators as usual for classical
-modal logics.
-
-\begin{definition}
-  \label{awarenessmodels}An {\tmstrong{awareness model}} $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V : \Phi
-  \cup \{\circlearrowleft\} \rightarrow 2^W$ and an awareness function
-  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$.  We will usually
-  denote $\mathcal{A} (w)$ as $\mathcal{A}_w$.
-
-  Define the semantic entailment relation $\vDash$ where atomic propositions,
-  logical connectives and modality are interpreted as usual.  We employ the
-  following novel definition:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \mathcal{A_w}
-  \end{eqnarray*}
-\end{definition}
-
-The following definition distinguishes us from previously investigations of
-awareness logic:
-
-\begin{definition}
-  Define the ``\tmtextbf{theory of a model} $\mathbbm{M}$'' as:
-  \[ \tmop{Th} (\mathbbm{M}) \assign \{\phi \hspace{1em} | \hspace{1em}
-     \mathbbm{M}, v \vDash \phi \text{ for all } v \in W\} \]
-  We define the following properties that a model $\mathbbm{M}$ may posses:
-
-  \begin{descriptiondash}
-    \item[CSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w \vdash \phi$
-
-    \item[SND] $\mathbbm{M}, w \vDash \circlearrowleft \text{ iff }
-    \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w$
-  \end{descriptiondash}
-
-  Here $\vdash$ is any logical consequence relation which is sound for
-  $\vDash$, making true \tmtextbf{modus ponens} and \tmtextbf{reflection} (ie,
-  $\Gamma \vdash \phi$ if $\phi \in \Gamma$)
-\end{definition}
-
-Neither \tmtextbf{CSQ} nor \tmtextbf{SND} correspond to simple modally
-definable properties.
-
-Intuitively, the \tmtextbf{CSQ} asserts that an agent believes a formula
-$\phi$ if and only if it follows logically from their knowledge base and their
-background knowledge, represented by $\tmop{Th} (\mathbbm{M})$. \
-\tmtextbf{CSQ} is Vincent Hendrik's principle of logical omniscience mentioned
-in {\S}\ref{intro}.
-
-\tmtextbf{SND} asserts that $\circlearrowleft$ corresponds to the agent's
-knowledge base being sound. A sound knowledge base will only render true
-conclusions when used in deductions.  If one considers ``the existance of a
-sound deduction'' sufficient for a kind of knowledge, then $\circlearrowleft$
-is suitable for investigating this notion of epistemology.  That is, if
-$\mathbbm{M}, w \vDash \circlearrowleft \wedge \Box \phi$, then we may
-naturally say that the agent (implicitly) {\tmem{knows}} $\phi$ on the basis
-of $\mathcal{A}_w$, rather than merely {\tmem{believing}} $\phi$ on the basis
-of $\mathcal{A}_w$.
-
-The logic of models making true \tmtextbf{CSQ} and \tmtextbf{SND} is provided
-in Table \ref{logic1}.
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash \Box(\phi \rightarrow \psi) \rightarrow \Box \phi \rightarrow \Box
-    \psi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$\\
-    $\vdash \circlearrowleft \rightarrow \Box \phi \rightarrow \phi$\\
-    \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box \phi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic1}Awareness Logic for \tmtextbf{CSQ} and
-  \tmtextbf{SND}}
-\end{table}
-
-\begin{theorem}
-  \label{completeness1}Assuming an infinite store of proposition letters
-  $\Phi$, the awareness logic presented is sound and weakly complete for
-  awareness models making true \tmtextbf{CSQ} and \tmtextbf{SND}.
-\end{theorem}
-
-\begin{proof}
-  Soundness is straightforward, so we will only address completeness.  Assume
-  $\nvdash \psi$.  Consider the finite canonical model $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A} \rangle$ formed of maximally consistent sets of
-  subformulae of $\phi$ (closed under single negations{\footnote{A discussion
-  of this property may be found in {\cite[pg.
-  243]{blackburn_modal_2001}}.}}), as per the finitary modal completeness
-  proofs found in {\cite[chapter 4.8]{blackburn_modal_2001}} and
-  {\cite[chapter 5]{boolos_logic_1995}}.  Typical presentations do not
-  include awareness, however it is defined intuitively in this case:
-  \[ \phi \in \mathcal{A}_w \Longleftrightarrow A : \phi \in w \]
-  Since $\psi$ is a subformula of itself, we have $\mathbbm{M}, w \nvDash
-  \psi$ for some world $w$ by a finitary {\tmem{Lindenbaum Lemma}} and
-  {\tmem{Truth Theorem}}.  Moreover, it is straightforward to verify that
-  $\mathbbm{M}$ makes true the following properties:
-  \begin{enumeratenumeric}
-    \item $W$ and $\mathcal{A}_v$ are finite, and $\psi \in \mathcal{A}_v$
-    only if $\psi$ is a (possibly negated) subformula of $\phi$
-
-    \item if $\mathbbm{M}, v \vDash A : \psi$ then $\mathbbm{M}, v \vDash \Box
-    \psi$
-
-    \item if $\mathbbm{M}, v \vDash \circlearrowleft$ then $v R v$
-  \end{enumeratenumeric}
-
-  We next produce a bisimular{\footnote{The notion of bisimulation is
-  discussed at length in {\cite[chapter 2.2]{blackburn_modal_2001}}.  We
-  note that the basic definition and all of the usual theorems (modal
-  equivalence, Henessy Milner, etc.) may be generalized to awareness models in
-  a straightforward fashion. }} model $\mathbbm{M}'$ which makes true (1), (2)
-  and a stronger from of (3):
-
-  {\hspace*{\fill}}\begin{tabular}{ll}
-    \tmtextbf{3$'$.} & $\mathbbm{M}', v \vDash \circlearrowleft$ iff $v R v$
-  \end{tabular}{\hspace*{\fill}}
-
-  To this end define $\mathbbm{M}' \assign \langle W', V', R', \mathcal{A}'
-  \rangle$ such that{\footnote{Throughout this article, we use $l$ and $r$ to
-  denote the two canonical injections associated with the coproduct $W \uplus
-  W$. We will use $v_l$ and $v_r$ as the shorthand for $l (v)$ and $r (v)$
-  respectively.}}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $R' \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v R
-    u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em} \mathbbm{M},
-    v \vDash \circlearrowleft\}$
-
-    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
-    (v)$
-  \end{itemizedot}
-
-  It is straightforward to verify that $\mathbbm{M}'$ makes true the desired
-  properties.  Let $Z \assign \{(v, v_l), (v, v_r) \hspace{1em} |
-  \hspace{1em} v \in W\}$.  then $Z$ is a bisimulation between $\mathbbm{M}$
-  and $\mathbbm{M}'$.  Therefore we know there is some $w \in W$ such that
-  $\mathbbm{M}', w_l \nvDash \psi$ and $\mathbbm{M}', w_r \nvDash \psi$.
-
-  Finally we construct a model $\mathbbm{M}''$ which agrees with
-  $\mathbbm{M}'$ for all subformulae of $\psi$, which makes true
-  \tmtextbf{CSQ} and \tmtextbf{SND}.  Let $\Lambda$ be the set of proposition
-  letters occuring in $\psi$.  We will make use members of $\Phi \backslash
-  \Lambda$ as {\tmem{nominals}}, as per the tradition in hybrid logic.  This
-  is possible since both $W'$ and $\Lambda$ are finite and $\Phi$ is infinite
-  by hypothesis.  Let $\iota : W \uplus W \hookrightarrow \Phi \backslash
-  \Lambda$ be an injection assigning a fresh nominal associated with each
-  world in $\mathbbm{M}'$.  Now define $\mathbbm{M}'' \assign \langle W'',
-  V'', R'', \mathcal{A}'' \rangle$, where:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
-      \begin{array}{ll}
-        V' (p) & p \in \Lambda\\
-        \{v\} & p = \iota (v)\\
-        \varnothing & o / w
-      \end{array} \right.$\\
-      $\bullet$ & $R'' \assign R'$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}''_v \assign \{\phi \hspace{1em} | \phi \in \mathcal{A}'_v
-      \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em} \neg v R' u\}$
-    \end{tabular}
-  \end{center}
-
-  By induction we have that for every subformula $\phi$ of $\psi$ that
-  $\mathbbm{M}', v \vDash \phi$ if and only if $\mathbbm{M}'', v \vDash \phi$,
-  hence $\mathbbm{M}'', w_l \nvDash \psi$.
-
-  All that is left to show is that $\mathbbm{M}''$ makes true \tmtextbf{CSQ}
-  and \tmtextbf{SND}.  $\mathbbm{M}''$ has three further properties:
-  \begin{enumerateroman}
-    \item $\mathcal{A}''_v$ is finite for all worlds $v$
-
-    \item  $v R' u$ if and only if $\mathbbm{M}'', u \vDash \bigwedge
-    \mathcal{A}'' (v)$
-
-    \item The logic presented in Table \ref{logic1} is sound for
-    $\mathbbm{M}''$
-  \end{enumerateroman}
-  From (ii) and the fact that $\mathbbm{M}'$ makes true (3$'$), we have
-  \tmtextbf{SND} for $\mathbbm{M}''$.
-
-  All that is left is to demonstrate \tmtextbf{CSQ} for some sound logic.  We
-  will use the logic in Table \ref{logic1} itself.  From (i), (ii), (iii),
-  and the \tmtextit{deduction theorem} for modal logic, we have the following
-  line of reasoning:
-
-  \begin{align*}
-    Th({\mathbbm{M}}''){\cup}\mathcal{A}''_v{\vdash}{\phi} &
-    {\Longleftrightarrow}Th({\mathbbm{M}}''){\vdash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\\
-    &
-    {\Longleftrightarrow}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}{\in}Th({\mathbbm{M}}'')\\
-    &
-    {\Longleftrightarrow}{\mathbbm{M}}'',u{\vDash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\text{
-    for all $u \in W''$}\\
-    & {\Longleftrightarrow}\text{ for all $u \in W''$, if
-    }{\mathbbm{M}}'',u{\vDash}\mathcal{A}''_v\text{ then
-    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
-    & {\Longleftrightarrow}\text{ for all $u \in W''$, if }v R 'u \text{ then
-    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
-    & {\Longleftrightarrow}{\mathbbm{M}}'',v{\models}\Box{\phi}
-  \end{align*}
-\end{proof}
-
-\subsection{Hybrid Awareness Logic}
-
-The method of the above completeness proof makes implicit use of concepts from
-hybrid logic{\footnote{Hybrid logic was first presented in
-{\cite{prior_revised_1969}} and later formally developed in
-{\cite{bull_approach_1970}}.}}.  In this section we adapt hybrid logic and
-show that it is a complete for reasoning about knowledge bases.  We note that
-because of the increased expressive power of hybrid logic, our completeness
-theorem is simpler.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
-  language $\mathcal{L}_H (\Phi, \Psi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} i \in \Psi \hspace{1em} | \hspace{1em} \bot \hspace{1em} |
-     \hspace{1em} \phi \rightarrow \psi \hspace{1em} | \hspace{1em} \Box \phi
-     \hspace{1em} | \hspace{1em} A : \phi \hspace{1em} | \hspace{1em} \forall
-     \phi \]
-\end{definition}
-
-Our approach in hybrid logic is to employ a universal modality along with
-nominals.  This framework presents a logic where the agent may reason about
-various labeled scenarios.  Scenarios may be multiply labeled or not labeled
-at all.  From these intuitions we have the following definition:
-
-\begin{definition}
-  \label{hybridsemantics}Let a \tmtextbf{hybrid model} $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A}, \ell \rangle$ be an awareness model as in Definition
-  \ref{awarenessmodels}, along with a partial labeling function $\ell : \Psi
-  \nrightarrow W$
-
-  The semantics for $\vDash$ are the same as in Definition
-  \ref{awarenessmodels}, only we have
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \forall \phi & \text{iff} & \forall v \in
-    W.\mathbbm{M}, v \vDash \phi\\
-    \mathbbm{M}, w \vDash i & \text{iff} & \ell (i) = w
-  \end{eqnarray*}
-\end{definition}
-
-The other connectives and operators are defined as usual, although we employ a
-few special shorthands:
-
-\begin{definition}
-  We employ the following special abbreviations:
-  \begin{eqnarray}
-    \text{\tmtextup{@}}_i \phi \assign \forall (i \rightarrow \phi)
-    \hspace{2em} & \exists \phi \assign \neg \forall \neg \phi \hspace{3em} &
-    \circlearrowleft_i \assign \diamondsuit i \nonumber
-  \end{eqnarray}
-\end{definition}
-
-This gives rise to a validity reflecting one of the axioms we saw in
-{\S}\ref{awarenesslogic}:
-\[ \vDash \circlearrowleft_i \rightarrow \Box \phi \rightarrow
-   \text{\tmtextup{@}}_i \phi \]
-This can be read as ``If the agent's knowledge base is sound at world $i$,
-then if they can deduce something from their knowledge base, what they deduce
-must be true at world $i$.'.  In a way, this may be considered as
-{\tmem{relativising}} knowledge particular named situations.
-
-The semantics in Definition \ref{hybridsemantics} obviates the \tmtextbf{SND}
-principle we previously presented, since there is no explicit
-$\circlearrowleft$ symbol in this setting. \tmtextbf{CSQ} still makes sense
-without modification, however.  The following gives a logic for hybrid models
-making true \tmtextbf{CSQ}:
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & $\vdash \forall (\phi
-    \rightarrow \psi) \rightarrow \forall \phi \rightarrow \forall \psi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & $\vdash \forall
-    \phi \rightarrow \phi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & $\vdash \forall \phi \rightarrow
-    \forall \forall \phi$\\
-    $\vdash \Box(\phi \rightarrow \psi) \rightarrow \Box \phi \rightarrow \Box
-    \psi$ & $\vdash \exists \phi \rightarrow \forall \exists \phi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$ & $\vdash \forall \phi \rightarrow
-    \Box \phi$\\
-    & $\vdash i \rightarrow \phi \rightarrow \text{\tmtextup{@}}_i \phi$\\
-    & \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi}{\vdash \Box \phi}$ &
-      {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \forall \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic2}Hybrid Awareness Logic for \tmtextbf{CSQ}}
-\end{table}
-
-\begin{theorem}
-  \label{completeness2}Assuming an infinite store of nominals $\Psi$, the
-  hybrid awareness logic presented is sound and weakly complete for all hybrid
-  models making true \tmtextbf{CSQ}.
-\end{theorem}
-
-\begin{proof}
-  As before, soundness is trivial.  Completeness is based on a modification
-  of techniques found in {\cite[chapter 5]{boolos_logic_1995}}.  Assume
-  that $\nvdash \psi$ and let $\Sigma_0$ be the set of subformulae of $\psi$,
-  and let $\Upsilon$ be the set of nominals occuring in $\psi$.  Define:
-
-  \begin{align*}
-    {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{{\forall}{\phi}{\hspace{1em}}|{\hspace{1em}}\Box{\phi}{\in}{\Sigma}_0\}\\
-    {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{\text{@}_i{\phi}{\hspace{1em}},i{\rightarrow}{\phi}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1{\hspace{1em}}\&{\hspace{1em}}i{\in}{\Upsilon}\}\\
-    {\Sigma}_3 &
-    {\assign}{\Sigma}_2{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_2\}
-  \end{align*}
-
-  It is easy to see that $\Sigma_3$ is finite and closed under subformulae and
-  single negations. Let $\mathbbm{M}= \langle W, V, R_{\Box}, \sim_{\forall},
-  \mathcal{A} \rangle$ be the finite cannonical model formed of maximally
-  consistent subsets of $\Sigma_3$, where everything is defined as usual,
-  except $\sim_{\forall}$, which obeys the following specification:
-
-  \begin{align*}
-    w {\sim}_{{\forall}}v & {\Longleftrightarrow}(({\forall}{\phi}){\in}w
-    {\Longleftrightarrow}({\forall}{\phi}){\in}v)
-  \end{align*}
-
-  This model makes true the following properties:
-  \begin{enumerateroman}
-    \item $\sim_{\forall}$ is an equivalence relation
-
-    \item $R_{\Box} \subseteq \sim_{\forall}$
-
-    \item In each equivalence class specified by $\sim_{\forall}$, there is at
-    most one world making true $i$ for all $i \in \Upsilon$
-  \end{enumerateroman}
-  As in our previous construction we have that there is some world $w$ where
-  $\mathbbm{M}, w \nvDash \psi$.  Let $\mathbbm{M}^1 = \langle W', V',
-  R_{\Box}', \sim_{\forall}', \mathcal{A}' \rangle$ be the submodel generated
-  by $\{w\}$; we have that $\mathbbm{M}', w \nvDash \psi$ (see {\cite[chapter
-  2.1]{blackburn_modal_2001}} for details on generated submodels).  In this
-  model $\forall$ is a universal modality and either $\left\llbracket i
-  \right\rrbracket^{\mathbbm{M}'} = \varnothing$ or $\left\llbracket i
-  \right\rrbracket^{\mathbbm{M}'} =\{v\}${\footnote{As per the usual
-  convention, here $\left\llbracket \phi \right\rrbracket^{\mathbbm{M}}$
-  denotes $\{w \in W \hspace{1em} | \hspace{1em} \mathbbm{M}, w \vDash
-  \phi\}$.  We will drop $\mathbbm{M}$ where it is unambiguous.}}. Since the
-  store $\Psi$ of nominals is infinite and $\Upsilon$ is finite, we have that
-  $\Psi \backslash \Upsilon$ is infinite, so there is some injection $\iota :
-  W' \hookrightarrow \Psi \backslash \Upsilon$ which assigns a fresh nominal
-  to every world.  Let $\mathbbm{M}'' = \langle W'', V'', R'', \mathcal{A}'',
-  \ell \rangle$, where:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign V' (p)$\\
-      $\bullet$ & $R'' \assign R'_{\Box}$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}'' (v) \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
-      \mathcal{A}' (v)\} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
-      \neg v R' u\}$\\
-      \begin{tabular}{ll}
-        $\bullet$ & $\ell (i) \assign \left\{ \begin{array}{ll}
-          w & i \in \Upsilon \hspace{1em} \& \hspace{1em} \mathbbm{M}, w
-          \vDash i\\
-          \iota^{- 1} (i) & i \in \iota [W]\\
-          \text{undefined} & \text{o/w}
-        \end{array} \right.$
-      \end{tabular} & $R'' \assign R'_{\Box}$ &  &  & 
-    \end{tabular}
-  \end{center}
-
-  The the worlds is $\mathbbm{M}'$ and $\mathbbm{M}''$ agree on all
-  subformulae of $\psi$, hence $\mathbbm{M}'', w \nvDash \psi$. The same
-  reasoning as in the proof of Theorem \ref{completeness1} establishes and
-  that the logic in Table \ref{logic2} itself is sound for $\mathbbm{M}''$ and
-  makes true \tmtextbf{CSQ}, establishing completeness.
-\end{proof}
-
-\section{Logics of Multiple Knowledge Bases}
-
-So far, we have only dealt with systems that reason over a single knowledge
-base.  In this section, we present various logics for reasoning over multiple
-knowledge bases.
-
-\subsection{Simple Justification Logic}
-
-Justification Logic (JL) was originally developed by Artemov as the
-\tmtextit{Logic of Proofs} (LP) {\cite{artemov_logic_1994}}.  Its original
-purpose was to provide a framework for reasoning about explicit provability in
-Peano Arithmetic.  The first introduction of Justification Logic can be found
-in {\cite{artemov_introducing_2005}}, where Artemov and Nogina propose LP as a
-logic for reasoning about evidence.  In {\cite{fitting_logic_2005}}, Melvin
-Fitting provided JL with Kripke model based semantics.
-
-The principle innovation of LP/JL is to extend awareness logic, such that
-awareness operations are now \tmtextit{proof terms}.  Informally, we say that
-``a proof term $X$ witnesses proposition $\phi$'', denoted ``$X : \phi$'',
-whenever $X$ represents a proof of $\phi$.  Proofs may have
-{\tmstrong{multiple-conclusions}} in this system, so it is possible that $X :
-\phi$ and $X : \psi$ can be true where $\phi \neq \psi$.  In Fitting's Kripke
-semantics, $X : \phi$ means that $\phi$ is in awareness set corresponding to
-$X$.  Proof terms are thought be operating in a \tmtextit{multi-conclusion}
-proof system, so the same proof term may witness many different propositions.
-
-The logics LP/JL include operators over proofs terms, so that new proof terms
-may be assembled.  One operation of particular interest to us is
-{\tmem{choice}}, denoted $\oplus$.  The expression ``$X \oplus Y : \phi$''
-denotes that either $X$ or $Y$ are proofs witnessing $\phi$.  There are other
-operations which correspond to \tmtextit{modus ponens} and
-\tmtextit{proof-theoretic reflection}, however we do not consider these
-operations here.
-
-In this section we consider a simplified form of JL suitable for reasoning
-over multiple knowledge bases, which we call \tmtextit{simple justification
-logic} (SJL). However, instead of thinking of terms as representing proofs, we
-use them to represent knowledge bases. This is in the spirit of JL as a logic
-of evidence: we consider each knowledge base to be a corpus of evidence. \
-Each term ``names'' a different knowledge base at a particular world.  Terms
-may not refer to the same knowledge base at different worlds, just as in how
-in awareness logic the agent need not be aware of the same formulae at
-different worlds.  Finally, we will make use of JL's {\tmem{choice}} operator
-as a mechanism for forming the union of knowledge bases, creating new ones.
-
-\begin{definition}
-  Let $\Pi$ be a set of primitive terms.  Define $\tau (\Pi)$ with the
-  following grammar:
-  \[ X \hspace{1em} : : = \hspace{1em} t \in \Pi \hspace{1em} | \hspace{1em} X
-     \oplus Y \]
-
-  Let $\Phi$ be a set of letters and $\Pi$ a set of primitive terms, and
-  define the language $\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi \]
-  where $X \in \tau (\Pi)$
-\end{definition}
-
-\begin{definition}
-  \label{justmodels}A {\tmstrong{simple justification model}} $\mathbbm{M}=
-  \langle W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V
-  : \Phi \cup \{\circlearrowleft_X \hspace{1em} | \hspace{1em} X \in \tau
-  (\Pi)\} \rightarrow 2^W$, an indexed relation $R : \tau (\Pi) \rightarrow
-  2^{W \times W}$, along with a modified awareness function $\mathcal{A} : W
-  \times \tau (\Pi) \rightarrow 2^{\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)}$. \
-  In practice we will denote $\mathcal{A} (w, X)$ by a curried shorthand,
-  namely $\mathcal{A}_w (X)$.
-
-  The semantics for $\vDash$ have the following modifications:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box_X \phi & \text{iff} & \text{for all $v \in W$
-    where $w R_X v$ we have $\mathbbm{M}, v \vDash v$}\\
-    \mathbbm{M}, w \vDash X : \phi & \text{iff} & \phi \in \mathcal{A}_w (X)
-  \end{eqnarray*}
-\end{definition}
-
-\begin{definition}
-  The following defines properties a simple justification model may make true:
-
-  \begin{descriptiondash}
-    \item[JCSQ] $\mathbbm{M}, w \vDash \Box_X \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w (X) \vdash \phi$
-
-    \item[JSND] $\mathbbm{M}, w \vDash \circlearrowleft_X \text{ iff
-    $\mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w (X)$}$
-
-    \item[CHOICE] $\mathcal{A}_w (X \oplus Y) = \mathcal{A}_w (X) \cup
-    \mathcal{A}_w (Y)$
-  \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
-\end{definition}
-
-The above semantics are similar to the ones given in previous sections. \
-\tmtextbf{JCSQ} is the same as \tmtextbf{CSQ} from {\S}\ref{awarenesslogic},
-only it is relativized to a knowledge base denoted by $X$ at $w$.  The
-awareness logic of knowledge bases is special case of simple justification
-logic where there is only one term.
-
-Simplified justification logic is given in Table \ref{logic5}.  We assert
-without proof that this is a conservative extension of the awareness logic in
-{\S}\ref{awarenesslogic}.
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
-    \Box_X \psi$ & \\
-    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash (X \oplus Y : \phi) \rightarrow X : \phi$ & $\vdash (X \oplus Y :
-    \phi) \rightarrow Y : \phi$\\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_X$ &
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_Y$\\
-    $\vdash \Box_X \phi \rightarrow \Box_{X \oplus Y} \phi$ & \\
-    $\vdash \Box_{X \oplus X} \phi \rightarrow \Box_X \phi$ & $\vdash \Box_{(X
-    \oplus X) \oplus Y} \phi \rightarrow \Box_{X \oplus Y} \phi$ \\
-    $\vdash \Box_{X \oplus Y} \phi \rightarrow \Box_{Y \oplus X} \phi$ &
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{(Y \oplus X)
-    \oplus Z} \phi$\\
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{X \oplus (Y
-    \oplus Z)} \phi$ & \\
-    & \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic5}Simple Justification Logic}
-\end{table}
-
-\begin{theorem}
-  \label{completeness5}Assuming an infinite store of proposition letters
-  $\Phi$, SJL is sound and weakly complete for simple justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND} and \tmtextbf{CHOICE}
-\end{theorem}
-
-\begin{proof}
-  As in the previous proofs, we only show completeness.  Assume that $\nvdash
-  \psi$.  Let $\Xi \subseteq \tau (\Pi)$ be all of the subterms occurring in
-  $\psi$; we assume that $\Xi$ is non-empty, since otherwise we may obtain the
-  theorem via the usual completeness theorem for classical propositional
-  logic. Let $\Sigma_0$ be the subformulae of $\psi$.  Define:
-
-  \begin{align*}
-    {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{\Box_Y{\phi}{\hspace{1em}}|{\hspace{1em}}\Box_X{\phi}{\in}{\Sigma}_0{\hspace{1em}}\&{\hspace{1em}}Y{\in}{\Xi}\}\\
-    {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1\}
-  \end{align*}
-
-  As in the proof of Theorem \ref{completeness2}, it is simple to verify that
-  $\Sigma_2$ is closed under subformulae and single negations.  Let
-  $\mathbbm{M} \assign \langle W, V, R, \mathcal{A} \rangle$ be the finite
-  cannonical model formed of maximally consistent subsets of $\Sigma_2$, where
-  $V$ and $\mathcal{A}$ are defined as usual, and $R : \Xi \rightarrow 2^{W
-  \times W}$ is defined by:
-  \[ w R_X v \Longleftrightarrow \{\phi \hspace{1em} | \hspace{1em} \Box_X
-     \phi \in w\} \subseteq v \]
-  As in previous constructions we may prove the usual Lindenbaum and Truth
-  Lemmas an use them obtain a world $w \in W$ where $\mathbbm{M}, w \nvDash
-  \psi$.
-
-  Next, define an operator $\twonotes : \tau (\Pi) \rightarrow 2^{\Pi}$ where:
-  \[ \twonotes (X) \assign \{t \in \Pi \hspace{1em} | \hspace{1em} t \text{
-     occurs in } X\} \]
-  In other words, $\twonotes (X)$ is the set of atomic terms in $X$.  As in
-  our construction for Theorem \ref{completeness1}, $\mathbbm{M}$ makes true
-  certain properties, along with some new properties:
-  \begin{enumeratenumeric}
-    \item \label{fin}$W$ and $\mathcal{A}_v (X)$ are finite, and $\phi \in
-    \mathcal{A}_v (X)$ only if $\phi \in \Sigma_2$
-
-    \item if $\mathbbm{M}, v \vDash X : \phi$ then $\mathbbm{M}, v \vDash
-    \Box_X \phi$
-
-    \item \label{refl}if $\mathbbm{M}, v \vDash \circlearrowleft_X$ then $v
-    R_X v$
-
-    \item \label{sndness}For all $X \oplus Y \in \Xi$, $\mathbbm{M}, v \vDash
-    \circlearrowleft_{X \oplus Y}$ if and only if $\mathbbm{M}, v \vDash
-    \circlearrowleft_X$ and $\mathbbm{M}, v \vDash \circlearrowleft_Y$
-
-    \item \label{union}For all $X \oplus Y \in \Xi$, $\mathcal{A}_v (X \oplus
-    Y) = \mathcal{A}_v (X) \cup \mathcal{A}_v (Y)$
-
-    \item \label{sub}For all $X, Y \in \Xi$, if $\twonotes (X) \subseteq
-    \twonotes (Y)$ then $R_Y \subseteq R_X$
-  \end{enumeratenumeric}
-  As in our previous constructions, it is necessary to refine this model using
-  bisimulations to achieve properties which are not modally definable.  In
-  particular, we shall strengthen (\ref{refl}) to a biconditional and
-  (\ref{sub}) to:
-
-  \begin{center}
-    \begin{tabular}{ll}
-      \tmtextbf{6$'$.} & For all $X, Y \in \Xi$, $R_{X \oplus Y} = R_X \cap
-      R_Y$
-    \end{tabular}
-  \end{center}
-
-  We first strengthen (\ref{refl}) by constructing $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}' \rangle$, just as in Theorem
-  \ref{completeness1}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $R'_X \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v
-    R_X u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em}
-    \mathbbm{M}, v \vDash \circlearrowleft_X \}$
-
-    \item $\mathcal{A}' (v_l, X) \assign \mathcal{A}' (v_r, X) \assign
-    \mathcal{A} (v, X)$
-  \end{itemizedot}
-  The same bisimulation relation $Z$ previously given suffices.
-
-  We next make a strengthened the model where (\ref{sub}$'$) holds.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that{\footnote{Let $\{i_X \hspace{1em} | \hspace{1em} X \in \Xi\}$ be the
-  family of canonical injections into the coproduct $\uplus_{\Xi} W$. As per
-  our previous convention, we use $v_X$ as shorthand for $i_X (v)$.}}:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em}
-    \twonotes (X) \subseteq \twonotes (Z)\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  Note that this construction makes use of the assumption that $\Xi$ is
-  non-empty.  Let $Z \assign \{(v, v_X) \hspace{1em} | \hspace{1em} X \in \Xi
-  \hspace{1em} \& \hspace{1em} v \in W' \}$; it is straightforward to prove
-  that $Z$ is a bisimulation between $\mathbbm{M}'$ and $\mathbbm{M}''$, for
-  all relations corresponding to terms $X \in \Xi$. Hence $\mathbbm{M}'', w_X
-  \nvDash \psi$ for some $w_X \in W''$.  In addition, $\mathbbm{M}''$
-  inherits (\ref{fin}) through (\ref{sub}) from $\mathbbm{M}'$, as well as the
-  converse of (\ref{refl}).  Next observe, forall $X \oplus Y \in \Xi$:
-  \begin{eqnarray*}
-    \text{$(v_V, u_Z) \in R''_X \cap R''_Y$} & \Longleftrightarrow & \exists Z
-    \in \Xi . \text{$v R'_Z u \hspace{1em} \& \hspace{1em} \twonotes (X)
-    \subseteq \twonotes (Z) \hspace{1em} \& \hspace{1em} \twonotes (Y)
-    \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X) \cup \twonotes (Y) \subseteq \twonotes
-    (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X \oplus Y) \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow &  \text{$(v_V, u_Z) \in R''_{X \oplus Y}$}
-  \end{eqnarray*}
-  We now turn to our final construction. As in previous constructions, let
-  $\iota : W'' \hookrightarrow \Phi \backslash \Psi$ be an injection assigning
-  fresh nominals to worlds.  Define $\mathbbm{M}''' \assign \langle W''',
-  V''', R''', \mathcal{A}''' \rangle$ just as in the final construction in the
-  proof of Theorem \ref{completeness1}, except that $R'''_X$ and
-  $\mathcal{A}_v''' (X)$ are defined inductively as follows:
-
-  \begin{center}
-    \begin{tabular}{lll}
-      $\bullet$ & $R'''_t \assign \left\{ \begin{array}{ll}
-        R''_t & t \in \Xi\\
-        W''' \times W''' & o / w
-      \end{array} \right.$ & \\
-      $\bullet$ & $R'''_{X \oplus Y} \assign R'''_X \cap R'''_Y$ & \\
-      &  & \\
-      $\bullet$ & $\mathcal{A}'''_v (t) \assign \{\phi \hspace{1em} | \phi \in
-      \mathcal{A}''_v \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
-      \neg v R'''_t u\}$ & where $t \in \Pi$\\
-      $\bullet$ & $\mathcal{A}'''_v (X \oplus Y) \assign \mathcal{A}'''_v (X)
-      \cup \mathcal{A}'''_v (Y)$ & 
-    \end{tabular}
-  \end{center}
-
-  Induction over complexity of subformulae $\phi$ of $\psi$ yields
-  $\mathbbm{M}'', w \vDash \phi \Longleftrightarrow \mathbbm{M}''', w \vDash
-  \phi$, so we know that there is some world $w \in W'''$ such that
-  $\mathbbm{M}''', w \nvDash \psi$.  All that is left is to illustrate that
-  $\mathbbm{M}'''$ has the properties we desire.
-
-  First note that by definition, $\mathbbm{M}'''$ makes true
-  \tmtextbf{CHOICE}.  Next, an induction argument on the complexity of a
-  terms $X$, making essential use of (\ref{sub}$'$), yields:
-  \[ u R_X''' v \Longleftrightarrow \mathbbm{M}''', v \vDash \bigwedge
-     \mathcal{A}'''_v (X) \]
-  With this, $\mathbbm{M}'''$ makes true \tmtextbf{JSND} since it inherits
-  (\ref{refl}).  Finally, we note that we may repeat our previous arguments
-  from Theorem \ref{completeness1} to prove \tmtextbf{JCSQ}.
-\end{proof}
-
-\subsection{Lattice Justification Logic}
-
-{\color{red} NOTE.  THIS SECTION HAS SOME SERIOUS PROBLEMS AND IT'S PROBABLY
-WRONG...}
-
-Implicit in our previous presentation of SJL.  $\oplus$ behaves like a union
-operation for knowledge bases, and dually like an intersection operation on
-accessibility relations.  It is natural to think of $\oplus$ as a join/meet
-operator over a {\tmem{semi-lattice}}.  In this section we make this
-explicit, by increasing the expressive power of simple JL to express the order
-theory inherent in knowledge bases.  We call the novel logic presented in
-this section \tmtextit{Lattice Justification Logic} (LJL){\footnote{We note
-that ``Semi-Lattice Justification Logic'' may be a more appropriate name,
-however we have decided to shorten semic-lattice to lattice in this article
-for purposes of concision.}}.  Lattice JL may be considered a novel logic for
-studying the dynamics of \tmtextit{theory change}, where the logic employed by
-the changing theories could be LJL itself.
-
-\begin{definition}
-  $\mathcal{L}_{\tmop{LJL}} (\Phi, \Pi)$ extends $\mathcal{L}_{\tmop{SJL}}
-  (\Phi, \Pi)$ to:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi
-     \hspace{1em} | \hspace{1em} X \sqsubseteq Y \]
-  where $X, Y \in \tau (\Pi)$
-\end{definition}
-
-\begin{definition}
-  \label{justmodels}A {\tmstrong{lattice justification model}} $\mathbbm{M}=
-  \langle W, V, R, \mathcal{A}, \preccurlyeq \rangle$ is a simple
-  justification model with a new relation $\preccurlyeq : W \rightarrow
-  2^{\tau (\Pi) \times \tau (\Pi)}$ between terms, indexed by worlds.  The
-  semantics of $\sqsubseteq$ correspond to $\preccurlyeq$ as follows:
-  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow X
-     \preccurlyeq_w Y \]
-\end{definition}
-
-\begin{definition}
-  A lattices justification model is said to make true \tmtextbf{LATTICE} if
-  and only if:
-  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow \mathcal{A}_w
-     (X) \subseteq \mathcal{A}_w (Y) \]
-\end{definition}
-
-Table \ref{logic6} lists the axioms for the logic of lattice justification
-models with the properties we have been investigating:
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
-    \Box_X \psi$ & \\
-    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash X \sqsubseteq Y \rightarrow (X : \phi) \rightarrow Y : \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_X$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow \Box_X \phi \rightarrow \Box_Y \phi$ &
-    \\
-    $\vdash X \sqsubseteq X$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow Y \sqsubseteq Z \rightarrow X
-    \sqsubseteq Z$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow X \sqsubseteq Z \oplus Y$ & $\vdash X
-    \sqsubseteq Y \rightarrow X \sqsubseteq Y \oplus Z$\\
-    $\vdash X \sqsubseteq Z \rightarrow Y \sqsubseteq Z \rightarrow X \oplus Y
-    \sqsubseteq Z$ & \\
-    & \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic6}Lattice Justification Logic}
-\end{table}
-
-\begin{theorem}
-  \label{completeness6}Assuming an infinite store of proposition letters
-  $\Phi$, LJL is sound and weakly complete for lattice justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND}, \tmtextbf{CHOICE} and
-  \tmtextbf{LATTICE}
-\end{theorem}
-
-\begin{proof}
-  Assume $\nvdash \psi$.  Let $\mathbbm{M} \assign \langle W, V, R,
-  \mathcal{A}, \preccurlyeq \rangle$ be the same as the finitary canonical
-  model we initially constructed in Theorem \ref{completeness5}, only
-  $\preccurlyeq$ is defined as:
-  \[ X \preccurlyeq_w Y \Longleftrightarrow w \vdash X \sqsubseteq Y \]
-  We may deduce that there is a world $w \in W$ such that $\mathbbm{M}, w
-  \nvDash \psi$.  This canonical model makes true properties (\ref{fin})
-  through (\ref{union}) we listed in Theorem \ref{completeness5}, as well as a
-  certain new properties:
-
-  \begin{descriptioncompact}
-    \item[6$\preccurlyeq$] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$
-    then $R_Y [v] \subseteq R_X [v]$
-
-    \item[7] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$ then
-    $\mathcal{A}_v (X) \subseteq \mathcal{A}_v (Y)$
-
-    \item[8] If $X \nin \Xi$, then $R_X = W \times W$ and $\mathcal{A}_v (X) =
-    \varnothing$ for all $v \in W$
-
-    \item[9] $\langle \preccurlyeq_v, \oplus \rangle$ is a join-semilattice
-    over $\tau (\Pi)$ for all $v \in W$
-  \end{descriptioncompact}
-
-  As in previous constructions, completeness is achieved by through a series
-  of model refinements.  Note that property 8 has been implicitly true in all
-  of our previous constructions, although we have not been interested in
-  enforcing it to be inherited by model refinements previously.
-
-  We first construct a model $\mathbbm{M}'$ which is bisimular to
-  $\mathbbm{M}$, where (\ref{refl}) is strengthened to a biconditional.  This
-  is done exactly as we proceeded in previous constructions. We note that the
-  notion of ``bisimulation'' here includes that two bisimular worlds $v$ and
-  $u$ must have isomorphic semi-lattices $\preccurlyeq_v$ and
-  $\preccurlyeq_w$.  This is achieved by enforcing that $\preccurlyeq_{v_l}
-  \assign \preccurlyeq_{v_r} \assign \preccurlyeq_v$. As before, we have that
-  $\mathbbm{M}', w \nvDash \psi$ for some world $w \in W'$.
-
-  We next strengthen (6$\preccurlyeq$) to a biconditional.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em} X
-    \preccurlyeq_v Z\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  $\mathbbm{M}''$ is bisimular to $\mathbbm{M}'$ by the same mechanism as the
-  previous construction.  The important feature of this structure is to
-  observe that the converse of (6$\preccurlyeq$) holds:
-  \begin{eqnarray*}
-    R_Y [v] \subseteq R_X [v] & \Longleftrightarrow & \forall Z \in \Xi
-    \forall u_Z \in W'' (v_Q R'_Z u_Z \Longrightarrow v_Q R_X' u_Z)\\
-    & \Longleftrightarrow & \forall Z \in \Xi \forall u_Z \in W'' (v R'_Z
-    \Longrightarrow v_Q R_X u_Z)
-  \end{eqnarray*}
-
-  Our first transformation strengthens (\ref{union}), (6$\preccurlyeq$a) and
-  (6$\preccurlyeq$b) so that they hold for all terms in $\tau (\Pi)$, rather
-  than being restricted to $\Xi$.  To this end define $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}', \preccurlyeq' \rangle$ where $W'$, $R'$
-  and $\preccurlyeq'$ are the same as in $\mathbbm{M}$, but $R'$ and
-  $\mathcal{A}'$ have the following modifications:
-  \begin{eqnarray}
-    R'_Y [v] & \assign & \bigcap_{X \preccurlyeq_v Y} R_X [v] \nonumber\\
-    \mathcal{A}'_v (Y) & \assign & \bigcup_{X \preccurlyeq_v Y} \mathcal{A}'_v
-    (X) \nonumber
-  \end{eqnarray}
-
-\end{proof}
-
-\subsection{Neighborhood Semantics}
-
-Neighborhood semantics were originally developed by Dana Scott and Richard
-Montague in the early 1970s as a generalization of Kripke semantics \
-{\cite{montague_universal_2008,scott_advice_1970}}.  In
-{\cite{fagin_belief_1988}}, Halpern and Fagin adapted neighborhood semantics
-for reasoning about epistemic agents without logical omniscience.  In this
-section will demonstrate how these semantics may be modified so that
-neighborhoods corresponds to the logical consequences of a different knowledge
-bases.  This allows for using logics with neighborhood semantics for
-reasoning about multiple knowledge bases.  A point of distinction of
-neighborhood semantics from JL is that it may be possible that two distinct
-knowledge bases cannot be merged by the agent.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
-  language $\mathcal{L}_N (\Phi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \bot \hspace{1em} | \hspace{1em} \phi \rightarrow \psi
-     \hspace{1em} | \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A :
-     \phi \hspace{1em} | \hspace{1em} K \phi \]
-\end{definition}
-
-Just as previous semantics, ``$\Box \phi$'' is intended to mean that the agent
-has an argument for $\phi$ from some knowledge base.  A novelty we present
-here is that ``$K \phi$'' means that the agent has an argument for $\phi$ from
-some \tmtextit{sound} knowledge base.
-
-\begin{definition}
-  \label{neighborhoodmodels}A {\tmstrong{neighborhood model}} $\mathbbm{M}=
-  \langle W, V, \mathcal{N}, \mathcal{A} \rangle$ has a neighborhood function
-  $\mathcal{N} : W \rightarrow 2^{2^W}$ and a multi-awareness function
-  $\mathcal{A} : W \rightarrow 2^{2^{\mathcal{L}_N (\Phi)}}$
-
-  The semantics for $\vDash$ have the following modifications:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box \phi & \text{iff} & \text{there exists a $U \in
-    \mathcal{N}_w$ where $\mathbbm{M}, v \vDash \phi$ for all $v \in U$}\\
-    \mathbbm{M}, w \vDash K \phi & \text{iff} & \text{there exists a $U \in
-    \mathcal{N}_w$ where $w \in U$ and $\mathbbm{M}, v \vDash \phi$ for all $v
-    \in U$}\\
-    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \bigcup
-    \mathcal{A_w}
-  \end{eqnarray*}
-\end{definition}
-
-Here we modify our previous notion of \tmtextbf{CSQ} and \tmtextbf{SND} to
-match how our semantics are intended for reasoning over multiple bases:
-
-\begin{definition}
-  The following defines properties a neighborhood model may make true:
-
-  \begin{descriptiondash}
-    \item[NCSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff there exists a set
-    $X \in \mathcal{A}_w$ such that } \tmop{Th} (\mathbbm{M}) \cup X \vdash
-    \phi$
-
-    \item[NSND] $\mathbbm{M}, w \vDash K \phi \text{ iff there exists a set $X
-    \in \mathcal{A}_w$ such that $\mathbbm{M}, w \vDash X$ and } \tmop{Th}
-    (\mathbbm{M}) \cup X \vdash \phi$
-  \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
-\end{definition}
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash K \phi \rightarrow \Box \phi$\\
-    $\vdash K \phi \rightarrow \phi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$\\
-    \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi \rightarrow \psi}{\vdash \Box
-      \phi \rightarrow \Box \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi
-      \rightarrow \psi}{\vdash K \phi \rightarrow K \psi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic3}A Neighborhood Logic for \tmtextbf{NCSQ} and
-  {\tmstrong{NSND}}}
-\end{table}
-
-\begin{theorem}
-  Assuming an infinite store of letters $\Phi$, the logic in Table
-  \ref{logic3} is sound and weakly complete for neighborhood semantics making
-  true \tmtextbf{NCSQ} and \tmtextbf{NSND}.
-\end{theorem}
-
-\begin{proof}
-  Assume that $\nvdash \psi$, and define the finitary canonical model
-  $\mathbbm{M}= \langle W, V, \mathcal{K}, \mathcal{N}, \mathcal{A} \rangle$
-  where:
-  \begin{itemizedot}
-    \item $W \assign \text{the maximally consistent sets of subformulae of
-    $\psi$, closed under single negation}$
-
-    \item $V (p) \assign \{v \in W \hspace{1em} | \hspace{1em} p \in v\}$
-
-    \item $\mathcal{K}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
-    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
-    \hspace{1em} K \phi \in w\}$
-
-    \item $\mathcal{N}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
-    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
-    \hspace{1em} \Box \phi \in w\}$
-
-    \item $\mathcal{A}_w \assign \{\{\phi\} \hspace{1em} | \hspace{1em} A :
-    \phi \in w\}$
-  \end{itemizedot}
-  Note that in this model, there are neighborhoods for both knowledge and
-  belief; more work is necessary to find a model based on this one which
-  conforms to the semantics in Definition \ref{neighborhoodmodels}.  For now,
-  assume that $K$ is just another modality governed by the neighborhoods in
-  $\mathcal{K}_w$.  In both neighborhood functions, our idea is that the
-  neighborhoods of $w$ in are supersets $S \supseteq \left\llbracket \phi
-  \right\rrbracket$ where $\Box \phi \in w$ or $K \phi \in w$, respectively.
-
-  There are steps of the inductive proof of the Truth Lemma for this structure
-  which are not obvious nor obviously documented elsewhere.  Assume
-  $\mathbbm{M}, w \vDash \Box \chi$, where the Truth Lemma has been proven to
-  hold for $\chi$; we must show $\Box \chi \in w$.  By our assumption there
-  is some $\phi$ and $S$ where $\Box \phi \in w$ and $S \supseteq \{v \in W
-  \hspace{1em} | \hspace{1em} \phi \in v\}$.  We argue that $\vdash \phi
-  \rightarrow \chi$; for if not then by the finitary Lindenbaum lemma there is
-  some $u \in W$ where $\phi \in u$ and $\chi \nin u$.  Hence $u \in S$ and
-  $\mathbbm{M}, u \nvDash \chi$, a contradiction.  Since $\vdash \phi
-  \rightarrow \chi$ then we know that $\vdash \Box \phi \rightarrow \Box \chi$
-  by our rules, which means that $\Box \chi \in w$ by maximality.
-
-  By the Lindenbaum Lemma we have that there is some $w \in W$ where
-  $\mathbbm{M}, w \nvDash \psi$.  $\mathbbm{M}$ makes true a number of
-  properties:
-  \begin{enumeratenumeric}
-    \item $W$ and $\mathcal{A}_v$ are finite for all $v \in W$, and $\psi \in
-    \bigcup \mathcal{A_w}$ only if $\psi$ is a subformula of $\phi$
-
-    \item $\mathcal{K}_w \subseteq \mathcal{N}_w$
-
-    \item If $S \in \mathcal{K}_w$ then $w \in S$
-
-    \item $\mathbbm{M}, v \vDash A : \phi \rightarrow \Box \phi$ for all $v
-    \in W$
-
-    \item $\mathcal{N}_w$ and $\mathcal{K}_w$ are closed under supersets
-  \end{enumeratenumeric}
-
-  As in the proof of Theorem \ref{completeness1}, we use a bisimulation to
-  move to a model where property (3) is strengthened to (3$'$): for all $S \in
-  \mathcal{N}_w$, $w \in S$ if and only if $S \in \mathcal{K}'_w$.  We defer
-  the reader to {\cite{hansen_bisimulation_2007,pauly_bisimulation_1999}} for
-  details regarding bisimulation in neighborhood semantics.  Define
-  $\mathbbm{M}' \assign \langle W', V', \mathcal{K}', \mathcal{N}',
-  \mathcal{A}' \rangle$ such that:
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$ wher.  $l, r$ its associated canonical
-    injections and $\theta (v_l) \assign \theta (v_r) \assign v$ is a
-    left-inverse of $l, r$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $\mathcal{K}' (v_i) \assign \{S \hspace{1em} | \hspace{1em} v_i \in
-    S \hspace{1em} \& \hspace{1em} \theta [S] \in \mathcal{K_v} \}$ where $i =
-    l, r$
-
-    \item $\mathcal{N}' (v_i) \assign \mathcal{K}' (v_i) \cup \{S \hspace{1em}
-    | \hspace{1em} v_i \nin S \hspace{1em} \& \hspace{1em} \theta [S] \in
-    \mathcal{N_v} \}$ where $i = l, r$
-
-    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
-    (v)$
-  \end{itemizedot}
-
-  If we let $Z \assign \{(v, v_r), (v, v_l) \hspace{1em} | \hspace{1em} v \in
-  W\}$, it is straightforward to verify that $Z$ is a neighborhood
-  bisimulation.  Hence $\mathbbm{M}, w_l \nvDash \psi$.  Along with (3$'$),
-  this model makes true (1), (2), (4).  In fact, in light of ($3'$), we can
-  see that this model does not need $\mathcal{K}'$, and conforms to the
-  semantics in Definition \ref{neighborhoodmodels}.{\hspace*{\fill}}
-
-  As in previous proofs, let $\Lambda$ be the proposition letters occuring in
-  $\psi$ and define an injection $\iota : W' \hookrightarrow \Phi \backslash
-  \Lambda$, assigning a nominal to every world in $\mathbbm{M}'$.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', \mathcal{N}'', \mathcal{A}''
-  \rangle$ such that:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
-      \begin{array}{ll}
-        V' (p) & p \in \Lambda\\
-        \{v\} & p = i (v)\\
-        \varnothing & o / w
-      \end{array} \right.$\\
-      $\bullet$ & $\mathcal{N}''_w \assign \mathcal{N}'_w$ & {\hspace{3em}} &
-      $\bullet$ & $\mathcal{A}''_v \assign \{\partial_v S \hspace{1em} |
-      \hspace{1em} S \in \mathcal{N}'_w \}$
-    \end{tabular}
-  \end{center}
-
-  Where $\partial_v S \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
-  \bigcup \mathcal{A}_v', \text{$\phi$ is a subformula of $\psi$ and}
-  \hspace{1em} S \subseteq \left\llbracket \phi
-  \right\rrbracket^{\mathbbm{M}'} \} \cup \{\neg \iota (u) \hspace{1em} |
-  \hspace{1em} u \nin S\}$.
-
-  As before, this model agrees with $\mathbbm{M}'$ on all subformulae of
-  $\psi$, using the semantics in Definition \ref{neighborhoodmodels}, hence
-  $\mathbbm{M}'', w_l \nvDash \phi$. \
-
-  All that is left is to show \tmtextbf{NCSQ} and \tmtextbf{NSND} from three
-  new properties:
-  \begin{enumerateroman}
-    \item For all words $v$ and all $X \in \mathcal{A}_v''$, $X$ is finite and
-  .  $X = \partial_v S$ for some $S \in \mathcal{N}_v''$
-
-    \item For all $v$ and all $S \in \mathcal{N}_v$, $u \in S$ if and only if
-    $\mathbbm{M}'', u \vDash \bigwedge \partial_v S$
-
-    \item The logic presented in Table \ref{logic3} is sound for
-    $\mathbbm{M}''$
-  \end{enumerateroman}
-  Along with the deduction theorem for $\vdash$, these properties establish
-  \tmtextbf{NCSQ} for this model using the logic of Table \ref{logic3} itself:
-
-  \begin{align*}
-    \text{$\exists X \in \mathcal{A''_v} \text{ s.t. } \tmop{Th}
-    (\mathbbm{M}'') \cup X \vdash \phi$} & {\Longleftrightarrow}\text{$\exists
-    S \in \mathcal{N''_v} \text{ s.t. } \tmop{Th} (\mathbbm{M}'') \cup
-    \partial_v S \vdash \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \tmop{Th} (\mathbbm{M}'') \vdash \bigwedge \partial_v S \rightarrow
-    \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \bigwedge \partial_v S \rightarrow \phi \in \tmop{Th} (\mathbbm{M}'')$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \left\llbracket \bigwedge \partial_v S \right\rrbracket \subseteq
-    \left\llbracket \phi \right\rrbracket$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t.
-    $\forall u \in W$ if } \mathbbm{M}, u \vDash \bigwedge \partial_v S \text{
-    then } \mathbbm{M}, u \vDash \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \mathbbm{M}, u \vDash \phi \text{ for all } u \in S$}\\
-    & {\Longleftrightarrow}{\mathbbm{M}},v{\vDash}\Box{\phi}
-  \end{align*}
-
-  \tmtextbf{NSND} follows from \tmtextbf{NCSQ} and the semantics of Definition
-  \ref{neighborhoodmodels}.
-\end{proof}
-
-It is not too hard to identify the fragment of this logic that governs
-knowledge alone.  The fragment given in Table \ref{logic4} has special
-significance to us, since it governs the notion of knowledge presented in
-{\S}\ref{quantifying}.
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash K \phi \rightarrow \phi$\\
-    \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ &  &  & $\frac{\vdash \phi \rightarrow \psi}{\vdash K \phi
-      \rightarrow K \psi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic4}A knowledge-only neighborhood logic for
-  \tmtextbf{NCSQ} and {\tmstrong{NSND}}}
-\end{table}
-
-\begin{proposition}
-  The knowledge-only logic presented governs the $\Box$-free fragment of the
-  logic in Table \ref{logic3}
-\end{proposition}
-
-This concludes our analysis of knowledge bases using neighborhood semantics.
-
-\subsection{\label{quantifying}Using Modalities to Quantify over Knowledge
-Bases}
-
-\section{Conclusions \& Further Research}
-
-The logic presented in Table \ref{logic1} is a conservative extension of the
-basic modal logic $K$, which means that its decision problem is
-\tmtextsf{PSPACE} hard (a lower bound).  Our finitary completeness proof
-establishes that its complexity is in \tmtextsf{EXP2-TIME} (an upper bound).
-
-Worlds in epistemic logic might correspond to fantastic, pretend scenarios;
-however, it may be desirable for some philosophers to model knowledge about
-imaginary lands.  After all, many children ``know'' a lot about Tolkien's
-{\tmem{middle earth}} or Rowling's {\tmem{Hogwarts}} (the school Harry Potter
-attends).
-
-\bibliographystyle{plain}
-\bibliography{zotero}
-
-\end{document}
+application to naturalized epistemology found in the psychological
+literature.
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "paper"
+%%% End:

### 2010-12-15 lattice_justification.tex
Refactored paper so all sections are seperate documents

--- 2010-12-15 paper.tex
@@
-\documentclass{article}
-\usepackage{geometry,amsmath,amssymb,wasysym,enumerate,bbm,color}
-\geometry{letterpaper}
-
-\usepackage{stmaryrd}
-
-%%%%%%%%%% Start TeXmacs macros
-\newcommand{\assign}{:=}
-\newcommand{\nin}{\not\in}
-\newcommand{\tmem}[1]{{\em #1\/}}
-\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
-\newcommand{\tmstrong}[1]{\textbf{#1}}
-\newcommand{\tmtextbf}[1]{{\bfseries{#1}}}
-\newcommand{\tmtextit}[1]{{\itshape{#1}}}
-\newcommand{\tmtextsf}[1]{{\sffamily{#1}}}
-\newcommand{\tmtextup}[1]{{\upshape{#1}}}
-\newenvironment{descriptioncompact}{\begin{description} }{\end{description}}
-\newenvironment{descriptiondash}{\begin{description} }{\end{description}}
-\newenvironment{enumeratenumeric}{\begin{enumerate}[1.] }{\end{enumerate}}
-\newenvironment{enumerateroman}{\begin{enumerate}[i.] }{\end{enumerate}}
-\newenvironment{itemizedot}{\begin{itemize} \renewcommand{\labelitemi}{$\bullet$}\renewcommand{\labelitemii}{$\bullet$}\renewcommand{\labelitemiii}{$\bullet$}\renewcommand{\labelitemiv}{$\bullet$}}{\end{itemize}}
-\newenvironment{proof}{\noindent\textbf{Proof\ }}{\hspace*{\fill}$\Box$\medskip}
-\definecolor{grey}{rgb}{0.75,0.75,0.75}
-\definecolor{orange}{rgb}{1.0,0.5,0.5}
-\definecolor{brown}{rgb}{0.5,0.25,0.0}
-\definecolor{pink}{rgb}{1.0,0.5,0.5}
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}{Proposition}
-\newtheorem{theorem}{Theorem}
-%%%%%%%%%% End TeXmacs macros
-
-\begin{document}
-
-\title{Epistemic Logics For Knowledge Bases}\author{Matthew P.
-Wampler-Doty}\maketitle
-
-\begin{abstract}
-  In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem
-  proposed a research program for logic of \tmtextit{explicit knowledge}. \
-  Two efforts have since emerged with proposals for logic of explicit
-  knowledge: the \tmtextit{Dynamics of Awareness}
-  {\cite{van_benthem_inference_2009}} and \tmtextit{Justification Logic}
-  {\cite{artemov_introducing_2005}}.  The purpose of this paper is to
-  repurpose various epistemic logics from these previous efforts for reasoning
-  about logical closures over knowledge bases.  The results in this paper are
-  based on previous work carried out in
-  {\cite{wampler-doty_evidentialist_2010}}.
-\end{abstract}
-
-\section{Introduction\label{intro}}
-
-The modern tradition in epistemic logic is to assume knowledge modalities
-conform to the $S 5$ axiom schema.  As noted in
-{\cite{halpern_set-theoretic_1999,rubinstein_modeling_1998}}, the semantics of
-$S 5$ knowledge correspond exactly to partitioning a collection of situations
-into \tmtextit{information sets}, which is the traditional approach in game
-theory and decision theory.  While it is not commonly acknowledged in
-epistemic logic, economists and philosophers accept that traditional decision
-theory is externalist and behaviourist in nature
-(FIXME)
-\footnote{An early essay by
-Amartya Sen on the philosophical foundations of traditional decision theory
-makes the behaviorist reading of decision theory clear
-\cite{sen_behaviour_1973}.  Kaushik Basu also discusses the behaviorist
-nature of decision theory {\cite[pgs. 53--54]{basu_revealed_1980}}. 
-Finally, Donald Davidson appeals to decision theory to motivate an externalist
-epistemology in \cite{davidson_could_1995}.}.
-
-In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem proposed
-a research program to find logics for explicit knowledge, providing the first
-suggestion of an internalist perspective on epistemic logic.  Subsequently,
-Sergei Artemov and Elena Nogina proposed a logic of explicit justification,
-which has come to be known as \tmtextit{Justification Logic} (JL)
-{\cite{artemov_introducing_2005}}, based on Artemov's \tmtextit{Logic of
-Proofs} {\cite{artemov_logic_1994}}.  While the original semantics of JL was
-interpretability into Peano Arithmetic, Melvin Fitting proposed Kripke
-semantics for JL in {\cite{fitting_logic_2005}}.  Recently, Fernando
-Vel\'azquez-Quesada and Johan van Benthem have developed a simpler framework
-for explicit epistemics in {\cite{van_benthem_inference_2009}}, entitled the
-\tmtextit{Dynamics of Awareness}.  This work was based on Joseph Halpern and
-Ronald Fagin's original \tmtextit{Awareness Logic} {\cite{fagin_belief_1987}}.
-
-In this essay we repurpose various externalist logics to take on an
-internalist reading.  The concept of a \tmtextit{knowledge base}, from which
-beliefs may be implicitly deduced, will play a crucial role in our discussion.
-\ We propose this as an avenue for representing foundationalist perspectives
-on epistemology in epistemic logic.  Our philosophical motivation is taken
-from two sources.  The first is Vincent Hendricks in
-{\cite{hendricks_mainstream_2006}}, where he characterizes the principal of
-{\tmem{logical omniscience}} for implicit knowledge in epistemic
-logic{\footnote{We have modified Hendricks' notation here slightly to match
-our own.}}:
-
-\begin{quote}
-  {\tmem{Whenever an agent $\Xi$ knows all of the formulae in $\mathcal{A}$,
-  and $\phi$ follows logically from $\mathcal{A}$, then $\Xi$ [implicitly]
-  knows $\phi$.}}
-\end{quote}
-
-We will design our semantics such that ``$\Box \phi$'' may be equated with
-``$\phi$ follows logically from a knowledge base $\mathcal{A}$,'' which is
-sometimes written as $\phi \in \tmop{Cn} ( \mathcal{A})$ in the artificial
-intelligence literature.  Our second inspiration comes from what Hilary
-Kornblith calls the \tmtextit{the arguments on paper thesis}
-{\cite{kornblith_beyond_1980}}, which he feels characterizes apsychological,
-internalist theories of knowledge:
-
-\begin{quote}
-  Let us suppose that, for any person, it is possible, at least in principle,
-  to list all of the propositions that person believes.  The
-  arguments-on-paper thesis is just the view that a person has a justified
-  belief that a particular proposition is true just in case that proposition
-  appears on the list of propositions that person believes, and either it
-  requires no argument, or a {\tmem{good argument}} can be given for it which
-  takes as premises certain other propositions on the list.
-\end{quote}
-
-Kornblith asserts that foundationalism and coherentism vie for accounts of a
-``good argument'' in the above thesis.  He provides an extensive bibliography
-citing proposals for this principle by a number of 20th century
-epistemologists, including figures such as A.J. Ayer and C.I. Lewis.  The
-rest of Kornblith's paper is devoted to attacking this view and proposing a
-form of naturalized epistemology; we will not address this debate here,
-however.
-
-We adopt a arguments-on-paper-thesis perspective on epistemic logic in this
-paper.  We consider a \tmtextit{good argument} to be a logical derivation
-from propositions present in a knowledge base.  In this fashion, ou.  \
-Special attention will be given to \tmtextit{sound derivations}, which will be
-thought of as a form of knowledge.  In Awareness Logic, we will interpret
-awareness of a formula as membership in a knowledge base.  We prove
-completeness for basic awareness logic and a hybrid logic extension.  Logics
-of multiple knowledge bases are also presented: a simplified form of
-Justification Logic, a logic with neighborhood semantics, an a logic with
-modalities for quantifying over knowledge bases.  We conclude with an
-application to naturalized epistemology found in the psychological literature.
-
-\section{Basic Explicit Logics of Knowledge Bases}
-
-\subsection{Awareness Logic\label{awarenesslogic}}
-
-In this section, we give the explicit semantics to basic awareness logic,
-originally presented in {\cite{fagin_belief_1987}}, with an additional axiom.
-\ One difference in our presentation is the inclusion of a novel letter and a
-superficial change in notation.  This work is inspired by the developments in
-van Benthem and Vel\'azquez-Quesada {\cite{van_benthem_inference_2009}}.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and define the language $\mathcal{L}_A
-  (\Phi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A : \phi \hspace{1em}
-  \]
-\end{definition}
-
-We define the other connectives and modal operators as usual for classical
-modal logics.
-
-\begin{definition}
-  \label{awarenessmodels}An {\tmstrong{awareness model}} $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V : \Phi
-  \cup \{\circlearrowleft\} \rightarrow 2^W$ and an awareness function
-  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$.  We will usually
-  denote $\mathcal{A} (w)$ as $\mathcal{A}_w$.
-
-  Define the semantic entailment relation $\vDash$ where atomic propositions,
-  logical connectives and modality are interpreted as usual.  We employ the
-  following novel definition:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \mathcal{A_w}
-  \end{eqnarray*}
-\end{definition}
-
-The following definition distinguishes us from previously investigations of
-awareness logic:
-
-\begin{definition}
-  Define the ``\tmtextbf{theory of a model} $\mathbbm{M}$'' as:
-  \[ \tmop{Th} (\mathbbm{M}) \assign \{\phi \hspace{1em} | \hspace{1em}
-     \mathbbm{M}, v \vDash \phi \text{ for all } v \in W\} \]
-  We define the following properties that a model $\mathbbm{M}$ may posses:
-
-  \begin{descriptiondash}
-    \item[CSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w \vdash \phi$
-
-    \item[SND] $\mathbbm{M}, w \vDash \circlearrowleft \text{ iff }
-    \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w$
-  \end{descriptiondash}
-
-  Here $\vdash$ is any logical consequence relation which is sound for
-  $\vDash$, making true \tmtextbf{modus ponens} and \tmtextbf{reflection} (ie,
-  $\Gamma \vdash \phi$ if $\phi \in \Gamma$)
-\end{definition}
-
-Neither \tmtextbf{CSQ} nor \tmtextbf{SND} correspond to simple modally
-definable properties.
-
-Intuitively, the \tmtextbf{CSQ} asserts that an agent believes a formula
-$\phi$ if and only if it follows logically from their knowledge base and their
-background knowledge, represented by $\tmop{Th} (\mathbbm{M})$. \
-\tmtextbf{CSQ} is Vincent Hendrik's principle of logical omniscience mentioned
-in {\S}\ref{intro}.
-
-\tmtextbf{SND} asserts that $\circlearrowleft$ corresponds to the agent's
-knowledge base being sound. A sound knowledge base will only render true
-conclusions when used in deductions.  If one considers ``the existance of a
-sound deduction'' sufficient for a kind of knowledge, then $\circlearrowleft$
-is suitable for investigating this notion of epistemology.  That is, if
-$\mathbbm{M}, w \vDash \circlearrowleft \wedge \Box \phi$, then we may
-naturally say that the agent (implicitly) {\tmem{knows}} $\phi$ on the basis
-of $\mathcal{A}_w$, rather than merely {\tmem{believing}} $\phi$ on the basis
-of $\mathcal{A}_w$.
-
-The logic of models making true \tmtextbf{CSQ} and \tmtextbf{SND} is provided
-in Table \ref{logic1}.
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash \Box(\phi \rightarrow \psi) \rightarrow \Box \phi \rightarrow \Box
-    \psi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$\\
-    $\vdash \circlearrowleft \rightarrow \Box \phi \rightarrow \phi$\\
-    \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box \phi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic1}Awareness Logic for \tmtextbf{CSQ} and
-  \tmtextbf{SND}}
-\end{table}
-
-\begin{theorem}
-  \label{completeness1}Assuming an infinite store of proposition letters
-  $\Phi$, the awareness logic presented is sound and weakly complete for
-  awareness models making true \tmtextbf{CSQ} and \tmtextbf{SND}.
-\end{theorem}
-
-\begin{proof}
-  Soundness is straightforward, so we will only address completeness.  Assume
-  $\nvdash \psi$.  Consider the finite canonical model $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A} \rangle$ formed of maximally consistent sets of
-  subformulae of $\phi$ (closed under single negations{\footnote{A discussion
-  of this property may be found in {\cite[pg.
-  243]{blackburn_modal_2001}}.}}), as per the finitary modal completeness
-  proofs found in {\cite[chapter 4.8]{blackburn_modal_2001}} and
-  {\cite[chapter 5]{boolos_logic_1995}}.  Typical presentations do not
-  include awareness, however it is defined intuitively in this case:
-  \[ \phi \in \mathcal{A}_w \Longleftrightarrow A : \phi \in w \]
-  Since $\psi$ is a subformula of itself, we have $\mathbbm{M}, w \nvDash
-  \psi$ for some world $w$ by a finitary {\tmem{Lindenbaum Lemma}} and
-  {\tmem{Truth Theorem}}.  Moreover, it is straightforward to verify that
-  $\mathbbm{M}$ makes true the following properties:
-  \begin{enumeratenumeric}
-    \item $W$ and $\mathcal{A}_v$ are finite, and $\psi \in \mathcal{A}_v$
-    only if $\psi$ is a (possibly negated) subformula of $\phi$
-
-    \item if $\mathbbm{M}, v \vDash A : \psi$ then $\mathbbm{M}, v \vDash \Box
-    \psi$
-
-    \item if $\mathbbm{M}, v \vDash \circlearrowleft$ then $v R v$
-  \end{enumeratenumeric}
-
-  We next produce a bisimular{\footnote{The notion of bisimulation is
-  discussed at length in {\cite[chapter 2.2]{blackburn_modal_2001}}.  We
-  note that the basic definition and all of the usual theorems (modal
-  equivalence, Henessy Milner, etc.) may be generalized to awareness models in
-  a straightforward fashion. }} model $\mathbbm{M}'$ which makes true (1), (2)
-  and a stronger from of (3):
-
-  {\hspace*{\fill}}\begin{tabular}{ll}
-    \tmtextbf{3$'$.} & $\mathbbm{M}', v \vDash \circlearrowleft$ iff $v R v$
-  \end{tabular}{\hspace*{\fill}}
-
-  To this end define $\mathbbm{M}' \assign \langle W', V', R', \mathcal{A}'
-  \rangle$ such that{\footnote{Throughout this article, we use $l$ and $r$ to
-  denote the two canonical injections associated with the coproduct $W \uplus
-  W$. We will use $v_l$ and $v_r$ as the shorthand for $l (v)$ and $r (v)$
-  respectively.}}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $R' \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v R
-    u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em} \mathbbm{M},
-    v \vDash \circlearrowleft\}$
-
-    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
-    (v)$
-  \end{itemizedot}
-
-  It is straightforward to verify that $\mathbbm{M}'$ makes true the desired
-  properties.  Let $Z \assign \{(v, v_l), (v, v_r) \hspace{1em} |
-  \hspace{1em} v \in W\}$.  then $Z$ is a bisimulation between $\mathbbm{M}$
-  and $\mathbbm{M}'$.  Therefore we know there is some $w \in W$ such that
-  $\mathbbm{M}', w_l \nvDash \psi$ and $\mathbbm{M}', w_r \nvDash \psi$.
-
-  Finally we construct a model $\mathbbm{M}''$ which agrees with
-  $\mathbbm{M}'$ for all subformulae of $\psi$, which makes true
-  \tmtextbf{CSQ} and \tmtextbf{SND}.  Let $\Lambda$ be the set of proposition
-  letters occuring in $\psi$.  We will make use members of $\Phi \backslash
-  \Lambda$ as {\tmem{nominals}}, as per the tradition in hybrid logic.  This
-  is possible since both $W'$ and $\Lambda$ are finite and $\Phi$ is infinite
-  by hypothesis.  Let $\iota : W \uplus W \hookrightarrow \Phi \backslash
-  \Lambda$ be an injection assigning a fresh nominal associated with each
-  world in $\mathbbm{M}'$.  Now define $\mathbbm{M}'' \assign \langle W'',
-  V'', R'', \mathcal{A}'' \rangle$, where:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
-      \begin{array}{ll}
-        V' (p) & p \in \Lambda\\
-        \{v\} & p = \iota (v)\\
-        \varnothing & o / w
-      \end{array} \right.$\\
-      $\bullet$ & $R'' \assign R'$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}''_v \assign \{\phi \hspace{1em} | \phi \in \mathcal{A}'_v
-      \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em} \neg v R' u\}$
-    \end{tabular}
-  \end{center}
-
-  By induction we have that for every subformula $\phi$ of $\psi$ that
-  $\mathbbm{M}', v \vDash \phi$ if and only if $\mathbbm{M}'', v \vDash \phi$,
-  hence $\mathbbm{M}'', w_l \nvDash \psi$.
-
-  All that is left to show is that $\mathbbm{M}''$ makes true \tmtextbf{CSQ}
-  and \tmtextbf{SND}.  $\mathbbm{M}''$ has three further properties:
-  \begin{enumerateroman}
-    \item $\mathcal{A}''_v$ is finite for all worlds $v$
-
-    \item  $v R' u$ if and only if $\mathbbm{M}'', u \vDash \bigwedge
-    \mathcal{A}'' (v)$
-
-    \item The logic presented in Table \ref{logic1} is sound for
-    $\mathbbm{M}''$
-  \end{enumerateroman}
-  From (ii) and the fact that $\mathbbm{M}'$ makes true (3$'$), we have
-  \tmtextbf{SND} for $\mathbbm{M}''$.
-
-  All that is left is to demonstrate \tmtextbf{CSQ} for some sound logic.  We
-  will use the logic in Table \ref{logic1} itself.  From (i), (ii), (iii),
-  and the \tmtextit{deduction theorem} for modal logic, we have the following
-  line of reasoning:
-
-  \begin{align*}
-    Th({\mathbbm{M}}''){\cup}\mathcal{A}''_v{\vdash}{\phi} &
-    {\Longleftrightarrow}Th({\mathbbm{M}}''){\vdash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\\
-    &
-    {\Longleftrightarrow}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}{\in}Th({\mathbbm{M}}'')\\
-    &
-    {\Longleftrightarrow}{\mathbbm{M}}'',u{\vDash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\text{
-    for all $u \in W''$}\\
-    & {\Longleftrightarrow}\text{ for all $u \in W''$, if
-    }{\mathbbm{M}}'',u{\vDash}\mathcal{A}''_v\text{ then
-    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
-    & {\Longleftrightarrow}\text{ for all $u \in W''$, if }v R 'u \text{ then
-    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
-    & {\Longleftrightarrow}{\mathbbm{M}}'',v{\models}\Box{\phi}
-  \end{align*}
-\end{proof}
-
-\subsection{Hybrid Awareness Logic}
-
-The method of the above completeness proof makes implicit use of concepts from
-hybrid logic{\footnote{Hybrid logic was first presented in
-{\cite{prior_revised_1969}} and later formally developed in
-{\cite{bull_approach_1970}}.}}.  In this section we adapt hybrid logic and
-show that it is a complete for reasoning about knowledge bases.  We note that
-because of the increased expressive power of hybrid logic, our completeness
-theorem is simpler.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
-  language $\mathcal{L}_H (\Phi, \Psi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} i \in \Psi \hspace{1em} | \hspace{1em} \bot \hspace{1em} |
-     \hspace{1em} \phi \rightarrow \psi \hspace{1em} | \hspace{1em} \Box \phi
-     \hspace{1em} | \hspace{1em} A : \phi \hspace{1em} | \hspace{1em} \forall
-     \phi \]
-\end{definition}
-
-Our approach in hybrid logic is to employ a universal modality along with
-nominals.  This framework presents a logic where the agent may reason about
-various labeled scenarios.  Scenarios may be multiply labeled or not labeled
-at all.  From these intuitions we have the following definition:
-
-\begin{definition}
-  \label{hybridsemantics}Let a \tmtextbf{hybrid model} $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A}, \ell \rangle$ be an awareness model as in Definition
-  \ref{awarenessmodels}, along with a partial labeling function $\ell : \Psi
-  \nrightarrow W$
-
-  The semantics for $\vDash$ are the same as in Definition
-  \ref{awarenessmodels}, only we have
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \forall \phi & \text{iff} & \forall v \in
-    W.\mathbbm{M}, v \vDash \phi\\
-    \mathbbm{M}, w \vDash i & \text{iff} & \ell (i) = w
-  \end{eqnarray*}
-\end{definition}
-
-The other connectives and operators are defined as usual, although we employ a
-few special shorthands:
-
-\begin{definition}
-  We employ the following special abbreviations:
-  \begin{eqnarray}
-    \text{\tmtextup{@}}_i \phi \assign \forall (i \rightarrow \phi)
-    \hspace{2em} & \exists \phi \assign \neg \forall \neg \phi \hspace{3em} &
-    \circlearrowleft_i \assign \diamondsuit i \nonumber
-  \end{eqnarray}
-\end{definition}
-
-This gives rise to a validity reflecting one of the axioms we saw in
-{\S}\ref{awarenesslogic}:
-\[ \vDash \circlearrowleft_i \rightarrow \Box \phi \rightarrow
-   \text{\tmtextup{@}}_i \phi \]
-This can be read as ``If the agent's knowledge base is sound at world $i$,
-then if they can deduce something from their knowledge base, what they deduce
-must be true at world $i$.'.  In a way, this may be considered as
-{\tmem{relativising}} knowledge particular named situations.
-
-The semantics in Definition \ref{hybridsemantics} obviates the \tmtextbf{SND}
-principle we previously presented, since there is no explicit
-$\circlearrowleft$ symbol in this setting. \tmtextbf{CSQ} still makes sense
-without modification, however.  The following gives a logic for hybrid models
-making true \tmtextbf{CSQ}:
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & $\vdash \forall (\phi
-    \rightarrow \psi) \rightarrow \forall \phi \rightarrow \forall \psi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & $\vdash \forall
-    \phi \rightarrow \phi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & $\vdash \forall \phi \rightarrow
-    \forall \forall \phi$\\
-    $\vdash \Box(\phi \rightarrow \psi) \rightarrow \Box \phi \rightarrow \Box
-    \psi$ & $\vdash \exists \phi \rightarrow \forall \exists \phi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$ & $\vdash \forall \phi \rightarrow
-    \Box \phi$\\
-    & $\vdash i \rightarrow \phi \rightarrow \text{\tmtextup{@}}_i \phi$\\
-    & \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi}{\vdash \Box \phi}$ &
-      {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \forall \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic2}Hybrid Awareness Logic for \tmtextbf{CSQ}}
-\end{table}
-
-\begin{theorem}
-  \label{completeness2}Assuming an infinite store of nominals $\Psi$, the
-  hybrid awareness logic presented is sound and weakly complete for all hybrid
-  models making true \tmtextbf{CSQ}.
-\end{theorem}
-
-\begin{proof}
-  As before, soundness is trivial.  Completeness is based on a modification
-  of techniques found in {\cite[chapter 5]{boolos_logic_1995}}.  Assume
-  that $\nvdash \psi$ and let $\Sigma_0$ be the set of subformulae of $\psi$,
-  and let $\Upsilon$ be the set of nominals occuring in $\psi$.  Define:
-
-  \begin{align*}
-    {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{{\forall}{\phi}{\hspace{1em}}|{\hspace{1em}}\Box{\phi}{\in}{\Sigma}_0\}\\
-    {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{\text{@}_i{\phi}{\hspace{1em}},i{\rightarrow}{\phi}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1{\hspace{1em}}\&{\hspace{1em}}i{\in}{\Upsilon}\}\\
-    {\Sigma}_3 &
-    {\assign}{\Sigma}_2{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_2\}
-  \end{align*}
-
-  It is easy to see that $\Sigma_3$ is finite and closed under subformulae and
-  single negations. Let $\mathbbm{M}= \langle W, V, R_{\Box}, \sim_{\forall},
-  \mathcal{A} \rangle$ be the finite cannonical model formed of maximally
-  consistent subsets of $\Sigma_3$, where everything is defined as usual,
-  except $\sim_{\forall}$, which obeys the following specification:
-
-  \begin{align*}
-    w {\sim}_{{\forall}}v & {\Longleftrightarrow}(({\forall}{\phi}){\in}w
-    {\Longleftrightarrow}({\forall}{\phi}){\in}v)
-  \end{align*}
-
-  This model makes true the following properties:
-  \begin{enumerateroman}
-    \item $\sim_{\forall}$ is an equivalence relation
-
-    \item $R_{\Box} \subseteq \sim_{\forall}$
-
-    \item In each equivalence class specified by $\sim_{\forall}$, there is at
-    most one world making true $i$ for all $i \in \Upsilon$
-  \end{enumerateroman}
-  As in our previous construction we have that there is some world $w$ where
-  $\mathbbm{M}, w \nvDash \psi$.  Let $\mathbbm{M}^1 = \langle W', V',
-  R_{\Box}', \sim_{\forall}', \mathcal{A}' \rangle$ be the submodel generated
-  by $\{w\}$; we have that $\mathbbm{M}', w \nvDash \psi$ (see {\cite[chapter
-  2.1]{blackburn_modal_2001}} for details on generated submodels).  In this
-  model $\forall$ is a universal modality and either $\left\llbracket i
-  \right\rrbracket^{\mathbbm{M}'} = \varnothing$ or $\left\llbracket i
-  \right\rrbracket^{\mathbbm{M}'} =\{v\}${\footnote{As per the usual
-  convention, here $\left\llbracket \phi \right\rrbracket^{\mathbbm{M}}$
-  denotes $\{w \in W \hspace{1em} | \hspace{1em} \mathbbm{M}, w \vDash
-  \phi\}$.  We will drop $\mathbbm{M}$ where it is unambiguous.}}. Since the
-  store $\Psi$ of nominals is infinite and $\Upsilon$ is finite, we have that
-  $\Psi \backslash \Upsilon$ is infinite, so there is some injection $\iota :
-  W' \hookrightarrow \Psi \backslash \Upsilon$ which assigns a fresh nominal
-  to every world.  Let $\mathbbm{M}'' = \langle W'', V'', R'', \mathcal{A}'',
-  \ell \rangle$, where:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign V' (p)$\\
-      $\bullet$ & $R'' \assign R'_{\Box}$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}'' (v) \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
-      \mathcal{A}' (v)\} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
-      \neg v R' u\}$\\
-      \begin{tabular}{ll}
-        $\bullet$ & $\ell (i) \assign \left\{ \begin{array}{ll}
-          w & i \in \Upsilon \hspace{1em} \& \hspace{1em} \mathbbm{M}, w
-          \vDash i\\
-          \iota^{- 1} (i) & i \in \iota [W]\\
-          \text{undefined} & \text{o/w}
-        \end{array} \right.$
-      \end{tabular} & $R'' \assign R'_{\Box}$ &  &  & 
-    \end{tabular}
-  \end{center}
-
-  The the worlds is $\mathbbm{M}'$ and $\mathbbm{M}''$ agree on all
-  subformulae of $\psi$, hence $\mathbbm{M}'', w \nvDash \psi$. The same
-  reasoning as in the proof of Theorem \ref{completeness1} establishes and
-  that the logic in Table \ref{logic2} itself is sound for $\mathbbm{M}''$ and
-  makes true \tmtextbf{CSQ}, establishing completeness.
-\end{proof}
-
-\section{Logics of Multiple Knowledge Bases}
-
-So far, we have only dealt with systems that reason over a single knowledge
-base.  In this section, we present various logics for reasoning over multiple
-knowledge bases.
-
-\subsection{Simple Justification Logic}
-
-Justification Logic (JL) was originally developed by Artemov as the
-\tmtextit{Logic of Proofs} (LP) {\cite{artemov_logic_1994}}.  Its original
-purpose was to provide a framework for reasoning about explicit provability in
-Peano Arithmetic.  The first introduction of Justification Logic can be found
-in {\cite{artemov_introducing_2005}}, where Artemov and Nogina propose LP as a
-logic for reasoning about evidence.  In {\cite{fitting_logic_2005}}, Melvin
-Fitting provided JL with Kripke model based semantics.
-
-The principle innovation of LP/JL is to extend awareness logic, such that
-awareness operations are now \tmtextit{proof terms}.  Informally, we say that
-``a proof term $X$ witnesses proposition $\phi$'', denoted ``$X : \phi$'',
-whenever $X$ represents a proof of $\phi$.  Proofs may have
-{\tmstrong{multiple-conclusions}} in this system, so it is possible that $X :
-\phi$ and $X : \psi$ can be true where $\phi \neq \psi$.  In Fitting's Kripke
-semantics, $X : \phi$ means that $\phi$ is in awareness set corresponding to
-$X$.  Proof terms are thought be operating in a \tmtextit{multi-conclusion}
-proof system, so the same proof term may witness many different propositions.
-
-The logics LP/JL include operators over proofs terms, so that new proof terms
-may be assembled.  One operation of particular interest to us is
-{\tmem{choice}}, denoted $\oplus$.  The expression ``$X \oplus Y : \phi$''
-denotes that either $X$ or $Y$ are proofs witnessing $\phi$.  There are other
-operations which correspond to \tmtextit{modus ponens} and
-\tmtextit{proof-theoretic reflection}, however we do not consider these
-operations here.
-
-In this section we consider a simplified form of JL suitable for reasoning
-over multiple knowledge bases, which we call \tmtextit{simple justification
-logic} (SJL). However, instead of thinking of terms as representing proofs, we
-use them to represent knowledge bases. This is in the spirit of JL as a logic
-of evidence: we consider each knowledge base to be a corpus of evidence. \
-Each term ``names'' a different knowledge base at a particular world.  Terms
-may not refer to the same knowledge base at different worlds, just as in how
-in awareness logic the agent need not be aware of the same formulae at
-different worlds.  Finally, we will make use of JL's {\tmem{choice}} operator
-as a mechanism for forming the union of knowledge bases, creating new ones.
-
-\begin{definition}
-  Let $\Pi$ be a set of primitive terms.  Define $\tau (\Pi)$ with the
-  following grammar:
-  \[ X \hspace{1em} : : = \hspace{1em} t \in \Pi \hspace{1em} | \hspace{1em} X
-     \oplus Y \]
-
-  Let $\Phi$ be a set of letters and $\Pi$ a set of primitive terms, and
-  define the language $\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi \]
-  where $X \in \tau (\Pi)$
-\end{definition}
-
-\begin{definition}
-  \label{justmodels}A {\tmstrong{simple justification model}} $\mathbbm{M}=
-  \langle W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V
-  : \Phi \cup \{\circlearrowleft_X \hspace{1em} | \hspace{1em} X \in \tau
-  (\Pi)\} \rightarrow 2^W$, an indexed relation $R : \tau (\Pi) \rightarrow
-  2^{W \times W}$, along with a modified awareness function $\mathcal{A} : W
-  \times \tau (\Pi) \rightarrow 2^{\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)}$. \
-  In practice we will denote $\mathcal{A} (w, X)$ by a curried shorthand,
-  namely $\mathcal{A}_w (X)$.
-
-  The semantics for $\vDash$ have the following modifications:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box_X \phi & \text{iff} & \text{for all $v \in W$
-    where $w R_X v$ we have $\mathbbm{M}, v \vDash v$}\\
-    \mathbbm{M}, w \vDash X : \phi & \text{iff} & \phi \in \mathcal{A}_w (X)
-  \end{eqnarray*}
-\end{definition}
-
-\begin{definition}
-  The following defines properties a simple justification model may make true:
-
-  \begin{descriptiondash}
-    \item[JCSQ] $\mathbbm{M}, w \vDash \Box_X \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w (X) \vdash \phi$
-
-    \item[JSND] $\mathbbm{M}, w \vDash \circlearrowleft_X \text{ iff
-    $\mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w (X)$}$
-
-    \item[CHOICE] $\mathcal{A}_w (X \oplus Y) = \mathcal{A}_w (X) \cup
-    \mathcal{A}_w (Y)$
-  \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
-\end{definition}
-
-The above semantics are similar to the ones given in previous sections. \
-\tmtextbf{JCSQ} is the same as \tmtextbf{CSQ} from {\S}\ref{awarenesslogic},
-only it is relativized to a knowledge base denoted by $X$ at $w$.  The
-awareness logic of knowledge bases is special case of simple justification
-logic where there is only one term.
-
-Simplified justification logic is given in Table \ref{logic5}.  We assert
-without proof that this is a conservative extension of the awareness logic in
-{\S}\ref{awarenesslogic}.
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
-    \Box_X \psi$ & \\
-    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash (X \oplus Y : \phi) \rightarrow X : \phi$ & $\vdash (X \oplus Y :
-    \phi) \rightarrow Y : \phi$\\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_X$ &
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_Y$\\
-    $\vdash \Box_X \phi \rightarrow \Box_{X \oplus Y} \phi$ & \\
-    $\vdash \Box_{X \oplus X} \phi \rightarrow \Box_X \phi$ & $\vdash \Box_{(X
-    \oplus X) \oplus Y} \phi \rightarrow \Box_{X \oplus Y} \phi$ \\
-    $\vdash \Box_{X \oplus Y} \phi \rightarrow \Box_{Y \oplus X} \phi$ &
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{(Y \oplus X)
-    \oplus Z} \phi$\\
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{X \oplus (Y
-    \oplus Z)} \phi$ & \\
-    & \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic5}Simple Justification Logic}
-\end{table}
-
-\begin{theorem}
-  \label{completeness5}Assuming an infinite store of proposition letters
-  $\Phi$, SJL is sound and weakly complete for simple justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND} and \tmtextbf{CHOICE}
-\end{theorem}
-
-\begin{proof}
-  As in the previous proofs, we only show completeness.  Assume that $\nvdash
-  \psi$.  Let $\Xi \subseteq \tau (\Pi)$ be all of the subterms occurring in
-  $\psi$; we assume that $\Xi$ is non-empty, since otherwise we may obtain the
-  theorem via the usual completeness theorem for classical propositional
-  logic. Let $\Sigma_0$ be the subformulae of $\psi$.  Define:
-
-  \begin{align*}
-    {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{\Box_Y{\phi}{\hspace{1em}}|{\hspace{1em}}\Box_X{\phi}{\in}{\Sigma}_0{\hspace{1em}}\&{\hspace{1em}}Y{\in}{\Xi}\}\\
-    {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1\}
-  \end{align*}
-
-  As in the proof of Theorem \ref{completeness2}, it is simple to verify that
-  $\Sigma_2$ is closed under subformulae and single negations.  Let
-  $\mathbbm{M} \assign \langle W, V, R, \mathcal{A} \rangle$ be the finite
-  cannonical model formed of maximally consistent subsets of $\Sigma_2$, where
-  $V$ and $\mathcal{A}$ are defined as usual, and $R : \Xi \rightarrow 2^{W
-  \times W}$ is defined by:
-  \[ w R_X v \Longleftrightarrow \{\phi \hspace{1em} | \hspace{1em} \Box_X
-     \phi \in w\} \subseteq v \]
-  As in previous constructions we may prove the usual Lindenbaum and Truth
-  Lemmas an use them obtain a world $w \in W$ where $\mathbbm{M}, w \nvDash
-  \psi$.
-
-  Next, define an operator $\twonotes : \tau (\Pi) \rightarrow 2^{\Pi}$ where:
-  \[ \twonotes (X) \assign \{t \in \Pi \hspace{1em} | \hspace{1em} t \text{
-     occurs in } X\} \]
-  In other words, $\twonotes (X)$ is the set of atomic terms in $X$.  As in
-  our construction for Theorem \ref{completeness1}, $\mathbbm{M}$ makes true
-  certain properties, along with some new properties:
-  \begin{enumeratenumeric}
-    \item \label{fin}$W$ and $\mathcal{A}_v (X)$ are finite, and $\phi \in
-    \mathcal{A}_v (X)$ only if $\phi \in \Sigma_2$
-
-    \item if $\mathbbm{M}, v \vDash X : \phi$ then $\mathbbm{M}, v \vDash
-    \Box_X \phi$
-
-    \item \label{refl}if $\mathbbm{M}, v \vDash \circlearrowleft_X$ then $v
-    R_X v$
-
-    \item \label{sndness}For all $X \oplus Y \in \Xi$, $\mathbbm{M}, v \vDash
-    \circlearrowleft_{X \oplus Y}$ if and only if $\mathbbm{M}, v \vDash
-    \circlearrowleft_X$ and $\mathbbm{M}, v \vDash \circlearrowleft_Y$
-
-    \item \label{union}For all $X \oplus Y \in \Xi$, $\mathcal{A}_v (X \oplus
-    Y) = \mathcal{A}_v (X) \cup \mathcal{A}_v (Y)$
-
-    \item \label{sub}For all $X, Y \in \Xi$, if $\twonotes (X) \subseteq
-    \twonotes (Y)$ then $R_Y \subseteq R_X$
-  \end{enumeratenumeric}
-  As in our previous constructions, it is necessary to refine this model using
-  bisimulations to achieve properties which are not modally definable.  In
-  particular, we shall strengthen (\ref{refl}) to a biconditional and
-  (\ref{sub}) to:
-
-  \begin{center}
-    \begin{tabular}{ll}
-      \tmtextbf{6$'$.} & For all $X, Y \in \Xi$, $R_{X \oplus Y} = R_X \cap
-      R_Y$
-    \end{tabular}
-  \end{center}
-
-  We first strengthen (\ref{refl}) by constructing $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}' \rangle$, just as in Theorem
-  \ref{completeness1}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $R'_X \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v
-    R_X u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em}
-    \mathbbm{M}, v \vDash \circlearrowleft_X \}$
-
-    \item $\mathcal{A}' (v_l, X) \assign \mathcal{A}' (v_r, X) \assign
-    \mathcal{A} (v, X)$
-  \end{itemizedot}
-  The same bisimulation relation $Z$ previously given suffices.
-
-  We next make a strengthened the model where (\ref{sub}$'$) holds.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that{\footnote{Let $\{i_X \hspace{1em} | \hspace{1em} X \in \Xi\}$ be the
-  family of canonical injections into the coproduct $\uplus_{\Xi} W$. As per
-  our previous convention, we use $v_X$ as shorthand for $i_X (v)$.}}:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em}
-    \twonotes (X) \subseteq \twonotes (Z)\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  Note that this construction makes use of the assumption that $\Xi$ is
-  non-empty.  Let $Z \assign \{(v, v_X) \hspace{1em} | \hspace{1em} X \in \Xi
-  \hspace{1em} \& \hspace{1em} v \in W' \}$; it is straightforward to prove
-  that $Z$ is a bisimulation between $\mathbbm{M}'$ and $\mathbbm{M}''$, for
-  all relations corresponding to terms $X \in \Xi$. Hence $\mathbbm{M}'', w_X
-  \nvDash \psi$ for some $w_X \in W''$.  In addition, $\mathbbm{M}''$
-  inherits (\ref{fin}) through (\ref{sub}) from $\mathbbm{M}'$, as well as the
-  converse of (\ref{refl}).  Next observe, forall $X \oplus Y \in \Xi$:
-  \begin{eqnarray*}
-    \text{$(v_V, u_Z) \in R''_X \cap R''_Y$} & \Longleftrightarrow & \exists Z
-    \in \Xi . \text{$v R'_Z u \hspace{1em} \& \hspace{1em} \twonotes (X)
-    \subseteq \twonotes (Z) \hspace{1em} \& \hspace{1em} \twonotes (Y)
-    \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X) \cup \twonotes (Y) \subseteq \twonotes
-    (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X \oplus Y) \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow &  \text{$(v_V, u_Z) \in R''_{X \oplus Y}$}
-  \end{eqnarray*}
-  We now turn to our final construction. As in previous constructions, let
-  $\iota : W'' \hookrightarrow \Phi \backslash \Psi$ be an injection assigning
-  fresh nominals to worlds.  Define $\mathbbm{M}''' \assign \langle W''',
-  V''', R''', \mathcal{A}''' \rangle$ just as in the final construction in the
-  proof of Theorem \ref{completeness1}, except that $R'''_X$ and
-  $\mathcal{A}_v''' (X)$ are defined inductively as follows:
-
-  \begin{center}
-    \begin{tabular}{lll}
-      $\bullet$ & $R'''_t \assign \left\{ \begin{array}{ll}
-        R''_t & t \in \Xi\\
-        W''' \times W''' & o / w
-      \end{array} \right.$ & \\
-      $\bullet$ & $R'''_{X \oplus Y} \assign R'''_X \cap R'''_Y$ & \\
-      &  & \\
-      $\bullet$ & $\mathcal{A}'''_v (t) \assign \{\phi \hspace{1em} | \phi \in
-      \mathcal{A}''_v \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
-      \neg v R'''_t u\}$ & where $t \in \Pi$\\
-      $\bullet$ & $\mathcal{A}'''_v (X \oplus Y) \assign \mathcal{A}'''_v (X)
-      \cup \mathcal{A}'''_v (Y)$ & 
-    \end{tabular}
-  \end{center}
-
-  Induction over complexity of subformulae $\phi$ of $\psi$ yields
-  $\mathbbm{M}'', w \vDash \phi \Longleftrightarrow \mathbbm{M}''', w \vDash
-  \phi$, so we know that there is some world $w \in W'''$ such that
-  $\mathbbm{M}''', w \nvDash \psi$.  All that is left is to illustrate that
-  $\mathbbm{M}'''$ has the properties we desire.
-
-  First note that by definition, $\mathbbm{M}'''$ makes true
-  \tmtextbf{CHOICE}.  Next, an induction argument on the complexity of a
-  terms $X$, making essential use of (\ref{sub}$'$), yields:
-  \[ u R_X''' v \Longleftrightarrow \mathbbm{M}''', v \vDash \bigwedge
-     \mathcal{A}'''_v (X) \]
-  With this, $\mathbbm{M}'''$ makes true \tmtextbf{JSND} since it inherits
-  (\ref{refl}).  Finally, we note that we may repeat our previous arguments
-  from Theorem \ref{completeness1} to prove \tmtextbf{JCSQ}.
-\end{proof}
-
-\subsection{Lattice Justification Logic}
-
 {\color{red} NOTE.  THIS SECTION HAS SOME SERIOUS PROBLEMS AND IT'S PROBABLY
@@
 \end{proof}
-
-\subsection{Neighborhood Semantics}
-
-Neighborhood semantics were originally developed by Dana Scott and Richard
-Montague in the early 1970s as a generalization of Kripke semantics \
-{\cite{montague_universal_2008,scott_advice_1970}}.  In
-{\cite{fagin_belief_1988}}, Halpern and Fagin adapted neighborhood semantics
-for reasoning about epistemic agents without logical omniscience.  In this
-section will demonstrate how these semantics may be modified so that
-neighborhoods corresponds to the logical consequences of a different knowledge
-bases.  This allows for using logics with neighborhood semantics for
-reasoning about multiple knowledge bases.  A point of distinction of
-neighborhood semantics from JL is that it may be possible that two distinct
-knowledge bases cannot be merged by the agent.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
-  language $\mathcal{L}_N (\Phi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \bot \hspace{1em} | \hspace{1em} \phi \rightarrow \psi
-     \hspace{1em} | \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A :
-     \phi \hspace{1em} | \hspace{1em} K \phi \]
-\end{definition}
-
-Just as previous semantics, ``$\Box \phi$'' is intended to mean that the agent
-has an argument for $\phi$ from some knowledge base.  A novelty we present
-here is that ``$K \phi$'' means that the agent has an argument for $\phi$ from
-some \tmtextit{sound} knowledge base.
-
-\begin{definition}
-  \label{neighborhoodmodels}A {\tmstrong{neighborhood model}} $\mathbbm{M}=
-  \langle W, V, \mathcal{N}, \mathcal{A} \rangle$ has a neighborhood function
-  $\mathcal{N} : W \rightarrow 2^{2^W}$ and a multi-awareness function
-  $\mathcal{A} : W \rightarrow 2^{2^{\mathcal{L}_N (\Phi)}}$
-
-  The semantics for $\vDash$ have the following modifications:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box \phi & \text{iff} & \text{there exists a $U \in
-    \mathcal{N}_w$ where $\mathbbm{M}, v \vDash \phi$ for all $v \in U$}\\
-    \mathbbm{M}, w \vDash K \phi & \text{iff} & \text{there exists a $U \in
-    \mathcal{N}_w$ where $w \in U$ and $\mathbbm{M}, v \vDash \phi$ for all $v
-    \in U$}\\
-    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \bigcup
-    \mathcal{A_w}
-  \end{eqnarray*}
-\end{definition}
-
-Here we modify our previous notion of \tmtextbf{CSQ} and \tmtextbf{SND} to
-match how our semantics are intended for reasoning over multiple bases:
-
-\begin{definition}
-  The following defines properties a neighborhood model may make true:
-
-  \begin{descriptiondash}
-    \item[NCSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff there exists a set
-    $X \in \mathcal{A}_w$ such that } \tmop{Th} (\mathbbm{M}) \cup X \vdash
-    \phi$
-
-    \item[NSND] $\mathbbm{M}, w \vDash K \phi \text{ iff there exists a set $X
-    \in \mathcal{A}_w$ such that $\mathbbm{M}, w \vDash X$ and } \tmop{Th}
-    (\mathbbm{M}) \cup X \vdash \phi$
-  \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
-\end{definition}
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash K \phi \rightarrow \Box \phi$\\
-    $\vdash K \phi \rightarrow \phi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$\\
-    \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi \rightarrow \psi}{\vdash \Box
-      \phi \rightarrow \Box \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi
-      \rightarrow \psi}{\vdash K \phi \rightarrow K \psi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic3}A Neighborhood Logic for \tmtextbf{NCSQ} and
-  {\tmstrong{NSND}}}
-\end{table}
-
-\begin{theorem}
-  Assuming an infinite store of letters $\Phi$, the logic in Table
-  \ref{logic3} is sound and weakly complete for neighborhood semantics making
-  true \tmtextbf{NCSQ} and \tmtextbf{NSND}.
-\end{theorem}
-
-\begin{proof}
-  Assume that $\nvdash \psi$, and define the finitary canonical model
-  $\mathbbm{M}= \langle W, V, \mathcal{K}, \mathcal{N}, \mathcal{A} \rangle$
-  where:
-  \begin{itemizedot}
-    \item $W \assign \text{the maximally consistent sets of subformulae of
-    $\psi$, closed under single negation}$
-
-    \item $V (p) \assign \{v \in W \hspace{1em} | \hspace{1em} p \in v\}$
-
-    \item $\mathcal{K}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
-    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
-    \hspace{1em} K \phi \in w\}$
-
-    \item $\mathcal{N}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
-    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
-    \hspace{1em} \Box \phi \in w\}$
-
-    \item $\mathcal{A}_w \assign \{\{\phi\} \hspace{1em} | \hspace{1em} A :
-    \phi \in w\}$
-  \end{itemizedot}
-  Note that in this model, there are neighborhoods for both knowledge and
-  belief; more work is necessary to find a model based on this one which
-  conforms to the semantics in Definition \ref{neighborhoodmodels}.  For now,
-  assume that $K$ is just another modality governed by the neighborhoods in
-  $\mathcal{K}_w$.  In both neighborhood functions, our idea is that the
-  neighborhoods of $w$ in are supersets $S \supseteq \left\llbracket \phi
-  \right\rrbracket$ where $\Box \phi \in w$ or $K \phi \in w$, respectively.
-
-  There are steps of the inductive proof of the Truth Lemma for this structure
-  which are not obvious nor obviously documented elsewhere.  Assume
-  $\mathbbm{M}, w \vDash \Box \chi$, where the Truth Lemma has been proven to
-  hold for $\chi$; we must show $\Box \chi \in w$.  By our assumption there
-  is some $\phi$ and $S$ where $\Box \phi \in w$ and $S \supseteq \{v \in W
-  \hspace{1em} | \hspace{1em} \phi \in v\}$.  We argue that $\vdash \phi
-  \rightarrow \chi$; for if not then by the finitary Lindenbaum lemma there is
-  some $u \in W$ where $\phi \in u$ and $\chi \nin u$.  Hence $u \in S$ and
-  $\mathbbm{M}, u \nvDash \chi$, a contradiction.  Since $\vdash \phi
-  \rightarrow \chi$ then we know that $\vdash \Box \phi \rightarrow \Box \chi$
-  by our rules, which means that $\Box \chi \in w$ by maximality.
-
-  By the Lindenbaum Lemma we have that there is some $w \in W$ where
-  $\mathbbm{M}, w \nvDash \psi$.  $\mathbbm{M}$ makes true a number of
-  properties:
-  \begin{enumeratenumeric}
-    \item $W$ and $\mathcal{A}_v$ are finite for all $v \in W$, and $\psi \in
-    \bigcup \mathcal{A_w}$ only if $\psi$ is a subformula of $\phi$
-
-    \item $\mathcal{K}_w \subseteq \mathcal{N}_w$
-
-    \item If $S \in \mathcal{K}_w$ then $w \in S$
-
-    \item $\mathbbm{M}, v \vDash A : \phi \rightarrow \Box \phi$ for all $v
-    \in W$
-
-    \item $\mathcal{N}_w$ and $\mathcal{K}_w$ are closed under supersets
-  \end{enumeratenumeric}
-
-  As in the proof of Theorem \ref{completeness1}, we use a bisimulation to
-  move to a model where property (3) is strengthened to (3$'$): for all $S \in
-  \mathcal{N}_w$, $w \in S$ if and only if $S \in \mathcal{K}'_w$.  We defer
-  the reader to {\cite{hansen_bisimulation_2007,pauly_bisimulation_1999}} for
-  details regarding bisimulation in neighborhood semantics.  Define
-  $\mathbbm{M}' \assign \langle W', V', \mathcal{K}', \mathcal{N}',
-  \mathcal{A}' \rangle$ such that:
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$ wher.  $l, r$ its associated canonical
-    injections and $\theta (v_l) \assign \theta (v_r) \assign v$ is a
-    left-inverse of $l, r$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $\mathcal{K}' (v_i) \assign \{S \hspace{1em} | \hspace{1em} v_i \in
-    S \hspace{1em} \& \hspace{1em} \theta [S] \in \mathcal{K_v} \}$ where $i =
-    l, r$
-
-    \item $\mathcal{N}' (v_i) \assign \mathcal{K}' (v_i) \cup \{S \hspace{1em}
-    | \hspace{1em} v_i \nin S \hspace{1em} \& \hspace{1em} \theta [S] \in
-    \mathcal{N_v} \}$ where $i = l, r$
-
-    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
-    (v)$
-  \end{itemizedot}
-
-  If we let $Z \assign \{(v, v_r), (v, v_l) \hspace{1em} | \hspace{1em} v \in
-  W\}$, it is straightforward to verify that $Z$ is a neighborhood
-  bisimulation.  Hence $\mathbbm{M}, w_l \nvDash \psi$.  Along with (3$'$),
-  this model makes true (1), (2), (4).  In fact, in light of ($3'$), we can
-  see that this model does not need $\mathcal{K}'$, and conforms to the
-  semantics in Definition \ref{neighborhoodmodels}.{\hspace*{\fill}}
-
-  As in previous proofs, let $\Lambda$ be the proposition letters occuring in
-  $\psi$ and define an injection $\iota : W' \hookrightarrow \Phi \backslash
-  \Lambda$, assigning a nominal to every world in $\mathbbm{M}'$.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', \mathcal{N}'', \mathcal{A}''
-  \rangle$ such that:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
-      \begin{array}{ll}
-        V' (p) & p \in \Lambda\\
-        \{v\} & p = i (v)\\
-        \varnothing & o / w
-      \end{array} \right.$\\
-      $\bullet$ & $\mathcal{N}''_w \assign \mathcal{N}'_w$ & {\hspace{3em}} &
-      $\bullet$ & $\mathcal{A}''_v \assign \{\partial_v S \hspace{1em} |
-      \hspace{1em} S \in \mathcal{N}'_w \}$
-    \end{tabular}
-  \end{center}
-
-  Where $\partial_v S \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
-  \bigcup \mathcal{A}_v', \text{$\phi$ is a subformula of $\psi$ and}
-  \hspace{1em} S \subseteq \left\llbracket \phi
-  \right\rrbracket^{\mathbbm{M}'} \} \cup \{\neg \iota (u) \hspace{1em} |
-  \hspace{1em} u \nin S\}$.
-
-  As before, this model agrees with $\mathbbm{M}'$ on all subformulae of
-  $\psi$, using the semantics in Definition \ref{neighborhoodmodels}, hence
-  $\mathbbm{M}'', w_l \nvDash \phi$. \
-
-  All that is left is to show \tmtextbf{NCSQ} and \tmtextbf{NSND} from three
-  new properties:
-  \begin{enumerateroman}
-    \item For all words $v$ and all $X \in \mathcal{A}_v''$, $X$ is finite and
-  .  $X = \partial_v S$ for some $S \in \mathcal{N}_v''$
-
-    \item For all $v$ and all $S \in \mathcal{N}_v$, $u \in S$ if and only if
-    $\mathbbm{M}'', u \vDash \bigwedge \partial_v S$
-
-    \item The logic presented in Table \ref{logic3} is sound for
-    $\mathbbm{M}''$
-  \end{enumerateroman}
-  Along with the deduction theorem for $\vdash$, these properties establish
-  \tmtextbf{NCSQ} for this model using the logic of Table \ref{logic3} itself:
-
-  \begin{align*}
-    \text{$\exists X \in \mathcal{A''_v} \text{ s.t. } \tmop{Th}
-    (\mathbbm{M}'') \cup X \vdash \phi$} & {\Longleftrightarrow}\text{$\exists
-    S \in \mathcal{N''_v} \text{ s.t. } \tmop{Th} (\mathbbm{M}'') \cup
-    \partial_v S \vdash \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \tmop{Th} (\mathbbm{M}'') \vdash \bigwedge \partial_v S \rightarrow
-    \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \bigwedge \partial_v S \rightarrow \phi \in \tmop{Th} (\mathbbm{M}'')$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \left\llbracket \bigwedge \partial_v S \right\rrbracket \subseteq
-    \left\llbracket \phi \right\rrbracket$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t.
-    $\forall u \in W$ if } \mathbbm{M}, u \vDash \bigwedge \partial_v S \text{
-    then } \mathbbm{M}, u \vDash \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \mathbbm{M}, u \vDash \phi \text{ for all } u \in S$}\\
-    & {\Longleftrightarrow}{\mathbbm{M}},v{\vDash}\Box{\phi}
-  \end{align*}
-
-  \tmtextbf{NSND} follows from \tmtextbf{NCSQ} and the semantics of Definition
-  \ref{neighborhoodmodels}.
-\end{proof}
-
-It is not too hard to identify the fragment of this logic that governs
-knowledge alone.  The fragment given in Table \ref{logic4} has special
-significance to us, since it governs the notion of knowledge presented in
-{\S}\ref{quantifying}.
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash K \phi \rightarrow \phi$\\
-    \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ &  &  & $\frac{\vdash \phi \rightarrow \psi}{\vdash K \phi
-      \rightarrow K \psi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic4}A knowledge-only neighborhood logic for
-  \tmtextbf{NCSQ} and {\tmstrong{NSND}}}
-\end{table}
-
-\begin{proposition}
-  The knowledge-only logic presented governs the $\Box$-free fragment of the
-  logic in Table \ref{logic3}
-\end{proposition}
-
-This concludes our analysis of knowledge bases using neighborhood semantics.
-
-\subsection{\label{quantifying}Using Modalities to Quantify over Knowledge
-Bases}
-
-\section{Conclusions \& Further Research}
-
-The logic presented in Table \ref{logic1} is a conservative extension of the
-basic modal logic $K$, which means that its decision problem is
-\tmtextsf{PSPACE} hard (a lower bound).  Our finitary completeness proof
-establishes that its complexity is in \tmtextsf{EXP2-TIME} (an upper bound).
-
-Worlds in epistemic logic might correspond to fantastic, pretend scenarios;
-however, it may be desirable for some philosophers to model knowledge about
-imaginary lands.  After all, many children ``know'' a lot about Tolkien's
-{\tmem{middle earth}} or Rowling's {\tmem{Hogwarts}} (the school Harry Potter
-attends).
-
-\bibliographystyle{plain}
-\bibliography{zotero}
-
-\end{document}
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "paper"
+%%% End:

### 2010-12-15 neighborhood_semantics.tex
Refactored paper so all sections are seperate documents

--- 2010-12-15 paper.tex
@@
-\documentclass{article}
-\usepackage{geometry,amsmath,amssymb,wasysym,enumerate,bbm,color}
-\geometry{letterpaper}
-
-\usepackage{stmaryrd}
-
-%%%%%%%%%% Start TeXmacs macros
-\newcommand{\assign}{:=}
-\newcommand{\nin}{\not\in}
-\newcommand{\tmem}[1]{{\em #1\/}}
-\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
-\newcommand{\tmstrong}[1]{\textbf{#1}}
-\newcommand{\tmtextbf}[1]{{\bfseries{#1}}}
-\newcommand{\tmtextit}[1]{{\itshape{#1}}}
-\newcommand{\tmtextsf}[1]{{\sffamily{#1}}}
-\newcommand{\tmtextup}[1]{{\upshape{#1}}}
-\newenvironment{descriptioncompact}{\begin{description} }{\end{description}}
-\newenvironment{descriptiondash}{\begin{description} }{\end{description}}
-\newenvironment{enumeratenumeric}{\begin{enumerate}[1.] }{\end{enumerate}}
-\newenvironment{enumerateroman}{\begin{enumerate}[i.] }{\end{enumerate}}
-\newenvironment{itemizedot}{\begin{itemize} \renewcommand{\labelitemi}{$\bullet$}\renewcommand{\labelitemii}{$\bullet$}\renewcommand{\labelitemiii}{$\bullet$}\renewcommand{\labelitemiv}{$\bullet$}}{\end{itemize}}
-\newenvironment{proof}{\noindent\textbf{Proof\ }}{\hspace*{\fill}$\Box$\medskip}
-\definecolor{grey}{rgb}{0.75,0.75,0.75}
-\definecolor{orange}{rgb}{1.0,0.5,0.5}
-\definecolor{brown}{rgb}{0.5,0.25,0.0}
-\definecolor{pink}{rgb}{1.0,0.5,0.5}
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}{Proposition}
-\newtheorem{theorem}{Theorem}
-%%%%%%%%%% End TeXmacs macros
-
-\begin{document}
-
-\title{Epistemic Logics For Knowledge Bases}\author{Matthew P.
-Wampler-Doty}\maketitle
-
-\begin{abstract}
-  In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem
-  proposed a research program for logic of \tmtextit{explicit knowledge}. \
-  Two efforts have since emerged with proposals for logic of explicit
-  knowledge: the \tmtextit{Dynamics of Awareness}
-  {\cite{van_benthem_inference_2009}} and \tmtextit{Justification Logic}
-  {\cite{artemov_introducing_2005}}.  The purpose of this paper is to
-  repurpose various epistemic logics from these previous efforts for reasoning
-  about logical closures over knowledge bases.  The results in this paper are
-  based on previous work carried out in
-  {\cite{wampler-doty_evidentialist_2010}}.
-\end{abstract}
-
-\section{Introduction\label{intro}}
-
-The modern tradition in epistemic logic is to assume knowledge modalities
-conform to the $S 5$ axiom schema.  As noted in
-{\cite{halpern_set-theoretic_1999,rubinstein_modeling_1998}}, the semantics of
-$S 5$ knowledge correspond exactly to partitioning a collection of situations
-into \tmtextit{information sets}, which is the traditional approach in game
-theory and decision theory.  While it is not commonly acknowledged in
-epistemic logic, economists and philosophers accept that traditional decision
-theory is externalist and behaviourist in nature
-(FIXME)
-\footnote{An early essay by
-Amartya Sen on the philosophical foundations of traditional decision theory
-makes the behaviorist reading of decision theory clear
-\cite{sen_behaviour_1973}.  Kaushik Basu also discusses the behaviorist
-nature of decision theory {\cite[pgs. 53--54]{basu_revealed_1980}}. 
-Finally, Donald Davidson appeals to decision theory to motivate an externalist
-epistemology in \cite{davidson_could_1995}.}.
-
-In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem proposed
-a research program to find logics for explicit knowledge, providing the first
-suggestion of an internalist perspective on epistemic logic.  Subsequently,
-Sergei Artemov and Elena Nogina proposed a logic of explicit justification,
-which has come to be known as \tmtextit{Justification Logic} (JL)
-{\cite{artemov_introducing_2005}}, based on Artemov's \tmtextit{Logic of
-Proofs} {\cite{artemov_logic_1994}}.  While the original semantics of JL was
-interpretability into Peano Arithmetic, Melvin Fitting proposed Kripke
-semantics for JL in {\cite{fitting_logic_2005}}.  Recently, Fernando
-Vel\'azquez-Quesada and Johan van Benthem have developed a simpler framework
-for explicit epistemics in {\cite{van_benthem_inference_2009}}, entitled the
-\tmtextit{Dynamics of Awareness}.  This work was based on Joseph Halpern and
-Ronald Fagin's original \tmtextit{Awareness Logic} {\cite{fagin_belief_1987}}.
-
-In this essay we repurpose various externalist logics to take on an
-internalist reading.  The concept of a \tmtextit{knowledge base}, from which
-beliefs may be implicitly deduced, will play a crucial role in our discussion.
-\ We propose this as an avenue for representing foundationalist perspectives
-on epistemology in epistemic logic.  Our philosophical motivation is taken
-from two sources.  The first is Vincent Hendricks in
-{\cite{hendricks_mainstream_2006}}, where he characterizes the principal of
-{\tmem{logical omniscience}} for implicit knowledge in epistemic
-logic{\footnote{We have modified Hendricks' notation here slightly to match
-our own.}}:
-
-\begin{quote}
-  {\tmem{Whenever an agent $\Xi$ knows all of the formulae in $\mathcal{A}$,
-  and $\phi$ follows logically from $\mathcal{A}$, then $\Xi$ [implicitly]
-  knows $\phi$.}}
-\end{quote}
-
-We will design our semantics such that ``$\Box \phi$'' may be equated with
-``$\phi$ follows logically from a knowledge base $\mathcal{A}$,'' which is
-sometimes written as $\phi \in \tmop{Cn} ( \mathcal{A})$ in the artificial
-intelligence literature.  Our second inspiration comes from what Hilary
-Kornblith calls the \tmtextit{the arguments on paper thesis}
-{\cite{kornblith_beyond_1980}}, which he feels characterizes apsychological,
-internalist theories of knowledge:
-
-\begin{quote}
-  Let us suppose that, for any person, it is possible, at least in principle,
-  to list all of the propositions that person believes.  The
-  arguments-on-paper thesis is just the view that a person has a justified
-  belief that a particular proposition is true just in case that proposition
-  appears on the list of propositions that person believes, and either it
-  requires no argument, or a {\tmem{good argument}} can be given for it which
-  takes as premises certain other propositions on the list.
-\end{quote}
-
-Kornblith asserts that foundationalism and coherentism vie for accounts of a
-``good argument'' in the above thesis.  He provides an extensive bibliography
-citing proposals for this principle by a number of 20th century
-epistemologists, including figures such as A.J. Ayer and C.I. Lewis.  The
-rest of Kornblith's paper is devoted to attacking this view and proposing a
-form of naturalized epistemology; we will not address this debate here,
-however.
-
-We adopt a arguments-on-paper-thesis perspective on epistemic logic in this
-paper.  We consider a \tmtextit{good argument} to be a logical derivation
-from propositions present in a knowledge base.  In this fashion, ou.  \
-Special attention will be given to \tmtextit{sound derivations}, which will be
-thought of as a form of knowledge.  In Awareness Logic, we will interpret
-awareness of a formula as membership in a knowledge base.  We prove
-completeness for basic awareness logic and a hybrid logic extension.  Logics
-of multiple knowledge bases are also presented: a simplified form of
-Justification Logic, a logic with neighborhood semantics, an a logic with
-modalities for quantifying over knowledge bases.  We conclude with an
-application to naturalized epistemology found in the psychological literature.
-
-\section{Basic Explicit Logics of Knowledge Bases}
-
-\subsection{Awareness Logic\label{awarenesslogic}}
-
-In this section, we give the explicit semantics to basic awareness logic,
-originally presented in {\cite{fagin_belief_1987}}, with an additional axiom.
-\ One difference in our presentation is the inclusion of a novel letter and a
-superficial change in notation.  This work is inspired by the developments in
-van Benthem and Vel\'azquez-Quesada {\cite{van_benthem_inference_2009}}.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and define the language $\mathcal{L}_A
-  (\Phi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A : \phi \hspace{1em}
-  \]
-\end{definition}
-
-We define the other connectives and modal operators as usual for classical
-modal logics.
-
-\begin{definition}
-  \label{awarenessmodels}An {\tmstrong{awareness model}} $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V : \Phi
-  \cup \{\circlearrowleft\} \rightarrow 2^W$ and an awareness function
-  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$.  We will usually
-  denote $\mathcal{A} (w)$ as $\mathcal{A}_w$.
-
-  Define the semantic entailment relation $\vDash$ where atomic propositions,
-  logical connectives and modality are interpreted as usual.  We employ the
-  following novel definition:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \mathcal{A_w}
-  \end{eqnarray*}
-\end{definition}
-
-The following definition distinguishes us from previously investigations of
-awareness logic:
-
-\begin{definition}
-  Define the ``\tmtextbf{theory of a model} $\mathbbm{M}$'' as:
-  \[ \tmop{Th} (\mathbbm{M}) \assign \{\phi \hspace{1em} | \hspace{1em}
-     \mathbbm{M}, v \vDash \phi \text{ for all } v \in W\} \]
-  We define the following properties that a model $\mathbbm{M}$ may posses:
-
-  \begin{descriptiondash}
-    \item[CSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w \vdash \phi$
-
-    \item[SND] $\mathbbm{M}, w \vDash \circlearrowleft \text{ iff }
-    \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w$
-  \end{descriptiondash}
-
-  Here $\vdash$ is any logical consequence relation which is sound for
-  $\vDash$, making true \tmtextbf{modus ponens} and \tmtextbf{reflection} (ie,
-  $\Gamma \vdash \phi$ if $\phi \in \Gamma$)
-\end{definition}
-
-Neither \tmtextbf{CSQ} nor \tmtextbf{SND} correspond to simple modally
-definable properties.
-
-Intuitively, the \tmtextbf{CSQ} asserts that an agent believes a formula
-$\phi$ if and only if it follows logically from their knowledge base and their
-background knowledge, represented by $\tmop{Th} (\mathbbm{M})$. \
-\tmtextbf{CSQ} is Vincent Hendrik's principle of logical omniscience mentioned
-in {\S}\ref{intro}.
-
-\tmtextbf{SND} asserts that $\circlearrowleft$ corresponds to the agent's
-knowledge base being sound. A sound knowledge base will only render true
-conclusions when used in deductions.  If one considers ``the existance of a
-sound deduction'' sufficient for a kind of knowledge, then $\circlearrowleft$
-is suitable for investigating this notion of epistemology.  That is, if
-$\mathbbm{M}, w \vDash \circlearrowleft \wedge \Box \phi$, then we may
-naturally say that the agent (implicitly) {\tmem{knows}} $\phi$ on the basis
-of $\mathcal{A}_w$, rather than merely {\tmem{believing}} $\phi$ on the basis
-of $\mathcal{A}_w$.
-
-The logic of models making true \tmtextbf{CSQ} and \tmtextbf{SND} is provided
-in Table \ref{logic1}.
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash \Box(\phi \rightarrow \psi) \rightarrow \Box \phi \rightarrow \Box
-    \psi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$\\
-    $\vdash \circlearrowleft \rightarrow \Box \phi \rightarrow \phi$\\
-    \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box \phi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic1}Awareness Logic for \tmtextbf{CSQ} and
-  \tmtextbf{SND}}
-\end{table}
-
-\begin{theorem}
-  \label{completeness1}Assuming an infinite store of proposition letters
-  $\Phi$, the awareness logic presented is sound and weakly complete for
-  awareness models making true \tmtextbf{CSQ} and \tmtextbf{SND}.
-\end{theorem}
-
-\begin{proof}
-  Soundness is straightforward, so we will only address completeness.  Assume
-  $\nvdash \psi$.  Consider the finite canonical model $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A} \rangle$ formed of maximally consistent sets of
-  subformulae of $\phi$ (closed under single negations{\footnote{A discussion
-  of this property may be found in {\cite[pg.
-  243]{blackburn_modal_2001}}.}}), as per the finitary modal completeness
-  proofs found in {\cite[chapter 4.8]{blackburn_modal_2001}} and
-  {\cite[chapter 5]{boolos_logic_1995}}.  Typical presentations do not
-  include awareness, however it is defined intuitively in this case:
-  \[ \phi \in \mathcal{A}_w \Longleftrightarrow A : \phi \in w \]
-  Since $\psi$ is a subformula of itself, we have $\mathbbm{M}, w \nvDash
-  \psi$ for some world $w$ by a finitary {\tmem{Lindenbaum Lemma}} and
-  {\tmem{Truth Theorem}}.  Moreover, it is straightforward to verify that
-  $\mathbbm{M}$ makes true the following properties:
-  \begin{enumeratenumeric}
-    \item $W$ and $\mathcal{A}_v$ are finite, and $\psi \in \mathcal{A}_v$
-    only if $\psi$ is a (possibly negated) subformula of $\phi$
-
-    \item if $\mathbbm{M}, v \vDash A : \psi$ then $\mathbbm{M}, v \vDash \Box
-    \psi$
-
-    \item if $\mathbbm{M}, v \vDash \circlearrowleft$ then $v R v$
-  \end{enumeratenumeric}
-
-  We next produce a bisimular{\footnote{The notion of bisimulation is
-  discussed at length in {\cite[chapter 2.2]{blackburn_modal_2001}}.  We
-  note that the basic definition and all of the usual theorems (modal
-  equivalence, Henessy Milner, etc.) may be generalized to awareness models in
-  a straightforward fashion. }} model $\mathbbm{M}'$ which makes true (1), (2)
-  and a stronger from of (3):
-
-  {\hspace*{\fill}}\begin{tabular}{ll}
-    \tmtextbf{3$'$.} & $\mathbbm{M}', v \vDash \circlearrowleft$ iff $v R v$
-  \end{tabular}{\hspace*{\fill}}
-
-  To this end define $\mathbbm{M}' \assign \langle W', V', R', \mathcal{A}'
-  \rangle$ such that{\footnote{Throughout this article, we use $l$ and $r$ to
-  denote the two canonical injections associated with the coproduct $W \uplus
-  W$. We will use $v_l$ and $v_r$ as the shorthand for $l (v)$ and $r (v)$
-  respectively.}}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $R' \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v R
-    u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em} \mathbbm{M},
-    v \vDash \circlearrowleft\}$
-
-    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
-    (v)$
-  \end{itemizedot}
-
-  It is straightforward to verify that $\mathbbm{M}'$ makes true the desired
-  properties.  Let $Z \assign \{(v, v_l), (v, v_r) \hspace{1em} |
-  \hspace{1em} v \in W\}$.  then $Z$ is a bisimulation between $\mathbbm{M}$
-  and $\mathbbm{M}'$.  Therefore we know there is some $w \in W$ such that
-  $\mathbbm{M}', w_l \nvDash \psi$ and $\mathbbm{M}', w_r \nvDash \psi$.
-
-  Finally we construct a model $\mathbbm{M}''$ which agrees with
-  $\mathbbm{M}'$ for all subformulae of $\psi$, which makes true
-  \tmtextbf{CSQ} and \tmtextbf{SND}.  Let $\Lambda$ be the set of proposition
-  letters occuring in $\psi$.  We will make use members of $\Phi \backslash
-  \Lambda$ as {\tmem{nominals}}, as per the tradition in hybrid logic.  This
-  is possible since both $W'$ and $\Lambda$ are finite and $\Phi$ is infinite
-  by hypothesis.  Let $\iota : W \uplus W \hookrightarrow \Phi \backslash
-  \Lambda$ be an injection assigning a fresh nominal associated with each
-  world in $\mathbbm{M}'$.  Now define $\mathbbm{M}'' \assign \langle W'',
-  V'', R'', \mathcal{A}'' \rangle$, where:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
-      \begin{array}{ll}
-        V' (p) & p \in \Lambda\\
-        \{v\} & p = \iota (v)\\
-        \varnothing & o / w
-      \end{array} \right.$\\
-      $\bullet$ & $R'' \assign R'$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}''_v \assign \{\phi \hspace{1em} | \phi \in \mathcal{A}'_v
-      \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em} \neg v R' u\}$
-    \end{tabular}
-  \end{center}
-
-  By induction we have that for every subformula $\phi$ of $\psi$ that
-  $\mathbbm{M}', v \vDash \phi$ if and only if $\mathbbm{M}'', v \vDash \phi$,
-  hence $\mathbbm{M}'', w_l \nvDash \psi$.
-
-  All that is left to show is that $\mathbbm{M}''$ makes true \tmtextbf{CSQ}
-  and \tmtextbf{SND}.  $\mathbbm{M}''$ has three further properties:
-  \begin{enumerateroman}
-    \item $\mathcal{A}''_v$ is finite for all worlds $v$
-
-    \item  $v R' u$ if and only if $\mathbbm{M}'', u \vDash \bigwedge
-    \mathcal{A}'' (v)$
-
-    \item The logic presented in Table \ref{logic1} is sound for
-    $\mathbbm{M}''$
-  \end{enumerateroman}
-  From (ii) and the fact that $\mathbbm{M}'$ makes true (3$'$), we have
-  \tmtextbf{SND} for $\mathbbm{M}''$.
-
-  All that is left is to demonstrate \tmtextbf{CSQ} for some sound logic.  We
-  will use the logic in Table \ref{logic1} itself.  From (i), (ii), (iii),
-  and the \tmtextit{deduction theorem} for modal logic, we have the following
-  line of reasoning:
-
-  \begin{align*}
-    Th({\mathbbm{M}}''){\cup}\mathcal{A}''_v{\vdash}{\phi} &
-    {\Longleftrightarrow}Th({\mathbbm{M}}''){\vdash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\\
-    &
-    {\Longleftrightarrow}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}{\in}Th({\mathbbm{M}}'')\\
-    &
-    {\Longleftrightarrow}{\mathbbm{M}}'',u{\vDash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\text{
-    for all $u \in W''$}\\
-    & {\Longleftrightarrow}\text{ for all $u \in W''$, if
-    }{\mathbbm{M}}'',u{\vDash}\mathcal{A}''_v\text{ then
-    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
-    & {\Longleftrightarrow}\text{ for all $u \in W''$, if }v R 'u \text{ then
-    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
-    & {\Longleftrightarrow}{\mathbbm{M}}'',v{\models}\Box{\phi}
-  \end{align*}
-\end{proof}
-
-\subsection{Hybrid Awareness Logic}
-
-The method of the above completeness proof makes implicit use of concepts from
-hybrid logic{\footnote{Hybrid logic was first presented in
-{\cite{prior_revised_1969}} and later formally developed in
-{\cite{bull_approach_1970}}.}}.  In this section we adapt hybrid logic and
-show that it is a complete for reasoning about knowledge bases.  We note that
-because of the increased expressive power of hybrid logic, our completeness
-theorem is simpler.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
-  language $\mathcal{L}_H (\Phi, \Psi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} i \in \Psi \hspace{1em} | \hspace{1em} \bot \hspace{1em} |
-     \hspace{1em} \phi \rightarrow \psi \hspace{1em} | \hspace{1em} \Box \phi
-     \hspace{1em} | \hspace{1em} A : \phi \hspace{1em} | \hspace{1em} \forall
-     \phi \]
-\end{definition}
-
-Our approach in hybrid logic is to employ a universal modality along with
-nominals.  This framework presents a logic where the agent may reason about
-various labeled scenarios.  Scenarios may be multiply labeled or not labeled
-at all.  From these intuitions we have the following definition:
-
-\begin{definition}
-  \label{hybridsemantics}Let a \tmtextbf{hybrid model} $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A}, \ell \rangle$ be an awareness model as in Definition
-  \ref{awarenessmodels}, along with a partial labeling function $\ell : \Psi
-  \nrightarrow W$
-
-  The semantics for $\vDash$ are the same as in Definition
-  \ref{awarenessmodels}, only we have
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \forall \phi & \text{iff} & \forall v \in
-    W.\mathbbm{M}, v \vDash \phi\\
-    \mathbbm{M}, w \vDash i & \text{iff} & \ell (i) = w
-  \end{eqnarray*}
-\end{definition}
-
-The other connectives and operators are defined as usual, although we employ a
-few special shorthands:
-
-\begin{definition}
-  We employ the following special abbreviations:
-  \begin{eqnarray}
-    \text{\tmtextup{@}}_i \phi \assign \forall (i \rightarrow \phi)
-    \hspace{2em} & \exists \phi \assign \neg \forall \neg \phi \hspace{3em} &
-    \circlearrowleft_i \assign \diamondsuit i \nonumber
-  \end{eqnarray}
-\end{definition}
-
-This gives rise to a validity reflecting one of the axioms we saw in
-{\S}\ref{awarenesslogic}:
-\[ \vDash \circlearrowleft_i \rightarrow \Box \phi \rightarrow
-   \text{\tmtextup{@}}_i \phi \]
-This can be read as ``If the agent's knowledge base is sound at world $i$,
-then if they can deduce something from their knowledge base, what they deduce
-must be true at world $i$.'.  In a way, this may be considered as
-{\tmem{relativising}} knowledge particular named situations.
-
-The semantics in Definition \ref{hybridsemantics} obviates the \tmtextbf{SND}
-principle we previously presented, since there is no explicit
-$\circlearrowleft$ symbol in this setting. \tmtextbf{CSQ} still makes sense
-without modification, however.  The following gives a logic for hybrid models
-making true \tmtextbf{CSQ}:
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & $\vdash \forall (\phi
-    \rightarrow \psi) \rightarrow \forall \phi \rightarrow \forall \psi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & $\vdash \forall
-    \phi \rightarrow \phi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & $\vdash \forall \phi \rightarrow
-    \forall \forall \phi$\\
-    $\vdash \Box(\phi \rightarrow \psi) \rightarrow \Box \phi \rightarrow \Box
-    \psi$ & $\vdash \exists \phi \rightarrow \forall \exists \phi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$ & $\vdash \forall \phi \rightarrow
-    \Box \phi$\\
-    & $\vdash i \rightarrow \phi \rightarrow \text{\tmtextup{@}}_i \phi$\\
-    & \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi}{\vdash \Box \phi}$ &
-      {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \forall \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic2}Hybrid Awareness Logic for \tmtextbf{CSQ}}
-\end{table}
-
-\begin{theorem}
-  \label{completeness2}Assuming an infinite store of nominals $\Psi$, the
-  hybrid awareness logic presented is sound and weakly complete for all hybrid
-  models making true \tmtextbf{CSQ}.
-\end{theorem}
-
-\begin{proof}
-  As before, soundness is trivial.  Completeness is based on a modification
-  of techniques found in {\cite[chapter 5]{boolos_logic_1995}}.  Assume
-  that $\nvdash \psi$ and let $\Sigma_0$ be the set of subformulae of $\psi$,
-  and let $\Upsilon$ be the set of nominals occuring in $\psi$.  Define:
-
-  \begin{align*}
-    {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{{\forall}{\phi}{\hspace{1em}}|{\hspace{1em}}\Box{\phi}{\in}{\Sigma}_0\}\\
-    {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{\text{@}_i{\phi}{\hspace{1em}},i{\rightarrow}{\phi}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1{\hspace{1em}}\&{\hspace{1em}}i{\in}{\Upsilon}\}\\
-    {\Sigma}_3 &
-    {\assign}{\Sigma}_2{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_2\}
-  \end{align*}
-
-  It is easy to see that $\Sigma_3$ is finite and closed under subformulae and
-  single negations. Let $\mathbbm{M}= \langle W, V, R_{\Box}, \sim_{\forall},
-  \mathcal{A} \rangle$ be the finite cannonical model formed of maximally
-  consistent subsets of $\Sigma_3$, where everything is defined as usual,
-  except $\sim_{\forall}$, which obeys the following specification:
-
-  \begin{align*}
-    w {\sim}_{{\forall}}v & {\Longleftrightarrow}(({\forall}{\phi}){\in}w
-    {\Longleftrightarrow}({\forall}{\phi}){\in}v)
-  \end{align*}
-
-  This model makes true the following properties:
-  \begin{enumerateroman}
-    \item $\sim_{\forall}$ is an equivalence relation
-
-    \item $R_{\Box} \subseteq \sim_{\forall}$
-
-    \item In each equivalence class specified by $\sim_{\forall}$, there is at
-    most one world making true $i$ for all $i \in \Upsilon$
-  \end{enumerateroman}
-  As in our previous construction we have that there is some world $w$ where
-  $\mathbbm{M}, w \nvDash \psi$.  Let $\mathbbm{M}^1 = \langle W', V',
-  R_{\Box}', \sim_{\forall}', \mathcal{A}' \rangle$ be the submodel generated
-  by $\{w\}$; we have that $\mathbbm{M}', w \nvDash \psi$ (see {\cite[chapter
-  2.1]{blackburn_modal_2001}} for details on generated submodels).  In this
-  model $\forall$ is a universal modality and either $\left\llbracket i
-  \right\rrbracket^{\mathbbm{M}'} = \varnothing$ or $\left\llbracket i
-  \right\rrbracket^{\mathbbm{M}'} =\{v\}${\footnote{As per the usual
-  convention, here $\left\llbracket \phi \right\rrbracket^{\mathbbm{M}}$
-  denotes $\{w \in W \hspace{1em} | \hspace{1em} \mathbbm{M}, w \vDash
-  \phi\}$.  We will drop $\mathbbm{M}$ where it is unambiguous.}}. Since the
-  store $\Psi$ of nominals is infinite and $\Upsilon$ is finite, we have that
-  $\Psi \backslash \Upsilon$ is infinite, so there is some injection $\iota :
-  W' \hookrightarrow \Psi \backslash \Upsilon$ which assigns a fresh nominal
-  to every world.  Let $\mathbbm{M}'' = \langle W'', V'', R'', \mathcal{A}'',
-  \ell \rangle$, where:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign V' (p)$\\
-      $\bullet$ & $R'' \assign R'_{\Box}$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}'' (v) \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
-      \mathcal{A}' (v)\} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
-      \neg v R' u\}$\\
-      \begin{tabular}{ll}
-        $\bullet$ & $\ell (i) \assign \left\{ \begin{array}{ll}
-          w & i \in \Upsilon \hspace{1em} \& \hspace{1em} \mathbbm{M}, w
-          \vDash i\\
-          \iota^{- 1} (i) & i \in \iota [W]\\
-          \text{undefined} & \text{o/w}
-        \end{array} \right.$
-      \end{tabular} & $R'' \assign R'_{\Box}$ &  &  & 
-    \end{tabular}
-  \end{center}
-
-  The the worlds is $\mathbbm{M}'$ and $\mathbbm{M}''$ agree on all
-  subformulae of $\psi$, hence $\mathbbm{M}'', w \nvDash \psi$. The same
-  reasoning as in the proof of Theorem \ref{completeness1} establishes and
-  that the logic in Table \ref{logic2} itself is sound for $\mathbbm{M}''$ and
-  makes true \tmtextbf{CSQ}, establishing completeness.
-\end{proof}
-
-\section{Logics of Multiple Knowledge Bases}
-
-So far, we have only dealt with systems that reason over a single knowledge
-base.  In this section, we present various logics for reasoning over multiple
-knowledge bases.
-
-\subsection{Simple Justification Logic}
-
-Justification Logic (JL) was originally developed by Artemov as the
-\tmtextit{Logic of Proofs} (LP) {\cite{artemov_logic_1994}}.  Its original
-purpose was to provide a framework for reasoning about explicit provability in
-Peano Arithmetic.  The first introduction of Justification Logic can be found
-in {\cite{artemov_introducing_2005}}, where Artemov and Nogina propose LP as a
-logic for reasoning about evidence.  In {\cite{fitting_logic_2005}}, Melvin
-Fitting provided JL with Kripke model based semantics.
-
-The principle innovation of LP/JL is to extend awareness logic, such that
-awareness operations are now \tmtextit{proof terms}.  Informally, we say that
-``a proof term $X$ witnesses proposition $\phi$'', denoted ``$X : \phi$'',
-whenever $X$ represents a proof of $\phi$.  Proofs may have
-{\tmstrong{multiple-conclusions}} in this system, so it is possible that $X :
-\phi$ and $X : \psi$ can be true where $\phi \neq \psi$.  In Fitting's Kripke
-semantics, $X : \phi$ means that $\phi$ is in awareness set corresponding to
-$X$.  Proof terms are thought be operating in a \tmtextit{multi-conclusion}
-proof system, so the same proof term may witness many different propositions.
-
-The logics LP/JL include operators over proofs terms, so that new proof terms
-may be assembled.  One operation of particular interest to us is
-{\tmem{choice}}, denoted $\oplus$.  The expression ``$X \oplus Y : \phi$''
-denotes that either $X$ or $Y$ are proofs witnessing $\phi$.  There are other
-operations which correspond to \tmtextit{modus ponens} and
-\tmtextit{proof-theoretic reflection}, however we do not consider these
-operations here.
-
-In this section we consider a simplified form of JL suitable for reasoning
-over multiple knowledge bases, which we call \tmtextit{simple justification
-logic} (SJL). However, instead of thinking of terms as representing proofs, we
-use them to represent knowledge bases. This is in the spirit of JL as a logic
-of evidence: we consider each knowledge base to be a corpus of evidence. \
-Each term ``names'' a different knowledge base at a particular world.  Terms
-may not refer to the same knowledge base at different worlds, just as in how
-in awareness logic the agent need not be aware of the same formulae at
-different worlds.  Finally, we will make use of JL's {\tmem{choice}} operator
-as a mechanism for forming the union of knowledge bases, creating new ones.
-
-\begin{definition}
-  Let $\Pi$ be a set of primitive terms.  Define $\tau (\Pi)$ with the
-  following grammar:
-  \[ X \hspace{1em} : : = \hspace{1em} t \in \Pi \hspace{1em} | \hspace{1em} X
-     \oplus Y \]
-
-  Let $\Phi$ be a set of letters and $\Pi$ a set of primitive terms, and
-  define the language $\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi \]
-  where $X \in \tau (\Pi)$
-\end{definition}
-
-\begin{definition}
-  \label{justmodels}A {\tmstrong{simple justification model}} $\mathbbm{M}=
-  \langle W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V
-  : \Phi \cup \{\circlearrowleft_X \hspace{1em} | \hspace{1em} X \in \tau
-  (\Pi)\} \rightarrow 2^W$, an indexed relation $R : \tau (\Pi) \rightarrow
-  2^{W \times W}$, along with a modified awareness function $\mathcal{A} : W
-  \times \tau (\Pi) \rightarrow 2^{\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)}$. \
-  In practice we will denote $\mathcal{A} (w, X)$ by a curried shorthand,
-  namely $\mathcal{A}_w (X)$.
-
-  The semantics for $\vDash$ have the following modifications:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box_X \phi & \text{iff} & \text{for all $v \in W$
-    where $w R_X v$ we have $\mathbbm{M}, v \vDash v$}\\
-    \mathbbm{M}, w \vDash X : \phi & \text{iff} & \phi \in \mathcal{A}_w (X)
-  \end{eqnarray*}
-\end{definition}
-
-\begin{definition}
-  The following defines properties a simple justification model may make true:
-
-  \begin{descriptiondash}
-    \item[JCSQ] $\mathbbm{M}, w \vDash \Box_X \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w (X) \vdash \phi$
-
-    \item[JSND] $\mathbbm{M}, w \vDash \circlearrowleft_X \text{ iff
-    $\mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w (X)$}$
-
-    \item[CHOICE] $\mathcal{A}_w (X \oplus Y) = \mathcal{A}_w (X) \cup
-    \mathcal{A}_w (Y)$
-  \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
-\end{definition}
-
-The above semantics are similar to the ones given in previous sections. \
-\tmtextbf{JCSQ} is the same as \tmtextbf{CSQ} from {\S}\ref{awarenesslogic},
-only it is relativized to a knowledge base denoted by $X$ at $w$.  The
-awareness logic of knowledge bases is special case of simple justification
-logic where there is only one term.
-
-Simplified justification logic is given in Table \ref{logic5}.  We assert
-without proof that this is a conservative extension of the awareness logic in
-{\S}\ref{awarenesslogic}.
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
-    \Box_X \psi$ & \\
-    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash (X \oplus Y : \phi) \rightarrow X : \phi$ & $\vdash (X \oplus Y :
-    \phi) \rightarrow Y : \phi$\\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_X$ &
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_Y$\\
-    $\vdash \Box_X \phi \rightarrow \Box_{X \oplus Y} \phi$ & \\
-    $\vdash \Box_{X \oplus X} \phi \rightarrow \Box_X \phi$ & $\vdash \Box_{(X
-    \oplus X) \oplus Y} \phi \rightarrow \Box_{X \oplus Y} \phi$ \\
-    $\vdash \Box_{X \oplus Y} \phi \rightarrow \Box_{Y \oplus X} \phi$ &
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{(Y \oplus X)
-    \oplus Z} \phi$\\
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{X \oplus (Y
-    \oplus Z)} \phi$ & \\
-    & \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic5}Simple Justification Logic}
-\end{table}
-
-\begin{theorem}
-  \label{completeness5}Assuming an infinite store of proposition letters
-  $\Phi$, SJL is sound and weakly complete for simple justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND} and \tmtextbf{CHOICE}
-\end{theorem}
-
-\begin{proof}
-  As in the previous proofs, we only show completeness.  Assume that $\nvdash
-  \psi$.  Let $\Xi \subseteq \tau (\Pi)$ be all of the subterms occurring in
-  $\psi$; we assume that $\Xi$ is non-empty, since otherwise we may obtain the
-  theorem via the usual completeness theorem for classical propositional
-  logic. Let $\Sigma_0$ be the subformulae of $\psi$.  Define:
-
-  \begin{align*}
-    {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{\Box_Y{\phi}{\hspace{1em}}|{\hspace{1em}}\Box_X{\phi}{\in}{\Sigma}_0{\hspace{1em}}\&{\hspace{1em}}Y{\in}{\Xi}\}\\
-    {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1\}
-  \end{align*}
-
-  As in the proof of Theorem \ref{completeness2}, it is simple to verify that
-  $\Sigma_2$ is closed under subformulae and single negations.  Let
-  $\mathbbm{M} \assign \langle W, V, R, \mathcal{A} \rangle$ be the finite
-  cannonical model formed of maximally consistent subsets of $\Sigma_2$, where
-  $V$ and $\mathcal{A}$ are defined as usual, and $R : \Xi \rightarrow 2^{W
-  \times W}$ is defined by:
-  \[ w R_X v \Longleftrightarrow \{\phi \hspace{1em} | \hspace{1em} \Box_X
-     \phi \in w\} \subseteq v \]
-  As in previous constructions we may prove the usual Lindenbaum and Truth
-  Lemmas an use them obtain a world $w \in W$ where $\mathbbm{M}, w \nvDash
-  \psi$.
-
-  Next, define an operator $\twonotes : \tau (\Pi) \rightarrow 2^{\Pi}$ where:
-  \[ \twonotes (X) \assign \{t \in \Pi \hspace{1em} | \hspace{1em} t \text{
-     occurs in } X\} \]
-  In other words, $\twonotes (X)$ is the set of atomic terms in $X$.  As in
-  our construction for Theorem \ref{completeness1}, $\mathbbm{M}$ makes true
-  certain properties, along with some new properties:
-  \begin{enumeratenumeric}
-    \item \label{fin}$W$ and $\mathcal{A}_v (X)$ are finite, and $\phi \in
-    \mathcal{A}_v (X)$ only if $\phi \in \Sigma_2$
-
-    \item if $\mathbbm{M}, v \vDash X : \phi$ then $\mathbbm{M}, v \vDash
-    \Box_X \phi$
-
-    \item \label{refl}if $\mathbbm{M}, v \vDash \circlearrowleft_X$ then $v
-    R_X v$
-
-    \item \label{sndness}For all $X \oplus Y \in \Xi$, $\mathbbm{M}, v \vDash
-    \circlearrowleft_{X \oplus Y}$ if and only if $\mathbbm{M}, v \vDash
-    \circlearrowleft_X$ and $\mathbbm{M}, v \vDash \circlearrowleft_Y$
-
-    \item \label{union}For all $X \oplus Y \in \Xi$, $\mathcal{A}_v (X \oplus
-    Y) = \mathcal{A}_v (X) \cup \mathcal{A}_v (Y)$
-
-    \item \label{sub}For all $X, Y \in \Xi$, if $\twonotes (X) \subseteq
-    \twonotes (Y)$ then $R_Y \subseteq R_X$
-  \end{enumeratenumeric}
-  As in our previous constructions, it is necessary to refine this model using
-  bisimulations to achieve properties which are not modally definable.  In
-  particular, we shall strengthen (\ref{refl}) to a biconditional and
-  (\ref{sub}) to:
-
-  \begin{center}
-    \begin{tabular}{ll}
-      \tmtextbf{6$'$.} & For all $X, Y \in \Xi$, $R_{X \oplus Y} = R_X \cap
-      R_Y$
-    \end{tabular}
-  \end{center}
-
-  We first strengthen (\ref{refl}) by constructing $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}' \rangle$, just as in Theorem
-  \ref{completeness1}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $R'_X \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v
-    R_X u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em}
-    \mathbbm{M}, v \vDash \circlearrowleft_X \}$
-
-    \item $\mathcal{A}' (v_l, X) \assign \mathcal{A}' (v_r, X) \assign
-    \mathcal{A} (v, X)$
-  \end{itemizedot}
-  The same bisimulation relation $Z$ previously given suffices.
-
-  We next make a strengthened the model where (\ref{sub}$'$) holds.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that{\footnote{Let $\{i_X \hspace{1em} | \hspace{1em} X \in \Xi\}$ be the
-  family of canonical injections into the coproduct $\uplus_{\Xi} W$. As per
-  our previous convention, we use $v_X$ as shorthand for $i_X (v)$.}}:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em}
-    \twonotes (X) \subseteq \twonotes (Z)\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  Note that this construction makes use of the assumption that $\Xi$ is
-  non-empty.  Let $Z \assign \{(v, v_X) \hspace{1em} | \hspace{1em} X \in \Xi
-  \hspace{1em} \& \hspace{1em} v \in W' \}$; it is straightforward to prove
-  that $Z$ is a bisimulation between $\mathbbm{M}'$ and $\mathbbm{M}''$, for
-  all relations corresponding to terms $X \in \Xi$. Hence $\mathbbm{M}'', w_X
-  \nvDash \psi$ for some $w_X \in W''$.  In addition, $\mathbbm{M}''$
-  inherits (\ref{fin}) through (\ref{sub}) from $\mathbbm{M}'$, as well as the
-  converse of (\ref{refl}).  Next observe, forall $X \oplus Y \in \Xi$:
-  \begin{eqnarray*}
-    \text{$(v_V, u_Z) \in R''_X \cap R''_Y$} & \Longleftrightarrow & \exists Z
-    \in \Xi . \text{$v R'_Z u \hspace{1em} \& \hspace{1em} \twonotes (X)
-    \subseteq \twonotes (Z) \hspace{1em} \& \hspace{1em} \twonotes (Y)
-    \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X) \cup \twonotes (Y) \subseteq \twonotes
-    (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X \oplus Y) \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow &  \text{$(v_V, u_Z) \in R''_{X \oplus Y}$}
-  \end{eqnarray*}
-  We now turn to our final construction. As in previous constructions, let
-  $\iota : W'' \hookrightarrow \Phi \backslash \Psi$ be an injection assigning
-  fresh nominals to worlds.  Define $\mathbbm{M}''' \assign \langle W''',
-  V''', R''', \mathcal{A}''' \rangle$ just as in the final construction in the
-  proof of Theorem \ref{completeness1}, except that $R'''_X$ and
-  $\mathcal{A}_v''' (X)$ are defined inductively as follows:
-
-  \begin{center}
-    \begin{tabular}{lll}
-      $\bullet$ & $R'''_t \assign \left\{ \begin{array}{ll}
-        R''_t & t \in \Xi\\
-        W''' \times W''' & o / w
-      \end{array} \right.$ & \\
-      $\bullet$ & $R'''_{X \oplus Y} \assign R'''_X \cap R'''_Y$ & \\
-      &  & \\
-      $\bullet$ & $\mathcal{A}'''_v (t) \assign \{\phi \hspace{1em} | \phi \in
-      \mathcal{A}''_v \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
-      \neg v R'''_t u\}$ & where $t \in \Pi$\\
-      $\bullet$ & $\mathcal{A}'''_v (X \oplus Y) \assign \mathcal{A}'''_v (X)
-      \cup \mathcal{A}'''_v (Y)$ & 
-    \end{tabular}
-  \end{center}
-
-  Induction over complexity of subformulae $\phi$ of $\psi$ yields
-  $\mathbbm{M}'', w \vDash \phi \Longleftrightarrow \mathbbm{M}''', w \vDash
-  \phi$, so we know that there is some world $w \in W'''$ such that
-  $\mathbbm{M}''', w \nvDash \psi$.  All that is left is to illustrate that
-  $\mathbbm{M}'''$ has the properties we desire.
-
-  First note that by definition, $\mathbbm{M}'''$ makes true
-  \tmtextbf{CHOICE}.  Next, an induction argument on the complexity of a
-  terms $X$, making essential use of (\ref{sub}$'$), yields:
-  \[ u R_X''' v \Longleftrightarrow \mathbbm{M}''', v \vDash \bigwedge
-     \mathcal{A}'''_v (X) \]
-  With this, $\mathbbm{M}'''$ makes true \tmtextbf{JSND} since it inherits
-  (\ref{refl}).  Finally, we note that we may repeat our previous arguments
-  from Theorem \ref{completeness1} to prove \tmtextbf{JCSQ}.
-\end{proof}
-
-\subsection{Lattice Justification Logic}
-
-{\color{red} NOTE.  THIS SECTION HAS SOME SERIOUS PROBLEMS AND IT'S PROBABLY
-WRONG...}
-
-Implicit in our previous presentation of SJL.  $\oplus$ behaves like a union
-operation for knowledge bases, and dually like an intersection operation on
-accessibility relations.  It is natural to think of $\oplus$ as a join/meet
-operator over a {\tmem{semi-lattice}}.  In this section we make this
-explicit, by increasing the expressive power of simple JL to express the order
-theory inherent in knowledge bases.  We call the novel logic presented in
-this section \tmtextit{Lattice Justification Logic} (LJL){\footnote{We note
-that ``Semi-Lattice Justification Logic'' may be a more appropriate name,
-however we have decided to shorten semic-lattice to lattice in this article
-for purposes of concision.}}.  Lattice JL may be considered a novel logic for
-studying the dynamics of \tmtextit{theory change}, where the logic employed by
-the changing theories could be LJL itself.
-
-\begin{definition}
-  $\mathcal{L}_{\tmop{LJL}} (\Phi, \Pi)$ extends $\mathcal{L}_{\tmop{SJL}}
-  (\Phi, \Pi)$ to:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi
-     \hspace{1em} | \hspace{1em} X \sqsubseteq Y \]
-  where $X, Y \in \tau (\Pi)$
-\end{definition}
-
-\begin{definition}
-  \label{justmodels}A {\tmstrong{lattice justification model}} $\mathbbm{M}=
-  \langle W, V, R, \mathcal{A}, \preccurlyeq \rangle$ is a simple
-  justification model with a new relation $\preccurlyeq : W \rightarrow
-  2^{\tau (\Pi) \times \tau (\Pi)}$ between terms, indexed by worlds.  The
-  semantics of $\sqsubseteq$ correspond to $\preccurlyeq$ as follows:
-  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow X
-     \preccurlyeq_w Y \]
-\end{definition}
-
-\begin{definition}
-  A lattices justification model is said to make true \tmtextbf{LATTICE} if
-  and only if:
-  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow \mathcal{A}_w
-     (X) \subseteq \mathcal{A}_w (Y) \]
-\end{definition}
-
-Table \ref{logic6} lists the axioms for the logic of lattice justification
-models with the properties we have been investigating:
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
-    \Box_X \psi$ & \\
-    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash X \sqsubseteq Y \rightarrow (X : \phi) \rightarrow Y : \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_X$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow \Box_X \phi \rightarrow \Box_Y \phi$ &
-    \\
-    $\vdash X \sqsubseteq X$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow Y \sqsubseteq Z \rightarrow X
-    \sqsubseteq Z$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow X \sqsubseteq Z \oplus Y$ & $\vdash X
-    \sqsubseteq Y \rightarrow X \sqsubseteq Y \oplus Z$\\
-    $\vdash X \sqsubseteq Z \rightarrow Y \sqsubseteq Z \rightarrow X \oplus Y
-    \sqsubseteq Z$ & \\
-    & \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic6}Lattice Justification Logic}
-\end{table}
-
-\begin{theorem}
-  \label{completeness6}Assuming an infinite store of proposition letters
-  $\Phi$, LJL is sound and weakly complete for lattice justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND}, \tmtextbf{CHOICE} and
-  \tmtextbf{LATTICE}
-\end{theorem}
-
-\begin{proof}
-  Assume $\nvdash \psi$.  Let $\mathbbm{M} \assign \langle W, V, R,
-  \mathcal{A}, \preccurlyeq \rangle$ be the same as the finitary canonical
-  model we initially constructed in Theorem \ref{completeness5}, only
-  $\preccurlyeq$ is defined as:
-  \[ X \preccurlyeq_w Y \Longleftrightarrow w \vdash X \sqsubseteq Y \]
-  We may deduce that there is a world $w \in W$ such that $\mathbbm{M}, w
-  \nvDash \psi$.  This canonical model makes true properties (\ref{fin})
-  through (\ref{union}) we listed in Theorem \ref{completeness5}, as well as a
-  certain new properties:
-
-  \begin{descriptioncompact}
-    \item[6$\preccurlyeq$] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$
-    then $R_Y [v] \subseteq R_X [v]$
-
-    \item[7] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$ then
-    $\mathcal{A}_v (X) \subseteq \mathcal{A}_v (Y)$
-
-    \item[8] If $X \nin \Xi$, then $R_X = W \times W$ and $\mathcal{A}_v (X) =
-    \varnothing$ for all $v \in W$
-
-    \item[9] $\langle \preccurlyeq_v, \oplus \rangle$ is a join-semilattice
-    over $\tau (\Pi)$ for all $v \in W$
-  \end{descriptioncompact}
-
-  As in previous constructions, completeness is achieved by through a series
-  of model refinements.  Note that property 8 has been implicitly true in all
-  of our previous constructions, although we have not been interested in
-  enforcing it to be inherited by model refinements previously.
-
-  We first construct a model $\mathbbm{M}'$ which is bisimular to
-  $\mathbbm{M}$, where (\ref{refl}) is strengthened to a biconditional.  This
-  is done exactly as we proceeded in previous constructions. We note that the
-  notion of ``bisimulation'' here includes that two bisimular worlds $v$ and
-  $u$ must have isomorphic semi-lattices $\preccurlyeq_v$ and
-  $\preccurlyeq_w$.  This is achieved by enforcing that $\preccurlyeq_{v_l}
-  \assign \preccurlyeq_{v_r} \assign \preccurlyeq_v$. As before, we have that
-  $\mathbbm{M}', w \nvDash \psi$ for some world $w \in W'$.
-
-  We next strengthen (6$\preccurlyeq$) to a biconditional.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em} X
-    \preccurlyeq_v Z\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  $\mathbbm{M}''$ is bisimular to $\mathbbm{M}'$ by the same mechanism as the
-  previous construction.  The important feature of this structure is to
-  observe that the converse of (6$\preccurlyeq$) holds:
-  \begin{eqnarray*}
-    R_Y [v] \subseteq R_X [v] & \Longleftrightarrow & \forall Z \in \Xi
-    \forall u_Z \in W'' (v_Q R'_Z u_Z \Longrightarrow v_Q R_X' u_Z)\\
-    & \Longleftrightarrow & \forall Z \in \Xi \forall u_Z \in W'' (v R'_Z
-    \Longrightarrow v_Q R_X u_Z)
-  \end{eqnarray*}
-
-  Our first transformation strengthens (\ref{union}), (6$\preccurlyeq$a) and
-  (6$\preccurlyeq$b) so that they hold for all terms in $\tau (\Pi)$, rather
-  than being restricted to $\Xi$.  To this end define $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}', \preccurlyeq' \rangle$ where $W'$, $R'$
-  and $\preccurlyeq'$ are the same as in $\mathbbm{M}$, but $R'$ and
-  $\mathcal{A}'$ have the following modifications:
-  \begin{eqnarray}
-    R'_Y [v] & \assign & \bigcap_{X \preccurlyeq_v Y} R_X [v] \nonumber\\
-    \mathcal{A}'_v (Y) & \assign & \bigcup_{X \preccurlyeq_v Y} \mathcal{A}'_v
-    (X) \nonumber
-  \end{eqnarray}
-
-\end{proof}
-
-\subsection{Neighborhood Semantics}
-
 Neighborhood semantics were originally developed by Dana Scott and Richard
@@
 
-This concludes our analysis of knowledge bases using neighborhood semantics.
-
-\subsection{\label{quantifying}Using Modalities to Quantify over Knowledge
-Bases}
-
-\section{Conclusions \& Further Research}
-
-The logic presented in Table \ref{logic1} is a conservative extension of the
-basic modal logic $K$, which means that its decision problem is
-\tmtextsf{PSPACE} hard (a lower bound).  Our finitary completeness proof
-establishes that its complexity is in \tmtextsf{EXP2-TIME} (an upper bound).
-
-Worlds in epistemic logic might correspond to fantastic, pretend scenarios;
-however, it may be desirable for some philosophers to model knowledge about
-imaginary lands.  After all, many children ``know'' a lot about Tolkien's
-{\tmem{middle earth}} or Rowling's {\tmem{Hogwarts}} (the school Harry Potter
-attends).
-
-\bibliographystyle{plain}
-\bibliography{zotero}
-
-\end{document}
+This concludes our analysis of knowledge bases using neighborhood
+semantics.
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "paper"
+%%% End:

### 2010-12-15 paper.tex
Refactored paper so all sections are seperate documents

@@
 \usepackage{stmaryrd}
+\usepackage[myoption=\fixme]{fixme}
 
@@
   In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem
-  proposed a research program for logic of \tmtextit{explicit knowledge}. \
+  proposed a research program for logic of \tmtextit{explicit knowledge}. 
   Two efforts have since emerged with proposals for logic of explicit
@@
 
-\section{Introduction\label{intro}}
-
-The modern tradition in epistemic logic is to assume knowledge modalities
-conform to the $S 5$ axiom schema.  As noted in
-{\cite{halpern_set-theoretic_1999,rubinstein_modeling_1998}}, the semantics of
-$S 5$ knowledge correspond exactly to partitioning a collection of situations
-into \tmtextit{information sets}, which is the traditional approach in game
-theory and decision theory.  While it is not commonly acknowledged in
-epistemic logic, economists and philosophers accept that traditional decision
-theory is externalist and behaviourist in nature
-(FIXME)
-\footnote{An early essay by
-Amartya Sen on the philosophical foundations of traditional decision theory
-makes the behaviorist reading of decision theory clear
-\cite{sen_behaviour_1973}.  Kaushik Basu also discusses the behaviorist
-nature of decision theory {\cite[pgs. 53--54]{basu_revealed_1980}}. 
-Finally, Donald Davidson appeals to decision theory to motivate an externalist
-epistemology in \cite{davidson_could_1995}.}.
-
-In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem proposed
-a research program to find logics for explicit knowledge, providing the first
-suggestion of an internalist perspective on epistemic logic.  Subsequently,
-Sergei Artemov and Elena Nogina proposed a logic of explicit justification,
-which has come to be known as \tmtextit{Justification Logic} (JL)
-{\cite{artemov_introducing_2005}}, based on Artemov's \tmtextit{Logic of
-Proofs} {\cite{artemov_logic_1994}}.  While the original semantics of JL was
-interpretability into Peano Arithmetic, Melvin Fitting proposed Kripke
-semantics for JL in {\cite{fitting_logic_2005}}.  Recently, Fernando
-Vel\'azquez-Quesada and Johan van Benthem have developed a simpler framework
-for explicit epistemics in {\cite{van_benthem_inference_2009}}, entitled the
-\tmtextit{Dynamics of Awareness}.  This work was based on Joseph Halpern and
-Ronald Fagin's original \tmtextit{Awareness Logic} {\cite{fagin_belief_1987}}.
-
-In this essay we repurpose various externalist logics to take on an
-internalist reading.  The concept of a \tmtextit{knowledge base}, from which
-beliefs may be implicitly deduced, will play a crucial role in our discussion.
-\ We propose this as an avenue for representing foundationalist perspectives
-on epistemology in epistemic logic.  Our philosophical motivation is taken
-from two sources.  The first is Vincent Hendricks in
-{\cite{hendricks_mainstream_2006}}, where he characterizes the principal of
-{\tmem{logical omniscience}} for implicit knowledge in epistemic
-logic{\footnote{We have modified Hendricks' notation here slightly to match
-our own.}}:
-
-\begin{quote}
-  {\tmem{Whenever an agent $\Xi$ knows all of the formulae in $\mathcal{A}$,
-  and $\phi$ follows logically from $\mathcal{A}$, then $\Xi$ [implicitly]
-  knows $\phi$.}}
-\end{quote}
-
-We will design our semantics such that ``$\Box \phi$'' may be equated with
-``$\phi$ follows logically from a knowledge base $\mathcal{A}$,'' which is
-sometimes written as $\phi \in \tmop{Cn} ( \mathcal{A})$ in the artificial
-intelligence literature.  Our second inspiration comes from what Hilary
-Kornblith calls the \tmtextit{the arguments on paper thesis}
-{\cite{kornblith_beyond_1980}}, which he feels characterizes apsychological,
-internalist theories of knowledge:
-
-\begin{quote}
-  Let us suppose that, for any person, it is possible, at least in principle,
-  to list all of the propositions that person believes.  The
-  arguments-on-paper thesis is just the view that a person has a justified
-  belief that a particular proposition is true just in case that proposition
-  appears on the list of propositions that person believes, and either it
-  requires no argument, or a {\tmem{good argument}} can be given for it which
-  takes as premises certain other propositions on the list.
-\end{quote}
-
-Kornblith asserts that foundationalism and coherentism vie for accounts of a
-``good argument'' in the above thesis.  He provides an extensive bibliography
-citing proposals for this principle by a number of 20th century
-epistemologists, including figures such as A.J. Ayer and C.I. Lewis.  The
-rest of Kornblith's paper is devoted to attacking this view and proposing a
-form of naturalized epistemology; we will not address this debate here,
-however.
-
-We adopt a arguments-on-paper-thesis perspective on epistemic logic in this
-paper.  We consider a \tmtextit{good argument} to be a logical derivation
-from propositions present in a knowledge base.  In this fashion, ou.  \
-Special attention will be given to \tmtextit{sound derivations}, which will be
-thought of as a form of knowledge.  In Awareness Logic, we will interpret
-awareness of a formula as membership in a knowledge base.  We prove
-completeness for basic awareness logic and a hybrid logic extension.  Logics
-of multiple knowledge bases are also presented: a simplified form of
-Justification Logic, a logic with neighborhood semantics, an a logic with
-modalities for quantifying over knowledge bases.  We conclude with an
-application to naturalized epistemology found in the psychological literature.
+\section{Introduction}
+\label{intro}
+\input{introduction.tex}
 
@@
 
-\subsection{Awareness Logic\label{awarenesslogic}}
-
-In this section, we give the explicit semantics to basic awareness logic,
-originally presented in {\cite{fagin_belief_1987}}, with an additional axiom.
-\ One difference in our presentation is the inclusion of a novel letter and a
-superficial change in notation.  This work is inspired by the developments in
-van Benthem and Vel\'azquez-Quesada {\cite{van_benthem_inference_2009}}.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and define the language $\mathcal{L}_A
-  (\Phi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A : \phi \hspace{1em}
-  \]
-\end{definition}
-
-We define the other connectives and modal operators as usual for classical
-modal logics.
-
-\begin{definition}
-  \label{awarenessmodels}An {\tmstrong{awareness model}} $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V : \Phi
-  \cup \{\circlearrowleft\} \rightarrow 2^W$ and an awareness function
-  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$.  We will usually
-  denote $\mathcal{A} (w)$ as $\mathcal{A}_w$.
-
-  Define the semantic entailment relation $\vDash$ where atomic propositions,
-  logical connectives and modality are interpreted as usual.  We employ the
-  following novel definition:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \mathcal{A_w}
-  \end{eqnarray*}
-\end{definition}
-
-The following definition distinguishes us from previously investigations of
-awareness logic:
-
-\begin{definition}
-  Define the ``\tmtextbf{theory of a model} $\mathbbm{M}$'' as:
-  \[ \tmop{Th} (\mathbbm{M}) \assign \{\phi \hspace{1em} | \hspace{1em}
-     \mathbbm{M}, v \vDash \phi \text{ for all } v \in W\} \]
-  We define the following properties that a model $\mathbbm{M}$ may posses:
-
-  \begin{descriptiondash}
-    \item[CSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w \vdash \phi$
-
-    \item[SND] $\mathbbm{M}, w \vDash \circlearrowleft \text{ iff }
-    \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w$
-  \end{descriptiondash}
-
-  Here $\vdash$ is any logical consequence relation which is sound for
-  $\vDash$, making true \tmtextbf{modus ponens} and \tmtextbf{reflection} (ie,
-  $\Gamma \vdash \phi$ if $\phi \in \Gamma$)
-\end{definition}
-
-Neither \tmtextbf{CSQ} nor \tmtextbf{SND} correspond to simple modally
-definable properties.
-
-Intuitively, the \tmtextbf{CSQ} asserts that an agent believes a formula
-$\phi$ if and only if it follows logically from their knowledge base and their
-background knowledge, represented by $\tmop{Th} (\mathbbm{M})$. \
-\tmtextbf{CSQ} is Vincent Hendrik's principle of logical omniscience mentioned
-in {\S}\ref{intro}.
-
-\tmtextbf{SND} asserts that $\circlearrowleft$ corresponds to the agent's
-knowledge base being sound. A sound knowledge base will only render true
-conclusions when used in deductions.  If one considers ``the existance of a
-sound deduction'' sufficient for a kind of knowledge, then $\circlearrowleft$
-is suitable for investigating this notion of epistemology.  That is, if
-$\mathbbm{M}, w \vDash \circlearrowleft \wedge \Box \phi$, then we may
-naturally say that the agent (implicitly) {\tmem{knows}} $\phi$ on the basis
-of $\mathcal{A}_w$, rather than merely {\tmem{believing}} $\phi$ on the basis
-of $\mathcal{A}_w$.
-
-The logic of models making true \tmtextbf{CSQ} and \tmtextbf{SND} is provided
-in Table \ref{logic1}.
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash \Box(\phi \rightarrow \psi) \rightarrow \Box \phi \rightarrow \Box
-    \psi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$\\
-    $\vdash \circlearrowleft \rightarrow \Box \phi \rightarrow \phi$\\
-    \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box \phi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic1}Awareness Logic for \tmtextbf{CSQ} and
-  \tmtextbf{SND}}
-\end{table}
-
-\begin{theorem}
-  \label{completeness1}Assuming an infinite store of proposition letters
-  $\Phi$, the awareness logic presented is sound and weakly complete for
-  awareness models making true \tmtextbf{CSQ} and \tmtextbf{SND}.
-\end{theorem}
-
-\begin{proof}
-  Soundness is straightforward, so we will only address completeness.  Assume
-  $\nvdash \psi$.  Consider the finite canonical model $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A} \rangle$ formed of maximally consistent sets of
-  subformulae of $\phi$ (closed under single negations{\footnote{A discussion
-  of this property may be found in {\cite[pg.
-  243]{blackburn_modal_2001}}.}}), as per the finitary modal completeness
-  proofs found in {\cite[chapter 4.8]{blackburn_modal_2001}} and
-  {\cite[chapter 5]{boolos_logic_1995}}.  Typical presentations do not
-  include awareness, however it is defined intuitively in this case:
-  \[ \phi \in \mathcal{A}_w \Longleftrightarrow A : \phi \in w \]
-  Since $\psi$ is a subformula of itself, we have $\mathbbm{M}, w \nvDash
-  \psi$ for some world $w$ by a finitary {\tmem{Lindenbaum Lemma}} and
-  {\tmem{Truth Theorem}}.  Moreover, it is straightforward to verify that
-  $\mathbbm{M}$ makes true the following properties:
-  \begin{enumeratenumeric}
-    \item $W$ and $\mathcal{A}_v$ are finite, and $\psi \in \mathcal{A}_v$
-    only if $\psi$ is a (possibly negated) subformula of $\phi$
-
-    \item if $\mathbbm{M}, v \vDash A : \psi$ then $\mathbbm{M}, v \vDash \Box
-    \psi$
-
-    \item if $\mathbbm{M}, v \vDash \circlearrowleft$ then $v R v$
-  \end{enumeratenumeric}
-
-  We next produce a bisimular{\footnote{The notion of bisimulation is
-  discussed at length in {\cite[chapter 2.2]{blackburn_modal_2001}}.  We
-  note that the basic definition and all of the usual theorems (modal
-  equivalence, Henessy Milner, etc.) may be generalized to awareness models in
-  a straightforward fashion. }} model $\mathbbm{M}'$ which makes true (1), (2)
-  and a stronger from of (3):
-
-  {\hspace*{\fill}}\begin{tabular}{ll}
-    \tmtextbf{3$'$.} & $\mathbbm{M}', v \vDash \circlearrowleft$ iff $v R v$
-  \end{tabular}{\hspace*{\fill}}
-
-  To this end define $\mathbbm{M}' \assign \langle W', V', R', \mathcal{A}'
-  \rangle$ such that{\footnote{Throughout this article, we use $l$ and $r$ to
-  denote the two canonical injections associated with the coproduct $W \uplus
-  W$. We will use $v_l$ and $v_r$ as the shorthand for $l (v)$ and $r (v)$
-  respectively.}}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $R' \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v R
-    u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em} \mathbbm{M},
-    v \vDash \circlearrowleft\}$
-
-    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
-    (v)$
-  \end{itemizedot}
-
-  It is straightforward to verify that $\mathbbm{M}'$ makes true the desired
-  properties.  Let $Z \assign \{(v, v_l), (v, v_r) \hspace{1em} |
-  \hspace{1em} v \in W\}$.  then $Z$ is a bisimulation between $\mathbbm{M}$
-  and $\mathbbm{M}'$.  Therefore we know there is some $w \in W$ such that
-  $\mathbbm{M}', w_l \nvDash \psi$ and $\mathbbm{M}', w_r \nvDash \psi$.
-
-  Finally we construct a model $\mathbbm{M}''$ which agrees with
-  $\mathbbm{M}'$ for all subformulae of $\psi$, which makes true
-  \tmtextbf{CSQ} and \tmtextbf{SND}.  Let $\Lambda$ be the set of proposition
-  letters occuring in $\psi$.  We will make use members of $\Phi \backslash
-  \Lambda$ as {\tmem{nominals}}, as per the tradition in hybrid logic.  This
-  is possible since both $W'$ and $\Lambda$ are finite and $\Phi$ is infinite
-  by hypothesis.  Let $\iota : W \uplus W \hookrightarrow \Phi \backslash
-  \Lambda$ be an injection assigning a fresh nominal associated with each
-  world in $\mathbbm{M}'$.  Now define $\mathbbm{M}'' \assign \langle W'',
-  V'', R'', \mathcal{A}'' \rangle$, where:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
-      \begin{array}{ll}
-        V' (p) & p \in \Lambda\\
-        \{v\} & p = \iota (v)\\
-        \varnothing & o / w
-      \end{array} \right.$\\
-      $\bullet$ & $R'' \assign R'$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}''_v \assign \{\phi \hspace{1em} | \phi \in \mathcal{A}'_v
-      \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em} \neg v R' u\}$
-    \end{tabular}
-  \end{center}
-
-  By induction we have that for every subformula $\phi$ of $\psi$ that
-  $\mathbbm{M}', v \vDash \phi$ if and only if $\mathbbm{M}'', v \vDash \phi$,
-  hence $\mathbbm{M}'', w_l \nvDash \psi$.
-
-  All that is left to show is that $\mathbbm{M}''$ makes true \tmtextbf{CSQ}
-  and \tmtextbf{SND}.  $\mathbbm{M}''$ has three further properties:
-  \begin{enumerateroman}
-    \item $\mathcal{A}''_v$ is finite for all worlds $v$
-
-    \item  $v R' u$ if and only if $\mathbbm{M}'', u \vDash \bigwedge
-    \mathcal{A}'' (v)$
-
-    \item The logic presented in Table \ref{logic1} is sound for
-    $\mathbbm{M}''$
-  \end{enumerateroman}
-  From (ii) and the fact that $\mathbbm{M}'$ makes true (3$'$), we have
-  \tmtextbf{SND} for $\mathbbm{M}''$.
-
-  All that is left is to demonstrate \tmtextbf{CSQ} for some sound logic.  We
-  will use the logic in Table \ref{logic1} itself.  From (i), (ii), (iii),
-  and the \tmtextit{deduction theorem} for modal logic, we have the following
-  line of reasoning:
-
-  \begin{align*}
-    Th({\mathbbm{M}}''){\cup}\mathcal{A}''_v{\vdash}{\phi} &
-    {\Longleftrightarrow}Th({\mathbbm{M}}''){\vdash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\\
-    &
-    {\Longleftrightarrow}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}{\in}Th({\mathbbm{M}}'')\\
-    &
-    {\Longleftrightarrow}{\mathbbm{M}}'',u{\vDash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\text{
-    for all $u \in W''$}\\
-    & {\Longleftrightarrow}\text{ for all $u \in W''$, if
-    }{\mathbbm{M}}'',u{\vDash}\mathcal{A}''_v\text{ then
-    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
-    & {\Longleftrightarrow}\text{ for all $u \in W''$, if }v R 'u \text{ then
-    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
-    & {\Longleftrightarrow}{\mathbbm{M}}'',v{\models}\Box{\phi}
-  \end{align*}
-\end{proof}
+\subsection{Awareness Logic}
+\label{awarenesslogic}
+\input{awareness.tex}
 
 \subsection{Hybrid Awareness Logic}
-
-The method of the above completeness proof makes implicit use of concepts from
-hybrid logic{\footnote{Hybrid logic was first presented in
-{\cite{prior_revised_1969}} and later formally developed in
-{\cite{bull_approach_1970}}.}}.  In this section we adapt hybrid logic and
-show that it is a complete for reasoning about knowledge bases.  We note that
-because of the increased expressive power of hybrid logic, our completeness
-theorem is simpler.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
-  language $\mathcal{L}_H (\Phi, \Psi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} i \in \Psi \hspace{1em} | \hspace{1em} \bot \hspace{1em} |
-     \hspace{1em} \phi \rightarrow \psi \hspace{1em} | \hspace{1em} \Box \phi
-     \hspace{1em} | \hspace{1em} A : \phi \hspace{1em} | \hspace{1em} \forall
-     \phi \]
-\end{definition}
-
-Our approach in hybrid logic is to employ a universal modality along with
-nominals.  This framework presents a logic where the agent may reason about
-various labeled scenarios.  Scenarios may be multiply labeled or not labeled
-at all.  From these intuitions we have the following definition:
-
-\begin{definition}
-  \label{hybridsemantics}Let a \tmtextbf{hybrid model} $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A}, \ell \rangle$ be an awareness model as in Definition
-  \ref{awarenessmodels}, along with a partial labeling function $\ell : \Psi
-  \nrightarrow W$
-
-  The semantics for $\vDash$ are the same as in Definition
-  \ref{awarenessmodels}, only we have
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \forall \phi & \text{iff} & \forall v \in
-    W.\mathbbm{M}, v \vDash \phi\\
-    \mathbbm{M}, w \vDash i & \text{iff} & \ell (i) = w
-  \end{eqnarray*}
-\end{definition}
-
-The other connectives and operators are defined as usual, although we employ a
-few special shorthands:
-
-\begin{definition}
-  We employ the following special abbreviations:
-  \begin{eqnarray}
-    \text{\tmtextup{@}}_i \phi \assign \forall (i \rightarrow \phi)
-    \hspace{2em} & \exists \phi \assign \neg \forall \neg \phi \hspace{3em} &
-    \circlearrowleft_i \assign \diamondsuit i \nonumber
-  \end{eqnarray}
-\end{definition}
-
-This gives rise to a validity reflecting one of the axioms we saw in
-{\S}\ref{awarenesslogic}:
-\[ \vDash \circlearrowleft_i \rightarrow \Box \phi \rightarrow
-   \text{\tmtextup{@}}_i \phi \]
-This can be read as ``If the agent's knowledge base is sound at world $i$,
-then if they can deduce something from their knowledge base, what they deduce
-must be true at world $i$.'.  In a way, this may be considered as
-{\tmem{relativising}} knowledge particular named situations.
-
-The semantics in Definition \ref{hybridsemantics} obviates the \tmtextbf{SND}
-principle we previously presented, since there is no explicit
-$\circlearrowleft$ symbol in this setting. \tmtextbf{CSQ} still makes sense
-without modification, however.  The following gives a logic for hybrid models
-making true \tmtextbf{CSQ}:
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & $\vdash \forall (\phi
-    \rightarrow \psi) \rightarrow \forall \phi \rightarrow \forall \psi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & $\vdash \forall
-    \phi \rightarrow \phi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & $\vdash \forall \phi \rightarrow
-    \forall \forall \phi$\\
-    $\vdash \Box(\phi \rightarrow \psi) \rightarrow \Box \phi \rightarrow \Box
-    \psi$ & $\vdash \exists \phi \rightarrow \forall \exists \phi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$ & $\vdash \forall \phi \rightarrow
-    \Box \phi$\\
-    & $\vdash i \rightarrow \phi \rightarrow \text{\tmtextup{@}}_i \phi$\\
-    & \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi}{\vdash \Box \phi}$ &
-      {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \forall \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic2}Hybrid Awareness Logic for \tmtextbf{CSQ}}
-\end{table}
-
-\begin{theorem}
-  \label{completeness2}Assuming an infinite store of nominals $\Psi$, the
-  hybrid awareness logic presented is sound and weakly complete for all hybrid
-  models making true \tmtextbf{CSQ}.
-\end{theorem}
-
-\begin{proof}
-  As before, soundness is trivial.  Completeness is based on a modification
-  of techniques found in {\cite[chapter 5]{boolos_logic_1995}}.  Assume
-  that $\nvdash \psi$ and let $\Sigma_0$ be the set of subformulae of $\psi$,
-  and let $\Upsilon$ be the set of nominals occuring in $\psi$.  Define:
-
-  \begin{align*}
-    {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{{\forall}{\phi}{\hspace{1em}}|{\hspace{1em}}\Box{\phi}{\in}{\Sigma}_0\}\\
-    {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{\text{@}_i{\phi}{\hspace{1em}},i{\rightarrow}{\phi}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1{\hspace{1em}}\&{\hspace{1em}}i{\in}{\Upsilon}\}\\
-    {\Sigma}_3 &
-    {\assign}{\Sigma}_2{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_2\}
-  \end{align*}
-
-  It is easy to see that $\Sigma_3$ is finite and closed under subformulae and
-  single negations. Let $\mathbbm{M}= \langle W, V, R_{\Box}, \sim_{\forall},
-  \mathcal{A} \rangle$ be the finite cannonical model formed of maximally
-  consistent subsets of $\Sigma_3$, where everything is defined as usual,
-  except $\sim_{\forall}$, which obeys the following specification:
-
-  \begin{align*}
-    w {\sim}_{{\forall}}v & {\Longleftrightarrow}(({\forall}{\phi}){\in}w
-    {\Longleftrightarrow}({\forall}{\phi}){\in}v)
-  \end{align*}
-
-  This model makes true the following properties:
-  \begin{enumerateroman}
-    \item $\sim_{\forall}$ is an equivalence relation
-
-    \item $R_{\Box} \subseteq \sim_{\forall}$
-
-    \item In each equivalence class specified by $\sim_{\forall}$, there is at
-    most one world making true $i$ for all $i \in \Upsilon$
-  \end{enumerateroman}
-  As in our previous construction we have that there is some world $w$ where
-  $\mathbbm{M}, w \nvDash \psi$.  Let $\mathbbm{M}^1 = \langle W', V',
-  R_{\Box}', \sim_{\forall}', \mathcal{A}' \rangle$ be the submodel generated
-  by $\{w\}$; we have that $\mathbbm{M}', w \nvDash \psi$ (see {\cite[chapter
-  2.1]{blackburn_modal_2001}} for details on generated submodels).  In this
-  model $\forall$ is a universal modality and either $\left\llbracket i
-  \right\rrbracket^{\mathbbm{M}'} = \varnothing$ or $\left\llbracket i
-  \right\rrbracket^{\mathbbm{M}'} =\{v\}${\footnote{As per the usual
-  convention, here $\left\llbracket \phi \right\rrbracket^{\mathbbm{M}}$
-  denotes $\{w \in W \hspace{1em} | \hspace{1em} \mathbbm{M}, w \vDash
-  \phi\}$.  We will drop $\mathbbm{M}$ where it is unambiguous.}}. Since the
-  store $\Psi$ of nominals is infinite and $\Upsilon$ is finite, we have that
-  $\Psi \backslash \Upsilon$ is infinite, so there is some injection $\iota :
-  W' \hookrightarrow \Psi \backslash \Upsilon$ which assigns a fresh nominal
-  to every world.  Let $\mathbbm{M}'' = \langle W'', V'', R'', \mathcal{A}'',
-  \ell \rangle$, where:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign V' (p)$\\
-      $\bullet$ & $R'' \assign R'_{\Box}$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}'' (v) \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
-      \mathcal{A}' (v)\} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
-      \neg v R' u\}$\\
-      \begin{tabular}{ll}
-        $\bullet$ & $\ell (i) \assign \left\{ \begin{array}{ll}
-          w & i \in \Upsilon \hspace{1em} \& \hspace{1em} \mathbbm{M}, w
-          \vDash i\\
-          \iota^{- 1} (i) & i \in \iota [W]\\
-          \text{undefined} & \text{o/w}
-        \end{array} \right.$
-      \end{tabular} & $R'' \assign R'_{\Box}$ &  &  & 
-    \end{tabular}
-  \end{center}
-
-  The the worlds is $\mathbbm{M}'$ and $\mathbbm{M}''$ agree on all
-  subformulae of $\psi$, hence $\mathbbm{M}'', w \nvDash \psi$. The same
-  reasoning as in the proof of Theorem \ref{completeness1} establishes and
-  that the logic in Table \ref{logic2} itself is sound for $\mathbbm{M}''$ and
-  makes true \tmtextbf{CSQ}, establishing completeness.
-\end{proof}
+\label{hybrid_awareness}
+\input{hybrid_awareness.tex}
 
@@
 \subsection{Simple Justification Logic}
-
-Justification Logic (JL) was originally developed by Artemov as the
-\tmtextit{Logic of Proofs} (LP) {\cite{artemov_logic_1994}}.  Its original
-purpose was to provide a framework for reasoning about explicit provability in
-Peano Arithmetic.  The first introduction of Justification Logic can be found
-in {\cite{artemov_introducing_2005}}, where Artemov and Nogina propose LP as a
-logic for reasoning about evidence.  In {\cite{fitting_logic_2005}}, Melvin
-Fitting provided JL with Kripke model based semantics.
-
-The principle innovation of LP/JL is to extend awareness logic, such that
-awareness operations are now \tmtextit{proof terms}.  Informally, we say that
-``a proof term $X$ witnesses proposition $\phi$'', denoted ``$X : \phi$'',
-whenever $X$ represents a proof of $\phi$.  Proofs may have
-{\tmstrong{multiple-conclusions}} in this system, so it is possible that $X :
-\phi$ and $X : \psi$ can be true where $\phi \neq \psi$.  In Fitting's Kripke
-semantics, $X : \phi$ means that $\phi$ is in awareness set corresponding to
-$X$.  Proof terms are thought be operating in a \tmtextit{multi-conclusion}
-proof system, so the same proof term may witness many different propositions.
-
-The logics LP/JL include operators over proofs terms, so that new proof terms
-may be assembled.  One operation of particular interest to us is
-{\tmem{choice}}, denoted $\oplus$.  The expression ``$X \oplus Y : \phi$''
-denotes that either $X$ or $Y$ are proofs witnessing $\phi$.  There are other
-operations which correspond to \tmtextit{modus ponens} and
-\tmtextit{proof-theoretic reflection}, however we do not consider these
-operations here.
-
-In this section we consider a simplified form of JL suitable for reasoning
-over multiple knowledge bases, which we call \tmtextit{simple justification
-logic} (SJL). However, instead of thinking of terms as representing proofs, we
-use them to represent knowledge bases. This is in the spirit of JL as a logic
-of evidence: we consider each knowledge base to be a corpus of evidence. \
-Each term ``names'' a different knowledge base at a particular world.  Terms
-may not refer to the same knowledge base at different worlds, just as in how
-in awareness logic the agent need not be aware of the same formulae at
-different worlds.  Finally, we will make use of JL's {\tmem{choice}} operator
-as a mechanism for forming the union of knowledge bases, creating new ones.
-
-\begin{definition}
-  Let $\Pi$ be a set of primitive terms.  Define $\tau (\Pi)$ with the
-  following grammar:
-  \[ X \hspace{1em} : : = \hspace{1em} t \in \Pi \hspace{1em} | \hspace{1em} X
-     \oplus Y \]
-
-  Let $\Phi$ be a set of letters and $\Pi$ a set of primitive terms, and
-  define the language $\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi \]
-  where $X \in \tau (\Pi)$
-\end{definition}
-
-\begin{definition}
-  \label{justmodels}A {\tmstrong{simple justification model}} $\mathbbm{M}=
-  \langle W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V
-  : \Phi \cup \{\circlearrowleft_X \hspace{1em} | \hspace{1em} X \in \tau
-  (\Pi)\} \rightarrow 2^W$, an indexed relation $R : \tau (\Pi) \rightarrow
-  2^{W \times W}$, along with a modified awareness function $\mathcal{A} : W
-  \times \tau (\Pi) \rightarrow 2^{\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)}$. \
-  In practice we will denote $\mathcal{A} (w, X)$ by a curried shorthand,
-  namely $\mathcal{A}_w (X)$.
-
-  The semantics for $\vDash$ have the following modifications:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box_X \phi & \text{iff} & \text{for all $v \in W$
-    where $w R_X v$ we have $\mathbbm{M}, v \vDash v$}\\
-    \mathbbm{M}, w \vDash X : \phi & \text{iff} & \phi \in \mathcal{A}_w (X)
-  \end{eqnarray*}
-\end{definition}
-
-\begin{definition}
-  The following defines properties a simple justification model may make true:
-
-  \begin{descriptiondash}
-    \item[JCSQ] $\mathbbm{M}, w \vDash \Box_X \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w (X) \vdash \phi$
-
-    \item[JSND] $\mathbbm{M}, w \vDash \circlearrowleft_X \text{ iff
-    $\mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w (X)$}$
-
-    \item[CHOICE] $\mathcal{A}_w (X \oplus Y) = \mathcal{A}_w (X) \cup
-    \mathcal{A}_w (Y)$
-  \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
-\end{definition}
-
-The above semantics are similar to the ones given in previous sections. \
-\tmtextbf{JCSQ} is the same as \tmtextbf{CSQ} from {\S}\ref{awarenesslogic},
-only it is relativized to a knowledge base denoted by $X$ at $w$.  The
-awareness logic of knowledge bases is special case of simple justification
-logic where there is only one term.
-
-Simplified justification logic is given in Table \ref{logic5}.  We assert
-without proof that this is a conservative extension of the awareness logic in
-{\S}\ref{awarenesslogic}.
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
-    \Box_X \psi$ & \\
-    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash (X \oplus Y : \phi) \rightarrow X : \phi$ & $\vdash (X \oplus Y :
-    \phi) \rightarrow Y : \phi$\\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_X$ &
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_Y$\\
-    $\vdash \Box_X \phi \rightarrow \Box_{X \oplus Y} \phi$ & \\
-    $\vdash \Box_{X \oplus X} \phi \rightarrow \Box_X \phi$ & $\vdash \Box_{(X
-    \oplus X) \oplus Y} \phi \rightarrow \Box_{X \oplus Y} \phi$ \\
-    $\vdash \Box_{X \oplus Y} \phi \rightarrow \Box_{Y \oplus X} \phi$ &
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{(Y \oplus X)
-    \oplus Z} \phi$\\
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{X \oplus (Y
-    \oplus Z)} \phi$ & \\
-    & \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic5}Simple Justification Logic}
-\end{table}
-
-\begin{theorem}
-  \label{completeness5}Assuming an infinite store of proposition letters
-  $\Phi$, SJL is sound and weakly complete for simple justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND} and \tmtextbf{CHOICE}
-\end{theorem}
-
-\begin{proof}
-  As in the previous proofs, we only show completeness.  Assume that $\nvdash
-  \psi$.  Let $\Xi \subseteq \tau (\Pi)$ be all of the subterms occurring in
-  $\psi$; we assume that $\Xi$ is non-empty, since otherwise we may obtain the
-  theorem via the usual completeness theorem for classical propositional
-  logic. Let $\Sigma_0$ be the subformulae of $\psi$.  Define:
-
-  \begin{align*}
-    {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{\Box_Y{\phi}{\hspace{1em}}|{\hspace{1em}}\Box_X{\phi}{\in}{\Sigma}_0{\hspace{1em}}\&{\hspace{1em}}Y{\in}{\Xi}\}\\
-    {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1\}
-  \end{align*}
-
-  As in the proof of Theorem \ref{completeness2}, it is simple to verify that
-  $\Sigma_2$ is closed under subformulae and single negations.  Let
-  $\mathbbm{M} \assign \langle W, V, R, \mathcal{A} \rangle$ be the finite
-  cannonical model formed of maximally consistent subsets of $\Sigma_2$, where
-  $V$ and $\mathcal{A}$ are defined as usual, and $R : \Xi \rightarrow 2^{W
-  \times W}$ is defined by:
-  \[ w R_X v \Longleftrightarrow \{\phi \hspace{1em} | \hspace{1em} \Box_X
-     \phi \in w\} \subseteq v \]
-  As in previous constructions we may prove the usual Lindenbaum and Truth
-  Lemmas an use them obtain a world $w \in W$ where $\mathbbm{M}, w \nvDash
-  \psi$.
-
-  Next, define an operator $\twonotes : \tau (\Pi) \rightarrow 2^{\Pi}$ where:
-  \[ \twonotes (X) \assign \{t \in \Pi \hspace{1em} | \hspace{1em} t \text{
-     occurs in } X\} \]
-  In other words, $\twonotes (X)$ is the set of atomic terms in $X$.  As in
-  our construction for Theorem \ref{completeness1}, $\mathbbm{M}$ makes true
-  certain properties, along with some new properties:
-  \begin{enumeratenumeric}
-    \item \label{fin}$W$ and $\mathcal{A}_v (X)$ are finite, and $\phi \in
-    \mathcal{A}_v (X)$ only if $\phi \in \Sigma_2$
-
-    \item if $\mathbbm{M}, v \vDash X : \phi$ then $\mathbbm{M}, v \vDash
-    \Box_X \phi$
-
-    \item \label{refl}if $\mathbbm{M}, v \vDash \circlearrowleft_X$ then $v
-    R_X v$
-
-    \item \label{sndness}For all $X \oplus Y \in \Xi$, $\mathbbm{M}, v \vDash
-    \circlearrowleft_{X \oplus Y}$ if and only if $\mathbbm{M}, v \vDash
-    \circlearrowleft_X$ and $\mathbbm{M}, v \vDash \circlearrowleft_Y$
-
-    \item \label{union}For all $X \oplus Y \in \Xi$, $\mathcal{A}_v (X \oplus
-    Y) = \mathcal{A}_v (X) \cup \mathcal{A}_v (Y)$
-
-    \item \label{sub}For all $X, Y \in \Xi$, if $\twonotes (X) \subseteq
-    \twonotes (Y)$ then $R_Y \subseteq R_X$
-  \end{enumeratenumeric}
-  As in our previous constructions, it is necessary to refine this model using
-  bisimulations to achieve properties which are not modally definable.  In
-  particular, we shall strengthen (\ref{refl}) to a biconditional and
-  (\ref{sub}) to:
-
-  \begin{center}
-    \begin{tabular}{ll}
-      \tmtextbf{6$'$.} & For all $X, Y \in \Xi$, $R_{X \oplus Y} = R_X \cap
-      R_Y$
-    \end{tabular}
-  \end{center}
-
-  We first strengthen (\ref{refl}) by constructing $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}' \rangle$, just as in Theorem
-  \ref{completeness1}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $R'_X \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v
-    R_X u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em}
-    \mathbbm{M}, v \vDash \circlearrowleft_X \}$
-
-    \item $\mathcal{A}' (v_l, X) \assign \mathcal{A}' (v_r, X) \assign
-    \mathcal{A} (v, X)$
-  \end{itemizedot}
-  The same bisimulation relation $Z$ previously given suffices.
-
-  We next make a strengthened the model where (\ref{sub}$'$) holds.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that{\footnote{Let $\{i_X \hspace{1em} | \hspace{1em} X \in \Xi\}$ be the
-  family of canonical injections into the coproduct $\uplus_{\Xi} W$. As per
-  our previous convention, we use $v_X$ as shorthand for $i_X (v)$.}}:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em}
-    \twonotes (X) \subseteq \twonotes (Z)\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  Note that this construction makes use of the assumption that $\Xi$ is
-  non-empty.  Let $Z \assign \{(v, v_X) \hspace{1em} | \hspace{1em} X \in \Xi
-  \hspace{1em} \& \hspace{1em} v \in W' \}$; it is straightforward to prove
-  that $Z$ is a bisimulation between $\mathbbm{M}'$ and $\mathbbm{M}''$, for
-  all relations corresponding to terms $X \in \Xi$. Hence $\mathbbm{M}'', w_X
-  \nvDash \psi$ for some $w_X \in W''$.  In addition, $\mathbbm{M}''$
-  inherits (\ref{fin}) through (\ref{sub}) from $\mathbbm{M}'$, as well as the
-  converse of (\ref{refl}).  Next observe, forall $X \oplus Y \in \Xi$:
-  \begin{eqnarray*}
-    \text{$(v_V, u_Z) \in R''_X \cap R''_Y$} & \Longleftrightarrow & \exists Z
-    \in \Xi . \text{$v R'_Z u \hspace{1em} \& \hspace{1em} \twonotes (X)
-    \subseteq \twonotes (Z) \hspace{1em} \& \hspace{1em} \twonotes (Y)
-    \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X) \cup \twonotes (Y) \subseteq \twonotes
-    (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X \oplus Y) \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow &  \text{$(v_V, u_Z) \in R''_{X \oplus Y}$}
-  \end{eqnarray*}
-  We now turn to our final construction. As in previous constructions, let
-  $\iota : W'' \hookrightarrow \Phi \backslash \Psi$ be an injection assigning
-  fresh nominals to worlds.  Define $\mathbbm{M}''' \assign \langle W''',
-  V''', R''', \mathcal{A}''' \rangle$ just as in the final construction in the
-  proof of Theorem \ref{completeness1}, except that $R'''_X$ and
-  $\mathcal{A}_v''' (X)$ are defined inductively as follows:
-
-  \begin{center}
-    \begin{tabular}{lll}
-      $\bullet$ & $R'''_t \assign \left\{ \begin{array}{ll}
-        R''_t & t \in \Xi\\
-        W''' \times W''' & o / w
-      \end{array} \right.$ & \\
-      $\bullet$ & $R'''_{X \oplus Y} \assign R'''_X \cap R'''_Y$ & \\
-      &  & \\
-      $\bullet$ & $\mathcal{A}'''_v (t) \assign \{\phi \hspace{1em} | \phi \in
-      \mathcal{A}''_v \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
-      \neg v R'''_t u\}$ & where $t \in \Pi$\\
-      $\bullet$ & $\mathcal{A}'''_v (X \oplus Y) \assign \mathcal{A}'''_v (X)
-      \cup \mathcal{A}'''_v (Y)$ & 
-    \end{tabular}
-  \end{center}
-
-  Induction over complexity of subformulae $\phi$ of $\psi$ yields
-  $\mathbbm{M}'', w \vDash \phi \Longleftrightarrow \mathbbm{M}''', w \vDash
-  \phi$, so we know that there is some world $w \in W'''$ such that
-  $\mathbbm{M}''', w \nvDash \psi$.  All that is left is to illustrate that
-  $\mathbbm{M}'''$ has the properties we desire.
-
-  First note that by definition, $\mathbbm{M}'''$ makes true
-  \tmtextbf{CHOICE}.  Next, an induction argument on the complexity of a
-  terms $X$, making essential use of (\ref{sub}$'$), yields:
-  \[ u R_X''' v \Longleftrightarrow \mathbbm{M}''', v \vDash \bigwedge
-     \mathcal{A}'''_v (X) \]
-  With this, $\mathbbm{M}'''$ makes true \tmtextbf{JSND} since it inherits
-  (\ref{refl}).  Finally, we note that we may repeat our previous arguments
-  from Theorem \ref{completeness1} to prove \tmtextbf{JCSQ}.
-\end{proof}
+\label{simple_justification}
+\input{simple_justification.tex}
 
 \subsection{Lattice Justification Logic}
-
-{\color{red} NOTE.  THIS SECTION HAS SOME SERIOUS PROBLEMS AND IT'S PROBABLY
-WRONG...}
-
-Implicit in our previous presentation of SJL.  $\oplus$ behaves like a union
-operation for knowledge bases, and dually like an intersection operation on
-accessibility relations.  It is natural to think of $\oplus$ as a join/meet
-operator over a {\tmem{semi-lattice}}.  In this section we make this
-explicit, by increasing the expressive power of simple JL to express the order
-theory inherent in knowledge bases.  We call the novel logic presented in
-this section \tmtextit{Lattice Justification Logic} (LJL){\footnote{We note
-that ``Semi-Lattice Justification Logic'' may be a more appropriate name,
-however we have decided to shorten semic-lattice to lattice in this article
-for purposes of concision.}}.  Lattice JL may be considered a novel logic for
-studying the dynamics of \tmtextit{theory change}, where the logic employed by
-the changing theories could be LJL itself.
-
-\begin{definition}
-  $\mathcal{L}_{\tmop{LJL}} (\Phi, \Pi)$ extends $\mathcal{L}_{\tmop{SJL}}
-  (\Phi, \Pi)$ to:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi
-     \hspace{1em} | \hspace{1em} X \sqsubseteq Y \]
-  where $X, Y \in \tau (\Pi)$
-\end{definition}
-
-\begin{definition}
-  \label{justmodels}A {\tmstrong{lattice justification model}} $\mathbbm{M}=
-  \langle W, V, R, \mathcal{A}, \preccurlyeq \rangle$ is a simple
-  justification model with a new relation $\preccurlyeq : W \rightarrow
-  2^{\tau (\Pi) \times \tau (\Pi)}$ between terms, indexed by worlds.  The
-  semantics of $\sqsubseteq$ correspond to $\preccurlyeq$ as follows:
-  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow X
-     \preccurlyeq_w Y \]
-\end{definition}
-
-\begin{definition}
-  A lattices justification model is said to make true \tmtextbf{LATTICE} if
-  and only if:
-  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow \mathcal{A}_w
-     (X) \subseteq \mathcal{A}_w (Y) \]
-\end{definition}
-
-Table \ref{logic6} lists the axioms for the logic of lattice justification
-models with the properties we have been investigating:
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
-    \Box_X \psi$ & \\
-    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash X \sqsubseteq Y \rightarrow (X : \phi) \rightarrow Y : \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_X$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow \Box_X \phi \rightarrow \Box_Y \phi$ &
-    \\
-    $\vdash X \sqsubseteq X$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow Y \sqsubseteq Z \rightarrow X
-    \sqsubseteq Z$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow X \sqsubseteq Z \oplus Y$ & $\vdash X
-    \sqsubseteq Y \rightarrow X \sqsubseteq Y \oplus Z$\\
-    $\vdash X \sqsubseteq Z \rightarrow Y \sqsubseteq Z \rightarrow X \oplus Y
-    \sqsubseteq Z$ & \\
-    & \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic6}Lattice Justification Logic}
-\end{table}
-
-\begin{theorem}
-  \label{completeness6}Assuming an infinite store of proposition letters
-  $\Phi$, LJL is sound and weakly complete for lattice justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND}, \tmtextbf{CHOICE} and
-  \tmtextbf{LATTICE}
-\end{theorem}
-
-\begin{proof}
-  Assume $\nvdash \psi$.  Let $\mathbbm{M} \assign \langle W, V, R,
-  \mathcal{A}, \preccurlyeq \rangle$ be the same as the finitary canonical
-  model we initially constructed in Theorem \ref{completeness5}, only
-  $\preccurlyeq$ is defined as:
-  \[ X \preccurlyeq_w Y \Longleftrightarrow w \vdash X \sqsubseteq Y \]
-  We may deduce that there is a world $w \in W$ such that $\mathbbm{M}, w
-  \nvDash \psi$.  This canonical model makes true properties (\ref{fin})
-  through (\ref{union}) we listed in Theorem \ref{completeness5}, as well as a
-  certain new properties:
-
-  \begin{descriptioncompact}
-    \item[6$\preccurlyeq$] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$
-    then $R_Y [v] \subseteq R_X [v]$
-
-    \item[7] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$ then
-    $\mathcal{A}_v (X) \subseteq \mathcal{A}_v (Y)$
-
-    \item[8] If $X \nin \Xi$, then $R_X = W \times W$ and $\mathcal{A}_v (X) =
-    \varnothing$ for all $v \in W$
-
-    \item[9] $\langle \preccurlyeq_v, \oplus \rangle$ is a join-semilattice
-    over $\tau (\Pi)$ for all $v \in W$
-  \end{descriptioncompact}
-
-  As in previous constructions, completeness is achieved by through a series
-  of model refinements.  Note that property 8 has been implicitly true in all
-  of our previous constructions, although we have not been interested in
-  enforcing it to be inherited by model refinements previously.
-
-  We first construct a model $\mathbbm{M}'$ which is bisimular to
-  $\mathbbm{M}$, where (\ref{refl}) is strengthened to a biconditional.  This
-  is done exactly as we proceeded in previous constructions. We note that the
-  notion of ``bisimulation'' here includes that two bisimular worlds $v$ and
-  $u$ must have isomorphic semi-lattices $\preccurlyeq_v$ and
-  $\preccurlyeq_w$.  This is achieved by enforcing that $\preccurlyeq_{v_l}
-  \assign \preccurlyeq_{v_r} \assign \preccurlyeq_v$. As before, we have that
-  $\mathbbm{M}', w \nvDash \psi$ for some world $w \in W'$.
-
-  We next strengthen (6$\preccurlyeq$) to a biconditional.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em} X
-    \preccurlyeq_v Z\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  $\mathbbm{M}''$ is bisimular to $\mathbbm{M}'$ by the same mechanism as the
-  previous construction.  The important feature of this structure is to
-  observe that the converse of (6$\preccurlyeq$) holds:
-  \begin{eqnarray*}
-    R_Y [v] \subseteq R_X [v] & \Longleftrightarrow & \forall Z \in \Xi
-    \forall u_Z \in W'' (v_Q R'_Z u_Z \Longrightarrow v_Q R_X' u_Z)\\
-    & \Longleftrightarrow & \forall Z \in \Xi \forall u_Z \in W'' (v R'_Z
-    \Longrightarrow v_Q R_X u_Z)
-  \end{eqnarray*}
-
-  Our first transformation strengthens (\ref{union}), (6$\preccurlyeq$a) and
-  (6$\preccurlyeq$b) so that they hold for all terms in $\tau (\Pi)$, rather
-  than being restricted to $\Xi$.  To this end define $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}', \preccurlyeq' \rangle$ where $W'$, $R'$
-  and $\preccurlyeq'$ are the same as in $\mathbbm{M}$, but $R'$ and
-  $\mathcal{A}'$ have the following modifications:
-  \begin{eqnarray}
-    R'_Y [v] & \assign & \bigcap_{X \preccurlyeq_v Y} R_X [v] \nonumber\\
-    \mathcal{A}'_v (Y) & \assign & \bigcup_{X \preccurlyeq_v Y} \mathcal{A}'_v
-    (X) \nonumber
-  \end{eqnarray}
-
-\end{proof}
+\label{lattice_justification}
+\input{lattice_justification.tex}
 
 \subsection{Neighborhood Semantics}
-
-Neighborhood semantics were originally developed by Dana Scott and Richard
-Montague in the early 1970s as a generalization of Kripke semantics \
-{\cite{montague_universal_2008,scott_advice_1970}}.  In
-{\cite{fagin_belief_1988}}, Halpern and Fagin adapted neighborhood semantics
-for reasoning about epistemic agents without logical omniscience.  In this
-section will demonstrate how these semantics may be modified so that
-neighborhoods corresponds to the logical consequences of a different knowledge
-bases.  This allows for using logics with neighborhood semantics for
-reasoning about multiple knowledge bases.  A point of distinction of
-neighborhood semantics from JL is that it may be possible that two distinct
-knowledge bases cannot be merged by the agent.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
-  language $\mathcal{L}_N (\Phi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \bot \hspace{1em} | \hspace{1em} \phi \rightarrow \psi
-     \hspace{1em} | \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A :
-     \phi \hspace{1em} | \hspace{1em} K \phi \]
-\end{definition}
-
-Just as previous semantics, ``$\Box \phi$'' is intended to mean that the agent
-has an argument for $\phi$ from some knowledge base.  A novelty we present
-here is that ``$K \phi$'' means that the agent has an argument for $\phi$ from
-some \tmtextit{sound} knowledge base.
-
-\begin{definition}
-  \label{neighborhoodmodels}A {\tmstrong{neighborhood model}} $\mathbbm{M}=
-  \langle W, V, \mathcal{N}, \mathcal{A} \rangle$ has a neighborhood function
-  $\mathcal{N} : W \rightarrow 2^{2^W}$ and a multi-awareness function
-  $\mathcal{A} : W \rightarrow 2^{2^{\mathcal{L}_N (\Phi)}}$
-
-  The semantics for $\vDash$ have the following modifications:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box \phi & \text{iff} & \text{there exists a $U \in
-    \mathcal{N}_w$ where $\mathbbm{M}, v \vDash \phi$ for all $v \in U$}\\
-    \mathbbm{M}, w \vDash K \phi & \text{iff} & \text{there exists a $U \in
-    \mathcal{N}_w$ where $w \in U$ and $\mathbbm{M}, v \vDash \phi$ for all $v
-    \in U$}\\
-    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \bigcup
-    \mathcal{A_w}
-  \end{eqnarray*}
-\end{definition}
-
-Here we modify our previous notion of \tmtextbf{CSQ} and \tmtextbf{SND} to
-match how our semantics are intended for reasoning over multiple bases:
-
-\begin{definition}
-  The following defines properties a neighborhood model may make true:
-
-  \begin{descriptiondash}
-    \item[NCSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff there exists a set
-    $X \in \mathcal{A}_w$ such that } \tmop{Th} (\mathbbm{M}) \cup X \vdash
-    \phi$
-
-    \item[NSND] $\mathbbm{M}, w \vDash K \phi \text{ iff there exists a set $X
-    \in \mathcal{A}_w$ such that $\mathbbm{M}, w \vDash X$ and } \tmop{Th}
-    (\mathbbm{M}) \cup X \vdash \phi$
-  \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
-\end{definition}
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash K \phi \rightarrow \Box \phi$\\
-    $\vdash K \phi \rightarrow \phi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$\\
-    \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi \rightarrow \psi}{\vdash \Box
-      \phi \rightarrow \Box \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi
-      \rightarrow \psi}{\vdash K \phi \rightarrow K \psi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic3}A Neighborhood Logic for \tmtextbf{NCSQ} and
-  {\tmstrong{NSND}}}
-\end{table}
-
-\begin{theorem}
-  Assuming an infinite store of letters $\Phi$, the logic in Table
-  \ref{logic3} is sound and weakly complete for neighborhood semantics making
-  true \tmtextbf{NCSQ} and \tmtextbf{NSND}.
-\end{theorem}
-
-\begin{proof}
-  Assume that $\nvdash \psi$, and define the finitary canonical model
-  $\mathbbm{M}= \langle W, V, \mathcal{K}, \mathcal{N}, \mathcal{A} \rangle$
-  where:
-  \begin{itemizedot}
-    \item $W \assign \text{the maximally consistent sets of subformulae of
-    $\psi$, closed under single negation}$
-
-    \item $V (p) \assign \{v \in W \hspace{1em} | \hspace{1em} p \in v\}$
-
-    \item $\mathcal{K}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
-    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
-    \hspace{1em} K \phi \in w\}$
-
-    \item $\mathcal{N}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
-    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
-    \hspace{1em} \Box \phi \in w\}$
-
-    \item $\mathcal{A}_w \assign \{\{\phi\} \hspace{1em} | \hspace{1em} A :
-    \phi \in w\}$
-  \end{itemizedot}
-  Note that in this model, there are neighborhoods for both knowledge and
-  belief; more work is necessary to find a model based on this one which
-  conforms to the semantics in Definition \ref{neighborhoodmodels}.  For now,
-  assume that $K$ is just another modality governed by the neighborhoods in
-  $\mathcal{K}_w$.  In both neighborhood functions, our idea is that the
-  neighborhoods of $w$ in are supersets $S \supseteq \left\llbracket \phi
-  \right\rrbracket$ where $\Box \phi \in w$ or $K \phi \in w$, respectively.
-
-  There are steps of the inductive proof of the Truth Lemma for this structure
-  which are not obvious nor obviously documented elsewhere.  Assume
-  $\mathbbm{M}, w \vDash \Box \chi$, where the Truth Lemma has been proven to
-  hold for $\chi$; we must show $\Box \chi \in w$.  By our assumption there
-  is some $\phi$ and $S$ where $\Box \phi \in w$ and $S \supseteq \{v \in W
-  \hspace{1em} | \hspace{1em} \phi \in v\}$.  We argue that $\vdash \phi
-  \rightarrow \chi$; for if not then by the finitary Lindenbaum lemma there is
-  some $u \in W$ where $\phi \in u$ and $\chi \nin u$.  Hence $u \in S$ and
-  $\mathbbm{M}, u \nvDash \chi$, a contradiction.  Since $\vdash \phi
-  \rightarrow \chi$ then we know that $\vdash \Box \phi \rightarrow \Box \chi$
-  by our rules, which means that $\Box \chi \in w$ by maximality.
-
-  By the Lindenbaum Lemma we have that there is some $w \in W$ where
-  $\mathbbm{M}, w \nvDash \psi$.  $\mathbbm{M}$ makes true a number of
-  properties:
-  \begin{enumeratenumeric}
-    \item $W$ and $\mathcal{A}_v$ are finite for all $v \in W$, and $\psi \in
-    \bigcup \mathcal{A_w}$ only if $\psi$ is a subformula of $\phi$
-
-    \item $\mathcal{K}_w \subseteq \mathcal{N}_w$
-
-    \item If $S \in \mathcal{K}_w$ then $w \in S$
-
-    \item $\mathbbm{M}, v \vDash A : \phi \rightarrow \Box \phi$ for all $v
-    \in W$
-
-    \item $\mathcal{N}_w$ and $\mathcal{K}_w$ are closed under supersets
-  \end{enumeratenumeric}
-
-  As in the proof of Theorem \ref{completeness1}, we use a bisimulation to
-  move to a model where property (3) is strengthened to (3$'$): for all $S \in
-  \mathcal{N}_w$, $w \in S$ if and only if $S \in \mathcal{K}'_w$.  We defer
-  the reader to {\cite{hansen_bisimulation_2007,pauly_bisimulation_1999}} for
-  details regarding bisimulation in neighborhood semantics.  Define
-  $\mathbbm{M}' \assign \langle W', V', \mathcal{K}', \mathcal{N}',
-  \mathcal{A}' \rangle$ such that:
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$ wher.  $l, r$ its associated canonical
-    injections and $\theta (v_l) \assign \theta (v_r) \assign v$ is a
-    left-inverse of $l, r$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $\mathcal{K}' (v_i) \assign \{S \hspace{1em} | \hspace{1em} v_i \in
-    S \hspace{1em} \& \hspace{1em} \theta [S] \in \mathcal{K_v} \}$ where $i =
-    l, r$
-
-    \item $\mathcal{N}' (v_i) \assign \mathcal{K}' (v_i) \cup \{S \hspace{1em}
-    | \hspace{1em} v_i \nin S \hspace{1em} \& \hspace{1em} \theta [S] \in
-    \mathcal{N_v} \}$ where $i = l, r$
-
-    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
-    (v)$
-  \end{itemizedot}
-
-  If we let $Z \assign \{(v, v_r), (v, v_l) \hspace{1em} | \hspace{1em} v \in
-  W\}$, it is straightforward to verify that $Z$ is a neighborhood
-  bisimulation.  Hence $\mathbbm{M}, w_l \nvDash \psi$.  Along with (3$'$),
-  this model makes true (1), (2), (4).  In fact, in light of ($3'$), we can
-  see that this model does not need $\mathcal{K}'$, and conforms to the
-  semantics in Definition \ref{neighborhoodmodels}.{\hspace*{\fill}}
-
-  As in previous proofs, let $\Lambda$ be the proposition letters occuring in
-  $\psi$ and define an injection $\iota : W' \hookrightarrow \Phi \backslash
-  \Lambda$, assigning a nominal to every world in $\mathbbm{M}'$.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', \mathcal{N}'', \mathcal{A}''
-  \rangle$ such that:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
-      \begin{array}{ll}
-        V' (p) & p \in \Lambda\\
-        \{v\} & p = i (v)\\
-        \varnothing & o / w
-      \end{array} \right.$\\
-      $\bullet$ & $\mathcal{N}''_w \assign \mathcal{N}'_w$ & {\hspace{3em}} &
-      $\bullet$ & $\mathcal{A}''_v \assign \{\partial_v S \hspace{1em} |
-      \hspace{1em} S \in \mathcal{N}'_w \}$
-    \end{tabular}
-  \end{center}
-
-  Where $\partial_v S \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
-  \bigcup \mathcal{A}_v', \text{$\phi$ is a subformula of $\psi$ and}
-  \hspace{1em} S \subseteq \left\llbracket \phi
-  \right\rrbracket^{\mathbbm{M}'} \} \cup \{\neg \iota (u) \hspace{1em} |
-  \hspace{1em} u \nin S\}$.
-
-  As before, this model agrees with $\mathbbm{M}'$ on all subformulae of
-  $\psi$, using the semantics in Definition \ref{neighborhoodmodels}, hence
-  $\mathbbm{M}'', w_l \nvDash \phi$. \
-
-  All that is left is to show \tmtextbf{NCSQ} and \tmtextbf{NSND} from three
-  new properties:
-  \begin{enumerateroman}
-    \item For all words $v$ and all $X \in \mathcal{A}_v''$, $X$ is finite and
-  .  $X = \partial_v S$ for some $S \in \mathcal{N}_v''$
-
-    \item For all $v$ and all $S \in \mathcal{N}_v$, $u \in S$ if and only if
-    $\mathbbm{M}'', u \vDash \bigwedge \partial_v S$
-
-    \item The logic presented in Table \ref{logic3} is sound for
-    $\mathbbm{M}''$
-  \end{enumerateroman}
-  Along with the deduction theorem for $\vdash$, these properties establish
-  \tmtextbf{NCSQ} for this model using the logic of Table \ref{logic3} itself:
-
-  \begin{align*}
-    \text{$\exists X \in \mathcal{A''_v} \text{ s.t. } \tmop{Th}
-    (\mathbbm{M}'') \cup X \vdash \phi$} & {\Longleftrightarrow}\text{$\exists
-    S \in \mathcal{N''_v} \text{ s.t. } \tmop{Th} (\mathbbm{M}'') \cup
-    \partial_v S \vdash \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \tmop{Th} (\mathbbm{M}'') \vdash \bigwedge \partial_v S \rightarrow
-    \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \bigwedge \partial_v S \rightarrow \phi \in \tmop{Th} (\mathbbm{M}'')$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \left\llbracket \bigwedge \partial_v S \right\rrbracket \subseteq
-    \left\llbracket \phi \right\rrbracket$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t.
-    $\forall u \in W$ if } \mathbbm{M}, u \vDash \bigwedge \partial_v S \text{
-    then } \mathbbm{M}, u \vDash \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \mathbbm{M}, u \vDash \phi \text{ for all } u \in S$}\\
-    & {\Longleftrightarrow}{\mathbbm{M}},v{\vDash}\Box{\phi}
-  \end{align*}
-
-  \tmtextbf{NSND} follows from \tmtextbf{NCSQ} and the semantics of Definition
-  \ref{neighborhoodmodels}.
-\end{proof}
-
-It is not too hard to identify the fragment of this logic that governs
-knowledge alone.  The fragment given in Table \ref{logic4} has special
-significance to us, since it governs the notion of knowledge presented in
-{\S}\ref{quantifying}.
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash K \phi \rightarrow \phi$\\
-    \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ &  &  & $\frac{\vdash \phi \rightarrow \psi}{\vdash K \phi
-      \rightarrow K \psi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic4}A knowledge-only neighborhood logic for
-  \tmtextbf{NCSQ} and {\tmstrong{NSND}}}
-\end{table}
-
-\begin{proposition}
-  The knowledge-only logic presented governs the $\Box$-free fragment of the
-  logic in Table \ref{logic3}
-\end{proposition}
-
-This concludes our analysis of knowledge bases using neighborhood semantics.
+\label{neighborhood_semantics}
+\input{neighborhood_semantics.tex}
 
@@
 Bases}
+\label{modal-modal}
+\input{modal-modal.tex}
 
 \section{Conclusions \& Further Research}
-
-The logic presented in Table \ref{logic1} is a conservative extension of the
-basic modal logic $K$, which means that its decision problem is
-\tmtextsf{PSPACE} hard (a lower bound).  Our finitary completeness proof
-establishes that its complexity is in \tmtextsf{EXP2-TIME} (an upper bound).
-
-Worlds in epistemic logic might correspond to fantastic, pretend scenarios;
-however, it may be desirable for some philosophers to model knowledge about
-imaginary lands.  After all, many children ``know'' a lot about Tolkien's
-{\tmem{middle earth}} or Rowling's {\tmem{Hogwarts}} (the school Harry Potter
-attends).
+\label{conclusions}
+\input{conclusions.tex}
 

### 2010-12-15 simple_justification.tex
Refactored paper so all sections are seperate documents

Justification Logic (JL) was originally developed by Artemov as the
\tmtextit{Logic of Proofs} (LP) {\cite{artemov_logic_1994}}.  Its original
purpose was to provide a framework for reasoning about explicit provability in
Peano Arithmetic.  The first introduction of Justification Logic can be found
in {\cite{artemov_introducing_2005}}, where Artemov and Nogina propose LP as a
logic for reasoning about evidence.  In {\cite{fitting_logic_2005}}, Melvin
Fitting provided JL with Kripke model based semantics.

The principle innovation of LP/JL is to extend awareness logic, such that
awareness operations are now \tmtextit{proof terms}.  Informally, we say that
``a proof term $X$ witnesses proposition $\phi$'', denoted ``$X : \phi$'',
whenever $X$ represents a proof of $\phi$.  Proofs may have
{\tmstrong{multiple-conclusions}} in this system, so it is possible that $X :
\phi$ and $X : \psi$ can be true where $\phi \neq \psi$.  In Fitting's Kripke
semantics, $X : \phi$ means that $\phi$ is in awareness set corresponding to
$X$.  Proof terms are thought be operating in a \tmtextit{multi-conclusion}
proof system, so the same proof term may witness many different propositions.

The logics LP/JL include operators over proofs terms, so that new proof terms
may be assembled.  One operation of particular interest to us is
{\tmem{choice}}, denoted $\oplus$.  The expression ``$X \oplus Y : \phi$''
denotes that either $X$ or $Y$ are proofs witnessing $\phi$.  There are other
operations which correspond to \tmtextit{modus ponens} and
\tmtextit{proof-theoretic reflection}, however we do not consider these
operations here.

In this section we consider a simplified form of JL suitable for reasoning
over multiple knowledge bases, which we call \tmtextit{simple justification
logic} (SJL). However, instead of thinking of terms as representing proofs, we
use them to represent knowledge bases. This is in the spirit of JL as a logic
of evidence: we consider each knowledge base to be a corpus of evidence. \
Each term ``names'' a different knowledge base at a particular world.  Terms
may not refer to the same knowledge base at different worlds, just as in how
in awareness logic the agent need not be aware of the same formulae at
different worlds.  Finally, we will make use of JL's {\tmem{choice}} operator
as a mechanism for forming the union of knowledge bases, creating new ones.

\begin{definition}
  Let $\Pi$ be a set of primitive terms.  Define $\tau (\Pi)$ with the
  following grammar:
  \[ X \hspace{1em} : : = \hspace{1em} t \in \Pi \hspace{1em} | \hspace{1em} X
     \oplus Y \]

  Let $\Phi$ be a set of letters and $\Pi$ a set of primitive terms, and
  define the language $\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)$ as:
  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi \]
  where $X \in \tau (\Pi)$
\end{definition}

\begin{definition}
  \label{justmodels}A {\tmstrong{simple justification model}} $\mathbbm{M}=
  \langle W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V
  : \Phi \cup \{\circlearrowleft_X \hspace{1em} | \hspace{1em} X \in \tau
  (\Pi)\} \rightarrow 2^W$, an indexed relation $R : \tau (\Pi) \rightarrow
  2^{W \times W}$, along with a modified awareness function $\mathcal{A} : W
  \times \tau (\Pi) \rightarrow 2^{\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)}$. \
  In practice we will denote $\mathcal{A} (w, X)$ by a curried shorthand,
  namely $\mathcal{A}_w (X)$.

  The semantics for $\vDash$ have the following modifications:
  \begin{eqnarray*}
    \mathbbm{M}, w \vDash \Box_X \phi & \text{iff} & \text{for all $v \in W$
    where $w R_X v$ we have $\mathbbm{M}, v \vDash v$}\\
    \mathbbm{M}, w \vDash X : \phi & \text{iff} & \phi \in \mathcal{A}_w (X)
  \end{eqnarray*}
\end{definition}

\begin{definition}
  The following defines properties a simple justification model may make true:

  \begin{descriptiondash}
    \item[JCSQ] $\mathbbm{M}, w \vDash \Box_X \phi \text{ iff } \tmop{Th}
    (\mathbbm{M}) \cup \mathcal{A}_w (X) \vdash \phi$

    \item[JSND] $\mathbbm{M}, w \vDash \circlearrowleft_X \text{ iff
    $\mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w (X)$}$

    \item[CHOICE] $\mathcal{A}_w (X \oplus Y) = \mathcal{A}_w (X) \cup
    \mathcal{A}_w (Y)$
  \end{descriptiondash}

  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
\end{definition}

The above semantics are similar to the ones given in previous sections. \
\tmtextbf{JCSQ} is the same as \tmtextbf{CSQ} from {\S}\ref{awarenesslogic},
only it is relativized to a knowledge base denoted by $X$ at $w$.  The
awareness logic of knowledge bases is special case of simple justification
logic where there is only one term.

Simplified justification logic is given in Table \ref{logic5}.  We assert
without proof that this is a conservative extension of the awareness logic in
{\S}\ref{awarenesslogic}.

\begin{table}[h]
  \begin{tabular}{ll}
    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
    \rightarrow \psi \rightarrow \phi$ & \\
    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
    \Box_X \psi$ & \\
    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
    \\
    $\vdash (X \oplus Y : \phi) \rightarrow X : \phi$ & $\vdash (X \oplus Y :
    \phi) \rightarrow Y : \phi$\\
    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
    \circlearrowleft_{X \oplus Y}$ & \\
    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_X$ &
    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_Y$\\
    $\vdash \Box_X \phi \rightarrow \Box_{X \oplus Y} \phi$ & \\
    $\vdash \Box_{X \oplus X} \phi \rightarrow \Box_X \phi$ & $\vdash \Box_{(X
    \oplus X) \oplus Y} \phi \rightarrow \Box_{X \oplus Y} \phi$ \\
    $\vdash \Box_{X \oplus Y} \phi \rightarrow \Box_{Y \oplus X} \phi$ &
    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{(Y \oplus X)
    \oplus Z} \phi$\\
    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{X \oplus (Y
    \oplus Z)} \phi$ & \\
    & \\
    \begin{tabular}{lll}
      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
    \end{tabular} & 
  \end{tabular}
  \caption{\label{logic5}Simple Justification Logic}
\end{table}

\begin{theorem}
  \label{completeness5}Assuming an infinite store of proposition letters
  $\Phi$, SJL is sound and weakly complete for simple justification models
  making true \tmtextbf{JCSQ}, \tmtextbf{JSND} and \tmtextbf{CHOICE}
\end{theorem}

\begin{proof}
  As in the previous proofs, we only show completeness.  Assume that $\nvdash
  \psi$.  Let $\Xi \subseteq \tau (\Pi)$ be all of the subterms occurring in
  $\psi$; we assume that $\Xi$ is non-empty, since otherwise we may obtain the
  theorem via the usual completeness theorem for classical propositional
  logic. Let $\Sigma_0$ be the subformulae of $\psi$.  Define:

  \begin{align*}
    {\Sigma}_1 &
    {\assign}{\Sigma}_0{\cup}\{\Box_Y{\phi}{\hspace{1em}}|{\hspace{1em}}\Box_X{\phi}{\in}{\Sigma}_0{\hspace{1em}}\&{\hspace{1em}}Y{\in}{\Xi}\}\\
    {\Sigma}_2 &
    {\assign}{\Sigma}_1{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1\}
  \end{align*}

  As in the proof of Theorem \ref{completeness2}, it is simple to verify that
  $\Sigma_2$ is closed under subformulae and single negations.  Let
  $\mathbbm{M} \assign \langle W, V, R, \mathcal{A} \rangle$ be the finite
  cannonical model formed of maximally consistent subsets of $\Sigma_2$, where
  $V$ and $\mathcal{A}$ are defined as usual, and $R : \Xi \rightarrow 2^{W
  \times W}$ is defined by:
  \[ w R_X v \Longleftrightarrow \{\phi \hspace{1em} | \hspace{1em} \Box_X
     \phi \in w\} \subseteq v \]
  As in previous constructions we may prove the usual Lindenbaum and Truth
  Lemmas an use them obtain a world $w \in W$ where $\mathbbm{M}, w \nvDash
  \psi$.

  Next, define an operator $\twonotes : \tau (\Pi) \rightarrow 2^{\Pi}$ where:
  \[ \twonotes (X) \assign \{t \in \Pi \hspace{1em} | \hspace{1em} t \text{
     occurs in } X\} \]
  In other words, $\twonotes (X)$ is the set of atomic terms in $X$.  As in
  our construction for Theorem \ref{completeness1}, $\mathbbm{M}$ makes true
  certain properties, along with some new properties:
  \begin{enumeratenumeric}
    \item \label{fin}$W$ and $\mathcal{A}_v (X)$ are finite, and $\phi \in
    \mathcal{A}_v (X)$ only if $\phi \in \Sigma_2$

    \item if $\mathbbm{M}, v \vDash X : \phi$ then $\mathbbm{M}, v \vDash
    \Box_X \phi$

    \item \label{refl}if $\mathbbm{M}, v \vDash \circlearrowleft_X$ then $v
    R_X v$

    \item \label{sndness}For all $X \oplus Y \in \Xi$, $\mathbbm{M}, v \vDash
    \circlearrowleft_{X \oplus Y}$ if and only if $\mathbbm{M}, v \vDash
    \circlearrowleft_X$ and $\mathbbm{M}, v \vDash \circlearrowleft_Y$

    \item \label{union}For all $X \oplus Y \in \Xi$, $\mathcal{A}_v (X \oplus
    Y) = \mathcal{A}_v (X) \cup \mathcal{A}_v (Y)$

    \item \label{sub}For all $X, Y \in \Xi$, if $\twonotes (X) \subseteq
    \twonotes (Y)$ then $R_Y \subseteq R_X$
  \end{enumeratenumeric}
  As in our previous constructions, it is necessary to refine this model using
  bisimulations to achieve properties which are not modally definable.  In
  particular, we shall strengthen (\ref{refl}) to a biconditional and
  (\ref{sub}) to:

  \begin{center}
    \begin{tabular}{ll}
      \tmtextbf{6$'$.} & For all $X, Y \in \Xi$, $R_{X \oplus Y} = R_X \cap
      R_Y$
    \end{tabular}
  \end{center}

  We first strengthen (\ref{refl}) by constructing $\mathbbm{M}' \assign
  \langle W', V', R', \mathcal{A}' \rangle$, just as in Theorem
  \ref{completeness1}: {\hspace*{\fill}}
  \begin{itemizedot}
    \item $W' \assign W \uplus W$

    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
    (p)\}$

    \item $R'_X \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v
    R_X u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em}
    \mathbbm{M}, v \vDash \circlearrowleft_X \}$

    \item $\mathcal{A}' (v_l, X) \assign \mathcal{A}' (v_r, X) \assign
    \mathcal{A} (v, X)$
  \end{itemizedot}
  The same bisimulation relation $Z$ previously given suffices.

  We next make a strengthened the model where (\ref{sub}$'$) holds.  Define
  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
  that{\footnote{Let $\{i_X \hspace{1em} | \hspace{1em} X \in \Xi\}$ be the
  family of canonical injections into the coproduct $\uplus_{\Xi} W$. As per
  our previous convention, we use $v_X$ as shorthand for $i_X (v)$.}}:
  \begin{itemizedot}
    \item $W'' \assign \uplus_{\Xi} W'$

    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$

    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em}
    \twonotes (X) \subseteq \twonotes (Z)\}$

    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
  \end{itemizedot}
  Note that this construction makes use of the assumption that $\Xi$ is
  non-empty.  Let $Z \assign \{(v, v_X) \hspace{1em} | \hspace{1em} X \in \Xi
  \hspace{1em} \& \hspace{1em} v \in W' \}$; it is straightforward to prove
  that $Z$ is a bisimulation between $\mathbbm{M}'$ and $\mathbbm{M}''$, for
  all relations corresponding to terms $X \in \Xi$. Hence $\mathbbm{M}'', w_X
  \nvDash \psi$ for some $w_X \in W''$.  In addition, $\mathbbm{M}''$
  inherits (\ref{fin}) through (\ref{sub}) from $\mathbbm{M}'$, as well as the
  converse of (\ref{refl}).  Next observe, forall $X \oplus Y \in \Xi$:
  \begin{eqnarray*}
    \text{$(v_V, u_Z) \in R''_X \cap R''_Y$} & \Longleftrightarrow & \exists Z
    \in \Xi . \text{$v R'_Z u \hspace{1em} \& \hspace{1em} \twonotes (X)
    \subseteq \twonotes (Z) \hspace{1em} \& \hspace{1em} \twonotes (Y)
    \subseteq \twonotes (Z)$}\\
    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
    \& \hspace{1em} \twonotes (X) \cup \twonotes (Y) \subseteq \twonotes
    (Z)$}\\
    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
    \& \hspace{1em} \twonotes (X \oplus Y) \subseteq \twonotes (Z)$}\\
    & \Longleftrightarrow &  \text{$(v_V, u_Z) \in R''_{X \oplus Y}$}
  \end{eqnarray*}
  We now turn to our final construction. As in previous constructions, let
  $\iota : W'' \hookrightarrow \Phi \backslash \Psi$ be an injection assigning
  fresh nominals to worlds.  Define $\mathbbm{M}''' \assign \langle W''',
  V''', R''', \mathcal{A}''' \rangle$ just as in the final construction in the
  proof of Theorem \ref{completeness1}, except that $R'''_X$ and
  $\mathcal{A}_v''' (X)$ are defined inductively as follows:

  \begin{center}
    \begin{tabular}{lll}
      $\bullet$ & $R'''_t \assign \left\{ \begin{array}{ll}
        R''_t & t \in \Xi\\
        W''' \times W''' & o / w
      \end{array} \right.$ & \\
      $\bullet$ & $R'''_{X \oplus Y} \assign R'''_X \cap R'''_Y$ & \\
      &  & \\
      $\bullet$ & $\mathcal{A}'''_v (t) \assign \{\phi \hspace{1em} | \phi \in
      \mathcal{A}''_v \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
      \neg v R'''_t u\}$ & where $t \in \Pi$\\
      $\bullet$ & $\mathcal{A}'''_v (X \oplus Y) \assign \mathcal{A}'''_v (X)
      \cup \mathcal{A}'''_v (Y)$ & 
    \end{tabular}
  \end{center}

  Induction over complexity of subformulae $\phi$ of $\psi$ yields
  $\mathbbm{M}'', w \vDash \phi \Longleftrightarrow \mathbbm{M}''', w \vDash
  \phi$, so we know that there is some world $w \in W'''$ such that
  $\mathbbm{M}''', w \nvDash \psi$.  All that is left is to illustrate that
  $\mathbbm{M}'''$ has the properties we desire.

  First note that by definition, $\mathbbm{M}'''$ makes true
  \tmtextbf{CHOICE}.  Next, an induction argument on the complexity of a
  terms $X$, making essential use of (\ref{sub}$'$), yields:
  \[ u R_X''' v \Longleftrightarrow \mathbbm{M}''', v \vDash \bigwedge
     \mathcal{A}'''_v (X) \]
  With this, $\mathbbm{M}'''$ makes true \tmtextbf{JSND} since it inherits
  (\ref{refl}).  Finally, we note that we may repeat our previous arguments
  from Theorem \ref{completeness1} to prove \tmtextbf{JCSQ}.
\end{proof}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

### 2010-12-15 conclusions.tex
another section factored out

(FIXME:  Needs to be extended a lot!)

The logic presented in Table \ref{logic1} is a conservative extension of the
basic modal logic $K$, which means that its decision problem is
\tmtextsf{PSPACE} hard (a lower bound).  Our finitary completeness proof
establishes that its complexity is in \tmtextsf{EXP2-TIME} (an upper bound).

Worlds in epistemic logic might correspond to fantastic, pretend scenarios;
however, it may be desirable for some philosophers to model knowledge about
imaginary lands.  After all, many children ``know'' a lot about Tolkien's
{\tmem{middle earth}} or Rowling's {\tmem{Hogwarts}} (the school Harry Potter
attends).

### 2010-12-15 awareness.tex
spell checking sections

@@
 knowledge base being sound. A sound knowledge base will only render true
-conclusions when used in deductions.  If one considers ``the existance of a
+conclusions when used in deductions.  If one considers ``the existence of a
 sound deduction'' sufficient for a kind of knowledge, then $\circlearrowleft$
@@
   note that the basic definition and all of the usual theorems (modal
-  equivalence, Henessy Milner, etc.) may be generalized to awareness models in
+  equivalence, Henessy-Milner, etc.) may be generalized to awareness models in
   a straightforward fashion. }} model $\mathbbm{M}'$ which makes true (1), (2)
@@
   {\hspace*{\fill}}\begin{tabular}{ll}
-    \tmtextbf{3$'$.} & $\mathbbm{M}', v \vDash \circlearrowleft$ iff $v R v$
+    \tmtextbf{3$'$.} & $\mathbbm{M}', v \vDash \circlearrowleft \iff v R v$
   \end{tabular}{\hspace*{\fill}}
@@
   \tmtextbf{CSQ} and \tmtextbf{SND}.  Let $\Lambda$ be the set of proposition
-  letters occuring in $\psi$.  We will make use members of $\Phi \backslash
+  letters occurring in $\psi$.  We will make use members of $\Phi \backslash
   \Lambda$ as {\tmem{nominals}}, as per the tradition in hybrid logic.  This

### 2010-12-15 lattice_justification.tex
Added todonotes

@@
-{\color{red} NOTE.  THIS SECTION HAS SOME SERIOUS PROBLEMS AND IT'S PROBABLY
-WRONG...}
-
-Implicit in our previous presentation of SJL.  $\oplus$ behaves like a union
+Implicit in our previous presentation of SJL is the following
+principle: 
+\todo[noline]{THIS SECTION IS  PROBABLY WRONG}
+ $\oplus$ behaves like a union
 operation for knowledge bases, and dually like an intersection operation on

### 2010-12-15 simple_justification.tex
spelling

@@
 \tmtextbf{JCSQ} is the same as \tmtextbf{CSQ} from {\S}\ref{awarenesslogic},
-only it is relativized to a knowledge base denoted by $X$ at $w$.  The
+only it is relativised to a knowledge base denoted by $X$ at $w$.  The
 awareness logic of knowledge bases is special case of simple justification
@@
   $\mathbbm{M} \assign \langle W, V, R, \mathcal{A} \rangle$ be the finite
-  cannonical model formed of maximally consistent subsets of $\Sigma_2$, where
+  canonical model formed of maximally consistent subsets of $\Sigma_2$, where
   $V$ and $\mathcal{A}$ are defined as usual, and $R : \Xi \rightarrow 2^{W

### 2010-12-15 lattice_justification.tex
more spell checking

@@
 accessibility relations.  It is natural to think of $\oplus$ as a join/meet
-operator over a {\tmem{semi-lattice}}.  In this section we make this
+operator over a {\tmem{semilattice}}.  In this section we make this
 explicit, by increasing the expressive power of simple JL to express the order
@@
 this section \tmtextit{Lattice Justification Logic} (LJL){\footnote{We note
-that ``Semi-Lattice Justification Logic'' may be a more appropriate name,
-however we have decided to shorten semic-lattice to lattice in this article
+that ``Semilattice Justification Logic'' may be a more appropriate name,
+however we have decided to shorten semilattice to lattice in this article
 for purposes of concision.}}.  Lattice JL may be considered a novel logic for
@@
   notion of ``bisimulation'' here includes that two bisimular worlds $v$ and
-  $u$ must have isomorphic semi-lattices $\preccurlyeq_v$ and
+  $u$ must have isomorphic semilattices $\preccurlyeq_v$ and
   $\preccurlyeq_w$.  This is achieved by enforcing that $\preccurlyeq_{v_l}

### 2010-12-15 awareness.tex
Factored out first completeness theorem

@@
 $\phi$ if and only if it follows logically from their knowledge base and their
-background knowledge, represented by $\tmop{Th} (\mathbbm{M})$. \
+background knowledge, represented by $\tmop{Th} (\mathbbm{M})$. 
 \tmtextbf{CSQ} is Vincent Hendrik's principle of logical omniscience mentioned
@@
 
-\begin{proof}
-  Soundness is straightforward, so we will only address completeness.  Assume
-  $\nvdash \psi$.  Consider the finite canonical model $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A} \rangle$ formed of maximally consistent sets of
-  subformulae of $\phi$ (closed under single negations{\footnote{A discussion
-  of this property may be found in {\cite[pg.
-  243]{blackburn_modal_2001}}.}}), as per the finitary modal completeness
-  proofs found in {\cite[chapter 4.8]{blackburn_modal_2001}} and
-  {\cite[chapter 5]{boolos_logic_1995}}.  Typical presentations do not
-  include awareness, however it is defined intuitively in this case:
-  \[ \phi \in \mathcal{A}_w \Longleftrightarrow A : \phi \in w \]
-  Since $\psi$ is a subformula of itself, we have $\mathbbm{M}, w \nvDash
-  \psi$ for some world $w$ by a finitary {\tmem{Lindenbaum Lemma}} and
-  {\tmem{Truth Theorem}}.  Moreover, it is straightforward to verify that
-  $\mathbbm{M}$ makes true the following properties:
-  \begin{enumeratenumeric}
-    \item $W$ and $\mathcal{A}_v$ are finite, and $\psi \in \mathcal{A}_v$
-    only if $\psi$ is a (possibly negated) subformula of $\phi$
-
-    \item if $\mathbbm{M}, v \vDash A : \psi$ then $\mathbbm{M}, v \vDash \Box
-    \psi$
-
-    \item if $\mathbbm{M}, v \vDash \circlearrowleft$ then $v R v$
-  \end{enumeratenumeric}
-
-  We next produce a bisimular{\footnote{The notion of bisimulation is
-  discussed at length in {\cite[chapter 2.2]{blackburn_modal_2001}}.  We
-  note that the basic definition and all of the usual theorems (modal
-  equivalence, Henessy-Milner, etc.) may be generalized to awareness models in
-  a straightforward fashion. }} model $\mathbbm{M}'$ which makes true (1), (2)
-  and a stronger from of (3):
-
-  {\hspace*{\fill}}\begin{tabular}{ll}
-    \tmtextbf{3$'$.} & $\mathbbm{M}', v \vDash \circlearrowleft \iff v R v$
-  \end{tabular}{\hspace*{\fill}}
-
-  To this end define $\mathbbm{M}' \assign \langle W', V', R', \mathcal{A}'
-  \rangle$ such that{\footnote{Throughout this article, we use $l$ and $r$ to
-  denote the two canonical injections associated with the coproduct $W \uplus
-  W$. We will use $v_l$ and $v_r$ as the shorthand for $l (v)$ and $r (v)$
-  respectively.}}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
-    (p)\}$
-
-    \item $R' \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v R
-    u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em} \mathbbm{M},
-    v \vDash \circlearrowleft\}$
-
-    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
-    (v)$
-  \end{itemizedot}
-
-  It is straightforward to verify that $\mathbbm{M}'$ makes true the desired
-  properties.  Let $Z \assign \{(v, v_l), (v, v_r) \hspace{1em} |
-  \hspace{1em} v \in W\}$.  then $Z$ is a bisimulation between $\mathbbm{M}$
-  and $\mathbbm{M}'$.  Therefore we know there is some $w \in W$ such that
-  $\mathbbm{M}', w_l \nvDash \psi$ and $\mathbbm{M}', w_r \nvDash \psi$.
-
-  Finally we construct a model $\mathbbm{M}''$ which agrees with
-  $\mathbbm{M}'$ for all subformulae of $\psi$, which makes true
-  \tmtextbf{CSQ} and \tmtextbf{SND}.  Let $\Lambda$ be the set of proposition
-  letters occurring in $\psi$.  We will make use members of $\Phi \backslash
-  \Lambda$ as {\tmem{nominals}}, as per the tradition in hybrid logic.  This
-  is possible since both $W'$ and $\Lambda$ are finite and $\Phi$ is infinite
-  by hypothesis.  Let $\iota : W \uplus W \hookrightarrow \Phi \backslash
-  \Lambda$ be an injection assigning a fresh nominal associated with each
-  world in $\mathbbm{M}'$.  Now define $\mathbbm{M}'' \assign \langle W'',
-  V'', R'', \mathcal{A}'' \rangle$, where:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
-      \begin{array}{ll}
-        V' (p) & p \in \Lambda\\
-        \{v\} & p = \iota (v)\\
-        \varnothing & o / w
-      \end{array} \right.$\\
-      $\bullet$ & $R'' \assign R'$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}''_v \assign \{\phi \hspace{1em} | \phi \in \mathcal{A}'_v
-      \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em} \neg v R' u\}$
-    \end{tabular}
-  \end{center}
-
-  By induction we have that for every subformula $\phi$ of $\psi$ that
-  $\mathbbm{M}', v \vDash \phi$ if and only if $\mathbbm{M}'', v \vDash \phi$,
-  hence $\mathbbm{M}'', w_l \nvDash \psi$.
-
-  All that is left to show is that $\mathbbm{M}''$ makes true \tmtextbf{CSQ}
-  and \tmtextbf{SND}.  $\mathbbm{M}''$ has three further properties:
-  \begin{enumerateroman}
-    \item $\mathcal{A}''_v$ is finite for all worlds $v$
-
-    \item  $v R' u$ if and only if $\mathbbm{M}'', u \vDash \bigwedge
-    \mathcal{A}'' (v)$
-
-    \item The logic presented in Table \ref{logic1} is sound for
-    $\mathbbm{M}''$
-  \end{enumerateroman}
-  From (ii) and the fact that $\mathbbm{M}'$ makes true (3$'$), we have
-  \tmtextbf{SND} for $\mathbbm{M}''$.
-
-  All that is left is to demonstrate \tmtextbf{CSQ} for some sound logic.  We
-  will use the logic in Table \ref{logic1} itself.  From (i), (ii), (iii),
-  and the \tmtextit{deduction theorem} for modal logic, we have the following
-  line of reasoning:
-
-  \begin{align*}
-    Th({\mathbbm{M}}''){\cup}\mathcal{A}''_v{\vdash}{\phi} &
-    {\Longleftrightarrow}Th({\mathbbm{M}}''){\vdash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\\
-    &
-    {\Longleftrightarrow}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}{\in}Th({\mathbbm{M}}'')\\
-    &
-    {\Longleftrightarrow}{\mathbbm{M}}'',u{\vDash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\text{
-    for all $u \in W''$}\\
-    & {\Longleftrightarrow}\text{ for all $u \in W''$, if
-    }{\mathbbm{M}}'',u{\vDash}\mathcal{A}''_v\text{ then
-    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
-    & {\Longleftrightarrow}\text{ for all $u \in W''$, if }v R 'u \text{ then
-    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
-    & {\Longleftrightarrow}{\mathbbm{M}}'',v{\models}\Box{\phi}
-  \end{align*}
-\end{proof}
+\input{completeness1.tex}
 

### 2010-12-15 completeness1.tex
Factored out first completeness theorem

\begin{proof}
  Soundness is straightforward, so we will only address completeness.  Assume
  $\nvdash \psi$.  Consider the finite canonical model $\mathbbm{M}= \langle
  W, V, R, \mathcal{A} \rangle$ formed of maximally consistent sets of
  subformulae of $\phi$ (closed under single negations{\footnote{A discussion
  of this property may be found in {\cite[pg.
  243]{blackburn_modal_2001}}.}}), as per the finitary modal completeness
  proofs found in {\cite[chapter 4.8]{blackburn_modal_2001}} and
  {\cite[chapter 5]{boolos_logic_1995}}.  Typical presentations do not
  include awareness, however it is defined intuitively in this case:
  \[ \phi \in \mathcal{A}_w \Longleftrightarrow A : \phi \in w \]
  Since $\psi$ is a subformula of itself, we have $\mathbbm{M}, w \nvDash
  \psi$ for some world $w$ by a finitary {\tmem{Lindenbaum Lemma}} and
  {\tmem{Truth Theorem}}.  Moreover, it is straightforward to verify that
  $\mathbbm{M}$ makes true the following properties:
  \begin{enumeratenumeric}
    \item $W$ and $\mathcal{A}_v$ are finite, and $\psi \in \mathcal{A}_v$
    only if $\psi$ is a (possibly negated) subformula of $\phi$

    \item if $\mathbbm{M}, v \vDash A : \psi$ then $\mathbbm{M}, v \vDash \Box
    \psi$

    \item if $\mathbbm{M}, v \vDash \circlearrowleft$ then $v R v$
  \end{enumeratenumeric}

  We next produce a bisimular{\footnote{The notion of bisimulation is
  discussed at length in {\cite[chapter 2.2]{blackburn_modal_2001}}.  We
  note that the basic definition and all of the usual theorems (modal
  equivalence, Henessy-Milner, etc.) may be generalized to awareness models in
  a straightforward fashion. }} model $\mathbbm{M}'$ which makes true (1), (2)
  and a stronger from of (3):

  {\hspace*{\fill}}\begin{tabular}{ll}
    \tmtextbf{3$'$.} & $\mathbbm{M}', v \vDash \circlearrowleft \iff v R v$
  \end{tabular}{\hspace*{\fill}}

  To this end define $\mathbbm{M}' \assign \langle W', V', R', \mathcal{A}'
  \rangle$ such that{\footnote{Throughout this article, we use $l$ and $r$ to
  denote the two canonical injections associated with the coproduct $W \uplus
  W$. We will use $v_l$ and $v_r$ as the shorthand for $l (v)$ and $r (v)$
  respectively.}}: {\hspace*{\fill}}
  \begin{itemizedot}
    \item $W' \assign W \uplus W$

    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
    (p)\}$

    \item $R' \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v R
    u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em} \mathbbm{M},
    v \vDash \circlearrowleft\}$

    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
    (v)$
  \end{itemizedot}

  It is straightforward to verify that $\mathbbm{M}'$ makes true the desired
  properties.  Let $Z \assign \{(v, v_l), (v, v_r) \hspace{1em} |
  \hspace{1em} v \in W\}$.  then $Z$ is a bisimulation between $\mathbbm{M}$
  and $\mathbbm{M}'$.  Therefore we know there is some $w \in W$ such that
  $\mathbbm{M}', w_l \nvDash \psi$ and $\mathbbm{M}', w_r \nvDash \psi$.

  Finally we construct a model $\mathbbm{M}''$ which agrees with
  $\mathbbm{M}'$ for all subformulae of $\psi$, which makes true
  \tmtextbf{CSQ} and \tmtextbf{SND}.  Let $\Lambda$ be the set of proposition
  letters occurring in $\psi$.  We will make use members of $\Phi \backslash
  \Lambda$ as {\tmem{nominals}}, as per the tradition in hybrid logic.  This
  is possible since both $W'$ and $\Lambda$ are finite and $\Phi$ is infinite
  by hypothesis.  Let $\iota : W \uplus W \hookrightarrow \Phi \backslash
  \Lambda$ be an injection assigning a fresh nominal associated with each
  world in $\mathbbm{M}'$.  Now define $\mathbbm{M}'' \assign \langle W'',
  V'', R'', \mathcal{A}'' \rangle$, where:

  \begin{center}
    \begin{tabular}{lllll}
      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
      \begin{array}{ll}
        V' (p) & p \in \Lambda\\
        \{v\} & p = \iota (v)\\
        \varnothing & o / w
      \end{array} \right.$\\
      $\bullet$ & $R'' \assign R'$ & {\hspace{3em}} & $\bullet$ &
      $\mathcal{A}''_v \assign \{\phi \hspace{1em} | \phi \in \mathcal{A}'_v
      \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em} \neg v R' u\}$
    \end{tabular}
  \end{center}

  By induction we have that for every subformula $\phi$ of $\psi$ that
  $\mathbbm{M}', v \vDash \phi$ if and only if $\mathbbm{M}'', v \vDash \phi$,
  hence $\mathbbm{M}'', w_l \nvDash \psi$.

  All that is left to show is that $\mathbbm{M}''$ makes true \tmtextbf{CSQ}
  and \tmtextbf{SND}.  $\mathbbm{M}''$ has three further properties:
  \begin{enumerateroman}
    \item $\mathcal{A}''_v$ is finite for all worlds $v$

    \item  $v R' u$ if and only if $\mathbbm{M}'', u \vDash \bigwedge
    \mathcal{A}'' (v)$

    \item The logic presented in Table \ref{logic1} is sound for
    $\mathbbm{M}''$
  \end{enumerateroman}
  From (ii) and the fact that $\mathbbm{M}'$ makes true (3$'$), we have
  \tmtextbf{SND} for $\mathbbm{M}''$.

  All that is left is to demonstrate \tmtextbf{CSQ} for some sound logic.  We
  will use the logic in Table \ref{logic1} itself.  From (i), (ii), (iii),
  and the \tmtextit{deduction theorem} for modal logic, we have the following
  line of reasoning:

  \begin{align*}
    Th({\mathbbm{M}}''){\cup}\mathcal{A}''_v{\vdash}{\phi} &
    {\Longleftrightarrow}Th({\mathbbm{M}}''){\vdash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\\
    &
    {\Longleftrightarrow}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}{\in}Th({\mathbbm{M}}'')\\
    &
    {\Longleftrightarrow}{\mathbbm{M}}'',u{\vDash}\bigwedge\mathcal{A}''_v{\rightarrow}{\phi}\text{
    for all $u \in W''$}\\
    & {\Longleftrightarrow}\text{ for all $u \in W''$, if
    }{\mathbbm{M}}'',u{\vDash}\mathcal{A}''_v\text{ then
    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
    & {\Longleftrightarrow}\text{ for all $u \in W''$, if }v R 'u \text{ then
    }{\mathbbm{M}}'',u{\vDash}{\phi}\\
    & {\Longleftrightarrow}{\mathbbm{M}}'',v{\models}\Box{\phi}
  \end{align*}
\end{proof}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

### 2010-12-15 completeness2.tex
Factored out another completeness theorem

--- 2010-12-15 hybrid_awareness.tex
@@
-The method of the previous completeness proof makes implicit use of concepts from
-hybrid logic{\footnote{Hybrid logic was first presented in
-{\cite{prior_revised_1969}} and later formally developed in
-{\cite{bull_approach_1970}}.}}.  In this section we adapt hybrid logic and
-show that it is a complete for reasoning about knowledge bases.  We note that
-because of the increased expressive power of hybrid logic, our completeness
-theorem is simpler.
-
-\begin{definition}
-  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
-  language $\mathcal{L}_H (\Phi, \Psi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} i \in \Psi \hspace{1em} | \hspace{1em} \bot \hspace{1em} |
-     \hspace{1em} \phi \rightarrow \psi \hspace{1em} | \hspace{1em} \Box \phi
-     \hspace{1em} | \hspace{1em} A : \phi \hspace{1em} | \hspace{1em} \forall
-     \phi \]
-\end{definition}
-
-Our approach in hybrid logic is to employ a universal modality along with
-nominals.  This framework presents a logic where the agent may reason about
-various labeled scenarios.  Scenarios may be multiply labeled or not labeled
-at all.  From these intuitions we have the following definition:
-
-\begin{definition}
-  \label{hybridsemantics}Let a \tmtextbf{hybrid model} $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A}, \ell \rangle$ be an awareness model as in Definition
-  \ref{awarenessmodels}, along with a partial labeling function $\ell : \Psi
-  \nrightarrow W$
-
-  The semantics for $\vDash$ are the same as in Definition
-  \ref{awarenessmodels}, only we have
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \forall \phi & \text{iff} & \forall v \in
-    W.\mathbbm{M}, v \vDash \phi\\
-    \mathbbm{M}, w \vDash i & \text{iff} & \ell (i) = w
-  \end{eqnarray*}
-\end{definition}
-
-The other connectives and operators are defined as usual, although we employ a
-few special shorthands:
-
-\begin{definition}
-  We employ the following special abbreviations:
-  \begin{eqnarray}
-    \text{\tmtextup{@}}_i \phi \assign \forall (i \rightarrow \phi)
-    \hspace{2em} & \exists \phi \assign \neg \forall \neg \phi \hspace{3em} &
-    \circlearrowleft_i \assign \diamondsuit i \nonumber
-  \end{eqnarray}
-\end{definition}
-
-This gives rise to a validity reflecting one of the axioms we saw in
-{\S}\ref{awarenesslogic}:
-\[ \vDash \circlearrowleft_i \rightarrow \Box \phi \rightarrow
-   \text{\tmtextup{@}}_i \phi \]
-This can be read as ``If the agent's knowledge base is sound at world $i$,
-then if they can deduce something from their knowledge base, what they deduce
-must be true at world $i$.'.  In a way, this may be considered as
-{\tmem{relativising}} knowledge particular named situations.
-
-The semantics in Definition \ref{hybridsemantics} obviates the \tmtextbf{SND}
-principle we previously presented, since there is no explicit
-$\circlearrowleft$ symbol in this setting. \tmtextbf{CSQ} still makes sense
-without modification, however.  The following gives a logic for hybrid models
-making true \tmtextbf{CSQ}:
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & $\vdash \forall (\phi
-    \rightarrow \psi) \rightarrow \forall \phi \rightarrow \forall \psi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & $\vdash \forall
-    \phi \rightarrow \phi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & $\vdash \forall \phi \rightarrow
-    \forall \forall \phi$\\
-    $\vdash \Box(\phi \rightarrow \psi) \rightarrow \Box \phi \rightarrow \Box
-    \psi$ & $\vdash \exists \phi \rightarrow \forall \exists \phi$\\
-    $\vdash A : \phi \rightarrow \Box \phi$ & $\vdash \forall \phi \rightarrow
-    \Box \phi$\\
-    & $\vdash i \rightarrow \phi \rightarrow \text{\tmtextup{@}}_i \phi$\\
-    & \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi}{\vdash \Box \phi}$ &
-      {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \forall \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic2}Hybrid Awareness Logic for \tmtextbf{CSQ}}
-\end{table}
-
-\begin{theorem}
-  \label{completeness2}Assuming an infinite store of nominals $\Psi$, the
-  hybrid awareness logic presented is sound and weakly complete for all hybrid
-  models making true \tmtextbf{CSQ}.
-\end{theorem}
-
 \begin{proof}
@@
   that $\nvdash \psi$ and let $\Sigma_0$ be the set of subformulae of $\psi$,
-  and let $\Upsilon$ be the set of nominals occuring in $\psi$.  Define:
+  and let $\Upsilon$ be the set of nominals occurring in $\psi$.  Define:
 
@@
   single negations. Let $\mathbbm{M}= \langle W, V, R_{\Box}, \sim_{\forall},
-  \mathcal{A} \rangle$ be the finite cannonical model formed of maximally
+  \mathcal{A} \rangle$ be the finite canonical model formed of maximally
   consistent subsets of $\Sigma_3$, where everything is defined as usual,

### 2010-12-15 hybrid_awareness.tex
spell checking sections
Factored out another completeness theorem

@@
 \end{theorem}
+\input{completeness2.tex}
 
-\begin{proof}
-  As before, soundness is trivial.  Completeness is based on a modification
-  of techniques found in {\cite[chapter 5]{boolos_logic_1995}}.  Assume
-  that $\nvdash \psi$ and let $\Sigma_0$ be the set of subformulae of $\psi$,
-  and let $\Upsilon$ be the set of nominals occuring in $\psi$.  Define:
-
-  \begin{align*}
-    {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{{\forall}{\phi}{\hspace{1em}}|{\hspace{1em}}\Box{\phi}{\in}{\Sigma}_0\}\\
-    {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{\text{@}_i{\phi}{\hspace{1em}},i{\rightarrow}{\phi}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1{\hspace{1em}}\&{\hspace{1em}}i{\in}{\Upsilon}\}\\
-    {\Sigma}_3 &
-    {\assign}{\Sigma}_2{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_2\}
-  \end{align*}
-
-  It is easy to see that $\Sigma_3$ is finite and closed under subformulae and
-  single negations. Let $\mathbbm{M}= \langle W, V, R_{\Box}, \sim_{\forall},
-  \mathcal{A} \rangle$ be the finite cannonical model formed of maximally
-  consistent subsets of $\Sigma_3$, where everything is defined as usual,
-  except $\sim_{\forall}$, which obeys the following specification:
-
-  \begin{align*}
-    w {\sim}_{{\forall}}v & {\Longleftrightarrow}(({\forall}{\phi}){\in}w
-    {\Longleftrightarrow}({\forall}{\phi}){\in}v)
-  \end{align*}
-
-  This model makes true the following properties:
-  \begin{enumerateroman}
-    \item $\sim_{\forall}$ is an equivalence relation
-
-    \item $R_{\Box} \subseteq \sim_{\forall}$
-
-    \item In each equivalence class specified by $\sim_{\forall}$, there is at
-    most one world making true $i$ for all $i \in \Upsilon$
-  \end{enumerateroman}
-  As in our previous construction we have that there is some world $w$ where
-  $\mathbbm{M}, w \nvDash \psi$.  Let $\mathbbm{M}^1 = \langle W', V',
-  R_{\Box}', \sim_{\forall}', \mathcal{A}' \rangle$ be the submodel generated
-  by $\{w\}$; we have that $\mathbbm{M}', w \nvDash \psi$ (see {\cite[chapter
-  2.1]{blackburn_modal_2001}} for details on generated submodels).  In this
-  model $\forall$ is a universal modality and either $\left\llbracket i
-  \right\rrbracket^{\mathbbm{M}'} = \varnothing$ or $\left\llbracket i
-  \right\rrbracket^{\mathbbm{M}'} =\{v\}${\footnote{As per the usual
-  convention, here $\left\llbracket \phi \right\rrbracket^{\mathbbm{M}}$
-  denotes $\{w \in W \hspace{1em} | \hspace{1em} \mathbbm{M}, w \vDash
-  \phi\}$.  We will drop $\mathbbm{M}$ where it is unambiguous.}}. Since the
-  store $\Psi$ of nominals is infinite and $\Upsilon$ is finite, we have that
-  $\Psi \backslash \Upsilon$ is infinite, so there is some injection $\iota :
-  W' \hookrightarrow \Psi \backslash \Upsilon$ which assigns a fresh nominal
-  to every world.  Let $\mathbbm{M}'' = \langle W'', V'', R'', \mathcal{A}'',
-  \ell \rangle$, where:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign V' (p)$\\
-      $\bullet$ & $R'' \assign R'_{\Box}$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}'' (v) \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
-      \mathcal{A}' (v)\} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
-      \neg v R' u\}$\\
-      \begin{tabular}{ll}
-        $\bullet$ & $\ell (i) \assign \left\{ \begin{array}{ll}
-          w & i \in \Upsilon \hspace{1em} \& \hspace{1em} \mathbbm{M}, w
-          \vDash i\\
-          \iota^{- 1} (i) & i \in \iota [W]\\
-          \text{undefined} & \text{o/w}
-        \end{array} \right.$
-      \end{tabular} & $R'' \assign R'_{\Box}$ &  &  & 
-    \end{tabular}
-  \end{center}
-
-  The the worlds is $\mathbbm{M}'$ and $\mathbbm{M}''$ agree on all
-  subformulae of $\psi$, hence $\mathbbm{M}'', w \nvDash \psi$. The same
-  reasoning as in the proof of Theorem \ref{completeness1} establishes and
-  that the logic in Table \ref{logic2} itself is sound for $\mathbbm{M}''$ and
-  makes true \tmtextbf{CSQ}, establishing completeness.
-\end{proof}
 %%% Local Variables: 

### 2010-12-15 completeness2.tex
Fixed lots of spacing

@@
     {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{{\forall}{\phi}{\hspace{1em}}|{\hspace{1em}}\Box{\phi}{\in}{\Sigma}_0\}\\
+    {\assign}{\Sigma}_0{\cup}\{{\forall}{\phi}{\ }|{\ }\Box{\phi}{\in}{\Sigma}_0\}\\
     {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{\text{@}_i{\phi}{\hspace{1em}},i{\rightarrow}{\phi}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1{\hspace{1em}}\&{\hspace{1em}}i{\in}{\Upsilon}\}\\
+    {\assign}{\Sigma}_1{\cup}\{\text{@}_i{\phi}{\ },i{\rightarrow}{\phi}|{\ }{\phi}{\in}{\Sigma}_1{\ }\&{\ }i{\in}{\Upsilon}\}\\
     {\Sigma}_3 &
-    {\assign}{\Sigma}_2{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_2\}
+    {\assign}{\Sigma}_2{\cup}\{{\neg}{\phi}{\ }|{\ }{\phi}{\in}{\Sigma}_2\}
   \end{align*}
@@
   convention, here $\left\llbracket \phi \right\rrbracket^{\mathbbm{M}}$
-  denotes $\{w \in W \hspace{1em} | \hspace{1em} \mathbbm{M}, w \vDash
+  denotes $\{w \in W \  | \  \mathbbm{M}, w \vDash
   \phi\}$.  We will drop $\mathbbm{M}$ where it is unambiguous.}}. Since the
@@
       $\bullet$ & $R'' \assign R'_{\Box}$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}'' (v) \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
-      \mathcal{A}' (v)\} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
+      $\mathcal{A}'' (v) \assign \{\phi \  | \  \phi \in
+      \mathcal{A}' (v)\} \cup \{\neg \iota (u) \  | \ 
       \neg v R' u\}$\\
@@
         $\bullet$ & $\ell (i) \assign \left\{ \begin{array}{ll}
-          w & i \in \Upsilon \hspace{1em} \& \hspace{1em} \mathbbm{M}, w
+          w & i \in \Upsilon \  \& \  \mathbbm{M}, w
           \vDash i\\

### 2010-12-15 neighborhood_semantics.tex
more spell checking
Fixed lots of spacing

@@
 \begin{definition}
-  Let $\Phi$ be a set of letters and $\Psi$ a set of nominals, and define the
-  language $\mathcal{L}_N (\Phi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \bot \hspace{1em} | \hspace{1em} \phi \rightarrow \psi
-     \hspace{1em} | \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A :
-     \phi \hspace{1em} | \hspace{1em} K \phi \]
+  Let $\Phi$ be a set of letters and define the language $\mathcal{L}_N (\Phi)$ as:
+  \[ \phi \  : : = \  p \in \Phi \  |
+     \  \bot \  | \  \phi \rightarrow \psi
+     \  | \  \Box \phi \  | \  A :
+     \phi \  | \  K \phi \]
 \end{definition}
@@
 
-    \item $V (p) \assign \{v \in W \hspace{1em} | \hspace{1em} p \in v\}$
+    \item $V (p) \assign \{v \in W \  | \  p \in v\}$
 
-    \item $\mathcal{K}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
-    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
-    \hspace{1em} K \phi \in w\}$
+    \item $\mathcal{K}_w \assign \{S \in 2^W \  | \  \{v
+    \in W \  | \  \phi \in v\} \subseteq S \  \&
+    \  K \phi \in w\}$
 
-    \item $\mathcal{N}_w \assign \{S \in 2^W \hspace{1em} | \hspace{1em} \{v
-    \in W \hspace{1em} | \hspace{1em} \phi \in v\} \subseteq S \hspace{1em} \&
-    \hspace{1em} \Box \phi \in w\}$
+    \item $\mathcal{N}_w \assign \{S \in 2^W \  | \  \{v
+    \in W \  | \  \phi \in v\} \subseteq S \  \&
+    \  \Box \phi \in w\}$
 
-    \item $\mathcal{A}_w \assign \{\{\phi\} \hspace{1em} | \hspace{1em} A :
+    \item $\mathcal{A}_w \assign \{\{\phi\} \  | \  A :
     \phi \in w\}$
@@
   is some $\phi$ and $S$ where $\Box \phi \in w$ and $S \supseteq \{v \in W
-  \hspace{1em} | \hspace{1em} \phi \in v\}$.  We argue that $\vdash \phi
+  \  | \  \phi \in v\}$.  We argue that $\vdash \phi
   \rightarrow \chi$; for if not then by the finitary Lindenbaum lemma there is
@@
 
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
+    \item $V' (p) \assign \{v_l, v_r \  | \  v \in V
     (p)\}$
 
-    \item $\mathcal{K}' (v_i) \assign \{S \hspace{1em} | \hspace{1em} v_i \in
-    S \hspace{1em} \& \hspace{1em} \theta [S] \in \mathcal{K_v} \}$ where $i =
+    \item $\mathcal{K}' (v_i) \assign \{S \  | \  v_i \in
+    S \  \& \  \theta [S] \in \mathcal{K_v} \}$ where $i =
     l, r$
 
-    \item $\mathcal{N}' (v_i) \assign \mathcal{K}' (v_i) \cup \{S \hspace{1em}
-    | \hspace{1em} v_i \nin S \hspace{1em} \& \hspace{1em} \theta [S] \in
+    \item $\mathcal{N}' (v_i) \assign \mathcal{K}' (v_i) \cup \{S \ 
+    | \  v_i \nin S \  \& \  \theta [S] \in
     \mathcal{N_v} \}$ where $i = l, r$
@@
 
-  If we let $Z \assign \{(v, v_r), (v, v_l) \hspace{1em} | \hspace{1em} v \in
+  If we let $Z \assign \{(v, v_r), (v, v_l) \  | \  v \in
   W\}$, it is straightforward to verify that $Z$ is a neighborhood
@@
       $\bullet$ & $\mathcal{N}''_w \assign \mathcal{N}'_w$ & {\hspace{3em}} &
-      $\bullet$ & $\mathcal{A}''_v \assign \{\partial_v S \hspace{1em} |
-      \hspace{1em} S \in \mathcal{N}'_w \}$
+      $\bullet$ & $\mathcal{A}''_v \assign \{\partial_v S \  |
+      \  S \in \mathcal{N}'_w \}$
     \end{tabular}
@@
 
-  Where $\partial_v S \assign \{\phi \hspace{1em} | \hspace{1em} \phi \in
+  Where $\partial_v S \assign \{\phi \  | \  \phi \in
   \bigcup \mathcal{A}_v', \text{$\phi$ is a subformula of $\psi$ and}
-  \hspace{1em} S \subseteq \left\llbracket \phi
-  \right\rrbracket^{\mathbbm{M}'} \} \cup \{\neg \iota (u) \hspace{1em} |
-  \hspace{1em} u \nin S\}$.
+  \  S \subseteq \left\llbracket \phi
+  \right\rrbracket^{\mathbbm{M}'} \} \cup \{\neg \iota (u) \  |
+  \  u \nin S\}$.
 

### 2010-12-15 simple_justification.tex
Fixed lots of spacing

@@
   following grammar:
-  \[ X \hspace{1em} : : = \hspace{1em} t \in \Pi \hspace{1em} | \hspace{1em} X
+  \[ X \  : : = \  t \in \Pi \  | \  X
      \oplus Y \]
@@
   define the language $\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi \]
+  \[ \phi \  : : = \  p \in \Phi \  |
+     \  \circlearrowleft_X \  | \  \bot
+     \  | \  \phi \rightarrow \psi \  |
+     \  \Box_X \phi \  | \  X : \phi \]
   where $X \in \tau (\Pi)$
@@
   \langle W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V
-  : \Phi \cup \{\circlearrowleft_X \hspace{1em} | \hspace{1em} X \in \tau
+  : \Phi \cup \{\circlearrowleft_X \  | \  X \in \tau
   (\Pi)\} \rightarrow 2^W$, an indexed relation $R : \tau (\Pi) \rightarrow
@@
     {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{\Box_Y{\phi}{\hspace{1em}}|{\hspace{1em}}\Box_X{\phi}{\in}{\Sigma}_0{\hspace{1em}}\&{\hspace{1em}}Y{\in}{\Xi}\}\\
+    {\assign}{\Sigma}_0{\cup}\{\Box_Y{\phi}{\ }|{\ }\Box_X{\phi}{\in}{\Sigma}_0{\ }\&{\ }Y{\in}{\Xi}\}\\
     {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{{\neg}{\phi}{\hspace{1em}}|{\hspace{1em}}{\phi}{\in}{\Sigma}_1\}
+    {\assign}{\Sigma}_1{\cup}\{{\neg}{\phi}{\ }|{\ }{\phi}{\in}{\Sigma}_1\}
   \end{align*}
@@
   \times W}$ is defined by:
-  \[ w R_X v \Longleftrightarrow \{\phi \hspace{1em} | \hspace{1em} \Box_X
+  \[ w R_X v \Longleftrightarrow \{\phi \  | \  \Box_X
      \phi \in w\} \subseteq v \]
@@
   Next, define an operator $\twonotes : \tau (\Pi) \rightarrow 2^{\Pi}$ where:
-  \[ \twonotes (X) \assign \{t \in \Pi \hspace{1em} | \hspace{1em} t \text{
+  \[ \twonotes (X) \assign \{t \in \Pi \  | \  t \text{
      occurs in } X\} \]
@@
 
-    \item $V' (p) \assign \{v_l, v_r \hspace{1em} | \hspace{1em} v \in V
+    \item $V' (p) \assign \{v_l, v_r \  | \  v \in V
     (p)\}$
 
-    \item $R'_X \assign \{(v_l, u_r), (v_r, u_l) \hspace{1em} | \hspace{1em} v
-    R_X u\} \cup \{(v_l, v_l), (v_r, v_r) \hspace{1em} | \hspace{1em}
+    \item $R'_X \assign \{(v_l, u_r), (v_r, u_l) \  | \  v
+    R_X u\} \cup \{(v_l, v_l), (v_r, v_r) \  | \ 
     \mathbbm{M}, v \vDash \circlearrowleft_X \}$
@@
   $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that{\footnote{Let $\{i_X \hspace{1em} | \hspace{1em} X \in \Xi\}$ be the
+  that{\footnote{Let $\{i_X \  | \  X \in \Xi\}$ be the
   family of canonical injections into the coproduct $\uplus_{\Xi} W$. As per
@@
 
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
+    \item $V'' (p) \assign \{v_X \  | \  X \in \Xi
+    \  \& \  v \in V' (p)\}$
 
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em}
+    \item $R''_X \assign \{(v_Y, u_Z) \  | \  Y, Z \in \Xi
+    \  \& \  v R'_Z u \  \& \ 
     \twonotes (X) \subseteq \twonotes (Z)\}$
@@
   Note that this construction makes use of the assumption that $\Xi$ is
-  non-empty.  Let $Z \assign \{(v, v_X) \hspace{1em} | \hspace{1em} X \in \Xi
-  \hspace{1em} \& \hspace{1em} v \in W' \}$; it is straightforward to prove
+  non-empty.  Let $Z \assign \{(v, v_X) \  | \  X \in \Xi
+  \  \& \  v \in W' \}$; it is straightforward to prove
   that $Z$ is a bisimulation between $\mathbbm{M}'$ and $\mathbbm{M}''$, for
@@
     \text{$(v_V, u_Z) \in R''_X \cap R''_Y$} & \Longleftrightarrow & \exists Z
-    \in \Xi . \text{$v R'_Z u \hspace{1em} \& \hspace{1em} \twonotes (X)
-    \subseteq \twonotes (Z) \hspace{1em} \& \hspace{1em} \twonotes (Y)
+    \in \Xi . \text{$v R'_Z u \  \& \  \twonotes (X)
+    \subseteq \twonotes (Z) \  \& \  \twonotes (Y)
     \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X) \cup \twonotes (Y) \subseteq \twonotes
+    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \ 
+    \& \  \twonotes (X) \cup \twonotes (Y) \subseteq \twonotes
     (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \hspace{1em}
-    \& \hspace{1em} \twonotes (X \oplus Y) \subseteq \twonotes (Z)$}\\
+    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \ 
+    \& \  \twonotes (X \oplus Y) \subseteq \twonotes (Z)$}\\
     & \Longleftrightarrow &  \text{$(v_V, u_Z) \in R''_{X \oplus Y}$}
@@
       &  & \\
-      $\bullet$ & $\mathcal{A}'''_v (t) \assign \{\phi \hspace{1em} | \phi \in
-      \mathcal{A}''_v \} \cup \{\neg \iota (u) \hspace{1em} | \hspace{1em}
+      $\bullet$ & $\mathcal{A}'''_v (t) \assign \{\phi \  | \phi \in
+      \mathcal{A}''_v \} \cup \{\neg \iota (u) \  | \ 
       \neg v R'''_t u\}$ & where $t \in \Pi$\\

### 2010-12-15 completeness3.tex
factored out completeness theorem

--- 2010-12-15 simple_justification.tex
@@
-Justification Logic (JL) was originally developed by Artemov as the
-\tmtextit{Logic of Proofs} (LP) {\cite{artemov_logic_1994}}.  Its original
-purpose was to provide a framework for reasoning about explicit provability in
-Peano Arithmetic.  The first introduction of Justification Logic can be found
-in {\cite{artemov_introducing_2005}}, where Artemov and Nogina propose LP as a
-logic for reasoning about evidence.  In {\cite{fitting_logic_2005}}, Melvin
-Fitting provided JL with Kripke model based semantics.
-
-The principle innovation of LP/JL is to extend awareness logic, such that
-awareness operations are now \tmtextit{proof terms}.  Informally, we say that
-``a proof term $X$ witnesses proposition $\phi$'', denoted ``$X : \phi$'',
-whenever $X$ represents a proof of $\phi$.  Proofs may have
-{\tmstrong{multiple-conclusions}} in this system, so it is possible that $X :
-\phi$ and $X : \psi$ can be true where $\phi \neq \psi$.  In Fitting's Kripke
-semantics, $X : \phi$ means that $\phi$ is in awareness set corresponding to
-$X$.  Proof terms are thought be operating in a \tmtextit{multi-conclusion}
-proof system, so the same proof term may witness many different propositions.
-
-The logics LP/JL include operators over proofs terms, so that new proof terms
-may be assembled.  One operation of particular interest to us is
-{\tmem{choice}}, denoted $\oplus$.  The expression ``$X \oplus Y : \phi$''
-denotes that either $X$ or $Y$ are proofs witnessing $\phi$.  There are other
-operations which correspond to \tmtextit{modus ponens} and
-\tmtextit{proof-theoretic reflection}, however we do not consider these
-operations here.
-
-In this section we consider a simplified form of JL suitable for reasoning
-over multiple knowledge bases, which we call \tmtextit{simple justification
-logic} (SJL). However, instead of thinking of terms as representing proofs, we
-use them to represent knowledge bases. This is in the spirit of JL as a logic
-of evidence: we consider each knowledge base to be a corpus of evidence. \
-Each term ``names'' a different knowledge base at a particular world.  Terms
-may not refer to the same knowledge base at different worlds, just as in how
-in awareness logic the agent need not be aware of the same formulae at
-different worlds.  Finally, we will make use of JL's {\tmem{choice}} operator
-as a mechanism for forming the union of knowledge bases, creating new ones.
-
-\begin{definition}
-  Let $\Pi$ be a set of primitive terms.  Define $\tau (\Pi)$ with the
-  following grammar:
-  \[ X \  : : = \  t \in \Pi \  | \  X
-     \oplus Y \]
-
-  Let $\Phi$ be a set of letters and $\Pi$ a set of primitive terms, and
-  define the language $\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)$ as:
-  \[ \phi \  : : = \  p \in \Phi \  |
-     \  \circlearrowleft_X \  | \  \bot
-     \  | \  \phi \rightarrow \psi \  |
-     \  \Box_X \phi \  | \  X : \phi \]
-  where $X \in \tau (\Pi)$
-\end{definition}
-
-\begin{definition}
-  \label{justmodels}A {\tmstrong{simple justification model}} $\mathbbm{M}=
-  \langle W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V
-  : \Phi \cup \{\circlearrowleft_X \  | \  X \in \tau
-  (\Pi)\} \rightarrow 2^W$, an indexed relation $R : \tau (\Pi) \rightarrow
-  2^{W \times W}$, along with a modified awareness function $\mathcal{A} : W
-  \times \tau (\Pi) \rightarrow 2^{\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)}$. \
-  In practice we will denote $\mathcal{A} (w, X)$ by a curried shorthand,
-  namely $\mathcal{A}_w (X)$.
-
-  The semantics for $\vDash$ have the following modifications:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box_X \phi & \text{iff} & \text{for all $v \in W$
-    where $w R_X v$ we have $\mathbbm{M}, v \vDash v$}\\
-    \mathbbm{M}, w \vDash X : \phi & \text{iff} & \phi \in \mathcal{A}_w (X)
-  \end{eqnarray*}
-\end{definition}
-
-\begin{definition}
-  The following defines properties a simple justification model may make true:
-
-  \begin{descriptiondash}
-    \item[JCSQ] $\mathbbm{M}, w \vDash \Box_X \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w (X) \vdash \phi$
-
-    \item[JSND] $\mathbbm{M}, w \vDash \circlearrowleft_X \text{ iff
-    $\mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w (X)$}$
-
-    \item[CHOICE] $\mathcal{A}_w (X \oplus Y) = \mathcal{A}_w (X) \cup
-    \mathcal{A}_w (Y)$
-  \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
-\end{definition}
-
-The above semantics are similar to the ones given in previous sections. \
-\tmtextbf{JCSQ} is the same as \tmtextbf{CSQ} from {\S}\ref{awarenesslogic},
-only it is relativised to a knowledge base denoted by $X$ at $w$.  The
-awareness logic of knowledge bases is special case of simple justification
-logic where there is only one term.
-
-Simplified justification logic is given in Table \ref{logic5}.  We assert
-without proof that this is a conservative extension of the awareness logic in
-{\S}\ref{awarenesslogic}.
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
-    \Box_X \psi$ & \\
-    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash (X \oplus Y : \phi) \rightarrow X : \phi$ & $\vdash (X \oplus Y :
-    \phi) \rightarrow Y : \phi$\\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_X$ &
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_Y$\\
-    $\vdash \Box_X \phi \rightarrow \Box_{X \oplus Y} \phi$ & \\
-    $\vdash \Box_{X \oplus X} \phi \rightarrow \Box_X \phi$ & $\vdash \Box_{(X
-    \oplus X) \oplus Y} \phi \rightarrow \Box_{X \oplus Y} \phi$ \\
-    $\vdash \Box_{X \oplus Y} \phi \rightarrow \Box_{Y \oplus X} \phi$ &
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{(Y \oplus X)
-    \oplus Z} \phi$\\
-    $\vdash \Box_{(X \oplus Y) \oplus Z} \phi \rightarrow \Box_{X \oplus (Y
-    \oplus Z)} \phi$ & \\
-    & \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic5}Simple Justification Logic}
-\end{table}
-
-\begin{theorem}
-  \label{completeness5}Assuming an infinite store of proposition letters
-  $\Phi$, SJL is sound and weakly complete for simple justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND} and \tmtextbf{CHOICE}
-\end{theorem}
-
 \begin{proof}
@@
 \end{proof}
+
 %%% Local Variables: 

### 2010-12-15 simple_justification.tex
factored out completeness theorem

@@
 \end{theorem}
+\input{completeness3}
 
-\begin{proof}
-  As in the previous proofs, we only show completeness.  Assume that $\nvdash
-  \psi$.  Let $\Xi \subseteq \tau (\Pi)$ be all of the subterms occurring in
-  $\psi$; we assume that $\Xi$ is non-empty, since otherwise we may obtain the
-  theorem via the usual completeness theorem for classical propositional
-  logic. Let $\Sigma_0$ be the subformulae of $\psi$.  Define:
-
-  \begin{align*}
-    {\Sigma}_1 &
-    {\assign}{\Sigma}_0{\cup}\{\Box_Y{\phi}{\ }|{\ }\Box_X{\phi}{\in}{\Sigma}_0{\ }\&{\ }Y{\in}{\Xi}\}\\
-    {\Sigma}_2 &
-    {\assign}{\Sigma}_1{\cup}\{{\neg}{\phi}{\ }|{\ }{\phi}{\in}{\Sigma}_1\}
-  \end{align*}
-
-  As in the proof of Theorem \ref{completeness2}, it is simple to verify that
-  $\Sigma_2$ is closed under subformulae and single negations.  Let
-  $\mathbbm{M} \assign \langle W, V, R, \mathcal{A} \rangle$ be the finite
-  canonical model formed of maximally consistent subsets of $\Sigma_2$, where
-  $V$ and $\mathcal{A}$ are defined as usual, and $R : \Xi \rightarrow 2^{W
-  \times W}$ is defined by:
-  \[ w R_X v \Longleftrightarrow \{\phi \  | \  \Box_X
-     \phi \in w\} \subseteq v \]
-  As in previous constructions we may prove the usual Lindenbaum and Truth
-  Lemmas an use them obtain a world $w \in W$ where $\mathbbm{M}, w \nvDash
-  \psi$.
-
-  Next, define an operator $\twonotes : \tau (\Pi) \rightarrow 2^{\Pi}$ where:
-  \[ \twonotes (X) \assign \{t \in \Pi \  | \  t \text{
-     occurs in } X\} \]
-  In other words, $\twonotes (X)$ is the set of atomic terms in $X$.  As in
-  our construction for Theorem \ref{completeness1}, $\mathbbm{M}$ makes true
-  certain properties, along with some new properties:
-  \begin{enumeratenumeric}
-    \item \label{fin}$W$ and $\mathcal{A}_v (X)$ are finite, and $\phi \in
-    \mathcal{A}_v (X)$ only if $\phi \in \Sigma_2$
-
-    \item if $\mathbbm{M}, v \vDash X : \phi$ then $\mathbbm{M}, v \vDash
-    \Box_X \phi$
-
-    \item \label{refl}if $\mathbbm{M}, v \vDash \circlearrowleft_X$ then $v
-    R_X v$
-
-    \item \label{sndness}For all $X \oplus Y \in \Xi$, $\mathbbm{M}, v \vDash
-    \circlearrowleft_{X \oplus Y}$ if and only if $\mathbbm{M}, v \vDash
-    \circlearrowleft_X$ and $\mathbbm{M}, v \vDash \circlearrowleft_Y$
-
-    \item \label{union}For all $X \oplus Y \in \Xi$, $\mathcal{A}_v (X \oplus
-    Y) = \mathcal{A}_v (X) \cup \mathcal{A}_v (Y)$
-
-    \item \label{sub}For all $X, Y \in \Xi$, if $\twonotes (X) \subseteq
-    \twonotes (Y)$ then $R_Y \subseteq R_X$
-  \end{enumeratenumeric}
-  As in our previous constructions, it is necessary to refine this model using
-  bisimulations to achieve properties which are not modally definable.  In
-  particular, we shall strengthen (\ref{refl}) to a biconditional and
-  (\ref{sub}) to:
-
-  \begin{center}
-    \begin{tabular}{ll}
-      \tmtextbf{6$'$.} & For all $X, Y \in \Xi$, $R_{X \oplus Y} = R_X \cap
-      R_Y$
-    \end{tabular}
-  \end{center}
-
-  We first strengthen (\ref{refl}) by constructing $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}' \rangle$, just as in Theorem
-  \ref{completeness1}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \  | \  v \in V
-    (p)\}$
-
-    \item $R'_X \assign \{(v_l, u_r), (v_r, u_l) \  | \  v
-    R_X u\} \cup \{(v_l, v_l), (v_r, v_r) \  | \ 
-    \mathbbm{M}, v \vDash \circlearrowleft_X \}$
-
-    \item $\mathcal{A}' (v_l, X) \assign \mathcal{A}' (v_r, X) \assign
-    \mathcal{A} (v, X)$
-  \end{itemizedot}
-  The same bisimulation relation $Z$ previously given suffices.
-
-  We next make a strengthened the model where (\ref{sub}$'$) holds.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that{\footnote{Let $\{i_X \  | \  X \in \Xi\}$ be the
-  family of canonical injections into the coproduct $\uplus_{\Xi} W$. As per
-  our previous convention, we use $v_X$ as shorthand for $i_X (v)$.}}:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \  | \  X \in \Xi
-    \  \& \  v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \  | \  Y, Z \in \Xi
-    \  \& \  v R'_Z u \  \& \ 
-    \twonotes (X) \subseteq \twonotes (Z)\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  Note that this construction makes use of the assumption that $\Xi$ is
-  non-empty.  Let $Z \assign \{(v, v_X) \  | \  X \in \Xi
-  \  \& \  v \in W' \}$; it is straightforward to prove
-  that $Z$ is a bisimulation between $\mathbbm{M}'$ and $\mathbbm{M}''$, for
-  all relations corresponding to terms $X \in \Xi$. Hence $\mathbbm{M}'', w_X
-  \nvDash \psi$ for some $w_X \in W''$.  In addition, $\mathbbm{M}''$
-  inherits (\ref{fin}) through (\ref{sub}) from $\mathbbm{M}'$, as well as the
-  converse of (\ref{refl}).  Next observe, forall $X \oplus Y \in \Xi$:
-  \begin{eqnarray*}
-    \text{$(v_V, u_Z) \in R''_X \cap R''_Y$} & \Longleftrightarrow & \exists Z
-    \in \Xi . \text{$v R'_Z u \  \& \  \twonotes (X)
-    \subseteq \twonotes (Z) \  \& \  \twonotes (Y)
-    \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \ 
-    \& \  \twonotes (X) \cup \twonotes (Y) \subseteq \twonotes
-    (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \ 
-    \& \  \twonotes (X \oplus Y) \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow &  \text{$(v_V, u_Z) \in R''_{X \oplus Y}$}
-  \end{eqnarray*}
-  We now turn to our final construction. As in previous constructions, let
-  $\iota : W'' \hookrightarrow \Phi \backslash \Psi$ be an injection assigning
-  fresh nominals to worlds.  Define $\mathbbm{M}''' \assign \langle W''',
-  V''', R''', \mathcal{A}''' \rangle$ just as in the final construction in the
-  proof of Theorem \ref{completeness1}, except that $R'''_X$ and
-  $\mathcal{A}_v''' (X)$ are defined inductively as follows:
-
-  \begin{center}
-    \begin{tabular}{lll}
-      $\bullet$ & $R'''_t \assign \left\{ \begin{array}{ll}
-        R''_t & t \in \Xi\\
-        W''' \times W''' & o / w
-      \end{array} \right.$ & \\
-      $\bullet$ & $R'''_{X \oplus Y} \assign R'''_X \cap R'''_Y$ & \\
-      &  & \\
-      $\bullet$ & $\mathcal{A}'''_v (t) \assign \{\phi \  | \phi \in
-      \mathcal{A}''_v \} \cup \{\neg \iota (u) \  | \ 
-      \neg v R'''_t u\}$ & where $t \in \Pi$\\
-      $\bullet$ & $\mathcal{A}'''_v (X \oplus Y) \assign \mathcal{A}'''_v (X)
-      \cup \mathcal{A}'''_v (Y)$ & 
-    \end{tabular}
-  \end{center}
-
-  Induction over complexity of subformulae $\phi$ of $\psi$ yields
-  $\mathbbm{M}'', w \vDash \phi \Longleftrightarrow \mathbbm{M}''', w \vDash
-  \phi$, so we know that there is some world $w \in W'''$ such that
-  $\mathbbm{M}''', w \nvDash \psi$.  All that is left is to illustrate that
-  $\mathbbm{M}'''$ has the properties we desire.
-
-  First note that by definition, $\mathbbm{M}'''$ makes true
-  \tmtextbf{CHOICE}.  Next, an induction argument on the complexity of a
-  terms $X$, making essential use of (\ref{sub}$'$), yields:
-  \[ u R_X''' v \Longleftrightarrow \mathbbm{M}''', v \vDash \bigwedge
-     \mathcal{A}'''_v (X) \]
-  With this, $\mathbbm{M}'''$ makes true \tmtextbf{JSND} since it inherits
-  (\ref{refl}).  Finally, we note that we may repeat our previous arguments
-  from Theorem \ref{completeness1} to prove \tmtextbf{JCSQ}.
-\end{proof}
 %%% Local Variables: 

### 2010-12-15 awareness.tex
fixing references

@@
 In this section, we give the explicit semantics to basic awareness logic,
-originally presented in {\cite{fagin_belief_1987}}, with an additional axiom.
+originally presented in {\cite{fagin_belief_1988}}, with an additional axiom.
  One difference in our presentation is the inclusion of a novel letter and a
 superficial change in notation.  This work is inspired by the developments in
-van Benthem and Vel\'azquez-Quesada {\cite{van_benthem_inference_2009}}.
+van Benthem and Vel\'azquez-Quesada {\cite{benthem_inference_2009}}.
 

### 2010-12-15 introduction.tex
spell checking sections
fixing references

@@
 
-In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem proposed
+In {\cite{benthem_reflections_1991}}, Johan van Benthem proposed
 a research program to find logics for explicit knowledge, providing the first
@@
 Vel\'azquez-Quesada and Johan van Benthem have developed a simpler framework
-for explicit epistemics in {\cite{van_benthem_inference_2009}}, entitled the
+for explicit epistemics in {\cite{benthem_inference_2009}}, entitled the
 \tmtextit{Dynamics of Awareness}.  This work was based on Joseph Halpern and

### 2010-12-15 paper.tex
spell checking sections
Added todonotes
trying to get hyper-refs working
Hyper-refs work now
No more "bbm.sty", black board fonts should be fixed now
fixing references

@@
 \documentclass{article}
-\usepackage{geometry,amsmath,amssymb,wasysym,enumerate,bbm,color}
+
+\usepackage{hyperref}
+ \hypersetup{
+     colorlinks,%
+     citecolor=black,%
+     filecolor=black,%
+     linkcolor=black,%
+     urlcolor=black
+ }
+
+\usepackage{stmaryrd}
+\usepackage{todonotes}
+
+\usepackage{geometry,amsmath,amssymb,wasysym,enumerate,color}
 \geometry{letterpaper}
 
-\usepackage{stmaryrd}
-\usepackage[myoption=\fixme]{fixme}
-
 %%%%%%%%%% Start TeXmacs macros
+\newcommand{\mathbbm}{\mathbb}
 \newcommand{\assign}{:=}
@@
 \title{Epistemic Logics For Knowledge Bases}\author{Matthew P.
-Wampler-Doty}\maketitle
+Wampler-Doty}\date{}\maketitle
 
 \begin{abstract}
-  In {\cite{van_benthem_reflectionsepistemic_1991}}, Johan van Benthem
+  In {\cite{benthem_reflections_1991}}, Johan van Benthem
   proposed a research program for logic of \tmtextit{explicit knowledge}. 
@@
   knowledge: the \tmtextit{Dynamics of Awareness}
-  {\cite{van_benthem_inference_2009}} and \tmtextit{Justification Logic}
+  {\cite{benthem_inference_2009}} and \tmtextit{Justification Logic}
   {\cite{artemov_introducing_2005}}.  The purpose of this paper is to
@@
 \end{abstract}
+
+\listoftodos
 

### 2010-12-15 completeness4.tex
factored out completeness theorem

--- 2010-12-15 lattice_justification.tex
@@
-Implicit in our previous presentation of SJL is the following
-principle: 
-\todo[noline]{THIS SECTION IS  PROBABLY WRONG}
- $\oplus$ behaves like a union
-operation for knowledge bases, and dually like an intersection operation on
-accessibility relations.  It is natural to think of $\oplus$ as a join/meet
-operator over a {\tmem{semilattice}}.  In this section we make this
-explicit, by increasing the expressive power of simple JL to express the order
-theory inherent in knowledge bases.  We call the novel logic presented in
-this section \tmtextit{Lattice Justification Logic} (LJL){\footnote{We note
-that ``Semilattice Justification Logic'' may be a more appropriate name,
-however we have decided to shorten semilattice to lattice in this article
-for purposes of concision.}}.  Lattice JL may be considered a novel logic for
-studying the dynamics of \tmtextit{theory change}, where the logic employed by
-the changing theories could be LJL itself.
-
-\begin{definition}
-  $\mathcal{L}_{\tmop{LJL}} (\Phi, \Pi)$ extends $\mathcal{L}_{\tmop{SJL}}
-  (\Phi, \Pi)$ to:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi
-     \hspace{1em} | \hspace{1em} X \sqsubseteq Y \]
-  where $X, Y \in \tau (\Pi)$
-\end{definition}
-
-\begin{definition}
-  \label{justmodels}A {\tmstrong{lattice justification model}} $\mathbbm{M}=
-  \langle W, V, R, \mathcal{A}, \preccurlyeq \rangle$ is a simple
-  justification model with a new relation $\preccurlyeq : W \rightarrow
-  2^{\tau (\Pi) \times \tau (\Pi)}$ between terms, indexed by worlds.  The
-  semantics of $\sqsubseteq$ correspond to $\preccurlyeq$ as follows:
-  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow X
-     \preccurlyeq_w Y \]
-\end{definition}
-
-\begin{definition}
-  A lattices justification model is said to make true \tmtextbf{LATTICE} if
-  and only if:
-  \[ \mathbbm{M}, w \vDash X \sqsubseteq Y \Longleftrightarrow \mathcal{A}_w
-     (X) \subseteq \mathcal{A}_w (Y) \]
-\end{definition}
-
-Table \ref{logic6} lists the axioms for the logic of lattice justification
-models with the properties we have been investigating:
-
-\begin{table}[h]
-  \begin{tabular}{ll}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$ & \\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$ & \\
-    $\vdash \Box_X (\phi \rightarrow \psi) \rightarrow \Box_X \phi \rightarrow
-    \Box_X \psi$ & \\
-    $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash X \sqsubseteq Y \rightarrow (X : \phi) \rightarrow Y : \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_X$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow \Box_X \phi \rightarrow \Box_Y \phi$ &
-    \\
-    $\vdash X \sqsubseteq X$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow Y \sqsubseteq Z \rightarrow X
-    \sqsubseteq Z$ & \\
-    $\vdash X \sqsubseteq Y \rightarrow X \sqsubseteq Z \oplus Y$ & $\vdash X
-    \sqsubseteq Y \rightarrow X \sqsubseteq Y \oplus Z$\\
-    $\vdash X \sqsubseteq Z \rightarrow Y \sqsubseteq Z \rightarrow X \oplus Y
-    \sqsubseteq Z$ & \\
-    & \\
-    \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
-  \end{tabular}
-  \caption{\label{logic6}Lattice Justification Logic}
-\end{table}
-
-\begin{theorem}
-  \label{completeness6}Assuming an infinite store of proposition letters
-  $\Phi$, LJL is sound and weakly complete for lattice justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND}, \tmtextbf{CHOICE} and
-  \tmtextbf{LATTICE}
-\end{theorem}
-
 \begin{proof}
@@
 
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
+    \item $V'' (p) \assign \{v_X \  | \  X \in \Xi
+    \  \& \  v \in V' (p)\}$
 
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em} X
+    \item $R''_X \assign \{(v_Y, u_Z) \  | \  Y, Z \in \Xi
+    \  \& \  v R'_Z u \  \& \  X
     \preccurlyeq_v Z\}$
@@
   \end{eqnarray}
-
   \end{proof}

### 2010-12-15 lattice_justification.tex
Fixed lots of spacing
fixed duplicate label
factored out completeness theorem

@@
   (\Phi, \Pi)$ to:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft_X \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box_X \phi \hspace{1em} | \hspace{1em} X : \phi
-     \hspace{1em} | \hspace{1em} X \sqsubseteq Y \]
+  \[ \phi \  : : = \  p \in \Phi \  |
+     \  \circlearrowleft_X \  | \  \bot
+     \  | \  \phi \rightarrow \psi \  |
+     \  \Box_X \phi \  | \  X : \phi
+     \  | \  X \sqsubseteq Y \]
   where $X, Y \in \tau (\Pi)$
@@
 \begin{definition}
-  \label{justmodels}A {\tmstrong{lattice justification model}} $\mathbbm{M}=
+  \label{latmodels}A {\tmstrong{lattice justification model}} $\mathbbm{M}=
   \langle W, V, R, \mathcal{A}, \preccurlyeq \rangle$ is a simple
@@
 
-\begin{proof}
-  Assume $\nvdash \psi$.  Let $\mathbbm{M} \assign \langle W, V, R,
-  \mathcal{A}, \preccurlyeq \rangle$ be the same as the finitary canonical
-  model we initially constructed in Theorem \ref{completeness5}, only
-  $\preccurlyeq$ is defined as:
-  \[ X \preccurlyeq_w Y \Longleftrightarrow w \vdash X \sqsubseteq Y \]
-  We may deduce that there is a world $w \in W$ such that $\mathbbm{M}, w
-  \nvDash \psi$.  This canonical model makes true properties (\ref{fin})
-  through (\ref{union}) we listed in Theorem \ref{completeness5}, as well as a
-  certain new properties:
-
-  \begin{descriptioncompact}
-    \item[6$\preccurlyeq$] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$
-    then $R_Y [v] \subseteq R_X [v]$
-
-    \item[7] For all $X, Y \in \Xi$, if $X \preccurlyeq_v Y$ then
-    $\mathcal{A}_v (X) \subseteq \mathcal{A}_v (Y)$
-
-    \item[8] If $X \nin \Xi$, then $R_X = W \times W$ and $\mathcal{A}_v (X) =
-    \varnothing$ for all $v \in W$
-
-    \item[9] $\langle \preccurlyeq_v, \oplus \rangle$ is a join-semilattice
-    over $\tau (\Pi)$ for all $v \in W$
-  \end{descriptioncompact}
-
-  As in previous constructions, completeness is achieved by through a series
-  of model refinements.  Note that property 8 has been implicitly true in all
-  of our previous constructions, although we have not been interested in
-  enforcing it to be inherited by model refinements previously.
-
-  We first construct a model $\mathbbm{M}'$ which is bisimular to
-  $\mathbbm{M}$, where (\ref{refl}) is strengthened to a biconditional.  This
-  is done exactly as we proceeded in previous constructions. We note that the
-  notion of ``bisimulation'' here includes that two bisimular worlds $v$ and
-  $u$ must have isomorphic semilattices $\preccurlyeq_v$ and
-  $\preccurlyeq_w$.  This is achieved by enforcing that $\preccurlyeq_{v_l}
-  \assign \preccurlyeq_{v_r} \assign \preccurlyeq_v$. As before, we have that
-  $\mathbbm{M}', w \nvDash \psi$ for some world $w \in W'$.
-
-  We next strengthen (6$\preccurlyeq$) to a biconditional.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \hspace{1em} | \hspace{1em} X \in \Xi
-    \hspace{1em} \& \hspace{1em} v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \hspace{1em} | \hspace{1em} Y, Z \in \Xi
-    \hspace{1em} \& \hspace{1em} v R'_Z u \hspace{1em} \& \hspace{1em} X
-    \preccurlyeq_v Z\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  $\mathbbm{M}''$ is bisimular to $\mathbbm{M}'$ by the same mechanism as the
-  previous construction.  The important feature of this structure is to
-  observe that the converse of (6$\preccurlyeq$) holds:
-  \begin{eqnarray*}
-    R_Y [v] \subseteq R_X [v] & \Longleftrightarrow & \forall Z \in \Xi
-    \forall u_Z \in W'' (v_Q R'_Z u_Z \Longrightarrow v_Q R_X' u_Z)\\
-    & \Longleftrightarrow & \forall Z \in \Xi \forall u_Z \in W'' (v R'_Z
-    \Longrightarrow v_Q R_X u_Z)
-  \end{eqnarray*}
-
-  Our first transformation strengthens (\ref{union}), (6$\preccurlyeq$a) and
-  (6$\preccurlyeq$b) so that they hold for all terms in $\tau (\Pi)$, rather
-  than being restricted to $\Xi$.  To this end define $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}', \preccurlyeq' \rangle$ where $W'$, $R'$
-  and $\preccurlyeq'$ are the same as in $\mathbbm{M}$, but $R'$ and
-  $\mathcal{A}'$ have the following modifications:
-  \begin{eqnarray}
-    R'_Y [v] & \assign & \bigcap_{X \preccurlyeq_v Y} R_X [v] \nonumber\\
-    \mathcal{A}'_v (Y) & \assign & \bigcup_{X \preccurlyeq_v Y} \mathcal{A}'_v
-    (X) \nonumber
-  \end{eqnarray}
-
-\end{proof}
+\input{completeness4}
 %%% Local Variables: 

### 2010-12-15 neighborhood_semantics.tex
factored out completeness theorem

@@
   Let $\Phi$ be a set of letters and define the language $\mathcal{L}_N (\Phi)$ as:
-  \[ \phi \  : : = \  p \in \Phi \  |
-     \  \bot \  | \  \phi \rightarrow \psi
-     \  | \  \Box \phi \  | \  A :
-     \phi \  | \  K \phi \]
+  \[ \phi\ : : =\ p \in \Phi\ |
+    \ \bot\ |\ \phi \rightarrow \psi
+    \ |\ \Box \phi\ |\ A :
+     \phi\ |\ K \phi \]
 \end{definition}
@@
 
-\begin{proof}
-  Assume that $\nvdash \psi$, and define the finitary canonical model
-  $\mathbbm{M}= \langle W, V, \mathcal{K}, \mathcal{N}, \mathcal{A} \rangle$
-  where:
-  \begin{itemizedot}
-    \item $W \assign \text{the maximally consistent sets of subformulae of
-    $\psi$, closed under single negation}$
-
-    \item $V (p) \assign \{v \in W \  | \  p \in v\}$
-
-    \item $\mathcal{K}_w \assign \{S \in 2^W \  | \  \{v
-    \in W \  | \  \phi \in v\} \subseteq S \  \&
-    \  K \phi \in w\}$
-
-    \item $\mathcal{N}_w \assign \{S \in 2^W \  | \  \{v
-    \in W \  | \  \phi \in v\} \subseteq S \  \&
-    \  \Box \phi \in w\}$
-
-    \item $\mathcal{A}_w \assign \{\{\phi\} \  | \  A :
-    \phi \in w\}$
-  \end{itemizedot}
-  Note that in this model, there are neighborhoods for both knowledge and
-  belief; more work is necessary to find a model based on this one which
-  conforms to the semantics in Definition \ref{neighborhoodmodels}.  For now,
-  assume that $K$ is just another modality governed by the neighborhoods in
-  $\mathcal{K}_w$.  In both neighborhood functions, our idea is that the
-  neighborhoods of $w$ in are supersets $S \supseteq \left\llbracket \phi
-  \right\rrbracket$ where $\Box \phi \in w$ or $K \phi \in w$, respectively.
-
-  There are steps of the inductive proof of the Truth Lemma for this structure
-  which are not obvious nor obviously documented elsewhere.  Assume
-  $\mathbbm{M}, w \vDash \Box \chi$, where the Truth Lemma has been proven to
-  hold for $\chi$; we must show $\Box \chi \in w$.  By our assumption there
-  is some $\phi$ and $S$ where $\Box \phi \in w$ and $S \supseteq \{v \in W
-  \  | \  \phi \in v\}$.  We argue that $\vdash \phi
-  \rightarrow \chi$; for if not then by the finitary Lindenbaum lemma there is
-  some $u \in W$ where $\phi \in u$ and $\chi \nin u$.  Hence $u \in S$ and
-  $\mathbbm{M}, u \nvDash \chi$, a contradiction.  Since $\vdash \phi
-  \rightarrow \chi$ then we know that $\vdash \Box \phi \rightarrow \Box \chi$
-  by our rules, which means that $\Box \chi \in w$ by maximality.
-
-  By the Lindenbaum Lemma we have that there is some $w \in W$ where
-  $\mathbbm{M}, w \nvDash \psi$.  $\mathbbm{M}$ makes true a number of
-  properties:
-  \begin{enumeratenumeric}
-    \item $W$ and $\mathcal{A}_v$ are finite for all $v \in W$, and $\psi \in
-    \bigcup \mathcal{A_w}$ only if $\psi$ is a subformula of $\phi$
-
-    \item $\mathcal{K}_w \subseteq \mathcal{N}_w$
-
-    \item If $S \in \mathcal{K}_w$ then $w \in S$
-
-    \item $\mathbbm{M}, v \vDash A : \phi \rightarrow \Box \phi$ for all $v
-    \in W$
-
-    \item $\mathcal{N}_w$ and $\mathcal{K}_w$ are closed under supersets
-  \end{enumeratenumeric}
-
-  As in the proof of Theorem \ref{completeness1}, we use a bisimulation to
-  move to a model where property (3) is strengthened to (3$'$): for all $S \in
-  \mathcal{N}_w$, $w \in S$ if and only if $S \in \mathcal{K}'_w$.  We defer
-  the reader to {\cite{hansen_bisimulation_2007,pauly_bisimulation_1999}} for
-  details regarding bisimulation in neighborhood semantics.  Define
-  $\mathbbm{M}' \assign \langle W', V', \mathcal{K}', \mathcal{N}',
-  \mathcal{A}' \rangle$ such that:
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$ wher.  $l, r$ its associated canonical
-    injections and $\theta (v_l) \assign \theta (v_r) \assign v$ is a
-    left-inverse of $l, r$
-
-    \item $V' (p) \assign \{v_l, v_r \  | \  v \in V
-    (p)\}$
-
-    \item $\mathcal{K}' (v_i) \assign \{S \  | \  v_i \in
-    S \  \& \  \theta [S] \in \mathcal{K_v} \}$ where $i =
-    l, r$
-
-    \item $\mathcal{N}' (v_i) \assign \mathcal{K}' (v_i) \cup \{S \ 
-    | \  v_i \nin S \  \& \  \theta [S] \in
-    \mathcal{N_v} \}$ where $i = l, r$
-
-    \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
-    (v)$
-  \end{itemizedot}
-
-  If we let $Z \assign \{(v, v_r), (v, v_l) \  | \  v \in
-  W\}$, it is straightforward to verify that $Z$ is a neighborhood
-  bisimulation.  Hence $\mathbbm{M}, w_l \nvDash \psi$.  Along with (3$'$),
-  this model makes true (1), (2), (4).  In fact, in light of ($3'$), we can
-  see that this model does not need $\mathcal{K}'$, and conforms to the
-  semantics in Definition \ref{neighborhoodmodels}.{\hspace*{\fill}}
-
-  As in previous proofs, let $\Lambda$ be the proposition letters occuring in
-  $\psi$ and define an injection $\iota : W' \hookrightarrow \Phi \backslash
-  \Lambda$, assigning a nominal to every world in $\mathbbm{M}'$.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', \mathcal{N}'', \mathcal{A}''
-  \rangle$ such that:
-
-  \begin{center}
-    \begin{tabular}{lllll}
-      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
-      \begin{array}{ll}
-        V' (p) & p \in \Lambda\\
-        \{v\} & p = i (v)\\
-        \varnothing & o / w
-      \end{array} \right.$\\
-      $\bullet$ & $\mathcal{N}''_w \assign \mathcal{N}'_w$ & {\hspace{3em}} &
-      $\bullet$ & $\mathcal{A}''_v \assign \{\partial_v S \  |
-      \  S \in \mathcal{N}'_w \}$
-    \end{tabular}
-  \end{center}
-
-  Where $\partial_v S \assign \{\phi \  | \  \phi \in
-  \bigcup \mathcal{A}_v', \text{$\phi$ is a subformula of $\psi$ and}
-  \  S \subseteq \left\llbracket \phi
-  \right\rrbracket^{\mathbbm{M}'} \} \cup \{\neg \iota (u) \  |
-  \  u \nin S\}$.
-
-  As before, this model agrees with $\mathbbm{M}'$ on all subformulae of
-  $\psi$, using the semantics in Definition \ref{neighborhoodmodels}, hence
-  $\mathbbm{M}'', w_l \nvDash \phi$. \
-
-  All that is left is to show \tmtextbf{NCSQ} and \tmtextbf{NSND} from three
-  new properties:
-  \begin{enumerateroman}
-    \item For all words $v$ and all $X \in \mathcal{A}_v''$, $X$ is finite and
-  .  $X = \partial_v S$ for some $S \in \mathcal{N}_v''$
-
-    \item For all $v$ and all $S \in \mathcal{N}_v$, $u \in S$ if and only if
-    $\mathbbm{M}'', u \vDash \bigwedge \partial_v S$
-
-    \item The logic presented in Table \ref{logic3} is sound for
-    $\mathbbm{M}''$
-  \end{enumerateroman}
-  Along with the deduction theorem for $\vdash$, these properties establish
-  \tmtextbf{NCSQ} for this model using the logic of Table \ref{logic3} itself:
-
-  \begin{align*}
-    \text{$\exists X \in \mathcal{A''_v} \text{ s.t. } \tmop{Th}
-    (\mathbbm{M}'') \cup X \vdash \phi$} & {\Longleftrightarrow}\text{$\exists
-    S \in \mathcal{N''_v} \text{ s.t. } \tmop{Th} (\mathbbm{M}'') \cup
-    \partial_v S \vdash \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \tmop{Th} (\mathbbm{M}'') \vdash \bigwedge \partial_v S \rightarrow
-    \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \bigwedge \partial_v S \rightarrow \phi \in \tmop{Th} (\mathbbm{M}'')$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \left\llbracket \bigwedge \partial_v S \right\rrbracket \subseteq
-    \left\llbracket \phi \right\rrbracket$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t.
-    $\forall u \in W$ if } \mathbbm{M}, u \vDash \bigwedge \partial_v S \text{
-    then } \mathbbm{M}, u \vDash \phi$}\\
-    & {\Longleftrightarrow}\text{$\exists S \in \mathcal{N''_v} \text{ s.t. }
-    \mathbbm{M}, u \vDash \phi \text{ for all } u \in S$}\\
-    & {\Longleftrightarrow}{\mathbbm{M}},v{\vDash}\Box{\phi}
-  \end{align*}
-
-  \tmtextbf{NSND} follows from \tmtextbf{NCSQ} and the semantics of Definition
-  \ref{neighborhoodmodels}.
-\end{proof}
+\input{completeness5.tex}
 

### 2011-01-23 awareness.tex
Lots of reorganizing the intro

@@
 originally presented in {\cite{fagin_belief_1988}}, with an additional axiom.
- One difference in our presentation is the inclusion of a novel letter and a
-superficial change in notation.  This work is inspired by the developments in
+%  One difference in our presentation is the inclusion of a novel letter and a
+% superficial change in notation. 
+ This work was inspired by the developments in
 van Benthem and Vel\'azquez-Quesada {\cite{benthem_inference_2009}}.
@@
 
-Intuitively, the \tmtextbf{CSQ} asserts that an agent believes a formula
-$\phi$ if and only if it follows logically from their knowledge base and their
-background knowledge, represented by $\tmop{Th} (\mathbbm{M})$. 
-\tmtextbf{CSQ} is Vincent Hendrik's principle of logical omniscience mentioned
-in {\S}\ref{intro}.
-
-\tmtextbf{SND} asserts that $\circlearrowleft$ corresponds to the agent's
-knowledge base being sound. A sound knowledge base will only render true
-conclusions when used in deductions.  If one considers ``the existence of a
-sound deduction'' sufficient for a kind of knowledge, then $\circlearrowleft$
-is suitable for investigating this notion of epistemology.  That is, if
-$\mathbbm{M}, w \vDash \circlearrowleft \wedge \Box \phi$, then we may
-naturally say that the agent (implicitly) {\tmem{knows}} $\phi$ on the basis
-of $\mathcal{A}_w$, rather than merely {\tmem{believing}} $\phi$ on the basis
-of $\mathcal{A}_w$.
-
 The logic of models making true \tmtextbf{CSQ} and \tmtextbf{SND} is provided

### 2011-01-23 awareness0.tex
Lots of reorganizing the intro

--- 2011-01-23 awareness.tex
@@
-In this section, we give the explicit semantics to basic awareness logic,
-originally presented in {\cite{fagin_belief_1988}}, with an additional axiom.
-%  One difference in our presentation is the inclusion of a novel letter and a
-% superficial change in notation. 
- This work was inspired by the developments in
-van Benthem and Vel\'azquez-Quesada {\cite{benthem_inference_2009}}.
+In this section, apply basic awareness logic to Russell's
+epistemology.  As we described in \S\ref{mod-russell}, we will use
+awareness to model \emph{acquaintance}, and modality to model \emph{knowledge by description}.
 
@@
   (\Phi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A : \phi \hspace{1em}
+  \[ \phi \  : : = \  p \in \Phi \  |
+     \  \circlearrowleft \  | \  \bot
+     \  | \  \phi \rightarrow \psi \  |
+     \  \Box \phi \  | \  A : \phi \ 
   \]
@@
 \begin{definition}
-  \label{awarenessmodels}An {\tmstrong{awareness model}} $\mathbbm{M}= \langle
+  \label{awarenessmodels0}An {\tmstrong{awareness model}} $\mathbbm{M}= \langle
   W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V : \Phi
@@
 
-  Define the semantic entailment relation $\vDash$ where atomic propositions,
-  logical connectives and modality are interpreted as usual.  We employ the
-  following novel definition:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \mathcal{A_w}
-  \end{eqnarray*}
+  Define the semantic entailment relation $\vDash$ according to
+  \textbf{awareness logic} as defined in \cite{fagin_belief_1988},
+  where $A : \phi$ denotes awareness of $\phi$. 
+% where atomic propositions,
+%   logical connectives and modality are interpreted as usual.  We employ the
+%   following novel definition:
+%   \begin{eqnarray*}
+%     \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \mathcal{A_w}
+%   \end{eqnarray*}
 \end{definition}
 
-The following definition distinguishes us from previously investigations of
-awareness logic:
+Define the following property, as sketched in \S\ref{mod-russell}:
 
 \begin{definition}
-  Define the ``\tmtextbf{theory of a model} $\mathbbm{M}$'' as:
-  \[ \tmop{Th} (\mathbbm{M}) \assign \{\phi \hspace{1em} | \hspace{1em}
-     \mathbbm{M}, v \vDash \phi \text{ for all } v \in W\} \]
-  We define the following properties that a model $\mathbbm{M}$ may posses:
-
   \begin{descriptiondash}
-    \item[CSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff } \tmop{Th}
+    \item[CSQ$_\vdash$] $\mathbbm{M}, w \vDash \Box \phi \text{ iff } \tmop{Th}
     (\mathbbm{M}) \cup \mathcal{A}_w \vdash \phi$
-
-    \item[SND] $\mathbbm{M}, w \vDash \circlearrowleft \text{ iff }
-    \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w$
+    % \item[SND] $\mathbbm{M}, w \vDash \circlearrowleft \text{ iff }
+    % \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w$
   \end{descriptiondash}
@@
 
-Neither \tmtextbf{CSQ} nor \tmtextbf{SND} correspond to simple modally
-definable properties.
+% Neither \tmtextbf{CSQ} nor \tmtextbf{SND} correspond to simple modally
+% definable properties.
 
-The logic of models making true \tmtextbf{CSQ} and \tmtextbf{SND} is provided
-in Table \ref{logic1}.
+The logic of models making true \tmtextbf{CSQ} % and \tmtextbf{SND} 
+is provided in Table \ref{logic0}.
 
@@
   \end{tabular}
-  \caption{\label{logic1}Awareness Logic for \tmtextbf{CSQ} and
-  \tmtextbf{SND}}
+  \caption{\label{logic0}Awareness Logic for Acquaintance and
+    Knowledge by Description}
 \end{table}
@@
 \begin{theorem}
-  \label{completeness1}Assuming an infinite store of proposition letters
+  \label{completeness0}Assuming an infinite store of proposition letters
   $\Phi$, the awareness logic presented is sound and weakly complete for

### 2011-01-23 foundationalism.tex
Lots of reorganizing the intro

\subsection{Russell's Theory of Knowledge}\label{Russell}

In this section we review Russell's epistemology, propose a reading of
Russell in
terms of modern epistemic logic, and review Hintikka's dismissal of a similar reading.

Russell's theory of knowledge is presented in Chapter XIII, entitled
\emph{Knowledge, Error, and Probable Opinion} \cite[pg. 52]{russell_problems_1936}:
\begin{quote}
We may now take a survey of the sources of our knowledge, as they have
appeared in the course of our analysis. We have first to distinguish knowledge
of things and knowledge of truths. In each there are two kinds, one immediate
and one derivative. Our immediate knowledge of things, which we called
\emph{acquaintance}, consists of two sorts, according as the things known are
particulars or universals. Among particulars, we have acquaintance with
sense-data and (probably) with ourselves.%  Among universals, there seems to
% be no principle by which we can decide which can be known by acquaintance,
% but it is clear that among those that can be so known are sensible qualities,
% relations of space and time, similarity, and certain abstract
% logical universals.
\ldots Our derivative knowledge of things, which we call knowledge by \emph{description},
always involves both acquaintance with something and knowledge of truths.
Our immediate knowledge of truths may be called \emph{intuitive} knowledge, and the
truths so known may be called \emph{self-evident} truths. Among such truths are
included those which merely state what is given in sense, and also certain
abstract logical and arithmetical principles, and (though with less certainty)
some ethical propositions. Our derivative knowledge of truths consists of
everything that we can deduce from self-evident truths by the use of self-
evident principles of deduction.
\end{quote}

  In this essay, we will focus on modeling Russell's ``knowledge of things'',
  although implicit knowledge in particular will play an important
  role.

  Russell epistemology equates naturally to the modern concepts in
  epistemic logic. 
  \emph{Acquaintance} can be seen as explicit knowledge, while
  \emph{knowledge by description} can be seen as implicit knowledge.
  In particular, knowledge by description is the logical closure of
  acquaintance and \emph{intuitive} knowledge.

Historically, Hintikka briefly entertains a similar reading of
epistemic logic in \emph{Knowledge and Belief}
\cite{hintikka_knowledge_1969}[pgs. 38--39].  He proposes that ``$K_a
p$" might be read as ``It follows from what $a$ knows that $p$.''
Hintikka then rejects this reading on the grounds that it appeals to
some given standard of logical consequence.  He asserts that this is
``diametrically opposed'' to his research program in epistemic logic,
which is intended to ascribe a definition of logical consequence in
terms of the semantics he invents.

Hintikka is too dismissive of the foundationalist reading
of epistemic logic.  While unintuitive from a semantic
standpoint, it is possible to enforce a reading of knowledge in terms
of logical consequence. In the next section we sketch how this may be
accomplished, by employing awareness
logic and following Russell's formulation of knowledge by description.

% % The modern tradition in epistemic logic is to assume knowledge modalities
% % conform to the $S 5$ axiom schema.  As noted in
% % {\cite{halpern_set-theoretic_1999,rubinstein_modeling_1998}}, the semantics of
% % $S 5$ knowledge correspond exactly to partitioning a collection of situations
% % into \tmtextit{information sets}, which is the traditional approach in game
% % theory and decision theory.  While it is not commonly acknowledged in
% % epistemic logic, economists and philosophers accept that traditional decision
% % theory is externalist and behaviorist in nature
% % \footnote{An early essay by
% % Amartya Sen on the philosophical foundations of traditional decision theory
% % makes the behaviorist reading of decision theory clear
% % \cite{sen_behaviour_1973}.  Kaushik Basu also discusses the behaviorist
% % nature of decision theory {\cite[pgs. 53--54]{basu_revealed_1980}}. 
% % Finally, Donald Davidson appeals to decision theory to motivate an externalist
% % epistemology in \cite{davidson_could_1995}.}.

% \subsection{Parallels in Epistemic Logic}

% Russell's theory of \emph{deductive} and \emph{intuitive}
% knowledge is paralleled by modern research into implicit and explicit
% belief. Levesque introduced these terms in his 1984 paper \emph{A Logic of Implicit and Explicit Belief}
% \cite{levesque_logic_1984}.

% \todo{Find quote by Levesque which exposes his reinvention of Russell}

% In 1991 Johan van Benthem proposed a research program to find logics
% for explicit knowledge {\cite{benthem_reflections_1991}}.  Subsequently,
% Sergei Artemov and Elena Nogina have proposed a logic of explicit justification,
% which has come to be known as \tmtextit{Justification Logic} (JL)
% {\cite{artemov_introducing_2005}}, based on Artemov's \tmtextit{Logic of
% Proofs} {\cite{artemov_logic_1994}}.  While the original semantics of
% JL were based on interpretability into Peano Arithmetic, Melvin Fitting proposed Kripke
% semantics for JL in {\cite{fitting_logic_2005}}.  One may understand
% JL as extend awareness logic with operations for combining and
% composing awareness sets, although we note that this was \emph{not}
% the intended interpretation of the original logic of proofs.  In
% \cite{velazquez-quesada_inference_2009}, Fernando Vel\'azquez
% develops a logic similar to JL, using update operations make changes
% to models corresponding to changes in knowledge, based on ordinary
% awareness logic.  Unfortunately,
% Vel\'azquez' logic has a severe grammar restriction on the formula
% permissible for awareness, making it unattractive. 
% In {\cite{benthem_inference_2009}},
% Vel\'azquez-Quesada and van Benthem simplified Vel\'azquez-Quesada's
% framework so that the grammar restriction is relaxed.  Unlike the other efforts, this
% logic is more abstract and does not attempt to semantically model
% deduction; there is in fact no relationship between explicit and
% implicit in this logic at all.

% The purpose of this essay is to propose novel awareness logics which
% connect the research program surrounding explicit knowledge to
% traditional foundationalism.

\subsection{Modeling Russell Using Awareness Logic}

In this section we introduce models of Russell's epistemology.  We
will make use of \emph{awareness models} $\mathbb{M}$, using semantics originally developed in \cite{fagin_belief_198}.

As we discussed in \S\ref{Russell}, \emph{Acquaintance with $\phi$} is
naturally interpreted as denoted as \emph{explicit awareness of
  $\phi$}.  We will denote this as $A:\phi$, with the usual
semantics of $\mathbb{M},w \models A:\phi \iff \phi \in \mathcal{A}_w$
where $\mathcal{A}_w$ is an awareness set.

Modeling descriptive knowledge is not as straightforward.  We will model
\emph{knowledge by description that $\phi$} as \emph{implicit knowledge
  that $\phi$}, denoted $\Box\phi$.  However, it is necessary to introduce
further constraints.
Minimally, we want to enforce that $\mathbb{M} \models A : \phi \to \Box \phi$ and
$\mathbb{M} \models \Box \phi \to \phi$, reflecting that knowledge by
description extends acquaintance and that knowledge is necessarily
\emph{true}.

All that is left is to establish a connection between knowledge by
description and logical
consequence.  Let $\vdash$ be any Hilbert-style calculus,
that is a sequent that takes a set of premises $\Gamma$ on the left and yields a
single conclusion $\phi$ on the right. Define the following terminology:
\begin{itemizedot}
\item $\vdash$ is \emph{relatively sound} for $\mathbb{M}$ if and only if
  when $\Gamma \vdash \phi$, then if $\mathbb{M},w\models \Gamma$ then
  $\mathbb{M},w \models \phi$.
\item $\vdash$ is \emph{reflexive} if and only if whenever $\phi \in
  \Gamma$ then $\Gamma \vdash \phi$
\item $\vdash$ makes true \emph{modus ponens} if and only if whenever
  $\Gamma \vdash \phi \to \psi$ and $\Gamma \vdash \phi$, then $\Gamma
  \vdash \psi$
\end{itemizedot}

A model $\mathbb{M}$ is thought to be suitable for Russell's epistemology just in
case there is some relatively sound,
reflexive Hilbert-style calculus making true modus ponens, such that for all
worlds $w$:

\[ \mathbb{M}, w \models \Box \phi \textup{ if and only if } Th(\mathbb{M}) \cup
\mathcal{A}_w \vdash \phi \]

Here $Th(\mathbb{M})$ is the \emph{theory of $\mathbb{M}$}, and
denotes the set $\{ \phi\ |\ \mathbb{M},w \models \phi$ for all worlds
$w \}$.  We take it to represent Russell's \emph{intuitive knowledge}
in our modeling\emph{knowledge by description}\footnote{A caveat: we are being very liberal with our interpretation
  of Russell's
  epistemology here.  The set $Th(\mathbb{M})$ contains, among other
  things, all tautologies for any logic $\mathbb{M}$ obeys.  Russell
  intended for intuitive knowledge to correspond to empirical
  knowledge and a small number of a priori truths, which serve as
  an axiom system for derivations.  We defend choice to call $Th(\mathbb{M})$ intuitive
  knowledge, since (1) it may be considered as a sort of a priori knowledge, (2) it fits the definition of knowledge by description well,
  and (3) it provides a framework for our subsequent formal results.}.

The property we suggest is \emph{not} definitional of modality.  Rather, it is a
feature that an awareness model might or might not make.  Restricting
oneself to models with the above property is
similar to restricting models to the class which has reflexive
relations.

Restricting our attention to models where implicit knowledge is
equated to the presence
of a derivation is a faithful to Russell's epistemology.  Our response
to Hintikka's criticism of this is that while epistemic logic may be
based on models, it could also be based on particular, special models
which have an associated logic suited to them.  Assuming that
knowledge in epistemic logic corresponds to \emph{some} notion of logical consequence
does not rely on the notion of logical consequence in epistemic
itself.  While logic about logic is circular, it is not
\emph{viciously} so.

The rest of this essay is devoted to developing awareness logics which have
the mechanics we have sketched here.

% In this essay we repurpose various externalist logics to take on an
% internalist reading.  The concept of a \tmtextit{knowledge base}, from which
% beliefs may be implicitly deduced, will play a crucial role in our discussion.
%  We propose this as an avenue for representing foundationalist perspectives
% on epistemology in epistemic logic.  Our philosophical motivation is taken
% from two sources.  The first is Vincent Hendricks in
% {\cite{hendricks_mainstream_2006}}, where he characterizes the principal of
% {\tmem{logical omniscience}} for implicit knowledge in epistemic
% logic{\footnote{We have modified Hendricks' notation here slightly to match
% our own.}}:

% \begin{quote}
%   {\tmem{Whenever an agent $X$ knows all of the formulae in $\mathcal{A}$,
%   and $\phi$ follows logically from $\mathcal{A}$, then $\Xi$ [implicitly]
%   knows $\phi$.}}
% \end{quote}

% We will design our semantics such that ``$\Box \phi$'' may be equated with
% ``$\phi$ follows logically from a knowledge base $\mathcal{A}$,'' which is
% sometimes written as $\phi \in \tmop{Cn} ( \mathcal{A})$ in the artificial
% intelligence literature.  Our second inspiration comes from what   The
% rest of Kornblith's paper is devoted to attacking this view and proposing a
% form of naturalized epistemology; we will not address this debate here,
% however.

% We adopt a arguments-on-paper-thesis perspective on epistemic logic in this
% paper.  We consider a \tmtextit{good argument} to be a logical derivation
% from propositions present in a knowledge base in this setting.  
% Special attention will be given to \tmtextit{sound derivations}, which will be
% thought of as a form of knowledge.  In \emph{Awareness Logic}, we will interpret
% awareness of a formula as membership in a knowledge base.  We prove
% completeness for basic awareness logic and a hybrid logic extension.  Logics
% of multiple knowledge bases are also presented: a simplified form of
% Justification Logic, a logic with neighborhood semantics, an a logic with
% modalities for quantifying over knowledge bases.  We conclude with an
% application to naturalized epistemology found in the psychological
% literature.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

### 2011-01-23 introduction.tex
Fixed another broken citation
Lots of reorganizing the intro

@@
-The modern tradition in epistemic logic is to assume knowledge modalities
-conform to the $S 5$ axiom schema.  As noted in
-{\cite{halpern_set-theoretic_1999,rubinstein_modeling_1998}}, the semantics of
-$S 5$ knowledge correspond exactly to partitioning a collection of situations
-into \tmtextit{information sets}, which is the traditional approach in game
-theory and decision theory.  While it is not commonly acknowledged in
-epistemic logic, economists and philosophers accept that traditional decision
-theory is externalist and behaviorist in nature
-\footnote{An early essay by
-Amartya Sen on the philosophical foundations of traditional decision theory
-makes the behaviorist reading of decision theory clear
-\cite{sen_behaviour_1973}.  Kaushik Basu also discusses the behaviorist
-nature of decision theory {\cite[pgs. 53--54]{basu_revealed_1980}}. 
-Finally, Donald Davidson appeals to decision theory to motivate an externalist
-epistemology in \cite{davidson_could_1995}.}.
+Modern epistemic logic is commonly acknowledged to begin with
+Hintikka's \emph{Knowledge and Belief}
+\cite{hintikka_knowledge_1969}. While Hintikka was steeped in
+profound philosophical insights, the introduction of epistemic logic
+bifurcated 20th century research into epistemology.  A number of
+logicians and philosophers have acknowledged this rift, most notably
+Vincent Hendricks \cite{hendricks_wheres_2006,
+  hendricks_mainstream_2006}.
 
-In {\cite{benthem_reflections_1991}}, Johan van Benthem proposed
-a research program to find logics for explicit knowledge, providing the first
-suggestion of an internalist perspective on epistemic logic.  Subsequently,
-Sergei Artemov and Elena Nogina proposed a logic of explicit justification,
-which has come to be known as \tmtextit{Justification Logic} (JL)
-{\cite{artemov_introducing_2005}}, based on Artemov's \tmtextit{Logic of
-Proofs} {\cite{artemov_logic_1994}}.  While the original semantics of
-JL were based on interpretability into Peano Arithmetic, Melvin Fitting proposed Kripke
-semantics for JL in {\cite{fitting_logic_2005}}.  Recently, Fernando
-Vel\'azquez-Quesada and Johan van Benthem have developed a simpler framework
-for explicit epistemics in {\cite{benthem_inference_2009}}, entitled the
-\tmtextit{Dynamics of Awareness}.  This work was based on Joseph Halpern and
-Ronald Fagin's original \tmtextit{Awareness Logic} {\cite{fagin_belief_1987}}.
+The purposes of this essay is to try to close the gap between these
+traditions, by showing that awareness logics are suitable for
+reasoning about the form of foundationalism proposed
+by Bertrand Russell in \emph{The Problems of Philosophy}
+\cite{russell_problems_1936}.  We begin by reviewing Russell's
+theory, and contrasting it with modern perspectives.  In particular,
+we illustrate that the modern concepts of \emph{explicit} and
+\emph{implicit}, due to Levesque\footnote{While we will refer often to
+  the terms coined by Levesque in this essay, we will not use his
+  proposed semantics.  We will instead prefer variations on
+  \emph{awareness logic}, originally developed by Fagin and Halpern \cite{fagin_belief_1988}.}\cite{levesque_logic_1984}, knowledge in epistemic logic are reinventions of
+Russell's distinction between \emph{immediate} and \emph{derivative}
+knowledge.  We propose a novel property of awareness models which
+directly reflects Russell's foundationalist epistemology.  The
+remainder of this paper is then devoted to exploring how awareness
+logics can be designed to express our this foundationalist property.
 
-In this essay we repurpose various externalist logics to take on an
-internalist reading.  The concept of a \tmtextit{knowledge base}, from which
-beliefs may be implicitly deduced, will play a crucial role in our discussion.
-\ We propose this as an avenue for representing foundationalist perspectives
-on epistemology in epistemic logic.  Our philosophical motivation is taken
-from two sources.  The first is Vincent Hendricks in
-{\cite{hendricks_mainstream_2006}}, where he characterizes the principal of
-{\tmem{logical omniscience}} for implicit knowledge in epistemic
-logic{\footnote{We have modified Hendricks' notation here slightly to match
-our own.}}:
-
-\begin{quote}
-  {\tmem{Whenever an agent $\Xi$ knows all of the formulae in $\mathcal{A}$,
-  and $\phi$ follows logically from $\mathcal{A}$, then $\Xi$ [implicitly]
-  knows $\phi$.}}
-\end{quote}
-
-We will design our semantics such that ``$\Box \phi$'' may be equated with
-``$\phi$ follows logically from a knowledge base $\mathcal{A}$,'' which is
-sometimes written as $\phi \in \tmop{Cn} ( \mathcal{A})$ in the artificial
-intelligence literature.  Our second inspiration comes from what Hilary
-Kornblith calls the \tmtextit{the arguments on paper thesis}
-{\cite{kornblith_beyond_1980}}, which he feels characterizes apsychological,
-internalist theories of knowledge:
-
-\begin{quote}
-  Let us suppose that, for any person, it is possible, at least in principle,
-  to list all of the propositions that person believes.  The
-  arguments-on-paper thesis is just the view that a person has a justified
-  belief that a particular proposition is true just in case that proposition
-  appears on the list of propositions that person believes, and either it
-  requires no argument, or a {\tmem{good argument}} can be given for it which
-  takes as premises certain other propositions on the list.
-\end{quote}
-
-Kornblith asserts that foundationalism and coherentism vie for accounts of a
-``good argument'' in the above thesis.  He provides an extensive bibliography
-citing proposals for this principle by a number of 20th century
-epistemologists, including figures such as A.J. Ayer and C.I. Lewis.  The
-rest of Kornblith's paper is devoted to attacking this view and proposing a
-form of naturalized epistemology; we will not address this debate here,
-however.
-
-We adopt a arguments-on-paper-thesis perspective on epistemic logic in this
-paper.  We consider a \tmtextit{good argument} to be a logical derivation
-from propositions present in a knowledge base in this setting.  \
-Special attention will be given to \tmtextit{sound derivations}, which will be
-thought of as a form of knowledge.  In \emph{Awareness Logic}, we will interpret
-awareness of a formula as membership in a knowledge base.  We prove
-completeness for basic awareness logic and a hybrid logic extension.  Logics
-of multiple knowledge bases are also presented: a simplified form of
-Justification Logic, a logic with neighborhood semantics, an a logic with
-modalities for quantifying over knowledge bases.  We conclude with an
-application to naturalized epistemology found in the psychological
-literature.
 %%% Local Variables: 

### 2011-01-23 paper.tex
Lots of reorganizing the intro

@@
 
-\title{Epistemic Logics For Knowledge Bases}\author{Matthew P.
+\title{Awareness and Russell's Epistemology}\author{Matthew P.
 Wampler-Doty}\date{}\maketitle
@@
 \begin{abstract}
-  In {\cite{benthem_reflections_1991}}, Johan van Benthem
-  proposed a research program for logic of \tmtextit{explicit knowledge}. 
-  Two efforts have since emerged with proposals for logic of explicit
-  knowledge: the \tmtextit{Dynamics of Awareness}
-  {\cite{benthem_inference_2009}} and \tmtextit{Justification Logic}
-  {\cite{artemov_introducing_2005}}.  The purpose of this paper is to
-  repurpose various epistemic logics from these previous efforts for reasoning
-  about logical closures over knowledge bases.  The results in this paper are
-  based on previous work carried out in
-  {\cite{wampler-doty_evidentialist_2010}}.
+  In this essay, we show that awareness logic is suitable for
+  formal modeling of Bertrand Russell's theory of knowledge,
+  originally developed in \cite{russell_problems_1936}.  This is done
+  by introducing a novel property to the semantics of 
+  awareness logics. 
+  We present a variety of sound and complete awareness
+  logics compatible which exhibit this property.
 \end{abstract}
+\todo{This abstract isn't flowery enough.  Lookup PhD comics
+  ``Abstract madlibs'' and use that as a template.}
 
@@
 
-\section{Basic Explicit Logics of Knowledge Bases}
+\section{Philosophical Background}
+\label{trad}
+\input{foundationalism.tex}
 
-\subsection{Awareness Logic}
+\section{Basic Explicit Logics of Foundationalism}
+
+\subsection{Acquaintance and Knowledge By Description}
+\label{awarenesslogic0}
+\input{awareness0.tex}
+
+\subsection{Knowledge and Belief}
 \label{awarenesslogic}
@@
 
-\subsection{Hybrid Awareness Logic}
+\subsection{Hybrid Logic}
 \label{hybrid_awareness}
@@
 
-\section{Logics of Multiple Knowledge Bases}
+\section{Logics of Multiple Awareness Sets}
 
-So far, we have only dealt with systems that reason over a single knowledge
+So far, we have only dealt with systems for reasoning over a single knowledge
 base.  In this section, we present various logics for reasoning over multiple
@@
 
-\subsection{Lattice Justification Logic}
-\label{lattice_justification}
-\input{lattice_justification.tex}
+% \subsection{Lattice Justification Logic}
+% \label{lattice_justification}
+% \input{lattice_justification.tex}
 
@@
 
-\subsection{\label{quantifying}Using Modalities to Quantify over Knowledge
-Bases}
+\subsection{\label{quantifying}Multi-Modal Logic}
 \label{modal-modal}

### 2011-01-27 awareness0.tex
Added very simplified completeness proof

@@
   \label{awarenessmodels0}An {\tmstrong{awareness model}} $\mathbbm{M}= \langle
-  W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V : \Phi
-  \cup \{\circlearrowleft\} \rightarrow 2^W$ and an awareness function
-  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$.  We will usually
-  denote $\mathcal{A} (w)$ as $\mathcal{A}_w$.
+  W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V : \Phi \rightarrow 2^W$ and an awareness function
+  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$.  We will
+  usually denote $\mathcal{A} (w)$ as $\mathcal{A}_w$.
 
-  Define the semantic entailment relation $\vDash$ according to
+  Define the semantic entailment relation $\vDash$ according to the
+  usual formulation of
   \textbf{awareness logic} as defined in \cite{fagin_belief_1988},
@@
 
-\begin{definition}
+\begin{definition}\label{csq0}
   \begin{descriptiondash}
@@
 
-The logic of models making true \tmtextbf{CSQ} % and \tmtextbf{SND} 
-is provided in Table \ref{logic0}.
+% The logic of models making true \tmtextbf{CSQ} % and \tmtextbf{SND} 
+% is provided in Table \ref{logic0}.
 
 \begin{table}[h]
+\begin{centering}
   \begin{tabular}{l}
@@
     $\vdash A : \phi \rightarrow \Box \phi$\\
-    $\vdash \circlearrowleft \rightarrow \Box \phi \rightarrow \phi$\\
+    $\vdash \Box \phi \rightarrow \phi$\\
     \\
     \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box \phi}$
+      $\displaystyle \frac{\vdash \phi \rightarrow \psi \ \  \vdash \phi}{\vdash
+      \psi}$ & {\ \ } & $\displaystyle \frac{\vdash \phi}{\vdash \Box \phi}$
     \end{tabular}
@@
     Knowledge by Description}
+\end{centering}
 \end{table}
+
+\begin{notation}
+For all Hilbert-style calculi, let $\Gamma \vdash \phi$
+denote that there is some sequence
+$\gamma_0,\gamma_1,\ldots,\gamma_n\in\Gamma$ such that $\vdash
+\gamma_0 \to \gamma_1 \to \cdots \to \gamma_n \to \phi$
+\end{notation}
 
@@
   \label{completeness0}Assuming an infinite store of proposition letters
-  $\Phi$, the awareness logic presented is sound and weakly complete for
-  awareness models making true \tmtextbf{CSQ} and \tmtextbf{SND}.
+  $\Phi$, $\vdash$ is sound and weakly complete for
+  reflexive awareness models $\mathbb{M}$ making true
+  $\text{\tmtextbf{CSQ}}_{\vdash'}$, for some suitable $\vdash'$.
 \end{theorem}
 
-\input{completeness1.tex}
+\input{completeness0.tex}
 

### 2011-01-27 completeness0.tex
Added very simplified completeness proof

\begin{proof}
  Soundness is straightforward, so we will only address completeness.  Assume
  $\nvdash \psi$.  Consider the finite canonical model $\mathbbm{M}= \langle
  W, V, R, \mathcal{A} \rangle$ formed of maximally consistent sets of
  subformulae of $\psi$ (closed under single negations{\footnote{A discussion
  of this property may be found in {\cite[pg.
  243]{blackburn_modal_2001}}.}}), as per the finitary modal completeness
  proofs found in {\cite[chapter 4.8]{blackburn_modal_2001}} and
  {\cite[chapter 5]{boolos_logic_1995}}.  Typical presentations do not
  include awareness, however it is defined intuitively in this case:
  \[ \phi \in \mathcal{A}_w \Longleftrightarrow A : \phi \in w \]
  Since $\psi$ is a subformula of itself, we have $\mathbbm{M}, w \nvDash
  \psi$ for some world $w$ by finitary forms of the {\tmem{Lindenbaum Lemma}} and
  {\tmem{Truth Theorem}}.  Moreover, it is straightforward to verify that
  $\mathbbm{M}$ makes true the following properties:
  \begin{enumeratenumeric}
    \item $W$ and $\mathcal{A}_v$ are finite, and $\psi \in \mathcal{A}_v$
    only if $\psi$ is a (possibly negated) subformula of $\phi$
    \item \label{awareness0-prop2} if $\mathbbm{M}, v \vDash A : \psi$ then $\mathbbm{M}, v \vDash \Box
    \psi$ 
    \item $v R v$ for all worlds $v$
  \end{enumeratenumeric}

  % We next produce a bisimular{\footnote{The notion of bisimulation is
  % discussed at length in {\cite[chapter 2.2]{blackburn_modal_2001}}.  We
  % note that the basic definition and all of the usual theorems (modal
  % equivalence, Henessy-Milner, etc.) may be generalized to awareness models in
  % a straightforward fashion. }} model $\mathbbm{M}'$ which makes true (1), (2)
  % and a stronger from of (3):

  % {\hspace*{\fill}}\begin{tabular}{ll}
  %   \tmtextbf{3$'$.} & $\mathbbm{M}', v \vDash \circlearrowleft \iff v R v$
  % \end{tabular}{\hspace*{\fill}}

  % To this end define $\mathbbm{M}' \assign \langle W', V', R', \mathcal{A}'
  % \rangle$ such that{\footnote{Throughout this article, we use $l$ and $r$ to
  % denote the two canonical injections associated with the coproduct $W \uplus
  % W$. We will use $v_l$ and $v_r$ as the shorthand for $l (v)$ and $r (v)$
  % respectively.}}: {\hspace*{\fill}}
  % \begin{itemizedot}
  %   \item $W' \assign W \uplus W$

  %   \item $V' (p) \assign \{v_l, v_r \  | \  v \in V
  %   (p)\}$

  %   \item $R' \assign \{(v_l, u_r), (v_r, u_l) \  | \  v R
  %   u\} \cup \{(v_l, v_l), (v_r, v_r) \  | \  \mathbbm{M},
  %   v \vDash \circlearrowleft\}$

  %   \item $\mathcal{A}' (v_l) \assign \mathcal{A}' (v_r) \assign \mathcal{A}
  %   (v)$
  % \end{itemizedot}

  % It is straightforward to verify that $\mathbbm{M}'$ makes true the desired
  % properties.  Let $Z \assign \{(v, v_l), (v, v_r) \  |
  % \  v \in W\}$.  then $Z$ is a bisimulation between $\mathbbm{M}$
  % and $\mathbbm{M}'$.  Therefore we know there is some $w \in W$ such that
  % $\mathbbm{M}', w_l \nvDash \psi$ and $\mathbbm{M}', w_r \nvDash \psi$.

  We next construct a model $\mathbbm{M}'$ which agrees with
  $\mathbbm{M}$ for all subformulae of $\psi$, but which also makes true
  \tmtextbf{CSQ}.  Let $\Lambda$ be the set of proposition
  letters occurring in $\psi$.  We will make use members of $\Phi \backslash
  \Lambda$ as {\tmem{nominals}}, as per the tradition in hybrid logic.  This
  is possible since both $W$ and $\Lambda$ are finite and $\Phi$ is infinite
  by hypothesis.  Let $\iota : W \uplus W \hookrightarrow \Phi \backslash
  \Lambda$ be an injection assigning a fresh nominal associated with each
  world in $W$.  Now define $\mathbbm{M}' \assign \langle W',
  V', R', \mathcal{A}' \rangle$, where:

  \begin{center}
    \begin{tabular}{lllll}
      $\bullet$ & $W' \assign W$ &  & $\bullet$ & $V' (p) \assign \left\{
      \begin{array}{ll}
        V (p) & p \in \Lambda\\
        \{v\} & p = \iota (v)\\
        \varnothing & o / w
      \end{array} \right.$\\
      $\bullet$ & $R' \assign R$ & {\hspace{3em}} & $\bullet$ &
      $\mathcal{A}'_v \assign \{\phi \  | \phi \in \mathcal{A}_v
      \} \cup \{\neg \iota (u) \  | \  \neg v R' u\}$
    \end{tabular}
  \end{center}

  By induction we have that for every subformula $\phi$ of $\psi$ that
  $\mathbbm{M}, v \vDash \phi$ if and only if $\mathbbm{M}', v \vDash \phi$,
  hence $\mathbbm{M}', w \nvDash \psi$.

  All that is left to show is that $\mathbbm{M}'$ is reflexive and
  makes true $\text{\tmtextbf{CSQ}}_{\vdash'}$ for some suitable logic $\vdash'$.  Since $\mathbb{M}$ was reflexive, $W' =
  W$ and $R' = R$, we know that $\mathbb{M}'$ is reflexive too.  We
  also have the following, additional properties:
  \begin{enumerateroman}
    \item \label{awareness0-one} $\mathcal{A}'_v$ is finite for all worlds $v$
    \item \label{awareness0-two} $\vdash$, the logic presented in Table \ref{logic0}, is
      relatively sound for $\mathbbm{M}'$
    \item\label{awareness0-three}  $v R' u$ if and only if $\mathbbm{M}', u \vDash \bigwedge
    \mathcal{A}'_v$
  \end{enumerateroman}

   We only prove \eqref{awareness0-three}.

  \begin{descriptiondash}
   \item[Left to Right]  Assume $v R' u$. We must show that if
   $\phi \in \mathcal{A}'_v$ then $\mathbb{M}', u \models \phi$.  If
   $\phi \in \mathcal{A}'_v$, either (a) $\phi \in \mathcal{A}_v$ or
   (b) $\phi = \neg \iota(x)$ for some world $x$ where $\neg v R x$. Note
   that by definition, $v R' u$ is equivalent to $v R u$.  So in the
   case of (a) we know have by property \eqref{awareness0-prop2} of
   our canonical model construction that $\mathbb{M}, u \models \phi$.
   Moreover, since $\phi$ is a subformula of $\psi$, we have that
   $\mathbb{M},u \models \phi \iff \mathbb{M}',u \models \phi$, which
   gives the desired result.  In the case of (b),
   suppose that $\mathbb{M},u \nmodels \phi$, then $\mathbb{M}',u
   \models \iota(x)$ for some $x$ such that $\neg v R' x$.  However,
   since $\iota$ is an injection, then by construction $\mathbb{M}',u
   \models \iota(x)$ if and only if $u = x$.  Hence $\neg v R' u$ after
   all, a contradiction.

   \item[Right to Left] It suffices to establish the contrapositive.  Assume $\neg v R' u$,
   we must find some formula $\phi \in \mathcal{A}'_v$ such that
   $\mathbb{M}, u \nmodels \phi$.  Evidently $\phi = \iota(u)$ suffices.
 \end{descriptiondash}

  We may now demonstrate $\textup{\tmtextbf{CSQ}}_{\vdash'}$ for some
  sound logic $\vdash'$.  Let $\vdash'$ be the logic presented in
  Table \ref{logic0}.  From \eqref{awareness0-one}, \eqref{awareness0-two}, \eqref{awareness0-three},
  and the \tmtextit{deduction theorem} for modal logic, we have the following
  line of reasoning:

  \begin{align*}
    Th({\mathbbm{M}}'){\cup}\mathcal{A}'_v{\vdash}{\phi}\ &
    {\Longleftrightarrow}\ Th({\mathbbm{M}}'){\vdash}\bigwedge\mathcal{A}'_v{\rightarrow}{\phi}\\
    &
    {\Longleftrightarrow}\ \bigwedge\mathcal{A}'_v{\rightarrow}{\phi}{\in}Th({\mathbbm{M}}')\\
    &
    {\Longleftrightarrow}\ {\mathbbm{M}}',u{\vDash}\bigwedge\mathcal{A}'_v{\rightarrow}{\phi}\text{
    for all $u \in W'$}\\
    & {\Longleftrightarrow}\ \text{for all $u \in W'$, if
    }{\mathbbm{M}}',u{\vDash}\bigwedge\mathcal{A}'_v\text{ then
    }{\mathbbm{M}}',u{\vDash}{\phi}\\
    & {\Longleftrightarrow}\ \text{for all $u \in W'$, if }v R 'u \text{ then
    }{\mathbbm{M}}',u{\vDash}{\phi}\\
    & {\Longleftrightarrow}\ {\mathbbm{M}}',v{\models}\Box{\phi}
  \end{align*}
\end{proof}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

### 2011-01-27 awareness.tex
threw away completeness proof in favor of a more economical remark

@@
-In this section, we give the explicit semantics to basic awareness logic,
-originally presented in {\cite{fagin_belief_1988}}, with an additional axiom.
-%  One difference in our presentation is the inclusion of a novel letter and a
-% superficial change in notation. 
- This work was inspired by the developments in
-van Benthem and Vel\'azquez-Quesada {\cite{benthem_inference_2009}}.
+In this section, we modify the framework we have previously given so that both
+knowledge and belief may be modeled.  Russell provides some intuition
+about what distinguishes knowledge from belief\cite[pg. 63]{russell_problems_1936}:
+\begin{quote}
+But are we to say that nothing is knowledge except what is validly deduced
+from true premisses? Obviously we cannot say this. Such a definition is at
+once too wide and too narrow. In the first place, it is too wide, because it is
+not enough that our premisses should be \emph{true}, they must also be
+known.
+\end{quote}
+Russell may be interpreted as taking immediate knowledge to be
+\emph{primitive} in the above passage.  To this end, we propose a new
+symbol: $\PP$, which is a kind of letter.  We will interpret it to mean ``All of propositions
+the agent is explicitly aware of are articles of knowledge.'' Unless $\PP$ is
+true, the agent can only be said to possess logical belief.
+
+It may be that everything the agent is explicitly aware of is accidentally true,
+and therefore all of her beliefs derivative beliefs are true.
+However, in this case we take it that the agent has a form of
+\emph{right opinion}.
+
+As before, we make the minimal assumption that knowledge is \emph{true}.
 
 \begin{definition}
-  Let $\Phi$ be a set of letters and define the language $\mathcal{L}_A
-  (\Phi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} \circlearrowleft \hspace{1em} | \hspace{1em} \bot
-     \hspace{1em} | \hspace{1em} \phi \rightarrow \psi \hspace{1em} |
-     \hspace{1em} \Box \phi \hspace{1em} | \hspace{1em} A : \phi \hspace{1em}
+   $\mathcal{L}_\PP
+  (\Phi)$ extends $\mathcal{L}_A(\Phi)$ as follows:
+  \[ \phi \  : : = \  p \in \Phi \  | \  \bot
+     \  | \  \phi \rightarrow \psi \  |
+     \  \Box \phi \  | \  A : \phi \ |\ \circlearrowleft 
   \]
@@
 
-We define the other connectives and modal operators as usual for classical
-modal logics.
-
 \begin{definition}
-  \label{awarenessmodels}An {\tmstrong{awareness model}} $\mathbbm{M}= \langle
+  \label{awarenessmodels}A {\tmstrong{$\PP$-awareness model}} $\mathbbm{M}= \langle
   W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V : \Phi
-  \cup \{\circlearrowleft\} \rightarrow 2^W$ and an awareness function
-  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$.  We will usually
-  denote $\mathcal{A} (w)$ as $\mathcal{A}_w$.
-
-  Define the semantic entailment relation $\vDash$ where atomic propositions,
-  logical connectives and modality are interpreted as usual.  We employ the
-  following novel definition:
-  \begin{eqnarray*}
-    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \mathcal{A_w}
-  \end{eqnarray*}
+  \cup \{\circlearrowleft\} \rightarrow 2^W$, which is otherwise the
+  same as an ordinary awareness model.  The semantics are unmodified,
+  except that $\mathbb{M},w \models \PP \iff w \in V(\PP)$.
 \end{definition}
 
-The following definition distinguishes us from previously investigations of
-awareness logic:
+Aside from \textbf{CSQ$_\vdash$}, we will be concerned with the
+following new property
 
-\begin{definition}
-  Define the ``\tmtextbf{theory of a model} $\mathbbm{M}$'' as:
-  \[ \tmop{Th} (\mathbbm{M}) \assign \{\phi \hspace{1em} | \hspace{1em}
-     \mathbbm{M}, v \vDash \phi \text{ for all } v \in W\} \]
-  We define the following properties that a model $\mathbbm{M}$ may posses:
-
+\begin{definition}\label{snd1}
   \begin{descriptiondash}
-    \item[CSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w \vdash \phi$
-
-    \item[SND] $\mathbbm{M}, w \vDash \circlearrowleft \text{ iff }
+    \item[SND] If $\mathbbm{M}, w \vDash \circlearrowleft \text{ then }
     \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w$
   \end{descriptiondash}
-
-  Here $\vdash$ is any logical consequence relation which is sound for
-  $\vDash$, making true \tmtextbf{modus ponens} and \tmtextbf{reflection} (ie,
-  $\Gamma \vdash \phi$ if $\phi \in \Gamma$)
 \end{definition}
 
-Neither \tmtextbf{CSQ} nor \tmtextbf{SND} correspond to simple modally
-definable properties.
-
-The logic of models making true \tmtextbf{CSQ} and \tmtextbf{SND} is provided
-in Table \ref{logic1}.
+The logic for \textbf{CSQ$_\vdash$} and \textbf{SND} differs from the
+logic given in \S\ref{awarenesslogic0} by a single axiom:
 
 \begin{table}[h]
+\begin{centering}
   \begin{tabular}{l}
@@
     $\vdash A : \phi \rightarrow \Box \phi$\\
-    $\vdash \circlearrowleft \rightarrow \Box \phi \rightarrow \phi$\\
+    $\vdash \PP \to \Box \phi \rightarrow \phi$\\
     \\
     \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box \phi}$
+      $\displaystyle \frac{\vdash \phi \rightarrow \psi \ \  \vdash \phi}{\vdash
+      \psi}$ & {\ \ } & $\displaystyle \frac{\vdash \phi}{\vdash \Box \phi}$
     \end{tabular}
   \end{tabular}
-  \caption{\label{logic1}Awareness Logic for \tmtextbf{CSQ} and
-  \tmtextbf{SND}}
+  \caption{\label{logic1}Awareness Logic for For Knowledge And
+    Derivative Belief}
+\end{centering}
 \end{table}
@@
   $\Phi$, the awareness logic presented is sound and weakly complete for
-  awareness models making true \tmtextbf{CSQ} and \tmtextbf{SND}.
+  awareness models making true \tmtextbf{CSQ}$_{\vdash'}$ and
+  \tmtextbf{SND} for a suitable logic $\vdash'$.
 \end{theorem}
-
-\input{completeness1.tex}
+\begin{proof}
+The proof proceeds exactly as the proof of Theorem
+\ref{completeness0}; the only difference is that the canonical model
+and modified model make true \textbf{SND} instead of being reflexive.
+\end{proof}
 

### 2011-01-27 completeness2.tex
Caught an error, changed some language of the proof

@@
     \item $\sim_{\forall}$ is an equivalence relation    
-
     \item $R_{\Box} \subseteq \sim_{\forall}$
-
     \item In each equivalence class specified by $\sim_{\forall}$, there is at
@@
   As in our previous construction we have that there is some world $w$ where
-  $\mathbbm{M}, w \nvDash \psi$.  Let $\mathbbm{M}^1 = \langle W', V',
+  $\mathbbm{M}, w \nvDash \psi$.  Let $\mathbbm{M}' = \langle W', V',
   R_{\Box}', \sim_{\forall}', \mathcal{A}' \rangle$ be the submodel generated
@@
   \ell \rangle$, where:
-
   \begin{center}
@@
       $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign V' (p)$\\
-      $\bullet$ & $R'' \assign R'_{\Box}$ & {\hspace{3em}} & $\bullet$ &
+      $\bullet$ & $R'' \assign R'_{\Box}$ & \ \  & $\bullet$ &
       $\mathcal{A}'' (v) \assign \{\phi \  | \  \phi \in
@@
       \neg v R' u\}$\\
-      \begin{tabular}{ll}
-        $\bullet$ & $\ell (i) \assign \left\{ \begin{array}{ll}
+       $\bullet$ & \begin{tabular}{ll}
+       $\ell (i) \assign \left\{ \begin{array}{ll}
           w & i \in \Upsilon \  \& \  \mathbbm{M}, w
@@
         \end{array} \right.$
-      \end{tabular} & $R'' \assign R'_{\Box}$ &  &  & 
+      \end{tabular} &  & $\bullet$ &  $R'' \assign R'_{\Box}$ 
     \end{tabular}
@@
   The the worlds is $\mathbbm{M}'$ and $\mathbbm{M}''$ agree on all
-  subformulae of $\psi$, hence $\mathbbm{M}'', w \nvDash \psi$. The same
-  reasoning as in the proof of Theorem \ref{completeness1} establishes and
-  that the logic in Table \ref{logic2} itself is sound for $\mathbbm{M}''$ and
-  makes true \tmtextbf{CSQ}, establishing completeness.
+  subformulae of $\psi$, hence $\mathbbm{M}'', w \nvDash
+  \psi$. Moreover, the logic in Table \ref{logic2} itself 
+  is suitable for $\mathbbm{M}''$ and
+  $\mathbbm{M}''$ makes true $\textup{\tmtextbf{CSQ}}_{\vdash}$.  From
+  this it follows that we have completeness.
 \end{proof}

### 2011-01-27 hybrid_awareness.tex
Fixed lots of spacing
Changed motivation

@@
-The method of the previous completeness proof makes implicit use of concepts from
+The method of the previous completeness proofs make implicit use of concepts from
 hybrid logic{\footnote{Hybrid logic was first presented in
 {\cite{prior_revised_1969}} and later formally developed in
-{\cite{bull_approach_1970}}.}}.  In this section we adapt hybrid logic and
-show that it is a complete for reasoning about knowledge bases.  We note that
-because of the increased expressive power of hybrid logic, our completeness
-theorem is simpler.
+{\cite{bull_approach_1970}}.}}.  In this section we extend the logic
+we have been developing to full hybrid logic.
+
+No such concept like hybrid logic is present in Russell's writing,
+however it is not hard to motivate an epistemic reading.
+Colloquially, we might describe a particular fantasy fiction
+as ``knowing a lot about Tolkien's \emph{middle earth}''.  One way of
+making sense of how she ``knows'' is that her explicit and implicit reasoning about
+Tolkien's fantasy world is  \emph{valid at middle
+  earth}.  To model this in a hybrid framework, assume there is a
+nominal entitled $\textup{\emph{middle earth}}$, and some world with
+that label. We denote that the agent's reasoning is valid there as $\PP^{\textup{\emph{middle
+      earth}}}$. 
+We permit that worlds may be multiply labeled or not labeled at
+all, and labels may fail to refer to anything.
+
+We do not express $\PP^i$ directly; rather, we will define it in terms
+of a universal modality.
 
@@
   language $\mathcal{L}_H (\Phi, \Psi)$ as:
-  \[ \phi \hspace{1em} : : = \hspace{1em} p \in \Phi \hspace{1em} |
-     \hspace{1em} i \in \Psi \hspace{1em} | \hspace{1em} \bot \hspace{1em} |
-     \hspace{1em} \phi \rightarrow \psi \hspace{1em} | \hspace{1em} \Box \phi
-     \hspace{1em} | \hspace{1em} A : \phi \hspace{1em} | \hspace{1em} \forall
+  \[ \phi \  : : = \  p \in \Phi \  |
+     \  i \in \Psi \  | \  \bot \  |
+     \  \phi \rightarrow \psi \  | \  \Box \phi
+     \  | \  A : \phi \  | \  \forall
      \phi \]
@@
 nominals.  This framework presents a logic where the agent may reason about
-various labeled scenarios.  Scenarios may be multiply labeled or not labeled
-at all.  From these intuitions we have the following definition:
+various labeled scenarios.    From these intuitions we have the following definition:
 
@@
   The semantics for $\vDash$ are the same as in Definition
-  \ref{awarenessmodels}, only we have
+  \ref{awarenessmodels0}, with the following extensions
   \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \forall \phi & \text{iff} & \forall v \in
+    \mathbbm{M}, w \vDash \forall \phi & \iff & \forall v \in
     W.\mathbbm{M}, v \vDash \phi\\
-    \mathbbm{M}, w \vDash i & \text{iff} & \ell (i) = w
+    \mathbbm{M}, w \vDash i & \iff & \ell (i) = w
   \end{eqnarray*}
@@
 
-The other connectives and operators are defined as usual, although we employ a
-few special shorthands:
+The other connectives and operators are defined as usual. We also employ a
+the following shorthand:
 
-\begin{definition}
+\begin{notation}
   We employ the following special abbreviations:
   \begin{eqnarray}
-    \text{\tmtextup{@}}_i \phi \assign \forall (i \rightarrow \phi)
+    \text{\tmtextup{@}}^i \phi \assign \forall (i \rightarrow \phi)
     \hspace{2em} & \exists \phi \assign \neg \forall \neg \phi \hspace{3em} &
-    \circlearrowleft_i \assign \diamondsuit i \nonumber
+    \circlearrowleft^i \assign \diamondsuit i \nonumber
   \end{eqnarray}
-\end{definition}
+\end{notation}
 
-This gives rise to a validity reflecting one of the axioms we saw in
+We have a validity reflecting one of the axioms we saw in
 {\S}\ref{awarenesslogic}:
-\[ \vDash \circlearrowleft_i \rightarrow \Box \phi \rightarrow
-   \text{\tmtextup{@}}_i \phi \]
+\[ \vDash \circlearrowleft^i \rightarrow \Box \phi \rightarrow
+   \text{\tmtextup{@}}^i \phi \]
 This can be read as ``If the agent's knowledge base is sound at world $i$,
@@
 making true \tmtextbf{CSQ}:
-
 \begin{table}[h]
+\begin{centering}
   \begin{tabular}{ll}
@@
     \Box \phi$\\
-    & $\vdash i \rightarrow \phi \rightarrow \text{\tmtextup{@}}_i \phi$\\
-    & \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi}{\vdash \Box \phi}$ &
-      {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \forall \phi}$
-    \end{tabular} & 
+    & $\vdash i \rightarrow \phi \rightarrow \text{\tmtextup{@}}^i \phi$\\
+    &  
+  \end{tabular}
+\begin{tabular}{lllll}
+      $\displaystyle\frac{\vdash \phi \rightarrow \psi \ \ \vdash \phi}{\vdash
+      \psi}$ & \ \  & $\displaystyle \frac{\vdash \phi}{\vdash \Box \phi}$ &
+      \ \  & $\displaystyle \frac{\vdash \phi}{\vdash \forall \phi}$
     \end{tabular}
   \caption{\label{logic2}Hybrid Awareness Logic for \tmtextbf{CSQ}}
+\end{centering}
 \end{table}
@@
   hybrid awareness logic presented is sound and weakly complete for all hybrid
-  models making true \tmtextbf{CSQ}.
+  models making true $\textup{\tmtextbf{CSQ}}_{\vdash'}$ for some
+  suitable logic $\vdash'$.
 \end{theorem}

### 2011-01-27 introduction.tex
Reworded abstract

@@
 Hintikka's \emph{Knowledge and Belief}
-\cite{hintikka_knowledge_1969}. While Hintikka was steeped in
-profound philosophical insights, the introduction of epistemic logic
-bifurcated 20th century research into epistemology.  A number of
+\cite{hintikka_knowledge_1969}. While Hintikka began by considering
+traditional topics in the theory of knowledge, epistemic logic
+resulted in a bifurcation 20th century research into epistemology.  A number of
 logicians and philosophers have acknowledged this rift, most notably
@@
 we illustrate that the modern concepts of \emph{explicit} and
-\emph{implicit}, due to Levesque\footnote{While we will refer often to
-  the terms coined by Levesque in this essay, we will not use his
-  proposed semantics.  We will instead prefer variations on
-  \emph{awareness logic}, originally developed by Fagin and Halpern \cite{fagin_belief_1988}.}\cite{levesque_logic_1984}, knowledge in epistemic logic are reinventions of
-Russell's distinction between \emph{immediate} and \emph{derivative}
+\emph{implicit} knowledge, originally due to Levesque\footnote{While we will refer often to
+  terms coined by Levesque in this essay, we will not use his
+  proposed semantics.  We instead prefer variations on
+  \emph{awareness logic}, originally developed by Fagin and Halpern
+  \cite{fagin_belief_1988}.}\cite{levesque_logic_1984},  are reflect Russell's distinction between \emph{immediate} and \emph{derivative}
 knowledge.  We propose a novel property of awareness models which
-directly reflects Russell's foundationalist epistemology.  The
+inspired by Russell's epistemology.  The
 remainder of this paper is then devoted to exploring how awareness
-logics can be designed to express our this foundationalist property.
+logics can be designed to express this foundationalist property.
 

### 2011-01-27 paper.tex
Some new boilerplate

@@
 \newtheorem{definition}{Definition}
+\newtheorem{notation}{Notation}
 \newtheorem{proposition}{Proposition}
@@
 
+\newcommand{\PP}{\circlearrowleft}
+\newcommand{\nmodels}{\nvDash}
 \begin{document}
@@
 \begin{abstract}
-  In this essay, we show that awareness logic is suitable for
-  formal modeling of Bertrand Russell's theory of knowledge,
-  originally developed in \cite{russell_problems_1936}.  This is done
-  by introducing a novel property to the semantics of 
-  awareness logics. 
-  We present a variety of sound and complete awareness
-  logics compatible which exhibit this property.
+This paper presents a novel approach to formulating epistemic directly
+in terms of logical inference.  Using awareness logic, $\Box_X \phi$ is
+taken to literally mean ``it follows from formulae $X$ is explicitly aware of
+that $\phi$''.  This is done by incorporating logic into the semantics
+of awareness logic.  Our approach corresponds closely to the framework
+for epistemology proposed by Bertrand
+Russell\cite{russell_problems_1936}, and illustrates that
+objections provided by Jaako Hintikka\cite{hintikka_knowledge_1969} to
+the proposed interpretation of epistemic logic should be considered invalid.
 \end{abstract}
-\todo{This abstract isn't flowery enough.  Lookup PhD comics
-  ``Abstract madlibs'' and use that as a template.}
 
 \listoftodos
-
 \section{Introduction}

### 2011-01-27 simple_justification.tex
changing motivation for sjl

@@
 
-In this section we consider a simplified form of JL suitable for reasoning
+We propose a stripped down, simplified form of JL suitable for reasoning
 over multiple knowledge bases, which we call \tmtextit{simple justification
-logic} (SJL). However, instead of thinking of terms as representing proofs, we
-use them to represent knowledge bases. This is in the spirit of JL as a logic
-of evidence: we consider each knowledge base to be a corpus of evidence. \
-Each term ``names'' a different knowledge base at a particular world.  Terms
-may not refer to the same knowledge base at different worlds, just as in how
-in awareness logic the agent need not be aware of the same formulae at
-different worlds.  Finally, we will make use of JL's {\tmem{choice}} operator
-as a mechanism for forming the union of knowledge bases, creating new ones.
+logic} (SJL). % However, instead of thinking of terms as representing proofs, we
+% use them to represent knowledge bases. This is in the spirit of JL as a logic
+% of evidence: we consider each knowledge base to be a corpus of evidence. \
+% Each term ``names'' a different knowledge base at a particular world.  Terms
+% may not refer to the same knowledge base at different worlds, just as in how
+% in awareness logic the agent need not be aware of the same formulae at
+% different worlds.
+We will only make use of JL's {\tmem{choice}} operator,
+and use it as a mechanism for forming the union of awareness sets, creating new ones.
 
@@
   following grammar:
-  \[ X \  : : = \  t \in \Pi \  | \  X
-     \oplus Y \]
+  \[ X \  : : = \  t \in \Pi \  | \  X    \oplus Y \]
 

### 2011-01-27 foundationalism.tex
Fixed reference to Fagin et al, reworded motivation of the formalism

@@
 
-\subsection{Modeling Russell Using Awareness Logic}
+\subsection{Modeling Russell}\label{mod-russell}
 
 In this section we introduce models of Russell's epistemology.  We
-will make use of \emph{awareness models} $\mathbb{M}$, using semantics originally developed in \cite{fagin_belief_198}.
+will make use of \emph{awareness models} $\mathbb{M}$, using semantics originally developed in \cite{fagin_belief_1988}.
 
@@
 \item $\vdash$ is \emph{relatively sound} for $\mathbb{M}$ if and only if
-  when $\Gamma \vdash \phi$, then if $\mathbb{M},w\models \Gamma$ then
+  when $\Gamma \vdash \phi$, then if $\mathbb{M},w\models \gamma$, for
+  all $\gamma \in \Gamma$, then
   $\mathbb{M},w \models \phi$.
@@
   \vdash \psi$
+\item $\vdash$ is said to be \emph{suitable} for $\mathbb{M}$ just in
+  case that it is reflexive, makes true modus ponens, and is
+  relatively sound for $\mathbb{M}$.
 \end{itemizedot}
 
-A model $\mathbb{M}$ is thought to be suitable for Russell's epistemology just in
-case there is some relatively sound,
-reflexive Hilbert-style calculus making true modus ponens, such that for all
+A model $\mathbb{M}$ is thought to model Russell's epistemology in the
+case that there is some suitable logic $\vdash$ such that for all
 worlds $w$:
@@
 denotes the set $\{ \phi\ |\ \mathbb{M},w \models \phi$ for all worlds
-$w \}$.  We take it to represent Russell's \emph{intuitive knowledge}
-in our modeling\emph{knowledge by description}\footnote{A caveat: we are being very liberal with our interpretation
+$w \}$.  We take it to represent Russell's \emph{intuitive
+  knowledge} \footnote{A caveat: we are being very liberal with our interpretation
   of Russell's
@@
   knowledge, since (1) it may be considered as a sort of a priori knowledge, (2) it fits the definition of knowledge by description well,
-  and (3) it provides a framework for our subsequent formal results.}.
+  and (3) it provides a framework for our subsequent formal
+  results.}.
 
@@
 
-Restricting our attention to models where implicit knowledge is
+Models where implicit knowledge is
 equated to the presence
-of a derivation is a faithful to Russell's epistemology.  Our response
-to Hintikka's criticism of this is that while epistemic logic may be
-based on models, it could also be based on particular, special models
-which have an associated logic suited to them.  Assuming that
+of a derivation are faithful to Russell's epistemology.  As we stated
+before, Russell's knowledge by description is the logical closure of
+acquaintance and intuitive knowledge, which is exactly our proposal.  Our response
+to Hintikka's criticism of this approach is that while epistemic logic may be
+based on models, it could also be based on particular models
+which have logic associated with them in a special way.  Assuming that
 knowledge in epistemic logic corresponds to \emph{some} notion of logical consequence
-does not rely on the notion of logical consequence in epistemic
-itself.  While logic about logic is circular, it is not
-\emph{viciously} so.
+does not require us to have already formulated the notion of logical
+consequence we will ultimately
+develop.  While logic about logic is circular, it is not
+\emph{viciously} so, and moreover poses no inescapable paradoxes.
 
 The rest of this essay is devoted to developing awareness logics which have
-the mechanics we have sketched here.
+the mechanics we have sketched.
 

### 2011-01-30 simple_justification.tex
Reworded introduction

@@
 
-We propose a stripped down, simplified form of JL suitable for reasoning
-over multiple knowledge bases, which we call \tmtextit{simple justification
-logic} (SJL). % However, instead of thinking of terms as representing proofs, we
+In this section we propose a stripped down, simplified form of JL suitable for reasoning
+about derivative knowledge from awareness sets, which we call 
+\tmtextit{simple justification logic} (SJL). Instead of reading $X :
+\phi$ as ``$X$ is a proof term deriving $\phi$'', we will read this
+expression as ``$X$ is acquainted with $\phi$''\footnote{This is
+  inspired by Fitting's semantics for JL proposed in
+  \cite{fitting_logic_2005}.}.  We read $\Box_X\phi$ as ``$X$ has
+derivative knowledge that $\phi$''.
+% However, instead of thinking of terms as representing proofs, we
 % use them to represent knowledge bases. This is in the spirit of JL as a logic
@@
 % different worlds.
-We will only make use of JL's {\tmem{choice}} operator,
-and use it as a mechanism for forming the union of awareness sets, creating new ones.
+SJL reduces JL to only the {\tmem{choice}} operator, which is used as a 
+mechanism for forming the union of awareness sets.
+
+While the intuition behind SJL cannot be found in
+Russell's writings, it may be found elsewhere in the epistemic logic
+literature.  For instance in
+\cite[pg. 67]{meyer_epistemic_1995}, Meyer et al. motivate logic for what they call
+\emph{implicit knowledge in a group} with the following thought experiment:
+\begin{quote}
+[A]ssume $\phi$ to be `P = NP'. We furthermore assume that three
+researchers 1, 2, 3 work on this long-standing and famous problem in
+order to discover a proof of the theorem. Suppose that the actual
+situation is such that $\phi$ follows from three lemmas: $\psi_1$,
+$\psi_2$ and $\psi_3$. Researcher 1 has proved $\psi_1$ -- so he knows
+$\psi_1$. Analogously for researchers 2 and 3 with respect to $\psi_2$
+and $\psi_3$, respectively. \ldots If the researchers would interact
+at a congress on theoretical computer science, they would be able to
+gather their partial knowledge and thereby know (a proof of) $\phi$.
+\end{quote}
+This motivation works just as well for SJL. We model this situation by
+employing the following symbolism:
+there are three awareness sets $\mathcal{A}_1(w)$, $\mathcal{A}_2(w)$ and
+$\mathcal{A}_3(w)$ which correspond to facts each researcher is
+acquainted with.  Moreover, each lemma may be derived from its
+respective base: $Th(\mathbb{M}) \cup \mathcal{A}_1(w) \vdash
+\psi_1$, $Th(\mathbb{M}) \cup \mathcal{A}_1(w) \vdash
+\psi_2$ and $Th(\mathbb{M}) \cup \mathcal{A}_1(w) \vdash
+\psi_3$.  Finally, it holds that the three lemmas prove the theorem:
+$Th(\mathbb{M}) \vdash \psi_1 \to \psi_2 \to \psi_3 \to \phi$.
+Provided that our notion of logical consequence is \emph{monotonic},
+and makes true modus ponens, it then follows that
+$Th(\mathbb{M}) \cup \mathcal{A}_1(w) \cup \mathcal{A}_2(w) \cup
+\mathcal{A}_3(w) \vdash \phi$.  In order to express this in the semantics, we represent $\mathcal{A}_1(w) \cup \mathcal{A}_2(w) \cup
+\mathcal{A}_3(w)$ as $\mathcal{A}_{1 \oplus 2 \oplus 3}(w)$, and
+$Th(\mathbb{M}) \cup \mathcal{A}_1(w) \cup \mathcal{A}_2(w) \cup
+\mathcal{A}_3(w) \vdash \phi$ as $\mathbb{M}, w \models \Box_{1 \oplus 2 \oplus 3} \phi$.
 
@@
   define the language $\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)$ as:
-  \[ \phi \  : : = \  p \in \Phi \  |
-     \  \circlearrowleft_X \  | \  \bot
+  \[ \phi \  : : = \  p \in \Phi \  | \  \bot
      \  | \  \phi \rightarrow \psi \  |
@@
   \langle W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V
-  : \Phi \cup \{\circlearrowleft_X \  | \  X \in \tau
-  (\Pi)\} \rightarrow 2^W$, an indexed relation $R : \tau (\Pi) \rightarrow
-  2^{W \times W}$, along with a modified awareness function $\mathcal{A} : W
-  \times \tau (\Pi) \rightarrow 2^{\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)}$. \
-  In practice we will denote $\mathcal{A} (w, X)$ by a curried shorthand,
-  namely $\mathcal{A}_w (X)$.
+  : \Phi  \rightarrow 2^W$, an indexed relation $R : \tau (\Pi) \rightarrow
+  2^{W \times W}$, along with a modified awareness function
+  $\mathcal{A} : \tau (\Pi) \times W
+   \rightarrow 2^{\mathcal{L}_{\tmop{SJL}} (\Phi, \Pi)}$. 
+  In practice we will denote $\mathcal{A} (X, w)$ by a curried shorthand, namely $\mathcal{A}_X (w)$.
 
@@
   \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box_X \phi & \text{iff} & \text{for all $v \in W$
+    \mathbbm{M}, w \vDash \Box_X \phi & \iff & \text{for all $v \in W$
     where $w R_X v$ we have $\mathbbm{M}, v \vDash v$}\\
-    \mathbbm{M}, w \vDash X : \phi & \text{iff} & \phi \in \mathcal{A}_w (X)
+    \mathbbm{M}, w \vDash X : \phi & \iff & \phi \in \mathcal{A}_X (w)
   \end{eqnarray*}
+\end{definition}
+
+\begin{definition}
+A Hilbert-style calculus $\vdash$ is said to be \textbf{SJL-suitable} for an SJL model
+$\mathbb{M}$ if and only if it makes true modus ponens, it is
+relatively sound for $\mathbb{M}$, and it is \textbf{monotonic}: if
+$\Gamma \vdash \phi$ and $\Gamma \subseteq \Delta$, then $\Delta
+\vdash \phi$.
 \end{definition}
@@
   \begin{descriptiondash}
-    \item[JCSQ] $\mathbbm{M}, w \vDash \Box_X \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w (X) \vdash \phi$
-
-    \item[JSND] $\mathbbm{M}, w \vDash \circlearrowleft_X \text{ iff
-    $\mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w (X)$}$
-
-    \item[CHOICE] $\mathcal{A}_w (X \oplus Y) = \mathcal{A}_w (X) \cup
-    \mathcal{A}_w (Y)$
+    \item[$\textup{\textbf{JCSQ}}_\vdash$] $\mathbbm{M}, w \vDash \Box_X \phi \iff \tmop{Th}
+    (\mathbbm{M}) \cup \mathcal{A}_X (W) \vdash \phi$
+    \item[CHOICE] $\mathcal{A}_{X \oplus Y}(w) = \mathcal{A}_X (w) \cup
+    \mathcal{A}_Y (w)$
   \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
 \end{definition}
 
-The above semantics are similar to the ones given in previous sections. \
-\tmtextbf{JCSQ} is the same as \tmtextbf{CSQ} from {\S}\ref{awarenesslogic},
-only it is relativised to a knowledge base denoted by $X$ at $w$.  The
-awareness logic of knowledge bases is special case of simple justification
-logic where there is only one term.
-
-Simplified justification logic is given in Table \ref{logic5}.  We assert
-without proof that this is a conservative extension of the awareness logic in
-{\S}\ref{awarenesslogic}.
-
 \begin{table}[h]
+\begin{centering}
   \begin{tabular}{ll}
@@
     $\vdash (X : \phi) \rightarrow \Box_X \phi$ & \\
-    $\vdash \circlearrowleft_X \rightarrow \Box_X \phi \rightarrow \phi$ & \\
-    $\vdash (X : \phi) \rightarrow (Y : \phi) \rightarrow X \oplus Y : \phi$ &
-    \\
-    $\vdash (X \oplus Y : \phi) \rightarrow X : \phi$ & $\vdash (X \oplus Y :
-    \phi) \rightarrow Y : \phi$\\
-    $\vdash \circlearrowleft_X \rightarrow \circlearrowleft_Y \rightarrow
-    \circlearrowleft_{X \oplus Y}$ & \\
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_X$ &
-    $\vdash \circlearrowleft_{X \oplus Y} \rightarrow \circlearrowleft_Y$\\
+    $\vdash \Box_X \phi \rightarrow \phi$ & \\
+    $\vdash (X \oplus Y : \phi) \leftrightarrow (X : \phi \vee Y :
+    \phi)$ & \\
     $\vdash \Box_X \phi \rightarrow \Box_{X \oplus Y} \phi$ & \\
@@
     \oplus Z)} \phi$ & \\
-    & \\
+    & 
+  \end{tabular}
 \begin{tabular}{lll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi}{\vdash \Box_X \phi}$
-    \end{tabular} & 
+      $\displaystyle\frac{\vdash \phi \rightarrow \psi \ \  \vdash \phi}{\vdash
+      \psi}$ & {\ \ } & $\displaystyle\frac{\vdash \phi}{\vdash \Box_X \phi}$
     \end{tabular}
   \caption{\label{logic5}Simple Justification Logic}
+\end{centering}
 \end{table}
+We assert without proof that SJL is a conservative extension of the awareness logic in
+{\S}\ref{awarenesslogic0}.
 
@@
   \label{completeness5}Assuming an infinite store of proposition letters
-  $\Phi$, SJL is sound and weakly complete for simple justification models
-  making true \tmtextbf{JCSQ}, \tmtextbf{JSND} and \tmtextbf{CHOICE}
+  $\Phi$, SJL (Table \ref{logic5}) is sound and weakly complete for reflexive simple justification models
+  which make true $\textup{\tmtextbf{JCSQ}}_{\vdash'}$ for some
+  SJL-suitable logic $\vdash'$ as well as
+  \tmtextbf{CHOICE}
 \end{theorem}

### 2011-01-30 completeness0.tex
changed how awareness sets are typeset

@@
   include awareness, however it is defined intuitively in this case:
-  \[ \phi \in \mathcal{A}_w \Longleftrightarrow A : \phi \in w \]
+  \[ \phi \in \mathcal{A}(w) \Longleftrightarrow A : \phi \in w \]
   Since $\psi$ is a subformula of itself, we have $\mathbbm{M}, w \nvDash
@@
   \begin{enumeratenumeric}
-    \item $W$ and $\mathcal{A}_v$ are finite, and $\psi \in \mathcal{A}_v$
+    \item\label{awareness0-prop1} $W$ and $\mathcal{A}(v)$ are finite, and $\psi \in \mathcal{A}(v)$
     only if $\psi$ is a (possibly negated) subformula of $\phi$
-    \item \label{awareness0-prop2} if $\mathbbm{M}, v \vDash A : \psi$ then $\mathbbm{M}, v \vDash \Box
+    \item \label{awareness0-prop2} If $\mathbbm{M}, v \vDash A : \psi$ then $\mathbbm{M}, v \vDash \Box
     \psi$ 
-    \item $v R v$ for all worlds $v$
+    \item \label{awareness0-prop3} $v R v$ for all worlds $v$
   \end{enumeratenumeric}
@@
   is possible since both $W$ and $\Lambda$ are finite and $\Phi$ is infinite
-  by hypothesis.  Let $\iota : W \uplus W \hookrightarrow \Phi \backslash
-  \Lambda$ be an injection assigning a fresh nominal associated with each
-  world in $W$.  Now define $\mathbbm{M}' \assign \langle W',
-  V', R', \mathcal{A}' \rangle$, where:
-
+  by hypothesis.  Let $\iota : W  \hookrightarrow \Phi \backslash
+  \Lambda$ be an injection assigning a fresh nominal to each
+  world in $W$.  Define $\mathbbm{M}' \assign \langle W',
+  V', R', \mathcal{A}' \rangle$ as follows:
   \begin{center}
@@
       $\bullet$ & $R' \assign R$ & {\hspace{3em}} & $\bullet$ &
-      $\mathcal{A}'_v \assign \{\phi \  | \phi \in \mathcal{A}_v
+      $\mathcal{A}'(v) \assign \{\phi \  |\ \phi \in \mathcal{A}(v)
       \} \cup \{\neg \iota (u) \  | \  \neg v R' u\}$
@@
   $\mathbbm{M}, v \vDash \phi$ if and only if $\mathbbm{M}', v \vDash \phi$,
-  hence $\mathbbm{M}', w \nvDash \psi$.
+  hence $\mathbbm{M}', w \nvDash \psi$.  % In addition, $\mathbb{M}'$
+  % inherits properties \ref{awareness0-prop1} through
+  % \ref{awareness0-prop3} from $\mathbb{M}$.
 
   All that is left to show is that $\mathbbm{M}'$ is reflexive and
-  makes true $\text{\tmtextbf{CSQ}}_{\vdash'}$ for some suitable logic $\vdash'$.  Since $\mathbb{M}$ was reflexive, $W' =
-  W$ and $R' = R$, we know that $\mathbb{M}'$ is reflexive too.  We
-  also have the following, additional properties:
+  makes true $\text{\tmtextbf{CSQ}}_{\vdash'}$ for some suitable logic
+  $\vdash'$.  Since $\mathbb{M}$ in reflexive, and $W' =
+  W$ and $R' = R$, we know that $\mathbb{M}'$ is reflexive too.
+
+  Now observe that $\mathbb{M}'$ has the following features:
   \begin{enumerateroman}
-    \item \label{awareness0-one} $\mathcal{A}'_v$ is finite for all worlds $v$
+    \item \label{awareness0-one} $\mathcal{A}'(v)$ is finite for all worlds $v$
     \item \label{awareness0-two} $\vdash$, the logic presented in Table \ref{logic0}, is
@@
     \item\label{awareness0-three}  $v R' u$ if and only if $\mathbbm{M}', u \vDash \bigwedge
-    \mathcal{A}'_v$
+    \mathcal{A}'(v)$
   \end{enumerateroman}
@@
    \item[Left to Right]  Assume $v R' u$. We must show that if
-   $\phi \in \mathcal{A}'_v$ then $\mathbb{M}', u \models \phi$.  If
-   $\phi \in \mathcal{A}'_v$, either (a) $\phi \in \mathcal{A}_v$ or
+   $\phi \in \mathcal{A}'(v)$ then $\mathbb{M}', u \models \phi$.  If
+   $\phi \in \mathcal{A}'(v)$, either (a) $\phi \in \mathcal{A}(v)$ or
    (b) $\phi = \neg \iota(x)$ for some world $x$ where $\neg v R x$. Note
@@
    \item[Right to Left] It suffices to establish the contrapositive.  Assume $\neg v R' u$,
-   we must find some formula $\phi \in \mathcal{A}'_v$ such that
+   we must find some formula $\phi \in \mathcal{A}'(v)$ such that
    $\mathbb{M}, u \nmodels \phi$.  Evidently $\phi = \iota(u)$ suffices.
@@
   \begin{align*}
-    Th({\mathbbm{M}}'){\cup}\mathcal{A}'_v{\vdash}{\phi}\ &
-    {\Longleftrightarrow}\ Th({\mathbbm{M}}'){\vdash}\bigwedge\mathcal{A}'_v{\rightarrow}{\phi}\\
+    Th({\mathbbm{M}}'){\cup}\mathcal{A}'(v){\vdash}{\phi}\ &
+    {\Longleftrightarrow}\ Th({\mathbbm{M}}'){\vdash}\bigwedge\mathcal{A}'(v){\rightarrow}{\phi}\\
     &
-    {\Longleftrightarrow}\ \bigwedge\mathcal{A}'_v{\rightarrow}{\phi}{\in}Th({\mathbbm{M}}')\\
+    {\Longleftrightarrow}\ \bigwedge\mathcal{A}'(v){\rightarrow}{\phi}{\in}Th({\mathbbm{M}}')\\
     &
-    {\Longleftrightarrow}\ {\mathbbm{M}}',u{\vDash}\bigwedge\mathcal{A}'_v{\rightarrow}{\phi}\text{
+    {\Longleftrightarrow}\ {\mathbbm{M}}',u{\vDash}\bigwedge\mathcal{A}'(v){\rightarrow}{\phi}\text{
     for all $u \in W'$}\\
     & {\Longleftrightarrow}\ \text{for all $u \in W'$, if
-    }{\mathbbm{M}}',u{\vDash}\bigwedge\mathcal{A}'_v\text{ then
+    }{\mathbbm{M}}',u{\vDash}\bigwedge\mathcal{A}'(v)\text{ then
     }{\mathbbm{M}}',u{\vDash}{\phi}\\
@@
   \end{align*}
+This suffices to prove $\textup{\tmtextbf{CSQ}}_{\vdash}$, which
+suffices the proof.
 \end{proof}

### 2011-01-30 completeness3.tex
Changed proof around

@@
   \psi$.  Let $\Xi \subseteq \tau (\Pi)$ be all of the subterms occurring in
-  $\psi$; we assume that $\Xi$ is non-empty, since otherwise we may obtain the
-  theorem via the usual completeness theorem for classical propositional
-  logic. Let $\Sigma_0$ be the subformulae of $\psi$.  Define:
+  $\psi$.
+
+  We assume that $\Xi$ is non-empty, since otherwise we may obtain the
+  theorem by using the usual completeness theorem for classical propositional
+  logic to find a valuation $V$, which we would use in trivial a
+  Kripke model $\mathbb{T}$ with a
+  single world $w$ corresponding to that valuation, such that
+  $\mathbb{T},w\nmodels \psi$.
+
+Let $\Sigma_0$ be the subformulae of $\psi$.  Define:
 
@@
 
-  Next, define an operator $\twonotes : \tau (\Pi) \rightarrow 2^{\Pi}$ where:
-  \[ \twonotes (X) \assign \{t \in \Pi \  | \  t \text{
-     occurs in } X\} \]
-  In other words, $\twonotes (X)$ is the set of atomic terms in $X$.  As in
-  our construction for Theorem \ref{completeness1}, $\mathbbm{M}$ makes true
-  certain properties, along with some new properties:
+ $\mathbbm{M}$ makes true various properties:
   \begin{enumeratenumeric}
-    \item \label{fin}$W$ and $\mathcal{A}_v (X)$ are finite, and $\phi \in
-    \mathcal{A}_v (X)$ only if $\phi \in \Sigma_2$
-
-    \item if $\mathbbm{M}, v \vDash X : \phi$ then $\mathbbm{M}, v \vDash
+     \item \label{fin}$W$ and $\mathcal{A}_X (v)$ are finite, and $\phi \in
+    \mathcal{A}_X (v)$ only if $\phi \in \Sigma_2$
+     \item All of the relations $R_X$ in $\mathbb{M}$ are reflexive    
+    \item If $\mathbbm{M}, v \vDash X : \phi$ then $\mathbbm{M}, v \vDash
     \Box_X \phi$
-
-    \item \label{refl}if $\mathbbm{M}, v \vDash \circlearrowleft_X$ then $v
-    R_X v$
-
-    \item \label{sndness}For all $X \oplus Y \in \Xi$, $\mathbbm{M}, v \vDash
-    \circlearrowleft_{X \oplus Y}$ if and only if $\mathbbm{M}, v \vDash
-    \circlearrowleft_X$ and $\mathbbm{M}, v \vDash \circlearrowleft_Y$
-
-    \item \label{union}For all $X \oplus Y \in \Xi$, $\mathcal{A}_v (X \oplus
-    Y) = \mathcal{A}_v (X) \cup \mathcal{A}_v (Y)$
-
+    \item \label{union}For all $X \oplus Y \in \Xi$, $\mathcal{A}_{X \oplus
+    Y}(v) = \mathcal{A}_X(v) \cup \mathcal{A}_Y (v)$
     \item \label{sub}For all $X, Y \in \Xi$, if $\twonotes (X) \subseteq
@@
   \end{enumeratenumeric}
-  As in our previous constructions, it is necessary to refine this model using
-  bisimulations to achieve properties which are not modally definable.  In
-  particular, we shall strengthen (\ref{refl}) to a biconditional and
-  (\ref{sub}) to:
+  Where the operator $\twonotes : \tau (\Pi) \rightarrow 2^{\Pi}$ is
+  defined as follows:
+  \[ \twonotes (X) \assign \{t \in \Pi \  | \  t \text{
+     occurs in } X\} \]
+  In other words, $\twonotes (X)$ is the set of atomic terms in $X$.
 
+  We next refine this model to achieve a property which is not
+  not modally definable.  To do this, we will construct a \emph{bisimular model}{\footnote{The notion of bisimulation is
+   discussed at length in {\cite[chapter 2.2]{blackburn_modal_2001}}.  We
+  note that the basic definition and all of the usual theorems
+  may be generalized to awareness models in a straightforward fashion,
+  such that bisimulation entails modal equivalence. }}.  
+  Define  $\mathbbm{M}' \assign \langle W', V', R'', \mathcal{A}' \rangle$ such
+  that{\footnote{Let $\{i_X \  | \  X \in \Xi\}$ be the
+  family of canonical injections into the coproduct $\biguplus_{\Xi}
+  W$. By convention we use $v_X$ as shorthand for $i_X (v)$.}}:
+  \begin{itemizedot}
+    \item $W' \assign \biguplus_{\Xi} W$
+    \item $V' (p) \assign \{v_X \  | \  X \in \Xi
+    \  \& \  v \in V (p)\}$
+    \item $R'_X \assign \{(v_Y, u_Z) \  | \  Y, Z \in \Xi
+    \  \& \  v R_Z u \  \& \ 
+    \twonotes (X) \subseteq \twonotes (Z)\}$
+    \item $\mathcal{A}'_X(v_Y) \assign \mathcal{A}_{X} (v)$
+  \end{itemizedot}
+  Note that this construction makes use of our assumption that $\Xi$ is
+  non-empty.  Let $Z \assign \{(v, v_X) \  | \  X \in \Xi
+  \  \& \  v \in W' \}$; it is straightforward to prove
+  that $Z$ is a bisimulation between $\mathbbm{M}$ and $\mathbbm{M}'$. Hence $\mathbbm{M}', w_X
+  \nvDash \psi$ for some $w_X \in W'$.  In addition, $\mathbbm{M}'$
+  inherits (\ref{fin}) through (\ref{sub}) from $\mathbbm{M}$.  Next
+  observe, forall terms $X$ and $Y$ where $X \oplus Y \in \Xi$:
+  \begin{eqnarray*}
+    \text{$(v_V, u_Z) \in R'_X \cap R'_Y$} & \Longleftrightarrow & \exists Z
+    \in \Xi . \text{$v R_Z u \  \& \  \twonotes (X)
+    \subseteq \twonotes (Z) \  \& \  \twonotes (Y)
+    \subseteq \twonotes (Z)$}\\
+    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R_Z u \ 
+    \& \  \twonotes (X) \cup \twonotes (Y) \subseteq \twonotes
+    (Z)$}\\
+    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R_Z u \ 
+    \& \  \twonotes (X \oplus Y) \subseteq \twonotes (Z)$}\\
+    & \Longleftrightarrow &  \text{$(v_V, u_Z) \in R'_{X \oplus Y}$}
+  \end{eqnarray*}
+  As in our previous proofs, let  $\iota : W' \hookrightarrow \Phi \backslash \Psi$ be an injection
+  assigning fresh nominals to worlds.  Define $\mathbbm{M}'' \assign \langle W'',
+  V'', R'', \mathcal{A}'' \rangle$ such that:
   \begin{center}
-    \begin{tabular}{ll}
-      \tmtextbf{6$'$.} & For all $X, Y \in \Xi$, $R_{X \oplus Y} = R_X \cap
-      R_Y$
+    \begin{tabular}{lllll}
+      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign \left\{
+      \begin{array}{ll}
+        V' (p) & p \in \Lambda\\
+        \{v\} & p = \iota (v)\\
+        \varnothing & o / w
+      \end{array} \right.$
     \end{tabular}
   \end{center}
-
-  We first strengthen (\ref{refl}) by constructing $\mathbbm{M}' \assign
-  \langle W', V', R', \mathcal{A}' \rangle$, just as in Theorem
-  \ref{completeness1}: {\hspace*{\fill}}
-  \begin{itemizedot}
-    \item $W' \assign W \uplus W$
-
-    \item $V' (p) \assign \{v_l, v_r \  | \  v \in V
-    (p)\}$
-
-    \item $R'_X \assign \{(v_l, u_r), (v_r, u_l) \  | \  v
-    R_X u\} \cup \{(v_l, v_l), (v_r, v_r) \  | \ 
-    \mathbbm{M}, v \vDash \circlearrowleft_X \}$
-
-    \item $\mathcal{A}' (v_l, X) \assign \mathcal{A}' (v_r, X) \assign
-    \mathcal{A} (v, X)$
-  \end{itemizedot}
-  The same bisimulation relation $Z$ previously given suffices.
-
-  We next make a strengthened the model where (\ref{sub}$'$) holds.  Define
-  $\mathbbm{M}'' \assign \langle W'', V'', R'', \mathcal{A}'' \rangle$ such
-  that{\footnote{Let $\{i_X \  | \  X \in \Xi\}$ be the
-  family of canonical injections into the coproduct $\uplus_{\Xi} W$. As per
-  our previous convention, we use $v_X$ as shorthand for $i_X (v)$.}}:
-  \begin{itemizedot}
-    \item $W'' \assign \uplus_{\Xi} W'$
-
-    \item $V'' (p) \assign \{v_X \  | \  X \in \Xi
-    \  \& \  v \in V' (p)\}$
-
-    \item $R''_X \assign \{(v_Y, u_Z) \  | \  Y, Z \in \Xi
-    \  \& \  v R'_Z u \  \& \ 
-    \twonotes (X) \subseteq \twonotes (Z)\}$
-
-    \item $\mathcal{A}'' (v_Y, X) \assign \mathcal{A}' (v, X)$
-  \end{itemizedot}
-  Note that this construction makes use of the assumption that $\Xi$ is
-  non-empty.  Let $Z \assign \{(v, v_X) \  | \  X \in \Xi
-  \  \& \  v \in W' \}$; it is straightforward to prove
-  that $Z$ is a bisimulation between $\mathbbm{M}'$ and $\mathbbm{M}''$, for
-  all relations corresponding to terms $X \in \Xi$. Hence $\mathbbm{M}'', w_X
-  \nvDash \psi$ for some $w_X \in W''$.  In addition, $\mathbbm{M}''$
-  inherits (\ref{fin}) through (\ref{sub}) from $\mathbbm{M}'$, as well as the
-  converse of (\ref{refl}).  Next observe, forall $X \oplus Y \in \Xi$:
-  \begin{eqnarray*}
-    \text{$(v_V, u_Z) \in R''_X \cap R''_Y$} & \Longleftrightarrow & \exists Z
-    \in \Xi . \text{$v R'_Z u \  \& \  \twonotes (X)
-    \subseteq \twonotes (Z) \  \& \  \twonotes (Y)
-    \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \ 
-    \& \  \twonotes (X) \cup \twonotes (Y) \subseteq \twonotes
-    (Z)$}\\
-    & \Longleftrightarrow & \exists Z \in \Xi . \text{$v R'_Z u \ 
-    \& \  \twonotes (X \oplus Y) \subseteq \twonotes (Z)$}\\
-    & \Longleftrightarrow &  \text{$(v_V, u_Z) \in R''_{X \oplus Y}$}
-  \end{eqnarray*}
-  We now turn to our final construction. As in previous constructions, let
-  $\iota : W'' \hookrightarrow \Phi \backslash \Psi$ be an injection assigning
-  fresh nominals to worlds.  Define $\mathbbm{M}''' \assign \langle W''',
-  V''', R''', \mathcal{A}''' \rangle$ just as in the final construction in the
-  proof of Theorem \ref{completeness1}, except that $R'''_X$ and
-  $\mathcal{A}_v''' (X)$ are defined inductively as follows:
-
+Moreover,  $R''_X$ and $\mathcal{A}_X'' (v)$ are defined inductively as follows:
   \begin{center}
     \begin{tabular}{lll}
-      $\bullet$ & $R'''_t \assign \left\{ \begin{array}{ll}
-        R''_t & t \in \Xi\\
-        W''' \times W''' & o / w
-      \end{array} \right.$ & \\
-      $\bullet$ & $R'''_{X \oplus Y} \assign R'''_X \cap R'''_Y$ & \\
+      $\bullet$ & $R''_t \assign \left\{ \begin{array}{ll}
+        R'_t & t \in \Xi\\
+        W'' \times W'' & o / w
+      \end{array} \right.$ & where $t \in \Pi$ \\
+      $\bullet$ & $R''_{X \oplus Y} \assign R''_X \cap R''_Y$ & \\
       &  & \\
-      $\bullet$ & $\mathcal{A}'''_v (t) \assign \{\phi \  | \phi \in
-      \mathcal{A}''_v \} \cup \{\neg \iota (u) \  | \ 
-      \neg v R'''_t u\}$ & where $t \in \Pi$\\
-      $\bullet$ & $\mathcal{A}'''_v (X \oplus Y) \assign \mathcal{A}'''_v (X)
-      \cup \mathcal{A}'''_v (Y)$ & 
+      $\bullet$ & $\mathcal{A}''_t (v) \assign \{\phi \  | \phi \in
+      \mathcal{A}'_t \} \cup \{\neg \iota (u) \  | \ 
+      \neg v R''_t u\}$ & where $t \in \Pi$\\
+      $\bullet$ & $\mathcal{A}''_{X \oplus Y} (v) \assign \mathcal{A}''_{X} (v)
+      \cup \mathcal{A}''_Y (v)$ & 
     \end{tabular}
   \end{center}
+  Induction over complexity of subformulae $\phi$ of $\psi$ yields
+  $\mathbbm{M}', w \vDash \phi \Longleftrightarrow \mathbbm{M}'', w \vDash
+  \phi$, so we know that there is some world $w \in W''$ such that
+  $\mathbbm{M}'', w \nvDash \psi$.  All that is left is to illustrate that
+  $\mathbbm{M}''$ has the properties we want.
 
-  Induction over complexity of subformulae $\phi$ of $\psi$ yields
-  $\mathbbm{M}'', w \vDash \phi \Longleftrightarrow \mathbbm{M}''', w \vDash
-  \phi$, so we know that there is some world $w \in W'''$ such that
-  $\mathbbm{M}''', w \nvDash \psi$.  All that is left is to illustrate that
-  $\mathbbm{M}'''$ has the properties we desire.
+  First note that by definition, $\mathbbm{M}''$ makes true
+  \tmtextbf{CHOICE}, since the awareness sets are defined inductively
+  to enforce this property. Next we may see that $\mathbbm{M}''$
+  inherits (\ref{fin}) through (\ref{sub}) from $\mathbbm{M}'$.  Hence
+  $\mathbb{M}''$ is reflexive.
 
-  First note that by definition, $\mathbbm{M}'''$ makes true
-  \tmtextbf{CHOICE}.  Next, an induction argument on the complexity of a
-  terms $X$, making essential use of (\ref{sub}$'$), yields:
-  \[ u R_X''' v \Longleftrightarrow \mathbbm{M}''', v \vDash \bigwedge
-     \mathcal{A}'''_v (X) \]
-  With this, $\mathbbm{M}'''$ makes true \tmtextbf{JSND} since it inherits
-  (\ref{refl}).  Finally, we note that we may repeat our previous arguments
-  from Theorem \ref{completeness1} to prove \tmtextbf{JCSQ}.
+  The model $\mathbb{M}''$ also inherits $(v,u) R''_{X \oplus Y} \iff
+  (v,u) \in  (R''_{X}\cap R''_{Y})$,
+  and strengthens this property to cover \emph{all} terms $X$ and $Y$,
+  not just those occurring in $\Xi$. This may
+  be verified by double induction on complexity of terms $X$ and $Y$.
+
+  A final induction argument on the complexity of a term $X$ yields:
+  \[ u R_X'' v \Longleftrightarrow \mathbbm{M}'', v \vDash \bigwedge
+     \mathcal{A}''_X (v) \]
+  From these facts, we have that SJL itself is SJL-suitable for $\mathbb{M}''$. By repeating our previous arguments
+  from Theorem \ref{completeness1} we can prove that $\textup{\tmtextbf{JCSQ}}_\vdash$.
 \end{proof}

### 2011-01-30 awareness0.tex
Changed how awareness sets are typeset

@@
   W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V : \Phi \rightarrow 2^W$ and an awareness function
-  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$.  We will
-  usually denote $\mathcal{A} (w)$ as $\mathcal{A}_w$.
+  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$.
 
@@
     \item[CSQ$_\vdash$] $\mathbbm{M}, w \vDash \Box \phi \text{ iff } \tmop{Th}
-    (\mathbbm{M}) \cup \mathcal{A}_w \vdash \phi$
+    (\mathbbm{M}) \cup \mathcal{A}(w) \vdash \phi$
     % \item[SND] $\mathbbm{M}, w \vDash \circlearrowleft \text{ iff }
-    % \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w$
+    % \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}(w)$
   \end{descriptiondash}
@@
   \label{completeness0}Assuming an infinite store of proposition letters
-  $\Phi$, $\vdash$ is sound and weakly complete for
+  $\Phi$, $\vdash$ (from Table \ref{logic0}) is sound and weakly complete for
   reflexive awareness models $\mathbb{M}$ making true

### 2011-01-30 introduction.tex
Reworded introduction slightly

@@
 knowledge.  We propose a novel property of awareness models which
-inspired by Russell's epistemology.  The
-remainder of this paper is then devoted to exploring how awareness
+is inspired by Russell's epistemology.  The
+remainder of this paper is then devoted to exploring how various awareness
 logics can be designed to express this foundationalist property.

### 2011-01-30 foundationalism.tex
changed discussion of hintikka's refutation

@@
 
-Russell's theory of knowledge is presented in Chapter XIII, entitled
-\emph{Knowledge, Error, and Probable Opinion} \cite[pg. 52]{russell_problems_1936}:
+Russell's theory of knowledge is a form of \emph{strong
+  foundationalism}.  We specifically focus on the view presented in
+Chapter XIII of \emph{The Problems of Philosophy}, entitled
+``Knowledge, Error, and Probable Opinion'' \cite[pg. 52]{russell_problems_1936}:
 \begin{quote}
@@
 
-Historically, Hintikka briefly entertains a similar reading of
-epistemic logic in \emph{Knowledge and Belief}
-\cite{hintikka_knowledge_1969}[pgs. 38--39].  He proposes that ``$K_a
-p$" might be read as ``It follows from what $a$ knows that $p$.''
-Hintikka then rejects this reading on the grounds that it appeals to
-some given standard of logical consequence.  He asserts that this is
-``diametrically opposed'' to his research program in epistemic logic,
-which is intended to ascribe a definition of logical consequence in
-terms of the semantics he invents.
+\subsection{Jaako Hintika}\label{Russell}
 
-Hintikka is too dismissive of the foundationalist reading
-of epistemic logic.  While unintuitive from a semantic
-standpoint, it is possible to enforce a reading of knowledge in terms
-of logical consequence. In the next section we sketch how this may be
-accomplished, by employing awareness
-logic and following Russell's formulation of knowledge by description.
+Jaako Hintikka briefly entertains a reading of
+epistemic logic similar to Russell's epistemology 
+in \emph{Knowledge and Belief}, where he provides the
+first formulation of epistemic logic
+\cite{hintikka_knowledge_1969}[pgs. 38--39].  
+There he proposes that ``$K_a
+p$" might be read as ``It follows from what $a$ knows that $p$''.
+
+Hintikka rejects the Russellian reading of epistemic logic after
+proposing it. His stated grounds are that
+such a reading appeals to some given standard of logical consequence.  
+He asserts that this is ``diametrically opposed'' to his research program in epistemic logic,
+which is intended to develop a system of logical consequence using his
+invented semantics as a foundation.
+
+Hintikka's objection is reasonable.  It is counter intuitive to assume
+a system of logical consequence is present at the semantic level in
+epistemic logic.
+However, it is not \emph{impossible}.  In the next section we sketch
+an approach to epistemic logic that incorporates logical consequence
+into awareness logic.  The intuition behind this move follows
+Russell's formulation of \emph{acquaintance} and \emph{knowledge by
+  description}.  After providing formal systems that express our
+proposed reading of epistemic modality, we return Hintikka's objection
+in \S\ref{hintikka-obj} in our concluding remarks.
 
@@
   $\phi$}.  We will denote this as $A:\phi$, with the usual
-semantics of $\mathbb{M},w \models A:\phi \iff \phi \in \mathcal{A}_w$
-where $\mathcal{A}_w$ is an awareness set.
+semantics of $\mathbb{M},w \models A:\phi \iff \phi \in \mathcal{A}(w)$
+where $\mathcal{A}(w)$ is an awareness set.
 
@@
 single conclusion $\phi$ on the right. Define the following terminology:
+\begin{definition}\ 
 \begin{itemizedot}
@@
   all $\gamma \in \Gamma$, then
-  $\mathbb{M},w \models \phi$.
+  $\mathbb{M},w \models \phi$
 \item $\vdash$ is \emph{reflexive} if and only if whenever $\phi \in
@@
   case that it is reflexive, makes true modus ponens, and is
-  relatively sound for $\mathbb{M}$.
+  relatively sound for $\mathbb{M}$
 \end{itemizedot}
+\end{definition}
 
@@
 \[ \mathbb{M}, w \models \Box \phi \textup{ if and only if } Th(\mathbb{M}) \cup
-\mathcal{A}_w \vdash \phi \]
+\mathcal{A}(w) \vdash \phi \]
 

### 2011-01-30 paper.tex
Changed title

@@
 \newcommand{\nmodels}{\nvDash}
+\renewcommand{\models}{\vDash}
 \begin{document}
 
-\title{Awareness and Russell's Epistemology}\author{Matthew P.
+\title{Awareness and Russellian Epistemology}\author{Matthew P.
 Wampler-Doty}\date{}\maketitle
@@
 This paper presents a novel approach to formulating epistemic directly
-in terms of logical inference.  Using awareness logic, $\Box_X \phi$ is
-taken to literally mean ``it follows from formulae $X$ is explicitly aware of
-that $\phi$''.  This is done by incorporating logic into the semantics
-of awareness logic.  Our approach corresponds closely to the framework
-for epistemology proposed by Bertrand
-Russell\cite{russell_problems_1936}, and illustrates that
-objections provided by Jaako Hintikka\cite{hintikka_knowledge_1969} to
-the proposed interpretation of epistemic logic should be considered invalid.
+in terms of logical inference.  Using variations on awareness logic,
+we develop systems where $\Box \phi$ is
+literally taken to mean ``it follows from formulae the agent is explicitly aware of
+that $\phi$''.  We accomplish this by incorporating logical inference into the semantics
+of awareness logic.  Our reading of awareness logic corresponds
+closely to a form of \emph{strong foundationalism} proposed by Bertrand
+Russell\cite{russell_problems_1936}.  Our findings illustrate that an
+objection provided by Jaako Hintikka\cite{hintikka_knowledge_1969} to
+the proposed interpretation of epistemic modality is invalid.
 \end{abstract}
@@
 
-\subsection{Neighborhood Semantics}
+\subsection{Neighborhood Semantics (Doxastic Logic)}
 \label{neighborhood_semantics}
@@
 
-\subsection{\label{quantifying}Multi-Modal Logic}
-\label{modal-modal}
-\input{modal-modal.tex}
+% \subsection{\label{quantifying}Multi-Modal Logic}
+% \label{modal-modal}
+% \input{modal-modal.tex}
 
-\section{Conclusions \& Further Research}
+\section{Closing Remarks \& Conclusions}
 \label{conclusions}

### 2011-01-30 neighborhood_semantics.tex
Reworded motivation for neighborhood semantics

@@
 for reasoning about epistemic agents without logical omniscience.  In this
-section will demonstrate how these semantics may be modified so that
-neighborhoods corresponds to the logical consequences of a different knowledge
-bases.  This allows for using logics with neighborhood semantics for
-reasoning about multiple knowledge bases.  A point of distinction of
-neighborhood semantics from JL is that it may be possible that two distinct
-knowledge bases cannot be merged by the agent.
+section will demonstrate how these semantics may be merged with
+awareness logic, such that each neighborhood corresponds to the
+logical consequences of a different
+awareness set.  
+%This allows for using logics with neighborhood semantics for
+%reasoning about multiple knowledge bases.
+
+Russell does not provide any intuition which motivates the logic we
+want to develop here.  
+Instead, we rely on a thought experiment of our own invention. Consider
+a physicist who has studied both \emph{classical thermodynamics} and
+\emph{statistical mechanics}.  The former theory supports a proposition
+known as \emph{Boltzman's $H$-theorem}, while the latter supports 
+a result known as \emph{Poincar\'{e}'s recurrence theorem}.
+  However, she refuses to recognize the \emph{conjunction} of these
+  two statements, because Boltzman's
+  $H$-theorem and Poincar\'{e}'s recurrence theorem logically exclusive.
+  The former implies that spilt milk will not go back into a bottle
+  unless work is performed, while the latter holds that given enough
+  time spilt milk will eventually \emph{unspill} itself all on its
+  own, infinitely often.  As a result, our
+  physicists picks and chooses assumptions from both classical
+  thermodynamics and statistical mechanics as application
+  demands, but she is careful to never \emph{combine} the two theories
+  entirely\footnote{This is a point of distinction of neighborhood
+    semantics from SJL, since in SJL two awareness sets can
+    \emph{always} be combined.}, on pain of contradiction.
+
+  We model our thought experiment by first interpreting
+  $\mathcal{A}(w)$ not as one
+  unified awareness set, as in previous sections, but rather as
+  \emph{a collection} of awareness sets.  Each awareness set
+  represents a different sets
+  of admissible assumptions.  The physicist can derive a
+  proposition only if she has a suitable set of assumptions $X$ at her
+  disposal.  We model this by stipulating that 
+  $\mathbb{M},w\models \Box \phi$ if and only if there is some 
+  $X \in \mathcal{A}(w)$ such that $Th(\mathbb{M}) \cup
+  X \vdash \phi$.  In the case of the physicist, we imagine there
+  being two sets of assumptions in $\mathcal{A}(w)$, $X$ and $Y$,
+  representing the assumptions of classical thermodynamics
+  and statistical mechanics respectively.  Likewise, we have represent
+  Boltzman's $H$-theorem and Poincar\'{e}'s recurrence theorem as
+  $\phi$ and $\psi$, respectively.  From the thought experiment we have $Th(\mathbb{M}) \cup
+  X \vdash \phi$ and $Th(\mathbb{M}) \cup
+  Y \vdash \psi$, while $Th(\mathbb{M})\vdash \phi \wedge \psi \to
+  \bot$.  
+  It is not hard to imagine cases, however, no such third set
+  $Z$ being available in $\mathcal{A}(w)$ such that $Th(\mathbb{M}) \cup
+  Z \vdash \phi \wedge \psi$, since the physicist is making an effort
+  to be rational.
+
+Unlike other sections, this section is not concerned with \emph{epistemic logic} in the strictest sense. 
+% using neighborhood semantics, and another
+% extending it with knowledge.  
+Reflecting on our thought experiment, it seems impossible to \emph{know} both
+Boltzman's $H$-theorem and Poincar\'{e}'s recurrence theorem, as they
+form an antimony.  Based on his writings, we feel that Russell would
+hold that neither principle is \emph{known}, and that each one of them
+constitutes a \emph{probable
+  opinion}\cite[pgs. 63--67]{russell_problems_1936} 
+that physicists entertain whenever convenient.  
+Accordingly, we interpret the neighborhood based logic we 
+develop here as a \emph{doxastic logic} of probable opinion.
 
@@
     \ |\ \Box \phi\ |\ A :
-     \phi\ |\ K \phi \]
+     \phi\  \]
 \end{definition}
 
-Just as previous semantics, ``$\Box \phi$'' is intended to mean that the agent
-has an argument for $\phi$ from some knowledge base.  A novelty we present
-here is that ``$K \phi$'' means that the agent has an argument for $\phi$ from
-some \tmtextit{sound} knowledge base.
+% Just as previous semantics, ``$\Box \phi$'' is intended to mean that the agent
+% has an argument for $\phi$ from some knowledge base.  A novelty we present
+% here is that ``$K \phi$'' means that the agent has an argument for $\phi$ from
+% some \tmtextit{sound} knowledge base.
 
@@
   \langle W, V, \mathcal{N}, \mathcal{A} \rangle$ has a neighborhood function
-  $\mathcal{N} : W \rightarrow 2^{2^W}$ and a multi-awareness function
-  $\mathcal{A} : W \rightarrow 2^{2^{\mathcal{L}_N (\Phi)}}$
+  $\mathcal{N} : W \rightarrow 2^{2^W}$ and a multi-awareness function $\mathcal{A} : W \rightarrow 2^{2^{\mathcal{L}_N (\Phi)}}$
 
@@
   \begin{eqnarray*}
-    \mathbbm{M}, w \vDash \Box \phi & \text{iff} & \text{there exists a $U \in
-    \mathcal{N}_w$ where $\mathbbm{M}, v \vDash \phi$ for all $v \in U$}\\
-    \mathbbm{M}, w \vDash K \phi & \text{iff} & \text{there exists a $U \in
-    \mathcal{N}_w$ where $w \in U$ and $\mathbbm{M}, v \vDash \phi$ for all $v
-    \in U$}\\
-    \mathbbm{M}, w \vDash A : \phi & \text{iff} & \phi \in \bigcup
-    \mathcal{A_w}
+    \mathbbm{M}, w \vDash \Box \phi & \iff & \text{there exists a $U \in
+    \mathcal{N}(w)$ where $\mathbbm{M}, v \vDash \phi$ for all $v \in U$}\\
+    % \mathbbm{M}, w \vDash K \phi & \text{iff} & \text{there exists a $U \in
+    % \mathcal{N}_w$ where $w \in U$ and $\mathbbm{M}, v \vDash \phi$ for all $v
+    % \in U$}\\
+    \mathbbm{M}, w \vDash A : \phi & \iff & \phi \in \bigcup
+    \mathcal{A}(w)
   \end{eqnarray*}
@@
 
-Here we modify our previous notion of \tmtextbf{CSQ} and \tmtextbf{SND} to
-match how our semantics are intended for reasoning over multiple bases:
+% Here we modify our previous notion of \tmtextbf{CSQ} and \tmtextbf{SND} to
+% match how our semantics are intended for reasoning over multiple bases:
 
@@
   The following defines properties a neighborhood model may make true:
-
   \begin{descriptiondash}
-    \item[NCSQ] $\mathbbm{M}, w \vDash \Box \phi \text{ iff there exists a set
-    $X \in \mathcal{A}_w$ such that } \tmop{Th} (\mathbbm{M}) \cup X \vdash
+    \item[NCSQ$_\vdash$] $\mathbbm{M}, w \vDash \Box \phi \text{ iff there exists a set
+    $X \in \mathcal{A}(w)$ such that } \tmop{Th} (\mathbbm{M}) \cup X \vdash
     \phi$
-
-    \item[NSND] $\mathbbm{M}, w \vDash K \phi \text{ iff there exists a set $X
-    \in \mathcal{A}_w$ such that $\mathbbm{M}, w \vDash X$ and } \tmop{Th}
-    (\mathbbm{M}) \cup X \vdash \phi$
+    \item[NON-EMPTY] $\mathcal{A}(w)
+      \neq \varnothing$ for all worlds $w$
+%    \item[NSND] $\mathbbm{M}, w \vDash K \phi \text{ iff there exists a set $X
+%    \in \mathcal{A}_w$ such that $\mathbbm{M}, w \vDash X$ and } \tmop{Th}
+ %   (\mathbbm{M}) \cup X \vdash \phi$
   \end{descriptiondash}
-
-  as before, $\vdash$ is any sound logical consequence relation for $\vDash$
-  with \tmtextbf{modus ponens} and \tmtextbf{reflection}
+  % as before, $\vdash$ is any sound logical consequence relation for $\vDash$
+  % with \tmtextbf{modus ponens} and \tmtextbf{reflection}
 \end{definition}
@@
 \begin{table}[h]
+\begin{centering}
   \begin{tabular}{l}
@@
     \rightarrow \psi \rightarrow \phi$\\
-    $\vdash K \phi \rightarrow \Box \phi$\\
-    $\vdash K \phi \rightarrow \phi$\\
+%    $\vdash K \phi \rightarrow \Box \phi$\\
+%    $\vdash K \phi \rightarrow \phi$\\
     $\vdash A : \phi \rightarrow \Box \phi$\\
-    \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ & {\hspace{6em}}$\frac{\vdash \phi \rightarrow \psi}{\vdash \Box
-      \phi \rightarrow \Box \psi}$ & {\hspace{6em}} & $\frac{\vdash \phi
-      \rightarrow \psi}{\vdash K \phi \rightarrow K \psi}$
+    $\vdash \Box \top$
   \end{tabular}
+
+    \begin{tabular}{lll}
+      $\displaystyle\frac{\vdash \phi \rightarrow \psi \ \ \vdash \phi}{\vdash
+      \psi}$ & \ \ & $\displaystyle\frac{\vdash \phi \rightarrow \psi}{\vdash \Box \phi
+      \rightarrow \Box \psi}$
     \end{tabular}
-  \caption{\label{logic3}A Neighborhood Logic for \tmtextbf{NCSQ} and
-  {\tmstrong{NSND}}}
+  \caption{\label{logic3}A Neighborhood Based Doxastic Logic of
+    Probable Opinion}
+\end{centering}
 \end{table}
@@
   \ref{logic3} is sound and weakly complete for neighborhood semantics making
-  true \tmtextbf{NCSQ} and \tmtextbf{NSND}.
+  true $\textup{\tmtextbf{NCSQ}}_\vdash$ and \tmtextbf{NON-EMPTY}.
 \end{theorem}
@@
 
-It is not too hard to identify the fragment of this logic that governs
-knowledge alone.  The fragment given in Table \ref{logic4} has special
-significance to us, since it governs the notion of knowledge presented in
-{\S}\ref{quantifying}.
-
-\begin{table}[h]
-  \begin{tabular}{l}
-    $\vdash \phi \rightarrow \psi \rightarrow \phi$\\
-    $\vdash (\phi \rightarrow \psi \rightarrow \chi) \rightarrow (\phi
-    \rightarrow \psi) \rightarrow \phi \rightarrow \chi$\\
-    $\vdash ((\phi \rightarrow \bot) \rightarrow (\psi \rightarrow \bot))
-    \rightarrow \psi \rightarrow \phi$\\
-    $\vdash K \phi \rightarrow \phi$\\
-    \\
-    \begin{tabular}{llll}
-      $\frac{\vdash \phi \rightarrow \psi \hspace{4em} \vdash \phi}{\vdash
-      \psi}$ &  &  & $\frac{\vdash \phi \rightarrow \psi}{\vdash K \phi
-      \rightarrow K \psi}$
-    \end{tabular}
-  \end{tabular}
-  \caption{\label{logic4}A knowledge-only neighborhood logic for
-  \tmtextbf{NCSQ} and {\tmstrong{NSND}}}
-\end{table}
-
-\begin{proposition}
-  The knowledge-only logic presented governs the $\Box$-free fragment of the
-  logic in Table \ref{logic3}
-\end{proposition}
-
-This concludes our analysis of knowledge bases using neighborhood
-semantics.
+% \subsection{Logic for Knowledge and Belief}
+% In this section, we conservatively extend the neighborhood semantics
+% based logic of belief to account for knowledge as well. According to
+% Russell, belief which is not knowledge falls into two categories:
+% \emph{probable opinion} and \emph{error
+% As in previous sections, we model knowledge as being minimally \emph{true}, however
+% we place no further constraints on it.  
 %%% Local Variables: 

### 2011-01-30 conclusions.tex
more spell checking
Wrote conclusion

@@
-(FIXME:  Needs to be extended a lot!)
+In this section we provide our final analysis of Hintikka's objection
+to our proposed reading of epistemic modality, connections of our
+logic to other approaches, and we propose future avenues of research.
 
-The logic presented in Table \ref{logic1} is a conservative extension of the
-basic modal logic $K$, which means that its decision problem is
-\tmtextsf{PSPACE} hard (a lower bound).  Our finitary completeness proof
-establishes that its complexity is in \tmtextsf{EXP2-TIME} (an upper bound).
+\subsection{Hintikka's Objection}\label{hintikka-conc}
 
-Worlds in epistemic logic might correspond to fantastic, pretend scenarios;
-however, it may be desirable for some philosophers to model knowledge about
-imaginary lands.  After all, many children ``know'' a lot about Tolkien's
-{\tmem{middle earth}} or Rowling's {\tmem{Hogwarts}} (the school Harry Potter
-attends).
+Contrary to Hintikka's opposition, we have demonstrated various logics
+where $\Box \phi$ has a Russellian interpretation: 
+``$\phi$ may be derived logically from basic propositions that the
+agent is aware of that $\phi$''.  This is accomplished
+by first providing basic semantics, and then restricting ourselves to
+classes of models which express the property we have labeled as 
+$\textup{\textbf{CSQ}}_\vdash$, where $\vdash$ is some suitable
+logic.  Our specification of what suitable means is minimal, although it
+is enough to determine a complete notion of logical consequence in
+every case.
+
+However, we propose that a more radical reading of $\Box \phi$ is adequate: ``$\phi$ may be derived logically from basic propositions that the
+agent is aware of that $\phi$, \emph{using epistemic logic itself}''.
+In other words, one may interpret epistemic agents as using the
+same logic we are ultimately developing.
+We take the relevant notion of epistemic logic to be application dependent;
+it may be awareness logic, hybrid logic, etc.
+  This is because of the
+following observation, which we assert without proof: \emph{for every
+  logic $\vdash_L$ we propose, $\vdash_L$ is sound and weakly complete
+  for an appropriate class of models $\mathbb{M}$ making true
+  $\textup{\textbf{CSQ}}_{\vdash_L}$}.
+To see why this is true, it is routine to verify soundness, and then
+check that each of our completeness proofs deliver suitable counter-models.
+
+Our more radical reading directly contradicts Hintikka: we are proposing that semantics
+may appeal to their own notion of logical consequence.  The method of
+developing systems that accomplish this is analogous to other
+techniques in mathematics.  In
+order to derive the static solution of a diffusion equation, one
+ minimally assumes the solution to be \emph{separable}.  
+From this assumption, the form of the solution may be derived, and one may
+check that the derived solution fulfills all of the initial assumptions.  Formulating logics that have
+semantics which incorporate themselves may be regarded as a similar
+exercise to solving differential equations, with our assumption of
+\emph{suitability} playing the similar r\^{o}le as \emph{separability}.
+
+\subsection{Related Work}
+
+All of the logics in this paper are variations of
+systems that have been developed elsewhere for different purposes.
+We defer to the cited literature for readers interested in the
+comparing our approach to others.
+
+There is a connection we did not anticipate between the neighborhood 
+logic in \S\ref{neighborhood_semantics} and a logic for statistical inference
+presented by Kyburg et al. \cite{kyburg_logic_2002}.  We assert
+without proof that the awareness free fragment of our logic is exactly
+the same as the logic developed in Kyburg et al., which is precisely Chellas'
+neighborhood logic $EMN$ \cite[chapter 9]{chellas_modal_1980}.
+
+An important similarity between Kyburg et al.'s approach and our own is
+our respective philosophical motivations.  In both systems, the guiding intuition lies in pragmatic
+considerations in scientific epistemology; specifically it is meant
+for reasoning about the ``Lottery Paradox''
+\cite[pg. 197]{kyburg_probability_1961}.  To sketch this puzzle, let
+$\phi_X$ denote ``$X$ will win the lottery'', for some lottery with
+1000 tickets.  For any given person $X$, call them ``$1$'', we have
+that $Pr(\neg \phi_1)
+\approx 1$, so one may reasonably conclude that $\neg\phi_1$.  One
+could similarly conclude $\neg \phi_2$, and it seems $Pr(\phi_1 \vee
+\phi_2) \approx 0$, so one could conclude $\neg\phi_1 \wedge \neg \phi_2$.
+However, can cannot rationally conclude that $\bigvee_{1 \leq X \leq 1000}
+\neg \phi_X$, since \emph{somebody} must win the lottery.
+
+One method of resolving this paradox is to employ a system of statistical
+inference known as the \emph{Evidential Probability
+  Calculus} \cite{kyburg_uncertain_2001}.  
+This may be seen as a variation on Maynard Keynes' interval probability 
+calculus \cite{keynes_treatise_1921}.  Using this system, Kyburg et
+al. write $\Gamma
+\vdash_\epsilon \phi$ to mean that a body of statistical evidence
+$\Gamma$ determines that $Pr(\phi) \in [p,q]$ where $p \geq
+1 - \epsilon$ (given certain other constraints).  They then propose semantics which equate doxastic
+modality $\Box_\epsilon \phi$ with an inference $\Gamma \vdash_\epsilon\phi$ for some
+body of statistical evidence $\Gamma$.  The similarity between this
+approach and the Russellian epistemic logics we propose is clear.
+
+Furthermore, we regard it as significant that two disparate efforts,
+both motivated by scientific epistemology,
+have converged Chellas' neighborhood logic $EMN$.
+
+\subsection{Conclusion}
+
+Philosophers and logicians have been informally reading $\Box \phi$ as
+``it follows from what the agent knows that $\phi$'' for years,
+contrary to Hintikka's rejection of this interpretation.  It is natural that formal systems
+may be developed with correspond to this intuition.  What is somewhat
+unexpected is that Russell's epistemology effectively fits this
+perspective, and anticipates awareness logic.  We have demonstrated that a Russellian
+reading is robustly applicable to modal, submodal, and hybrid awareness
+logics.  In future work, we want to investigate the relationship
+between our approach and Kyburg et al.'s, given that the two
+employ similar semantics and share a common logic.
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "paper"
+%%% End:

### 2011-01-30 awareness.tex
Changed how awareness sets are typeset

@@
 
-Aside from \textbf{CSQ$_\vdash$}, we will be concerned with the
-following new property
+Aside from $\textup{\textbf{CSQ}}_\vdash$, we will be concerned with
+the following new property
 
@@
     \item[SND] If $\mathbbm{M}, w \vDash \circlearrowleft \text{ then }
-    \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w$
+    \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}(w)$
   \end{descriptiondash}
@@
 
-The logic for \textbf{CSQ$_\vdash$} and \textbf{SND} differs from the
+The logic for  $\textup{\textbf{CSQ}}_\vdash$ and \textbf{SND} differs from the
 logic given in \S\ref{awarenesslogic0} by a single axiom:
@@
   \label{completeness1}Assuming an infinite store of proposition letters
-  $\Phi$, the awareness logic presented is sound and weakly complete for
-  awareness models making true \tmtextbf{CSQ}$_{\vdash'}$ and
-  \tmtextbf{SND} for a suitable logic $\vdash'$.
+  $\Phi$, the awareness logic presented in Table \ref{logic1} is sound and weakly complete for
+  $\PP$-awareness models making true \tmtextbf{CSQ}$_{\vdash'}$ for a
+  suitable logic $\vdash'$ as well as
+  \tmtextbf{SND}.
 \end{theorem}

### 2011-01-30 completeness2.tex
Reworked completeness

@@
   \begin{enumerateroman}
-    \item $\sim_{\forall}$ is an equivalence relation    
+    \item \label{hybprop1} $\sim_{\forall}$ is an equivalence relation
+    \item If $\mathbbm{M}, v \vDash A : \psi$ then $\mathbbm{M}, v
+      \vDash \Box \psi$     
     \item $R_{\Box} \subseteq \sim_{\forall}$
-    \item In each equivalence class specified by $\sim_{\forall}$, there is at
+    \item \label{hybprop4}In each equivalence class specified by $\sim_{\forall}$, there is at
     most one world making true $i$ for all $i \in \Upsilon$
@@
 
-  The the worlds is $\mathbbm{M}'$ and $\mathbbm{M}''$ agree on all
-  subformulae of $\psi$, hence $\mathbbm{M}'', w \nvDash
-  \psi$. Moreover, the logic in Table \ref{logic2} itself 
-  is suitable for $\mathbbm{M}''$ and
-  $\mathbbm{M}''$ makes true $\textup{\tmtextbf{CSQ}}_{\vdash}$.  From
-  this it follows that we have completeness.
+  The the worlds is $\mathbbm{M}'$ and $\mathbbm{M}''$ agree on all  subformulae of $\psi$, hence $\mathbbm{M}'', w \nvDash
+  \psi$. Note that both $\mathbb{M}'$ and $\mathbb{M}''$ inherit
+  properties \ref{hybprop1} through \ref{hybprop4} from $\mathbb{M}$.
+  This implies that the logic in Table \ref{logic2} itself 
+  is suitable for $\mathbbm{M}''$. Moreover, one can show that
+  $\mathbbm{M}''$ makes true $\textup{\tmtextbf{CSQ}}_{\vdash}$, using
+  a line of argument analogous to what we have provided in previous proofs.
+  From this we have enough to establish completeness.
 \end{proof}

### 2011-01-30 conclusions.tex
Fixed reference to Hintikka

@@
 
-Contrary to Hintikka's opposition, we have demonstrated various logics
+Contrary to Hintikka's opposition (as we presented in \S\ref{Hintikka}), we have demonstrated various logics
 where $\Box \phi$ has a Russellian interpretation: 

### 2011-01-30 foundationalism.tex
Fixed label for Hintikka section

@@
 
-\subsection{Jaako Hintika}\label{Russell}
+\subsection{Jaako Hintika}\label{Hintikka}
 
@@
 proposed reading of epistemic modality, we return Hintikka's objection
-in \S\ref{hintikka-obj} in our concluding remarks.
+in \S\ref{Hintikka} in our concluding remarks.
 

### 2011-01-30 introduction.tex
Fixed reference to hendricks

@@
 logicians and philosophers have acknowledged this rift, most notably
-Vincent Hendricks \cite{hendricks_wheres_2006,
-  hendricks_mainstream_2006}.
+Vincent Hendricks\cite{hendricks_wheres_2006,hendricks_mainstream_2006}.
 
@@
 traditions, by showing that awareness logics are suitable for
-reasoning about the form of foundationalism proposed
+reasoning about a form of strong foundationalism proposed
 by Bertrand Russell in \emph{The Problems of Philosophy}
